### 2015-11-18 article/article.tex
Added schema + abstract

\documentclass[]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
    \usepackage{xltxtra,xunicode}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Mapping=tex-text,Scale=MatchLowercase}
  \newcommand{\euro}{€}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\ifxetex
  \usepackage[setpagesize=false, % page size defined by xetex
              unicode=false, % unicode breaks when used with xetex
              xetex]{hyperref}
\else
  \usepackage[unicode=true]{hyperref}
\fi
\usepackage[usenames,dvipsnames]{color}
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor={Antoine GRÉA Samir AKNINE Laetitia MATIGNON},
            pdftitle={SODA POP : Robust online Partial Ordering Planning for real life applications},
            colorlinks=true,
            citecolor=blue,
            urlcolor=blue,
            linkcolor=magenta,
            pdfborder={0 0 0}}
\urlstyle{same}  % don't use monospace font for urls
\usepackage{listings}
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{5}

\title{SODA POP : Robust online Partial Ordering Planning for real life
applications}
\author{Antoine GRÉA Samir AKNINE Laetitia MATIGNON}
\date{}
\usepackage{xcolor, listings}
\usepackage{latex/aaai}
\usepackage{times}
\usepackage{helvet}
\usepackage{courier}
\usepackage{algorithm, algpseudocode}
\usepackage{amsthm}

\newtheorem{definition}{Definition}

% We now define the sixteen \solarized{} colors.
\definecolor{solarized-base03} {RGB}{000, 043, 054}
\definecolor{solarized-base02} {RGB}{007, 054, 066}
\definecolor{solarized-base01} {RGB}{088, 110, 117}
\definecolor{solarized-base00} {RGB}{101, 123, 131}
\definecolor{solarized-base0}  {RGB}{131, 148, 150}
\definecolor{solarized-base1}  {RGB}{147, 161, 161}
\definecolor{solarized-base2}  {RGB}{238, 232, 213}
\definecolor{solarized-base3}  {RGB}{253, 246, 227}
\definecolor{solarized-yellow} {RGB}{181, 137, 000}
\definecolor{solarized-orange} {RGB}{203, 075, 022}
\definecolor{solarized-red}    {RGB}{220, 050, 047}
\definecolor{solarized-magenta}{RGB}{211, 054, 130}
\definecolor{solarized-violet} {RGB}{108, 113, 196}
\definecolor{solarized-blue}   {RGB}{038, 139, 210}
\definecolor{solarized-cyan}   {RGB}{042, 161, 152}
\definecolor{solarized-green}  {RGB}{133, 153, 000}

\lstset{
    basicstyle={\footnotesize\ttfamily},
    numbers=left,
    keywordstyle=\color{solarized-orange}\bfseries,
%    identifierstyle=\color{solarized-base02},
    stringstyle=\color{solarized-cyan},
    commentstyle=\color{solarized-base1}\itshape,
    numberstyle=\tiny\color{solarized-base0},
    columns=flexible,
    stepnumber=1,
    numbersep=5pt,
    backgroundcolor=\color{solarized-base3},
    showspaces=false,
    showstringspaces=false,
    showtabs=false,
    tabsize=2,
    captionpos=b,
    breaklines=true,
    breakatwhitespace=true,
    breakautoindent=true,
    escapeinside={\%*}{*)},
    linewidth=\textwidth,
    basewidth=0.5em,
}

% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

\begin{document}
\maketitle
\begin{abstract}
This is the best of all abstracts ever !

It consists of two paragraphs but that is more than enough for it to be
awesome.
\end{abstract}

\section*{Introduction}\label{introduction}
\addcontentsline{toc}{section}{Introduction}

For some time Partial Order Planning (POP) has been the most popular
approach to planning resolution. This kind of algorithms are based on
\emph{least commitment strategy} on plan step ordering that can allow
actions to be flexibly interleaved during execution {[}1{]}. Thus the
way the search is made using flexible partial plan as a search space
allowed for more versatility for a wide variety of uses. As of more
recent years, new state space search models and heuristics {[}2{]} have
been demonstrated to be more efficient than POP planners due to the
simplicity and relevance of states representation opposed to partial
plans {[}3{]}. This have made the search of performance the main axis of
research for planning in the community.

While this goal is justified, it shadows other problems that some
practical applications cause. For example, the flexibility of Plan Space
Planning (PSP) is an obvious advantage for applications needing online
planning: plans can be repaired on the fly as new informations and
objectives enter the system. The idea of using POP for online planning
and repairing plans instead of replanning everything is not new {[}4{]},
but has never been paired with the resilience that some other cognitive
applications may need, especially when dealing with sensors data and
noise.

This resilience makes fixing errors easier than with an external
algorithm as the plan logic allows for context driven decision on the
way to repair the issues. For example if an action becomes unrelevant or
incoherent the flaw in the partial plan makes the problem to fix
explicit and therefore easier to fix. The client softwares might
sometimes provide plans that can contain errors and imperfections that
will decrease significantly the efficiency of the computation and the
quality of the output plan.

Adding to that, these plans may become totally unsolvable. This problem
is to our knowledge not treated in planning of all forms (state
planning, PSP, and even constraint satisfaction planning) as usually the
aim is to find a solution relative to the original plan (which makes
sense). But as we proceed a mechanism of \emph{problem} fixing may be
required. This will allow soft solving of any problem regardless of its
solvability.

One of the application that needs these improvements is plan recognition
with the particular use of off-the-shelf planners to infer the pursued
goal of an agent where online planning and resilience is particularly
important.

These problems call for new ways to improve the answer and behavior of a
planner. These improvements must provide relevant plan information
pointing out exactly what needs to be done in order to make a planning
problem solvable, even in the case of obviously broken input data. We
aim to solve this in this paper while preserving the advantages of PSP
algorithms (flexibly, easy fixing of plans, soudness and
completeness)\textgreater{}. Our Soft Ordering and Defect Aware Partial
Ordering Planning (SODA POP) algorithm will target those issues.

Our new set of auxiliary algorithms allows to make POP algorithm more
resilient, efficient and relevant. This is done by pre-emptively
computing proper plans for goals, by solving new kinds of defects that
input plans may provide, and by healing compromised plan by extending
the initial problem to allow resolution.

To explain this work we first describe a few notions, notations and
specificities of existing POP algorithms. Then we present and illustrate
their limitations, categorising the different defects arising from the
resilience problem and explaining our complementary algorithms, their
uses and properties. To finish we compare the performance, resilence and
quality of POP and our solution.

\section{Definitions}\label{definitions}

In order to present our work and explain examples we introduce a way of
representation for schema in figure \ref{fig:legend} and notations for
mathematical representation.

\begin{figure}[htbp]
\centering
\includegraphics{graphics/legend.pdf}
\caption{Global legend for how partial plans are represented in the
current paper\label{fig:legend}}
\end{figure}

\subsection{Classic planning}\label{classic-planning}

\begin{definition}[Fluents]

A fluent is a property of the world. It is often represented by first
order logical propositions but in our case we choose to focus on the
algorithm and to represent fluents as simple literals (fully
instantiated). We note \(\lnot f\) the complementary fluent of \(f\)
meaning that \(f\) is true when \(\lnot f\) is false and vice-versa.

In order to make our example simpler we use \(\mathbb{Q}^*\), the set of
relative integers without \(0\), as the fluent domain. We use negative
integers to represent opposite fluents.

\end{definition}

\begin{definition}[State]

We define a state as a set of fluents. States can be additively
combined. We note
\(s_1 + s_2 = \left( s_1 \cup s_2 \right) - \left\{ f \middle| f \in s_1 \land \lnot f \in s_2 \right\}\)
such operation. It is the union of the fluents with an erasure of the
complementary ones.

\end{definition}

\begin{definition}[Action]

An action is a state operator. It is represented as a tuple
\(a = \langle pre, eff \rangle\) with \(pre\) and \(eff\) being sets of
fluents, respectively the preconditions and the effects of \(a\). An
action can be used only in a state that verifies its preconditions. We
note \(s \models a \Leftrightarrow pre(a) \subset s\) the verification
of an action \(a\) by a state \(s\).

An action \(a\) can be functionally applied to a state \(s\) following :
\[a:= \substack{ \left\{ s \models a \middle| s \in S\right\} \to S\\
    a(s) \mapsto s + eff(a)}\] with \(S\) being the set of all states.
There are some special names for actions. An action with no
preconditions is synonymous to a state and one with empty effect is
called a goal.

\end{definition}

\subsection{Plan Space Planning}\label{plan-space-planning}

\subsubsection{Problem}\label{problem}

We define a partial plan satisfaction problem as a tuple noted
\(P = \langle A, I, G, p \rangle\) with :

\begin{itemize}
\tightlist
\item
  \(I\) and \(G\) being the pseudo actions representing respectively the
  initial state and the goal.
\item
  \(p\) being a partial plan to refine.
\item
  \(A\) the set of all actions.
\end{itemize}

\begin{definition}[Partial Plan]

A \emph{partial plan} is a tuple \(p = \langle A_p, L\rangle\) where
\(A_p\) is a set of steps (actions) and \(L\) is a set of causal links
of the form \(a_i \xrightarrow{f} a_j\), such that
\(\{ a_i, a_j \} \subset A_p \land f \in eff(a_i) \cap pre(a_j)\) or
said otherwise that \(f\) is provided by \(a_i\) to \(a_j\) via this
causal link. We include the ordering constraints of PSP in the causal
links. An ordering constraint is noted \(a_i \to a_j\) and means that
the plan consider \(a_i\) as a step that is prior to \(a_j\) without
specific cause (usually because of threat resolution).

\end{definition}

\subsubsection{Flaws}\label{flaws}

When refining a partial plan, we need to fix flaws. Those could be
present or be created by the refining process. Flaws can either be
unsatisfied subgoals or threats to causal links.

\begin{definition}[Subgoal]

A subgoal \(s\) is a precondition of an action \(a_s \in A_p\) with
\(s \in pre(a_s)\) that isn't satisfied by any causal link. We can note
a subgoal as :
\[a_i \xrightarrow{s} a_s \notin L \mid \{ a_i, a_s \} \subset A_p \]

A resolver for a subgoal is an action \(a_r \in A\) that has \(s\) as an
effect \(s \in eff(a_r)\). It is inserted along with a causal link noted
\(a_r \xrightarrow{s} a_s\).

\end{definition}

\begin{definition}[Threat]

A step \(a_t\) is said to threaten a causal link
\(a_i \xrightarrow{t} a_j\) if and only if
\[\neg t \in eff(a_t) \land a_i \succ a_t \succ a_j \models L\] Said
otherwise, the action has a possible complementary effect that can be
inserted between two actions needing this fluent while being consistant
with the ordering constraint in \(L\).

The usual resolvers are either \(a_t \to a_i\) or \(a_j \to a_t\) which
are called respectively promotion and demotion links. Another resolver
is called a white knight that is an action \(a_k\) that reestablish
\(t\) after \(a_t\).

\end{definition}

\subsubsection{Solution}\label{solution}

The solution of a PSP problem is a valid partial plan that respect the
specification of said problem (only using actions in \(A\) and having
the correct initial and goal step).

\begin{definition}[Consistency]

A partial plan is consistent if it contains no ordering cycles. That
means that the directed graph formed by step as vertices and causal
links as edges isn't cyclical. This is important to guarantee the
soundness of the algorithm.

\end{definition}

\begin{definition}[Flat Plan]

We can instantiate one or several flat plans from a partial plan. A flat
plan is an ordered sequence of actions \(\pi = [ a_1, a_2 \ldots a_n]\)
that acts like a pseudo action
\(\pi = \langle pre_\pi, eff_\pi \rangle\) and can be applied to a state
\(s\) using functional composition operation
\(\pi := \bigcirc_{i=1}^n a_n\).

We call a flat plan valid if and only if it can be functionally applied
on an empty state. We note that this is different from classic state
planning because in our case the initial state is the first action that
is already included in the plan.

\end{definition}

\begin{definition}[Validity]

A partial plan is valid if and only if it is consistent and if all the
flat plan that can be generated are valid.

\end{definition}

\section{Classical POP}\label{classical-pop}

Partial Order Planning (POP) is a popular implementation of the general
PSP algorithm. It is proven to be sound and complete {[}5{]}. The
completeness of the algorithm guarantees that if the problem has a
solution it will be found by the algorithm. The soundness assures that
any answer from the algorithm is valid. POP refines a partial plan by
trying to fix its flaws.

\subsection{Description}\label{description}

\begin{algorithm}\caption{Classical Partial Order Planning algorithm}\label{pop}\begin{algorithmic}

\Function{pop}{Queue of Flaws $agenda$, Problem $P$}
\State \Call{populate}{$agenda$, $P$} \Comment{Only on first call}
\If{$agenda = \emptyset$} \State \Return Success
\Comment{Stop all recursion} \EndIf
    \State Flaw \(f\gets agenda.pop\)
\Comment{First element of the queue} \State Resolvers \(R \gets\)
\Call{resolvers}{$f$, $P$} \Comment{Ordered list of resolvers to try}
\ForAll{$r \in R$} \Comment{Choice operator}
\State \Call{apply}{$r$, $P.p$} \If{\Call{consistent}{$P.p$}}
\State \Call{pop}{$agenda \cup$ \protect\Call{relatedFlaws}{$f$}, $P$}
\Else 
            \State \Call{revert}{$r$, $P.p$} \EndIf
    \EndFor
    \State \Return Failure \Comment{Return to last choice of resolver}
\EndFunction

\end{algorithmic}\end{algorithm}

From that point the base algorithm is very similar for any
implementation of POP : using an agenda of flaws that is efficiently
updated after each refinement of the plan. A flaw is selected for
resolution and we use a non deterministic choice operator to pick a
resolver for the flaw. The resolver is inserted in the plan and we
recursively call the algorithm on the new plan. On failure we return to
the last non deterministic choice to pick another resolver. The
algorithm ends when the agenda is empty or when there is no more
resolver to pick for a given flaw.

\subsection{Limitations}\label{limitations}

This standard way of doing have seen multiple improvements over
expressiveness like with UCPOP {[}6{]}, hierarchical task network to add
more user control over sub-plans {[}7{]}, cognition with defeasible
reasoning {[}8{]}, or speed with multiple ways to implement the popular
fast forward method from state planning {[}9{]}. However, all these
variants do not treat the problem of online planning, resilience and
soft solving.

Some other closer works like {[}4{]} treats the problem of online
planning by removing big chuncks of the partial plan by identifying
incorect trees in the plan. This causes an heavy replanning of the
problem even if only one action needed removal. This is a big problem
when trying to adapt a plan with minimal changes due to replanning.

Indeed, all these problems can affect POP's performance and quality as
they can interfere with POP's inner working when the algorithm is able
to give an answer at all.

\begin{figure}[htbp]
\centering
\includegraphics{graphics/problem.pdf}
\caption{A simple problem that will be used throughout this
paper\label{fig:problem}}
\end{figure}

Before continuing, we present a simple example of classical POP
execution with the problem represented in figure \ref{fig:problem}. We
did not represent empty preconditions or effects to improve readability.
Here we have an initial state
\(I = \langle \emptyset , \{ 1, 2 \} \rangle\) and a goal
\(G = \langle \{ 3, 4, -5, 6 \}, \emptyset \rangle\) encoded as dummy
steps. We also introduce actions that are not steps yet but that are
provided by \(A\). The actions \(a\), \(b\) and \(c\) are normal actions
that are useful to achieve the goal. The action \(t\) is meant to be
threatening to the plan's integrity and will generate threats. We
introduce \(u\) as a useless action, \(v\) as a toxic action, \(w\) as a
dead-end action and \(x\) as a contradictory action.

\begin{figure}[htbp]
\centering
\includegraphics{graphics/pop.pdf}
\caption{Standard POP result to the problem\label{fig:pop}}
\end{figure}

This example has been crafted to illustrate problems with standard POP
implementations. We give a possible resulting plan of standard POP in
figure \ref{fig:pop}. We can see some issues as for how the plan has
been built. The action \(v\) is being used even if it is useless since
\(b\) already provided fluent \(4\). We can also notice that despite
being contradictory the action \(x\) raised no alarm. As for ordering
constraints we can clearly see that the link \(a \to t\) is redundant
with the path \(a \xrightarrow{5} c \to t\) that already puts that
constraint by transitivity. Also some problems arise during execution
with the selection of \(w\) that causes a dead-end.

Of course the flaw selection mechanism of certain variant can prevent
that to happen in that case. But often flaw selection mechanisms are
more speed oriented and will do little if a toxic action seems to fit
better than a more coherent but complex one.

All these issues are caused by what we call \emph{defects} as they are
not regular PSP flaws but they still cause problems with execution and
results. We will address these defects and propose a way to fix them in
\hyperref[defects]{the next section}.

\section{Auxiliary algorithms to POP}\label{auxiliary-algorithms-to-pop}

In order to improve POP algorithms' resilience, online performance and
plan quality, we propose a set of auxiliary algorithms that provides POP
with a clean and efficiently populated initial plan.

\subsection{Proper plan generation}\label{proper-plan-generation}

\begin{algorithm}\caption{Proper plan generation algorithm for a given goal $g$}\label{properplan}\begin{algorithmic}

\Function{properPlan}{Goal $g$, Actions $A$} \State Partial Plan
\(p \gets \emptyset\) \State Actions \(relevants \gets\)
\Call{satisfy}{$g$, $A$, $p$}
\Comment{Satisfy given goal with all necessary actions and causal links}
\State Queue of Actions \(open \gets relevants\)
\While{$open \neq \emptyset$} \State Action \(a\gets open.pop\)
\State Actions \(candidates \gets\) \Call{satisfy}{$a$, $A$, $p$}
\ForAll{$candidate \in candidates$} \If{$candidate \notin relevants$}
\State \(open.push(candidate)\) \EndIf
        \EndFor
    \EndWhile
\EndFunction

\end{algorithmic}\end{algorithm}

As in online planning goals can be known in advance, we add a new
mechanism that generates proper plans for goals. We take advantage of
the fact that this step can be done offline to improve performance for
online planning. This offline execution prevents us to access the
details of the initial state of the world as it will be defined at
runtime. We define for that the concept of \emph{participating action}.
An action \(a \in A\) participates in a goal \(G\) if and only if \(a\)
has an effect \(f\) that is needed to accomplish \(G\) or that is needed
to accomplish another participating action's preconditions. A proper
plan is a partial plan that contains all participating actions as steps
and causal links that bind them with the step they are participating in.
This proper plan is independent from the initial step because we might
not have the initial step at the time of the proper plan generation.

This auxiliary algorithm is therefore used as a caching mechanism for
online planning. The algorithm starts to populate the proper plan with a
quick and incomplete backward chaining.

\hyperdef{}{defects}{\subsection{Defect resolution}\label{defects}}

\begin{algorithm}\caption{Defect resolution algorithm}\label{defectresolution}\begin{algorithmic}

\Function{clean}{Problem $P$} \State \Call{illegal}{$P$}
\State \Call{interfering}{$P$} \EndFunction

\Function{illegal}{Problem $P$}
\State \Call{assert}{$pre(P.I) = \emptyset$}
\State \Call{assert}{$eff(P.G) = \emptyset$}
\State \(P.p.A_p \gets P.p.A_p \cup \{P.I, P.G\}\)
\State \Call{breakCycles}{$P$} \State Actions
\(actions \gets P.A \cup P.p.A_p\) \ForAll{Action $a \in actions$}
\State \Call{inconsistent}{$a$, $P$} \State \Call{toxic}{$a$, $P$}
\EndFor
    \State \Call{liarLinks}{$P$} \EndFunction

\Function{interfering}{Problem $P$} \State \Call{repeating}{$P$}
\State \Call{useless}{$P$} \EndFunction

\end{algorithmic}\end{algorithm}

When the POP algorithm is used to refine a given plan (that was not
generated with POP or that was altered), a set of new defects can be
present in it interfering in the resolution and sometimes making it
impossible to solve. We emphasize that these defects are not regular POP
flaws but new problems that classical POP can't solve. The aim of this
auxiliary algorithm is to clean the plans from such defects in order to
improve computational time, resilience and plan quality . It should be
noted that in some cases cleaning plans will increase the number of
flaws in the plan but will always improve the overall quality of it.

There are two kinds of defects: the illegal defects that violate base
hypothesis of PSP and the interference defects that can lead to
excessive computational time and to poor plan quality.

\begin{definition}[Illegal defects]

These defects are usually hypothesized out by regular models. They are
illegal use of partial plan representation and shouldn't happen under
regular circumstances. They may appear if the input is generated by an
approximate cognitive model that doesn't ensure consistency of the
output or by unchecked corrupted data.

\end{definition}

\begin{definition}[Cycles]

A plan cannot contain cycles as it makes it impossible to complete.
Cycles are usually detected as they are inserted in a plan but poor
input can potentially contains them and breaks the POP algorithm as it
cannot undo cycles.

We use a popular and simple Depth First Search (DFS) algorithm to detect
cycles. Upon cycle detection the algorithm can remove arbitrarily a link
in the cycle to break it. The most effective solution is to remove the
link that is the farthest from the goal travelling backward as it would
be that link that would have been last added in the regular POP
algorithm.

\end{definition}

\begin{definition}[Inconsistent actions]

In a plan some actions can be illegal for POP. Those are the actions
that are contradictory. An action \(a\) is contradictory if and only if
\[\{f, \lnot f \} \in eff(a) \lor \{f, \lnot f \} \in pre(a)\]

We remove only one of those effect or preconditions based on the usage
of the action in the rest of the plan. If none of those are used we
choose to remove both.

\end{definition}

\begin{definition}[Toxic actions]

These actions are those that have effects that are already in their
preconditions. This can damage a plan as well as make the execution of
POP algorithm much longer than necessary. They are defined as :
\[a | pre(a) \cap eff(a) \neq \emptyset\]

This is fixed of one of two ways : if the action has only some of its
fluent toxic (\(pre(a) \nsubseteq eff(a)\)) then the toxic fluents are
removed following \(eff(a) = eff(a)-pre(a)\), otherwise the action is
removed alltogether from plan and \(A\).

\end{definition}

\begin{definition}[Liar links]

The defects can be related to incorrect links. The first of which are
liar links : a link that doesn't reflect the preconditions or effect of
its source and target. We can note
\[a_i \xrightarrow{f} a_j | f \notin eff(a_i) \cap pre(a_j)\]

These can form with the way inconsistent actions are fixed : a deleted
fluent could still have links in the plan .

To resolve the problem we either replace \(f\) with a saviour, i.e.~a
fluent in \(eff(a_i) \cap pre(a_j)\) that isn't already provided, or we
delete the link all together.

\end{definition}

\subsubsection{Interference defects}\label{interference-defects}

This kind of defects is not as toxic as the illegal ones: they won't
make the plan unsolvable but they can still cause performance drops in
POP execution. These can appear more often in regular POP results as
they are not targeted by standard implementations.

\begin{definition}[Redundant links]

This defect can happen in POP generated plans to some extends. A
redundant link have a transitive equivalent of longer length. It means
that a link \(a_i \to a_j\) is redundant if and only if it exists
another path from \(a_i\) to \(a_j\) of length greater to \(1\). Since
POP relies on those additional links, this part focus on removing the
ones that were generated for threat removal purpose to simplify the
plan.

\end{definition}

\begin{definition}[Competing causal links]

Causal links can be found to compete with one another. A competing link
\(a_i \xrightarrow{f} a_k\) competes with another link
\(a_j \xrightarrow{f} a_k\) if it provides the same fluent to the same
action. This cannot happen in classical POP algorithm so it is not
handled by it

In order to prune the least useful actions , we need to remove the least
interesting link. In order to elect the best one , we compare their
respective providing action. We choose the link having the providing
action with the smaller outgoing degree in the planning graph. This
indicates that the action is participating to more other actions. If
both actions have the same outgoing degree then we remove the action
with the most incoming degree . This means that we remove the more needy
action .

\end{definition}

\begin{definition}[Useless actions]

Actions can sometimes have no use in a plan as they don't contribute to
it. It is the case of orphans actions (actions without any links) and .
We also consider useless actions that have no effects (except the goal
step).

\end{definition}

\subsection{Soft resolution}\label{soft-resolution}

\begin{algorithm}\caption{Soft resolution healing algorithm}\label{softresolution}\begin{algorithmic}

\Function{heal}{Problem $P$} \State int \(minViolation \gets \infty\)
\State Plan \(best \gets P.p\) \State Flaw \(annoyer\)
\ForAll{$\langle flaw, plan \rangle \in P.partialSolutions$} \State int
\(currentViolation \gets\) \Call{violation}{$plan$, $P.G$}
\If{$currentViolation < minViolation$} \State \(best \gets plan\)
\State \(annoyer \gets flaw\)
\State \(minViolation \gets currentViolation\) \EndIf
    \EndFor
    \State \(P.p \gets best\)
\State \(P.partialSolutions \gets \emptyset\)
\ForAll{Resolver $resolver \in$ \Call{healers}{$annoyer$}}
\State \Call{apply}{$resolver$, $P.p$} \EndFor
\EndFunction

\end{algorithmic}\end{algorithm}

This auxiliary algorithm is meant to deal with failure. It will heal the
plan to make the failure recoverable for the next iteration of POP. Of
course it can't fix the plan by keeping the problem as it is. This
obviously breaks some properties as the algorithm no longer adheres to
the specification of the input, but in exchange it will always issue a
valid plan whatever happens. For more information on this property go
take a look at the \hyperref[hypersoundness]{appropriate section
bellow}.

Soft failure is useful when the precision and validity of the output is
not the most important criteria we look for. In some cases (like in
recognition processes) it is more useful to have an output even if it is
not exact than no output at all. That is why we propose a soft failing
mechanism for POP algorithms.

\subsubsection{Definitions}\label{definitions-1}

We define first some new notions, then we will explain the healing
algorithm.

\begin{definition}[Needer]

A needer is an action that needs a resolution related to a flaw. We
define different types of needer according to the type of the flaw.

\begin{itemize}
\item
  Subgoal needer For a subgoal \(a_n \xrightarrow{s} a_s\) the needer is
  the action \(a_n\) that has an unsatisfied precondition in the current
  partial plan.
\item
  Threat needer The needer of a threat \(a_t\) of a link
  \(a_p \xrightarrow{t} a_n\) is the target \(a_n\) of the threatened
  causal link.
\end{itemize}

\end{definition}

\begin{definition}[Proper fluents]

A proper fluent of a flaw is the one that caused the flaw. For a subgoal
\(a_n \xrightarrow{s} a_s\) it is the unsatisfied precondition \(s\).
For a threat \(a_t\) of a causal link \(a_p \xrightarrow{t} a_n\) it is
the fluent \(t\) held by the threatened causal link.

\end{definition}

\begin{definition}[Saviour]

The saviour of a flaw is the forged action
\(a_s = \langle \emptyset, \{p\} \rangle | a_s \notin A\) with \(p\)
being the proper fluent of the flaw.

\end{definition}

\begin{definition}[Healers]

The concept of healer is made to target rogue flaws that caused total
failure. A healer is a resolver that is built around the saviour of the
flaw to provide for it . The general formula of a healer is the
following : \[a_s \xrightarrow{p} a_n\] with \(a_s\) being the saviour
of the flaw.

For threats we need an additional healer specified as an ordering
constraint from the threatening action to the saviour \(a_t \to a_s\) to
ensure that the saviour acts after the threat and therefore provides the
proper fluent for the needer.

\end{definition}

\begin{definition}[Violation degree]

The violation degree \(v(p)\) of a plan \(p\) is an indicator of the
health of a partial plan. It is the sum of the number of flaws and the
number of saviours in the plan.

\end{definition}

\subsubsection{Healing process}\label{healing-process}

The healing method is to keep track of reversions in the algorithm by
storing the partial plan and the unsatisfiable flaw each time a non
deterministic choice fails. We note the set of these failed plans \(F\).
As the POP algorithm encounters a final failure, this auxiliary
algorithm get invoked. The aim is to evaluate each backtracking partial
plan to choose the best one.

Therefore we add an order relation for \(F\) noted
\[\prec : p \prec q \iff v(p) < v(q) | \{p, q\} \subset F\]

Once the POP algorithm fails completely the soft failing algorithm can
be invoked to heal the plan. It chooses the best plan
\(b | \forall p \in F, b \prec p\) to heal it. If two plans have the
same violation degree, the algorithm chooses one arbitrarily .

The healing process is similar to how POP works : we apply the healer of
the flaw that caused the failure of the partial plan we chosen. We empty
the set \(F\) to allow POP to iterate further since the flaw is
resolved. The healing process can be done for each unsolved flaws as POP
fails repeatedly. This ensures some interesting properties explained in
the following section.

\section{SODA POP and its properties}\label{soda-pop-and-its-properties}

After defining the way our algorithms work we will focus on the
properties that can be achieved by combining them together.

\begin{algorithm}\caption{Combining all algorithms into SODA POP}\label{soda}\begin{algorithmic}

\Function{soda}{Problem $P$} \State \(P.p \gets\)
\Call{properPlan}{$P.G$, $P.A$} \State \Call{clean}{$P$} \State bool
\(valid \gets false\) \While{$\lnot valid$} \(valid \gets\)
\State \Call{pop}{$P$} \(= Success\) \If{$valid$}
\State \Call{clean}{$P$} \State \Return \(Success\) \EndIf
        \State \Call{heal}{$P$} \EndWhile
\EndFunction

\end{algorithmic}\end{algorithm}

\subsection{Convergence of POP}\label{convergence}

As to our knowledge no proof of the convergence of POP has been done we
want to explicitly formulate one.

The classic planning problem is already proven to be decidable without
functions in the fluents {[}3{]}. Therefore we can categorise the
termination cases. In the case of a solvable problem, POP is proven to
be complete. This ensures convergence in that case. Now for the more
complex case of unsolvable problems we need to refer to the way POP
works. POP algorithm will seek to solve flaws. At any time there is a
finite number of flaws since the plans have a finite number of steps. As
POP resolves these flaws it will either continue until resolution or
until failure. The problem is that POP can encounter loops in the
dependancies of actions or in threats resolution. These loops can't
occur in POP algorithm since a cycle in the ordering constraints
instantly causes a failure as the plan isn't consistent anymore. This
prooves that POP always converges.

\subsection{Hyper soundness}\label{hypersoundeness}

Now that we proved that regular POP converges we can introduce the next
property : hyper soundness. An algorithm is said to be hyper sound when
it gives a valid solution for all problems including unsolvable ones. We
note that this property isn't compatible with consistency regarding the
original problem but still does regarding the derived problem that
includes all fake actions in \(A\).

The hyper soundness of our combined algorithm is proven using the
convergence of POP and the way the Soft solving behaves. As a POP fails
it will issue flawed partial plans. As we fix the flaws artificially we
make sure that this failure won't happen again in the next iteration of
POP on the fixed plan. As the number of flaws is finite and POP
converges, the whole algorithm will converge with all flaws solved
therefore issuing a valid plan.

\subsection{Enhancement for online
planning}\label{enhancement-for-online-planning}

\section{Experimental results}\label{experimental-results}

\section*{Conclusion}\label{conclusion}
\addcontentsline{toc}{section}{Conclusion}

\section*{References}\label{references}
\addcontentsline{toc}{section}{References}

\hyperdef{}{ref-weldux5fintroductionux5f1994}{\label{ref-weldux5fintroductionux5f1994}}
{[}1{]} D. S. Weld, ``An introduction to least commitment planning,''
\emph{AI magazine}, vol. 15, no. 4, p. 27, 1994.

\hyperdef{}{ref-richterux5flamaux5f2011}{\label{ref-richterux5flamaux5f2011}}
{[}2{]} S. Richter, M. Westphal, and M. Helmert, ``LAMA 2008 and 2011,''
in \emph{International Planning Competition}, 2011, pp. 117--124.

\hyperdef{}{ref-ghallabux5fautomatedux5f2004}{\label{ref-ghallabux5fautomatedux5f2004}}
{[}3{]} M. Ghallab, D. S. Nau, and P. Traverso, \emph{Automated
planning: theory and practice}. Amsterdam ; Boston: Elsevier/Morgan
Kaufmann, 2004.

\hyperdef{}{ref-vanux5fderux5fkrogtux5fplanux5f2005}{\label{ref-vanux5fderux5fkrogtux5fplanux5f2005}}
{[}4{]} R. Van Der Krogt and M. De Weerdt, ``Plan Repair as an Extension
of Planning.'' in \emph{ICAPS}, 2005, vol. 5, pp. 161--170.

\hyperdef{}{ref-erolux5fumcp:ux5f1994}{\label{ref-erolux5fumcp:ux5f1994}}
{[}5{]} K. Erol, J. A. Hendler, and D. S. Nau, ``UMCP: A Sound and
Complete Procedure for Hierarchical Task-network Planning.'' in
\emph{AIPS}, 1994, vol. 94, pp. 249--254.

\hyperdef{}{ref-penberthyux5fucpop:ux5f1992}{\label{ref-penberthyux5fucpop:ux5f1992}}
{[}6{]} J. S. Penberthy, D. S. Weld, and others, ``UCPOP: A Sound,
Complete, Partial Order Planner for ADL.'' \emph{Kr}, vol. 92, pp.
103--114, 1992.

\hyperdef{}{ref-bechonux5fhipop:ux5f2014}{\label{ref-bechonux5fhipop:ux5f2014}}
{[}7{]} P. Bechon, M. Barbier, G. Infantes, C. Lesire, and V. Vidal,
``HiPOP: Hierarchical Partial-Order Planning,'' in \emph{STAIRS 2014:
Proceedings of the 7th European Starting AI Researcher Symposium}, 2014,
vol. 264, p. 51.

\hyperdef{}{ref-garciaux5fdefeasibleux5f2008}{\label{ref-garciaux5fdefeasibleux5f2008}}
{[}8{]} D. R. García, A. J. García, and G. R. Simari, ``Defeasible
reasoning and partial order planning,'' in \emph{Foundations of
Information and Knowledge Systems}, Springer, 2008, pp. 311--328.

\hyperdef{}{ref-colesux5fforward-chainingux5f2010}{\label{ref-colesux5fforward-chainingux5f2010}}
{[}9{]} A. J. Coles, A. Coles, M. Fox, and D. Long, ``Forward-Chaining
Partial-Order Planning.'' in \emph{ICAPS}, 2010, pp. 42--49.

\end{document}

### 2015-11-19 article/article.tex
new gitignore + redaction + examples

@@
     \usepackage{mathspec}
-    \usepackage{xltxtra,xunicode}
   \else
@@
   \fi
-  \defaultfontfeatures{Mapping=tex-text,Scale=MatchLowercase}
+  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
   \newcommand{\euro}{€}
@@
 }{}
-\ifxetex
-  \usepackage[setpagesize=false, % page size defined by xetex
-              unicode=false, % unicode breaks when used with xetex
-              xetex]{hyperref}
-\else
-  \usepackage[unicode=true]{hyperref}
-\fi
-\usepackage[usenames,dvipsnames]{color}
-\hypersetup{breaklinks=true,
-            bookmarks=true,
+\usepackage{hyperref}
+\PassOptionsToPackage{usenames,dvipsnames}{color} % color is loaded by hyperref
+\hypersetup{unicode=true,
+            pdftitle={SODA POP : Robust online Partial Ordering Planning for real life applications},
             pdfauthor={Antoine GRÉA Samir AKNINE Laetitia MATIGNON},
-            pdftitle={SODA POP : Robust online Partial Ordering Planning for real life applications},
-            colorlinks=true,
-            citecolor=blue,
-            urlcolor=blue,
-            linkcolor=magenta,
-            pdfborder={0 0 0}}
+            pdfborder={0 0 0},
+            breaklinks=true}
 \urlstyle{same}  % don't use monospace font for urls
@@
 \begin{abstract}
-This is the best of all abstracts ever !
-
-It consists of two paragraphs but that is more than enough for it to be
-awesome.
+In cognitive applications the needs of ordering action to reach a goal
+created the dommain of automated planning. This domain is actually
+domined by researches arround performance and the advances in state
+based planning has eclipsed other less efficient ways of doing. Partial
+Ordering Planning (POP) is one of the most flexible way to order actions
+and create plan that can be refined easily. This can be used to achieve
+greater resilience, repairing capabilities and soft resolution that
+applications like online plan recognision or decision making can benefit
+from. This calls for new solutions that our set of algorithm named Soft
+Ordering and Defect Aware Partial Ordering Planning (SODA POP) targets
+with plan quality in mind. The algorithm seeks a new set of defects in
+broken input and actions in order to fix them and even to derive the
+problem in order to always output a valid plan in case the problem is
+imposible to solve.
 \end{abstract}
@@
 aim to solve this in this paper while preserving the advantages of PSP
-algorithms (flexibly, easy fixing of plans, soudness and
-completeness)\textgreater{}. Our Soft Ordering and Defect Aware Partial
-Ordering Planning (SODA POP) algorithm will target those issues.
+algorithms (flexibly, easy fixing of plans, soudness and completeness).
+Our Soft Ordering and Defect Aware Partial Ordering Planning (SODA POP)
+algorithm will target those issues.
 
@@
 results. We will address these defects and propose a way to fix them in
-\hyperref[defects]{the next section}.
+\protect\hyperlink{defects}{the next section}.
 
@@
 
+On our example it illustrate really well the need for resilience. The
+algorithm simply recursively chose the actions and end up with the
+partial plan represented in figure \ref{fig:proper}. The partial plan
+doesn't have an initial state (because of its offline nature). This plan
+also shows several cycles and obvious problems. Moreover the plan has
+all the steps of the correct final plan and therefore remove the subgoal
+search in POP if it uses this plan has input (after it has been cleaned
+obviously).
+
+\begin{figure}[htbp]
+\centering
+\includegraphics{graphics/proper.pdf}
+\caption{Proper plan of the example goal\label{fig:proper}}
+\end{figure}
+
 This auxiliary algorithm is therefore used as a caching mechanism for
@@
 
-\hyperdef{}{defects}{\subsection{Defect resolution}\label{defects}}
+\hypertarget{defects}{\subsection{Defect resolution}\label{defects}}
 
@@
 valid plan whatever happens. For more information on this property go
-take a look at the \hyperref[hypersoundness]{appropriate section
-bellow}.
+take a look at the \protect\hyperlink{hypersoundness}{appropriate
+section bellow}.
 
@@
 \Call{properPlan}{$P.G$, $P.A$} \State \Call{clean}{$P$} \State bool
-\(valid \gets false\) \While{$\lnot valid$} \(valid \gets\)
-\State \Call{pop}{$P$} \(= Success\) \If{$valid$}
-\State \Call{clean}{$P$} \State \Return \(Success\) \EndIf
+\(valid \gets false\) \While{$\lnot valid$} \State \(valid \gets\)
+\Call{pop}{$P$} \(= Success\) \If{$valid$} \State \Call{clean}{$P$}
+\State \Return \(Success\) \EndIf
         \State \Call{heal}{$P$} \EndWhile
@@
 
-\hyperdef{}{ref-weldux5fintroductionux5f1994}{\label{ref-weldux5fintroductionux5f1994}}
+\hypertarget{refs}{}
+\hypertarget{ref-weldux5fintroductionux5f1994}{}
 {[}1{]} D. S. Weld, ``An introduction to least commitment planning,''
@@
 
-\hyperdef{}{ref-richterux5flamaux5f2011}{\label{ref-richterux5flamaux5f2011}}
+\hypertarget{ref-richterux5flamaux5f2011}{}
 {[}2{]} S. Richter, M. Westphal, and M. Helmert, ``LAMA 2008 and 2011,''
@@
 
-\hyperdef{}{ref-ghallabux5fautomatedux5f2004}{\label{ref-ghallabux5fautomatedux5f2004}}
+\hypertarget{ref-ghallabux5fautomatedux5f2004}{}
 {[}3{]} M. Ghallab, D. S. Nau, and P. Traverso, \emph{Automated
@@
 
-\hyperdef{}{ref-vanux5fderux5fkrogtux5fplanux5f2005}{\label{ref-vanux5fderux5fkrogtux5fplanux5f2005}}
+\hypertarget{ref-vanux5fderux5fkrogtux5fplanux5f2005}{}
 {[}4{]} R. Van Der Krogt and M. De Weerdt, ``Plan Repair as an Extension
@@
 
-\hyperdef{}{ref-erolux5fumcp:ux5f1994}{\label{ref-erolux5fumcp:ux5f1994}}
+\hypertarget{ref-erolux5fumcp:ux5f1994}{}
 {[}5{]} K. Erol, J. A. Hendler, and D. S. Nau, ``UMCP: A Sound and
@@
 
-\hyperdef{}{ref-penberthyux5fucpop:ux5f1992}{\label{ref-penberthyux5fucpop:ux5f1992}}
+\hypertarget{ref-penberthyux5fucpop:ux5f1992}{}
 {[}6{]} J. S. Penberthy, D. S. Weld, and others, ``UCPOP: A Sound,
@@
 
-\hyperdef{}{ref-bechonux5fhipop:ux5f2014}{\label{ref-bechonux5fhipop:ux5f2014}}
+\hypertarget{ref-bechonux5fhipop:ux5f2014}{}
 {[}7{]} P. Bechon, M. Barbier, G. Infantes, C. Lesire, and V. Vidal,
@@
 
-\hyperdef{}{ref-garciaux5fdefeasibleux5f2008}{\label{ref-garciaux5fdefeasibleux5f2008}}
+\hypertarget{ref-garciaux5fdefeasibleux5f2008}{}
 {[}8{]} D. R. García, A. J. García, and G. R. Simari, ``Defeasible
@@
 
-\hyperdef{}{ref-colesux5fforward-chainingux5f2010}{\label{ref-colesux5fforward-chainingux5f2010}}
+\hypertarget{ref-colesux5fforward-chainingux5f2010}{}
 {[}9{]} A. J. Coles, A. Coles, M. Fox, and D. Long, ``Forward-Chaining

### 2015-11-21 article/filters/algorithm.py
Finish main redaction (no check) + new defects

@@ -36,7 +36,7 @@ def algorithms(key, value, format, meta):
                     caption = '\\caption{' + value + '}'
                 else:
                     caption = ""
-                return([latex('\\begin{algorithm}' + caption + label + '\\begin{algorithmic}')] + contents +
+                return([latex('\\begin{algorithm}' + caption + label + '\\begin{algorithmic}[1]')] + contents +
                        [latex('\\end{algorithmic}\\end{algorithm}')])
             elif format == "html" or format == "html5":
                 global theoremcount

### 2015-11-22 article/article.tex
Redacted Experiments + Proofs + Conclusions + sugested corrections + proof reading

@@
             pdftitle={SODA POP : Robust online Partial Ordering Planning for real life applications},
-            pdfauthor={Antoine GRÉA Samir AKNINE Laetitia MATIGNON},
+            pdfauthor={Paper ID\#232},
             pdfborder={0 0 0},
@@
 applications}
-\author{Antoine GRÉA Samir AKNINE Laetitia MATIGNON}
+\author{Paper ID\#232}
 \date{}
@@
 \usepackage{courier}
-\usepackage{algorithm, algpseudocode}
+\usepackage{algorithm}
+\usepackage[noend]{algpseudocode}
 \usepackage{amsthm}
-
-\newtheorem{definition}{Definition}
 
@@
 
+\newtheorem{definition}{Definition}
+
+%%%%%% for algorithms
+\errorcontextlines\maxdimen
+\algrenewcommand\alglinenumber[1]{\tiny\color{solarized-base0} #1}
+
+% begin vertical rule patch for algorithmicx (http://tex.stackexchange.com/questions/144840/vertical-loop-block-lines-in-algorithmicx-with-noend-option)
+\makeatletter
+% start with some helper code
+% This is the vertical rule that is inserted
+    \newcommand*{\algrule}[1][\algorithmicindent]{\makebox[#1][l]{\color{solarized-base0}\hspace*{.5em}\thealgruleextra\vrule height \thealgruleheight depth \thealgruledepth}}%
+% its height and depth need to be adjustable
+\newcommand*{\thealgruleextra}{}
+\newcommand*{\thealgruleheight}{.75\baselineskip}
+\newcommand*{\thealgruledepth}{.25\baselineskip}
+
+\newcount\ALG@printindent@tempcnta
+\def\ALG@printindent{%
+    \ifnum \theALG@nested>0% is there anything to print
+        \ifx\ALG@text\ALG@x@notext% is this an end group without any text?
+            % do nothing
+        \else
+            \unskip
+            \addvspace{-1pt}% FUDGE to make the rules line up
+            % draw a rule for each indent level
+            \ALG@printindent@tempcnta=1
+            \loop
+                \algrule[\csname ALG@ind@\the\ALG@printindent@tempcnta\endcsname]%
+                \advance \ALG@printindent@tempcnta 1
+            \ifnum \ALG@printindent@tempcnta<\numexpr\theALG@nested+1\relax% can't do <=, so add one to RHS and use < instead
+            \repeat
+        \fi
+    \fi
+    }%
+\usepackage{etoolbox}
+% the following line injects our new indent handling code in place of the default spacing
+\patchcmd{\ALG@doentity}{\noindent\hskip\ALG@tlm}{\ALG@printindent}{}{\errmessage{failed to patch}}
+\makeatother
+
+% the required height and depth are set by measuring the content to be shown
+% this means that the content is processed twice
+\newbox\statebox
+\newcommand{\myState}[1]{%
+    \setbox\statebox=\vbox{#1}%
+    \edef\thealgruleheight{\dimexpr \the\ht\statebox+1pt\relax}%
+    \edef\thealgruledepth{\dimexpr \the\dp\statebox+1pt\relax}%
+    \ifdim\thealgruleheight<.75\baselineskip
+        \def\thealgruleheight{\dimexpr .75\baselineskip+1pt\relax}%
+    \fi
+    \ifdim\thealgruledepth<.25\baselineskip
+        \def\thealgruledepth{\dimexpr .25\baselineskip+1pt\relax}%
+    \fi
+    %\showboxdepth=100
+    %\showboxbreadth=100
+    %\showbox\statebox
+    \State #1%
+    %\State \usebox\statebox
+    %\State \unvbox\statebox
+    %reset in case the next command is not wrapped in \myState
+    \def\thealgruleheight{\dimexpr .75\baselineskip+1pt\relax}%
+    \def\thealgruledepth{\dimexpr .25\baselineskip+1pt\relax}%
+}
+% end vertical rule patch for algorithmicx
+
+%%%% For listings (code blocks)
 \lstset{
@@
 
+%%%% For links URL
+\hypersetup{colorlinks=true, linkcolor=solarized-blue, citecolor=solarized-base1, filecolor=solarized-magenta, urlcolor=solarized-cyan}
+
 % Redefines (sub)paragraphs to behave more like sections
@@
 \begin{abstract}
-In cognitive applications the needs of ordering action to reach a goal
-created the dommain of automated planning. This domain is actually
-domined by researches arround performance and the advances in state
-based planning has eclipsed other less efficient ways of doing. Partial
-Ordering Planning (POP) is one of the most flexible way to order actions
-and create plan that can be refined easily. This can be used to achieve
-greater resilience, repairing capabilities and soft resolution that
-applications like online plan recognision or decision making can benefit
-from. This calls for new solutions that our set of algorithm named Soft
-Ordering and Defect Aware Partial Ordering Planning (SODA POP) targets
-with plan quality in mind. The algorithm seeks a new set of defects in
-broken input and actions in order to fix them and even to derive the
-problem in order to always output a valid plan in case the problem is
-imposible to solve.
+As of recent years, automated planning domain has mainly focused on
+performances and advances in state space planning to improve
+scalability. That orientation shadows other less efficient ways of doing
+like Partial Ordering Planning (POP) that has the advantage to be much
+more flexible. This approach \emph{generates} plans that can be refined
+easily and can be used to achieve greater resilience, repairing
+capabilities and soft resolution that applications \emph{based on}
+online plan recognition or decision-making can benefit from. \emph{This
+paper presents} a set of algorithms, named Soft Ordering and Defect
+Aware Partial Ordering Planning (SODA POP), that aims at targeting these
+objectives and maintain a high plan quality. Our algorithms create
+proper offline plans for goals and use an effective defect fixing
+\emph{algorithm} to repair input plans even if these plans are
+corrupted. SODA POP can also use healer actions and links in order to
+always return a valid plan even in cases where the problem is impossible
+to solve using problem derivation. Some relevant properties of these
+algorithms are analyzed in this article and experimental results show
+interesting performances for online planning and repairing.
 \end{abstract}
@@
 \emph{least commitment strategy} on plan step ordering that can allow
-actions to be flexibly interleaved during execution {[}1{]}. Thus the
+actions to be flexibly interleaved during execution {[}1{]}. Thus, the
 way the search is made using flexible partial plan as a search space
@@
 plans {[}3{]}. This have made the search of performance the main axis of
-research for planning in the community.
+research for planning in the community .
 
@@
 but has never been paired with the resilience that some other cognitive
-applications may need, especially when dealing with sensors data and
-noise.
+applications may need, especially when dealing with sensors noise in
+input data.
 
@@
 way to repair the issues. For example if an action becomes unrelevant or
-incoherent the flaw in the partial plan makes the problem to fix
-explicit and therefore easier to fix. The client softwares might
-sometimes provide plans that can contain errors and imperfections that
-will decrease significantly the efficiency of the computation and the
-quality of the output plan.
+incoherent, the flaw in the partial plan makes the issue explicit and
+therefore easier to fix. Softwares might sometimes provide plans that
+can contain errors and imperfections that will decrease significantly
+the efficiency of the computation and the quality of the output plan.
 
@@
 aim is to find a solution relative to the original plan (which makes
-sense). But as we proceed a mechanism of \emph{problem} fixing may be
-required. This will allow soft solving of any problem regardless of its
-solvability.
-
-One of the application that needs these improvements is plan recognition
-with the particular use of off-the-shelf planners to infer the pursued
-goal of an agent where online planning and resilience is particularly
-important.
-
-These problems call for new ways to improve the answer and behavior of a
-planner. These improvements must provide relevant plan information
-pointing out exactly what needs to be done in order to make a planning
-problem solvable, even in the case of obviously broken input data. We
-aim to solve this in this paper while preserving the advantages of PSP
-algorithms (flexibly, easy fixing of plans, soudness and completeness).
-Our Soft Ordering and Defect Aware Partial Ordering Planning (SODA POP)
-algorithm will target those issues.
-
-Our new set of auxiliary algorithms allows to make POP algorithm more
+sense). But as we proceed a mechanism of \emph{problem derivation} may
+be required. This will allow soft solving of any problem regardless of
+its resolvability.
+
+One of the applications that needs these improvements is plan
+recognition with the particular use of off-the-shelf planners to infer
+the pursued goal of an agent where online planning and resilience is
+particularly important {[}5{]}. This method adds dummy actions that need
+to be satisfied by modifying the goal to ensure that the observed plan
+is selected by the planner. A system that is able to repair plan in real
+time will ease such an application. Another application is
+decision-making in dynamical environments. Indeed, having a plan that
+details all steps and explicits the ones that are not possible, can help
+decide of the line of action to take.
+
+These problems call for new ways to improve the answer of a planner.
+These improvements must provide relevant plan information pointing out
+exactly what needs to be done in order to make a planning problem
+solvable, even in the case of obviously inconsistent input data. This
+paper aims to solve this while preserving the advantages of PSP
+algorithms (flexibility, easy fixing of plans, soundness and
+completeness). Our Soft Ordering and Defect Aware Partial Ordering
+Planning (SODA POP) algorithm will target those issues.
+
+Our new set of auxiliary algorithms allows making POP algorithm more
 resilient, efficient and relevant. This is done by pre-emptively
 computing proper plans for goals, by solving new kinds of defects that
-input plans may provide, and by healing compromised plan by extending
-the initial problem to allow resolution.
-
-To explain this work we first describe a few notions, notations and
+input plans may exhibit, and by healing compromised plan by deriving the
+initial problem with forged actions to allow resolution.
+
+To explain this work we first introduce a few notions, notations and
 specificities of existing POP algorithms. Then we present and illustrate
-their limitations, categorising the different defects arising from the
-resilience problem and explaining our complementary algorithms, their
-uses and properties. To finish we compare the performance, resilence and
+their limitations, categorizing the different defects arising from the
+resilience problem and explaining our auxiliary algorithms, their uses
+and properties. To finish we compare the performance, resilience and
 quality of POP and our solution.
@@
 
-In order to present our work and explain examples we introduce a way of
-representation for schema in figure \ref{fig:legend} and notations for
-mathematical representation.
-
-\begin{figure}[htbp]
-\centering
-\includegraphics{graphics/legend.pdf}
-\caption{Global legend for how partial plans are represented in the
-current paper\label{fig:legend}}
-\end{figure}
-
-\subsection{Classic planning}\label{classic-planning}
+First we introduce some definitions and notations for mathematical
+representation to present our model.
+
+\subsection{Classical planning}\label{classical-planning}
 
@@
 
-A fluent is a property of the world. It is often represented by first
-order logical propositions but in our case we choose to focus on the
-algorithm and to represent fluents as simple literals (fully
-instantiated). We note \(\lnot f\) the complementary fluent of \(f\)
-meaning that \(f\) is true when \(\lnot f\) is false and vice-versa.
-
-In order to make our example simpler we use \(\mathbb{Q}^*\), the set of
+A fluent is a property of the world. We note \(\lnot f\) the
+complementary fluent of \(f\) meaning that \(f\) is true when
+\(\lnot f\) is false and vice-versa.
+
+\end{definition}
+
+It is often represented by first order logical propositions but in this
+paper we choose to focus on the algorithm and to represent fluents as
+simple literals (fully instantiated) using \(\mathbb{Q}^*\), the set of
 relative integers without \(0\), as the fluent domain. We use negative
@@
 
-\end{definition}
-
 \begin{definition}[State]
 
-We define a state as a set of fluents. States can be additively
+A state is defined as a set of fluents. States can be additively
 combined. We note
@@
 
-An action \(a\) can be functionally applied to a state \(s\) following :
-\[a:= \substack{ \left\{ s \models a \middle| s \in S\right\} \to S\\
+An action \(a\) can be functionally applied to a state \(s\) as follows
+: \[a:= \substack{ \left\{ s \models a \middle| s \in S\right\} \to S\\
     a(s) \mapsto s + eff(a)}\] with \(S\) being the set of all states.
-There are some special names for actions. An action with no
-preconditions is synonymous to a state and one with empty effect is
+This means that an action adds all its effect to the state of the world
+on application (by removing complementary fluents if needed)
+
+\end{definition}
+
+We distinguish between two specific kinds of actions : actions with no
+preconditions are synonymous to a state and those with empty effect are
 called a goal.
-
-\end{definition}
 
@@
 \(\{ a_i, a_j \} \subset A_p \land f \in eff(a_i) \cap pre(a_j)\) or
-said otherwise that \(f\) is provided by \(a_i\) to \(a_j\) via this
-causal link. We include the ordering constraints of PSP in the causal
-links. An ordering constraint is noted \(a_i \to a_j\) and means that
-the plan consider \(a_i\) as a step that is prior to \(a_j\) without
-specific cause (usually because of threat resolution).
-
-\end{definition}
+said otherwise, this causal link means that the fluent \(f\) is provided
+by an effect of \(a_i\) to a precondition of \(a_j\). We include the
+ordering constraints of PSP in the causal links. An ordering constraint
+is noted \(a_i \to a_j\) and means that the plan means \(a_i\) as a step
+that is prior to \(a_j\) without specific cause (usually because of
+threat resolution). We note the order relation over \(A\) for an action
+\(a_i\) that is prior to the action \(a_j\) following all the causal
+links and ordering constraints \(a_i \succ a_j\) .
+
+\end{definition}
+
+The figure \ref{fig:legend} details how the elements of partial plans
+are represented in the rest of this paper.
+
+\begin{figure}[htbp]
+\centering
+\includegraphics{graphics/legend.pdf}
+\caption{Global legend for how partial plans are represented in this
+paper\label{fig:legend}}
+\end{figure}
+
+In this figure the fluent \(5\) is a precondition of the action \(a\)
+and the fluent \(6\) an effect. The causal link is providing the fluent
+\(7\) (only as a representation example or it would be a liar link). The
+dotted line is an ordering constraint that would mean that \(a\) should
+be placed before \(a\) (for representation still or it would be a
+cycle). \(I\) and \(G\) are respectively the initial and goal step.
 
@@
 When refining a partial plan, we need to fix flaws. Those could be
-present or be created by the refining process. Flaws can either be
-unsatisfied subgoals or threats to causal links.
+present in the input or created by the refining process. Flaws can
+either be unsatisfied subgoals or threats to causal links.
 
@@
 
-A resolver for a subgoal is an action \(a_r \in A\) that has \(s\) as an
-effect \(s \in eff(a_r)\). It is inserted along with a causal link noted
-\(a_r \xrightarrow{s} a_s\).
-
 \end{definition}
@@
 \(a_i \xrightarrow{t} a_j\) if and only if
-\[\neg t \in eff(a_t) \land a_i \succ a_t \succ a_j \models L\] Said
-otherwise, the action has a possible complementary effect that can be
-inserted between two actions needing this fluent while being consistant
-with the ordering constraint in \(L\).
-
-The usual resolvers are either \(a_t \to a_i\) or \(a_j \to a_t\) which
-are called respectively promotion and demotion links. Another resolver
-is called a white knight that is an action \(a_k\) that reestablish
-\(t\) after \(a_t\).
-
-\end{definition}
+\[\neg t \in eff(a_t) \land a_i \succ a_t \succ a_j \models L\]
+
+\end{definition}
+
+In other words, the action has a possible complementary effect that can
+be inserted between two actions needing this fluent while being
+consistent with the ordering constraint in \(L\).
+
+\subsubsection{Resolvers}\label{resolvers}
+
+Resolvers are a set of actions and causal links
+\(r = \langle A_r , L_r \rangle\) that fixes flaws. A resolver for a
+subgoal is an action \(a_r \in A\) that has \(s\) as an effect
+\(s \in eff(a_r)\) inserted along with a causal link noted
+\(a_r \xrightarrow{s} a_s\). The usual resolvers for a threat are either
+\(a_t \to a_i\) or \(a_j \to a_t\) which are called respectively
+promotion and demotion links. Another resolver is called a white knight
+that is an action \(a_k\) that reestablishes \(t\) after \(a_t\) along
+with an ordering constraint \(a_t \to a_k\) and a causal link
+\(a_k \xrightarrow{t} a_j\).
 
@@
 
+\end{definition}
+
 We call a flat plan valid if and only if it can be functionally applied
@@
 
-\end{definition}
-
 \begin{definition}[Validity]
@@
 Partial Order Planning (POP) is a popular implementation of the general
-PSP algorithm. It is proven to be sound and complete {[}5{]}. The
+PSP algorithm. It is proven to be sound and complete {[}6{]}. The
 completeness of the algorithm guarantees that if the problem has a
@@
 
-\begin{algorithm}\caption{Classical Partial Order Planning algorithm}\label{pop}\begin{algorithmic}
+\begin{algorithm}\caption{Classical Partial Order Planning algorithm}\label{pop}\begin{algorithmic}[1]
 
@@
 This standard way of doing have seen multiple improvements over
-expressiveness like with UCPOP {[}6{]}, hierarchical task network to add
-more user control over sub-plans {[}7{]}, cognition with defeasible
-reasoning {[}8{]}, or speed with multiple ways to implement the popular
-fast forward method from state planning {[}9{]}. However, all these
+expressiveness like with UCPOP {[}7{]}, hierarchical task network to add
+more user control over sub-plans {[}8{]}, cognition with defeasible
+reasoning {[}9{]}, or speed with multiple ways to implement the popular
+fast forward method from state planning {[}10{]}. However, all these
 variants do not treat the problem of online planning, resilience and
@@
 Some other closer works like {[}4{]} treats the problem of online
-planning by removing big chuncks of the partial plan by identifying
-incorect trees in the plan. This causes an heavy replanning of the
-problem even if only one action needed removal. This is a big problem
-when trying to adapt a plan with minimal changes due to replanning.
+planning by removing big chunks of the partial plan by identifying
+incorrect trees in the plan. This along with heuristic choice of
+unrefinemment strategies. This causes a heavy replanning of the problem
+even if only one action needed removal. This also lead to an exponential
+number of plan to consider. This is a big problem when trying to adapt a
+plan with minimal changes due to replanning.
 
@@
 threatening to the plan's integrity and will generate threats. We
-introduce \(u\) as a useless action, \(v\) as a toxic action, \(w\) as a
-dead-end action and \(x\) as a contradictory action.
+introduce \(u\) and \(v\) as a toxic action, \(w\) as a dead-end action
+and \(x\) as a contradictory action. These notions will be defined
+\protect\hyperlink{defects}{later}.
 
@@
 being contradictory the action \(x\) raised no alarm. As for ordering
-constraints we can clearly see that the link \(a \to t\) is redundant
+constraints, we can clearly see that the link \(a \to t\) is redundant
 with the path \(a \xrightarrow{5} c \to t\) that already puts that
-constraint by transitivity. Also some problems arise during execution
+constraint by transitivity. Also, some problems arise during execution
 with the selection of \(w\) that causes a dead-end.
@@
 plan quality, we propose a set of auxiliary algorithms that provides POP
-with a clean and efficiently populated initial plan.
+with a clean and efficiently populated initial plan. The complete
+algorithm will be presented in \protect\hyperlink{soda}{the next
+section} as a combination of all auxiliary algorithms and regular POP.
 
@@
 
-\begin{algorithm}\caption{Proper plan generation algorithm for a given goal $g$}\label{properplan}\begin{algorithmic}
+\begin{algorithm}\caption{Proper plan generation algorithm for a given goal $g$}\label{properplan}\begin{algorithmic}[1]
 
@@
 
-On our example it illustrate really well the need for resilience. The
-algorithm simply recursively chose the actions and end up with the
-partial plan represented in figure \ref{fig:proper}. The partial plan
-doesn't have an initial state (because of its offline nature). This plan
-also shows several cycles and obvious problems. Moreover the plan has
-all the steps of the correct final plan and therefore remove the subgoal
-search in POP if it uses this plan has input (after it has been cleaned
-obviously).
-
 \begin{figure}[htbp]
@@
 
+On our example it illustrates really well the need for resilience. The
+algorithm simply recursively chose the actions and end up with the
+partial plan represented in figure \ref{fig:proper}. The partial plan
+doesn't have an initial state (because of its offline nature). This plan
+also shows several cycles and obvious problems. Moreover, the plan has
+all the steps of the correct final plan and therefore remove the subgoal
+search in POP if it uses this plan has input (after it has been cleaned
+obviously).
+
 This auxiliary algorithm is therefore used as a caching mechanism for
@@
 
-\begin{algorithm}\caption{Defect resolution algorithm}\label{defectresolution}\begin{algorithmic}
-
-\Function{clean}{Problem $P$} \State \Call{illegal}{$P$}
-\State \Call{interfering}{$P$} \EndFunction
-
-\Function{illegal}{Problem $P$}
+\begin{algorithm}\caption{Defect resolution algorithm}\label{defectresolution}\begin{algorithmic}[1]
+
+\Function{clean}{Problem $P$}
 \State \Call{assert}{$pre(P.I) = \emptyset$}
@@
 \State \(P.p.A_p \gets P.p.A_p \cup \{P.I, P.G\}\)
-\State \Call{breakCycles}{$P$} \State Actions
-\(actions \gets P.A \cup P.p.A_p\) \ForAll{Action $a \in actions$}
-\State \Call{inconsistent}{$a$, $P$} \State \Call{toxic}{$a$, $P$}
-\EndFor
-    \State \Call{liarLinks}{$P$} \EndFunction
-
-\Function{interfering}{Problem $P$} \State \Call{repeating}{$P$}
-\State \Call{useless}{$P$} \EndFunction
+\State \(defects \gets\) \Call{findDefects}{$P$}
+\State \Call{fix}{$defects$, $P$} \EndFunction
+
+\Function{fix}{Defects $defects$, Problem $P$}
+\ForAll{Defect $d \in defects$} \State \(defect.\)\Call{fix}{}
+\Comment{Fixing is proper to the defect} \EndFor
+\EndFunction
+
+\Function{findDefects}{Problem $P$} \State \Return \Call{illegal}{$P$}
+\(+\) \Call{interfering}{$P$} \EndFunction
 
@@
 auxiliary algorithm is to clean the plans from such defects in order to
-improve computational time, resilience and plan quality . It should be
+improve computational time, resilience and plan quality. It should be
 noted that in some cases cleaning plans will increase the number of
 flaws in the plan but will always improve the overall quality of it.
+
+\begin{definition}[Plan Quality]
+
+Plan quality is an indicator that is measured by the number of defects
+in a partial plan. There are two specific indicators for a plan quality
+: the action quality and the link quality. We define the link and action
+quality as respectively the number of link or action related defects
+divided by the number of links or actions in the resulting plan.
+\[quality_{action}(p) =  1 - \left( \#ActionDefects(p) \over \#p.A_p \right)\]
+
+\end{definition}
+
+From there it is obvious that plan quality will improve over POP since
+the present algorithm is guaranteed to remove all defects in a plan.
 
@@
 
-\begin{definition}[Illegal defects]
+\subsubsection{Illegal defects}\label{illegal-defects}
 
@@
 approximate cognitive model that doesn't ensure consistency of the
-output or by unchecked corrupted data.
-
-\end{definition}
+output or by unchecked corrupted data. These defects will most of the
+time simply break regular POP algorithms (from existing cycles) or at
+least make the performances decrease significantly (from toxic actions).
 
@@
 Cycles are usually detected as they are inserted in a plan but poor
-input can potentially contains them and breaks the POP algorithm as it
+input can potentially contain them and breaks the POP algorithm as it
 cannot undo cycles.
 
-We use a popular and simple Depth First Search (DFS) algorithm to detect
+\end{definition}
+
+We use strongly connected component detection algorithm to detect
 cycles. Upon cycle detection the algorithm can remove arbitrarily a link
 in the cycle to break it. The most effective solution is to remove the
-link that is the farthest from the goal travelling backward as it would
+link that is the farthest from the goal traveling backward as it would
 be that link that would have been last added in the regular POP
-algorithm.
-
-\end{definition}
+algorithm. But finding this is extremely time consuming and most of the
+time the cycles are of one or two actions so we choose to keep that
+algorithm simpler and faster.
 
@@
 that are contradictory. An action \(a\) is contradictory if and only if
-\[\{f, \lnot f \} \in eff(a) \lor \{f, \lnot f \} \in pre(a)\]
+\[\exists f \{f, \lnot f \} \in eff(a) \lor \{f, \lnot f \} \in pre(a)\]
+
+\end{definition}
 
 We remove only one of those effect or preconditions based on the usage
-of the action in the rest of the plan. If none of those are used we
-choose to remove both.
-
-\end{definition}
+of the action in the rest of the plan. If none of those are used, we
+choose to remove both. In our example in figure \ref{fig:problem} the
+action \(x\) is one of these inconsistent actions with fluent \(2\) and
+\(-2\) in its effects.
 
@@
 These actions are those that have effects that are already in their
-preconditions. This can damage a plan as well as make the execution of
-POP algorithm much longer than necessary. They are defined as :
-\[a | pre(a) \cap eff(a) \neq \emptyset\]
-
-This is fixed of one of two ways : if the action has only some of its
-fluent toxic (\(pre(a) \nsubseteq eff(a)\)) then the toxic fluents are
-removed following \(eff(a) = eff(a)-pre(a)\), otherwise the action is
-removed alltogether from plan and \(A\).
-
-\end{definition}
+preconditions or empty effects. This can damage a plan as well as make
+the execution of POP algorithm much longer than necessary. They are
+defined as :
+\[a | pre(a) \cap eff(a) \neq \emptyset \lor eff(a) = \emptyset\]
+
+\end{definition}
+
+This is fixed by removing the toxic fluents
+(\(pre(a) \nsubseteq eff(a)\)) following \(eff(a) = eff(a)-pre(a)\). If
+the effects gets empty the action is removed altogether from plan and
+\(A\). For example in figure \ref{fig:problem} the actions \(u\) and
+\(v\) are a toxic action as the fluent \(4\) is in the effects and
+preconditions of \(v\). In this case these actions will be removed by
+the algorithm as it doesn't have any other effects.
 
@@
 
-These can form with the way inconsistent actions are fixed : a deleted
-fluent could still have links in the plan .
-
-To resolve the problem we either replace \(f\) with a saviour, i.e.~a
-fluent in \(eff(a_i) \cap pre(a_j)\) that isn't already provided, or we
-delete the link all together.
-
-\end{definition}
+\end{definition}
+
+A liar link can be either already present in the data or created by the
+removal of an effect of an inconsistent or toxic action (with the causal
+link still remaining).
+
+We call lies fluents that participates in the lies. To resolve the
+problem we remove \(f\) and add all savior fluents, i.e.~a fluent in
+\(eff(a_i) \cap pre(a_j)\) that isn't already provided. We delete the
+link all together if it doesn't link any fluents.
 
@@
 that a link \(a_i \to a_j\) is redundant if and only if it exists
-another path from \(a_i\) to \(a_j\) of length greater to \(1\). Since
-POP relies on those additional links, this part focus on removing the
-ones that were generated for threat removal purpose to simplify the
-plan.
-
-\end{definition}
+another path from \(a_i\) to \(a_j\) of length greater to \(1\).
+
+\end{definition}
+
+Since POP relies on those additional links, this part focus on removing
+the ones that were generated for threat removal purpose to simplify the
+plan. For example in the figure \ref{fig:pop} we can see that the
+ordering constraint from \(a\) to \(t\) is redundant with the path
+\(a \xrightarrow{5} c \to t\) in that it isn't needed to resolve the
+threat. Therefore, the algorithm would remove it. This reduce the number
+of edges in the plan and therefore simplify it.
 
@@
 \(a_j \xrightarrow{f} a_k\) if it provides the same fluent to the same
-action. This cannot happen in classical POP algorithm so it is not
-handled by it
-
-In order to prune the least useful actions , we need to remove the least
-interesting link. In order to elect the best one , we compare their
-respective providing action. We choose the link having the providing
-action with the smaller outgoing degree in the planning graph. This
-indicates that the action is participating to more other actions. If
-both actions have the same outgoing degree then we remove the action
-with the most incoming degree . This means that we remove the more needy
-action .
-
-\end{definition}
-
-\begin{definition}[Useless actions]
+action.
+
+\end{definition}
+
+This cannot happen in classical POP algorithm so it is not handled by
+it. The multiple links providing the same fluent to the same action is
+making the plan more complex like redundant links but also can hide
+useless actions. This is why they must be removed in a way that reveals
+them and reduce the need for extra unnecessary actions in the plan that
+would cause more flaws for POP to handle.
+
+\begin{figure}[htbp]
+\centering
+\includegraphics{graphics/competing.pdf}
+\caption{Example of choice for cutting competing links based on
+usefulness of actions\label{fig:competing}}
+\end{figure}
+
+In order to prune the least useful actions, we need to remove the least
+interesting link. In order to elect the best one, we compare their
+respective providing action.
+
+\begin{definition}[Usefulness of an action]
+
+The usefulness of an action is the number of participating links
+(outgoing causal links) divided by the number of needing links (incoming
+causal links). If there are no needing links, or the action is either an
+initial step or a goal the usefulness is \(+\infty\). The usefulness of
+savior action is \(0\).
+
+\end{definition}
+
+We choose the link with the source action having the highest usefulness.
+This makes replacing unnecessary savior actions and allows to therefore
+reduce the usefulness of the least action in the hope it will become
+orphan and pruned from the plan.
+
+In the example figure \ref{fig:competing} the action \(a_j\) on the left
+participates much more than the action \(a_i\) and therefore the link to
+be removed would be \(a_i \xrightarrow{f} a_k\). On the right example
+the actions doesn't have different outgoing links but the action \(a_j\)
+is here much needier than its competitor and therefore the link to be
+removed is the link \(a_j \xrightarrow{f} a_k\).
+
+\begin{definition}[Orphan actions]
 
 Actions can sometimes have no use in a plan as they don't contribute to
-it. It is the case of orphans actions (actions without any links) and .
-We also consider useless actions that have no effects (except the goal
-step).
-
-\end{definition}
+it. It is the case of orphans actions (actions without any links) and
+action with no outgoing path to the goal (meaning that it doesn't
+participate in the plan). That also concerns action that would become
+orphan if another orphan action is removed.
+
+\end{definition}
+
+In order to fix this we derive the idea of the backward removal tree of
+{[}4{]}. The idea is to remove an action if all its outgoing causal
+links are leading to useless actions. We iterate over all actions until
+no new useless action is discovered. All useless actions are then
+removed from the plan.
+
+\begin{algorithm}\caption{Orphan actions finding algorithm}\label{orphanaction_find}\begin{algorithmic}[1]
+
+\Function{$OrphanAction.$find}{Problem $P$} \State Actions
+\(orphan \gets \emptyset\) \State int \(oldSize\) \Repeat
+        \State \(oldSize \gets \#orphan\)
+\ForAll{Action $step \in P.p.A_p$} \If{$step \in orphan$}
+\State continue \EndIf
+            \State int \(towardOrphan \gets 0\) \State Causal Links
+\(outgoing \gets\) \protect\Call{outgoingEdgesOf}{$step$, $P.p$}
+\ForAll{Causal Link $link \in outgoing$} \If{$link.target \in orphan$}
+\State \(towardOrphan ++\) \EndIf
+            \EndFor
+            \If{$\#outgoing = towardOrphan \land step \notin \{ P.I, P.G\}$}
+\State \(orphan \gets orphan \cup \{step\}\) \EndIf
+        \EndFor
+    \Until{$oldSize \neq \#orphan$} \State \Return \(orphan\)
+\EndFunction
+
+\end{algorithmic}\end{algorithm}
+
+\begin{definition}[Competing actions]
+
+In the same way links can be competing toward a common needer, there are
+sometimes in the plan actions that are more suited to achieve a goal.
+These actions are taken into account if they are more useful than the
+source of the link, if they wouldn't cause a cycle and if they have
+effects that are carried by the link.
+
+\end{definition}
+
+In such a case the link is removed and another one is formed by the
+better suited action.
 
@@
 
-\begin{algorithm}\caption{Soft resolution healing algorithm}\label{softresolution}\begin{algorithmic}
+\begin{algorithm}\caption{Soft resolution healing algorithm}\label{softresolution}\begin{algorithmic}[1]
 
@@
 
-\begin{definition}[Saviour]
-
-The saviour of a flaw is the forged action
+\begin{definition}[Savior]
+
+The savior of a flaw is the forged action
 \(a_s = \langle \emptyset, \{p\} \rangle | a_s \notin A\) with \(p\)
@@
 The concept of healer is made to target rogue flaws that caused total
-failure. A healer is a resolver that is built around the saviour of the
-flaw to provide for it . The general formula of a healer is the
-following : \[a_s \xrightarrow{p} a_n\] with \(a_s\) being the saviour
-of the flaw.
+failure. A healer is a resolver that is built around the savior of the
+flaw in order to provide the missing fluents to it. The general formula
+of a healer is the following : \[a_s \xrightarrow{p} a_n\] with \(a_s\)
+being the savior of the flaw.
 
 For threats we need an additional healer specified as an ordering
-constraint from the threatening action to the saviour \(a_t \to a_s\) to
-ensure that the saviour acts after the threat and therefore provides the
+constraint from the threatening action to the savior \(a_t \to a_s\) to
+ensure that the savior acts after the threat and therefore provides the
 proper fluent for the needer.
@@
 health of a partial plan. It is the sum of the number of flaws and the
-number of saviours in the plan.
+number of saviors in the plan.
 
@@
 
-Therefore we add an order relation for \(F\) noted
+Therefore, we add an order relation for \(F\) noted
 \[\prec : p \prec q \iff v(p) < v(q) | \{p, q\} \subset F\]
 
-Once the POP algorithm fails completely the soft failing algorithm can
+Once the POP algorithm fails completely, the soft failing algorithm can
 be invoked to heal the plan. It chooses the best plan
@@
 
-\section{SODA POP and its properties}\label{soda-pop-and-its-properties}
-
-After defining the way our algorithms work we will focus on the
+\hypertarget{soda}{\section{SODA POP and its properties}\label{soda}}
+
+After defining the way our algorithms work, we will focus on the
 properties that can be achieved by combining them together.
 
-\begin{algorithm}\caption{Combining all algorithms into SODA POP}\label{soda}\begin{algorithmic}
+\begin{algorithm}\caption{Combining all algorithms into SODA POP}\label{soda}\begin{algorithmic}[1]
 
 \Function{soda}{Problem $P$} \State \(P.p \gets\)
-\Call{properPlan}{$P.G$, $P.A$} \State \Call{clean}{$P$} \State bool
-\(valid \gets false\) \While{$\lnot valid$} \State \(valid \gets\)
-\Call{pop}{$P$} \(= Success\) \If{$valid$} \State \Call{clean}{$P$}
+\Call{properPlan}{$P.G$, $P.A$} \Comment Offline execution then this
+will be replaced by the previous online plan adjusted with the
+environment. \State \Call{clean}{$P$} \State bool \(valid \gets false\)
+\While{$\lnot valid$} \State \(valid \gets\) \Call{pop}{$P$}
+\(= Success\) \If{$valid$} \State \Call{clean}{$P$}
 \State \Return \(Success\) \EndIf
@@
 
-As to our knowledge no proof of the convergence of POP has been done we
+As to our knowledge, no proof of the convergence of POP has been done we
 want to explicitly formulate one.
@@
 The classic planning problem is already proven to be decidable without
-functions in the fluents {[}3{]}. Therefore we can categorise the
-termination cases. In the case of a solvable problem, POP is proven to
-be complete. This ensures convergence in that case. Now for the more
-complex case of unsolvable problems we need to refer to the way POP
-works. POP algorithm will seek to solve flaws. At any time there is a
-finite number of flaws since the plans have a finite number of steps. As
-POP resolves these flaws it will either continue until resolution or
-until failure. The problem is that POP can encounter loops in the
-dependancies of actions or in threats resolution. These loops can't
-occur in POP algorithm since a cycle in the ordering constraints
-instantly causes a failure as the plan isn't consistent anymore. This
-prooves that POP always converges.
-
-\subsection{Hyper soundness}\label{hypersoundeness}
+functions in the fluents {[}3{]}. Therefore, we can categorize the
+termination cases.
+
+\begin{proof}[Convergence of POP over solvable problemes]
+
+In the case of a solvable problem, POP is proven to be complete. This
+ensures that it will find a solution for the problem and therefore
+terminate.
+
+\end{proof}
+
+Now for the more complex case of unsolvable problems we need to refer to
+the way POP works.
+
+\begin{proof}[Convergence of POP over unsolvable problemes]
+
+POP algorithm will seek to solve flaws. Be \(flaws(p)\) the set of flaws
+of a given partial plan.
+
+The number of flaws is the number of subgoals plus the number of threats
+\[flaws(p) = subgoals(p) \cup threats(p)\]
+
+We consider the number of actions \(\#A\) as being finite. Therefore,
+the number of steps in the plan is at worse \(\#A_p = \#A\). We also
+assume that actions has a finite number of preconditions and effects
+(since we don't use functions over fluents). This leads to :
+\[\#subgoals(p) < \sum_{a \in A_p} \#pre(a) < \infty\]
+\[\#threats(p) < \#L \le \sum_{a \in A_p} \#pre(a) < \infty\]
+
+This means the number of all possible flaws is finite. As POP resolves
+these flaws it will decrease their numbers and iterate over resolvers.
+The number of resolver is \(\#subgoals(p) * \#A + \#threats(p) * 2\) and
+is also finite. This means that the iteration will in the worst case be
+of the number of resolvers before failing and this proves that the
+algorithm terminates.
+
+\end{proof}
+
+\subsection{Hypersoundness}\label{hypersoundeness}
 
 Now that we proved that regular POP converges we can introduce the next
-property : hyper soundness. An algorithm is said to be hyper sound when
-it gives a valid solution for all problems including unsolvable ones. We
-note that this property isn't compatible with consistency regarding the
-original problem but still does regarding the derived problem that
-includes all fake actions in \(A\).
-
-The hyper soundness of our combined algorithm is proven using the
-convergence of POP and the way the Soft solving behaves. As a POP fails
-it will issue flawed partial plans. As we fix the flaws artificially we
-make sure that this failure won't happen again in the next iteration of
-POP on the fixed plan. As the number of flaws is finite and POP
-converges, the whole algorithm will converge with all flaws solved
-therefore issuing a valid plan.
+property : hyper soundness.
+
+\begin{definition}[Hypersoundness]
+
+An algorithm is said to be hypersound when it gives a valid solution for
+all problems regardless of their resolvability.
+
+\end{definition}
+
+We note that this property isn't compatible with consistency regarding
+the original problem and then doesn't fit the classical idea of
+soundness that implicitly states that the validity of a solution is
+relative to the problem. In the case of hypersoundness the problem is
+valid and a solution to a problem \(P' = \langle A', I, G, p\rangle\).
+We note the new set \(A' = A \cup S\) with \(S\) being the set of
+saviors for all flaws that made the POP algorithm fails during the
+execution of SODA.
+
+The hypersoundness of our combined algorithm is proven using the
+convergence of POP and the way the Soft solving behaves.
+
+\begin{proof}[Hypersoundness of SODA POP]
+
+The proper plan and defect fixing algorithms are obviously convergent.
+The proper plan algorithm can't iterate more than the number of actions
+(since duplicates are forbidden) and the defect resolution will fix the
+finite numbers of defects present in the finite partial plan issued by
+the proper plan algorithm.
+
+POP is sound and converges. Therefore, if SODA converges it will return
+a valid solution for \(P'\). In the same way we proved for POP, the new
+healing process converges because it reduces the number of flaws in the
+partial plan and since this number is finite, the algorithm converges.
+
+\end{proof}
 
@@
 
+SODA POP algorithms can be used in dynamic online environments to allow
+a robust way to replan an existing obsolete plan. The first thing to
+execute prior to the runtime is the generation of the proper plans of
+all the goals that will be considered.
+
+For the first execution of the online planning the initial state is
+added to the problem and the defect detection is applied with the rest
+of the SODA POP algorithms. This will give the first plan.
+
+On change of environment the previous plan is modified accordingly and
+then fed to the defect detection and SODA algorithm again. This must be
+done each time the plan is modified in order to actualize the plan. The
+new plan will have all defects fixed. For example a savior action can be
+removed if the initial step or a new action becomes competing with it
+and actions with liar link to a removed fluent in the goal will become
+probably an orphan.
+
+In practice this will generate little to no iteration of the algorithm.
+
 \section{Experimental results}\label{experimental-results}
+
+In order to test the validity of these algorithms we implemented a
+prototype in Java. This prototype is exactly derived from the
+definitions and pseudo code presented in this paper. We used basic
+actions with integer fluents to focus on the way the algorithm behaves.
+
+For the simulation runs we used a computer with an Intel® Core™
+i7-4720HQ CPU clocking at 2.60GHz for 8 cores and 8GB of memory. The
+speed was measured in nano seconds before and after the call to the
+solve function. The process has a warming up phase that compute random
+plans for a few seconds before starting the benchmarks. The computer was
+left idle during the test to remove any related noise to the
+measurements.
+
+\subsection{Quality of classical POP}\label{quality-of-classical-pop}
+
+The first metric we decided to measure was the performance of our
+reference POP algorithm. We measured the solving time for valid problems
+and the quality of the resulting plans. In figure \ref{fig:quality} we
+can see a plot of these measures.
+
+\begin{figure}[htbp]
+\centering
+\includegraphics{graphics/quality.pdf}
+\caption{Action and link quality and solving time of POP over \(10 000\)
+valid problems for each difficulty\label{fig:quality}}
+\end{figure}
+
+We tested the algorithm with randomly generated valid problems. We
+generated those by randomly creating plans based on a difficulty setting
+that was the upper bound for the number of actions and half the possible
+number of fluents. This difficulty setting also made the initial and
+goal step larger accordingly. The actions were cleaned of any toxicity
+and was built using a forward chaining algorithm. We added also random
+unrelated actions. Each problem was verified by POP before being
+generated to ensure resolvability.
+
+As we clearly see in the figure \ref{fig:quality}, POP linearly increase
+its solving time depending on the problem difficulty. That obviously
+follows the fact that POP has more flaws to fix and therefore more
+iterations.
+
+As we can observe, POP has a rather high link quality with almost no
+problems issued with causal link regardless of the difficulty of the
+problem. This can be linked to either the way we generated our valid
+plans or to a real tendency of POP to not create that kind of defects on
+its own.
+
+The action quality on the other hand drops significantly as the
+difficulty gets higher. This is linked to the number of competing and
+useless actions that can make the plan simpler but are kept by the flaw
+selection mechanism of POP.
+
+\subsection{Performance of SODA POP}\label{performance-of-soda-pop}
+
+As SODA POP and regular POP doesn't have the same range of capabilities
+we can't compare them hand to hand. Indeed, our algorithm will always
+output plans with 100\% quality since the defect detection system aims
+to remove them all and since our algorithms is hypersound it will give
+valid plans for unsolvable problems by derivation. In these case POP
+won't be able to return a result and will terminate much quicker as the
+plan is found unsolvable.
+
+Therefore, we measured the performances of our set of algorithms on
+completely random problems. Each time the algorithm outputted a solution
+with the lowest possible violation despite the complete invalidity of
+the input. In figure \ref{fig:performance} we can see the way SODA POP
+scales up on larger problems.
+
+\begin{figure}[htbp]
+\centering
+\includegraphics{graphics/performance.pdf}
+\caption{Average solving time of SODA POP over \(10 000\) random
+problems for each difficulty\label{fig:performance}}
+\end{figure}
+
+The performances display logarithmic solving time. This is explained by
+the fact that POP has to be called recursively on the healed problems.
+The defect detection participates too in the increase of solving time
+especially the competing action detection that needs to iterate over all
+actions and edges and calculate usefulness for two actions each time.
 
@@
 \addcontentsline{toc}{section}{Conclusion}
+
+We defined our SODA POP algorithm and demonstrated its properties. The
+set of algorithms has extended capabilities of plan repairing and soft
+solving as shown in examples and simulations. While slower than POP, the
+resilience of SODA POP can be used in various applications. We aim to
+use it on the particular case of online plan recognition and decision
+making as the capabilities to derive plans and repair them will prove
+useful when comparing potential goals with observed plans.
+
+The algorithm can be improved with a better defect detection algorithm
+that can rank them and start fixing the most offensive defects before
+targeting others. Also, if the competing action detection can be
+improved, it can be used as heuristic for resolver selection to improve
+the performances.
+
+Another way the present work can be improved is by extending it to the
+use of more expressive fluents and port all notions to variable choices.
+One possible goal would be to combine this work with ontologies or an
+argumentation language in order to significantly boost expressiveness.
+
+We hope that this work will be useful and that it will be extended and
+used in various applications in the future and that is why we plan to
+release the software with an open source license soon.
 
@@
 
+\hypertarget{ref-ramirezux5fplanux5f2009}{}
+{[}5{]} M. Ramırez and H. Geffner, ``Plan recognition as planning,'' in
+\emph{Proceedings of the 21st international joint conference on
+Artifical intelligence. Morgan Kaufmann Publishers Inc}, 2009, pp.
+1778--1783.
+
 \hypertarget{ref-erolux5fumcp:ux5f1994}{}
-{[}5{]} K. Erol, J. A. Hendler, and D. S. Nau, ``UMCP: A Sound and
+{[}6{]} K. Erol, J. A. Hendler, and D. S. Nau, ``UMCP: A Sound and
 Complete Procedure for Hierarchical Task-network Planning.'' in
@@
 \hypertarget{ref-penberthyux5fucpop:ux5f1992}{}
-{[}6{]} J. S. Penberthy, D. S. Weld, and others, ``UCPOP: A Sound,
+{[}7{]} J. S. Penberthy, D. S. Weld, and others, ``UCPOP: A Sound,
 Complete, Partial Order Planner for ADL.'' \emph{Kr}, vol. 92, pp.
@@
 \hypertarget{ref-bechonux5fhipop:ux5f2014}{}
-{[}7{]} P. Bechon, M. Barbier, G. Infantes, C. Lesire, and V. Vidal,
+{[}8{]} P. Bechon, M. Barbier, G. Infantes, C. Lesire, and V. Vidal,
 ``HiPOP: Hierarchical Partial-Order Planning,'' in \emph{STAIRS 2014:
@@
 \hypertarget{ref-garciaux5fdefeasibleux5f2008}{}
-{[}8{]} D. R. García, A. J. García, and G. R. Simari, ``Defeasible
+{[}9{]} D. R. García, A. J. García, and G. R. Simari, ``Defeasible
 reasoning and partial order planning,'' in \emph{Foundations of
@@
 \hypertarget{ref-colesux5fforward-chainingux5f2010}{}
-{[}9{]} A. J. Coles, A. Coles, M. Fox, and D. Long, ``Forward-Chaining
+{[}10{]} A. J. Coles, A. Coles, M. Fox, and D. Long, ``Forward-Chaining
 Partial-Order Planning.'' in \emph{ICAPS}, 2010, pp. 42--49.

### 2015-11-22 article/article.tex
fixing comments and reducting the size

@@
 details all steps and explicits the ones that are not possible, can help
-decide of the line of action to take.
+decide of the plan of action to take.
 
@@
 
+\end{definition}
+
 An action \(a\) can be functionally applied to a state \(s\) as follows
@@
 on application (by removing complementary fluents if needed)
-
-\end{definition}
 
@@
 
-A partial plan is valid if and only if it is consistent and if all the
-flat plan that can be generated are valid.
+A partial plan is valid if and only if it is consistent and if all flat
+plans that can be generated are valid.
 
@@
 Partial Order Planning (POP) is a popular implementation of the general
-PSP algorithm. It is proven to be sound and complete {[}6{]}. The
-completeness of the algorithm guarantees that if the problem has a
-solution it will be found by the algorithm. The soundness assures that
-any answer from the algorithm is valid. POP refines a partial plan by
-trying to fix its flaws.
+PSP algorithm. It refines a partial plan by trying to fix its flaws and
+is proven to be sound and complete {[}6{]}.
 
@@
 
-\begin{algorithm}\caption{Classical Partial Order Planning algorithm}\label{pop}\begin{algorithmic}[1]
+\begin{algorithm}\caption{Classical Partial Order Planning}\label{pop}\begin{algorithmic}[1]
 
@@
 
-From that point the base algorithm is very similar for any
-implementation of POP : using an agenda of flaws that is efficiently
-updated after each refinement of the plan. A flaw is selected for
-resolution and we use a non deterministic choice operator to pick a
-resolver for the flaw. The resolver is inserted in the plan and we
-recursively call the algorithm on the new plan. On failure we return to
-the last non deterministic choice to pick another resolver. The
-algorithm ends when the agenda is empty or when there is no more
-resolver to pick for a given flaw.
+Algorithm 1 presents the base algorithm for a planer in the plan space.
+POP implementation uses an agenda of flaws that is efficiently updated
+after each refinement of the plan. A flaw is selected for resolution and
+we use a non deterministic choice operator to pick a resolver for the
+flaw. The resolver is inserted in the plan and we recursively call the
+algorithm on the new plan. On failure we return to the last non
+deterministic choice to pick another resolver. The algorithm ends when
+the agenda is empty or when there is no more resolver to pick for a
+given flaw.
 
@@
 planning by removing big chunks of the partial plan by identifying
-incorrect trees in the plan. This along with heuristic choice of
-unrefinemment strategies. This causes a heavy replanning of the problem
-even if only one action needed removal. This also lead to an exponential
+incorrect trees in the plan. This along with a heuristic of choice of
+unrefinemment strategies causes a heavy replanning of the problem even
+if only one action needs removal. This also lead to an exponential
 number of plan to consider. This is a big problem when trying to adapt a
@@
 
-\begin{figure}[htbp]
-\centering
-\includegraphics{graphics/problem.pdf}
-\caption{A simple problem that will be used throughout this
-paper\label{fig:problem}}
-\end{figure}
-
 Before continuing, we present a simple example of classical POP
-execution with the problem represented in figure \ref{fig:problem}. We
-did not represent empty preconditions or effects to improve readability.
-Here we have an initial state
+execution with the following problem. We have an initial state
 \(I = \langle \emptyset , \{ 1, 2 \} \rangle\) and a goal
@@
 steps. We also introduce actions that are not steps yet but that are
-provided by \(A\). The actions \(a\), \(b\) and \(c\) are normal actions
-that are useful to achieve the goal. The action \(t\) is meant to be
-threatening to the plan's integrity and will generate threats. We
-introduce \(u\) and \(v\) as a toxic action, \(w\) as a dead-end action
-and \(x\) as a contradictory action. These notions will be defined
-\protect\hyperlink{defects}{later}.
+provided by \(A\). The actions \(a \langle \{1\}, \{3,5\} \rangle\),
+\(b \langle \{2\}, \{4\} \rangle\) and
+\(c \langle \{5\}, \{6\} \rangle\) are normal actions that are useful to
+achieve the goal. The actions \(n \langle \{-8, 7\}, \{-7, 8\} \rangle\)
+and \(l \langle \{-7, 8\}, \{-8, 7\} \rangle\) are looping actions that
+are meant to cause cycles. The action
+\(t \langle \{4\}, \{-5\} \rangle\) is meant to be threatening to the
+plan's integrity and will generate threats. We introduce
+\(u \langle \{4\}, \emptyset \rangle\) and
+\(v \langle \{4\}, \{4\} \rangle\) as toxic actions,
+\(w \langle \{9\}, \{3\} \rangle\) as a dead-end action and
+\(x \langle \{7\}, \{-2,2\} \rangle\) as a contradictory action. These
+notions will be defined \protect\hyperlink{defects}{later}.
 
@@
 more speed oriented and will do little if a toxic action seems to fit
-better than a more coherent but complex one.
+better than a more coherent but complex one .
 
@@
 algorithm will be presented in \protect\hyperlink{soda}{the next
-section} as a combination of all auxiliary algorithms and regular POP.
+section} as a combination of all auxiliary algorithms and classical POP.
 
@@
 
-\begin{algorithm}\caption{Proper plan generation algorithm for a given goal $g$}\label{properplan}\begin{algorithmic}[1]
+\begin{algorithm}\caption{Proper plan generation for a given goal $g$}\label{properplan}\begin{algorithmic}[1]
 
@@
 
-As in online planning goals can be known in advance, we add a new
+As in online planning goals can be known in advance, we propose a new
 mechanism that generates proper plans for goals. We take advantage of
-the fact that this step can be done offline to improve performance for
-online planning. This offline execution prevents us to access the
+the fact that this step can be done offline to improve the performance
+of online planning. This offline execution prevents us to access the
 details of the initial state of the world as it will be defined at
@@
 
-On our example it illustrates really well the need for resilience. The
-algorithm simply recursively chose the actions and end up with the
-partial plan represented in figure \ref{fig:proper}. The partial plan
-doesn't have an initial state (because of its offline nature). This plan
-also shows several cycles and obvious problems. Moreover, the plan has
-all the steps of the correct final plan and therefore remove the subgoal
-search in POP if it uses this plan has input (after it has been cleaned
-obviously).
-
-This auxiliary algorithm is therefore used as a caching mechanism for
-online planning. The algorithm starts to populate the proper plan with a
-quick and incomplete backward chaining.
+We define the concept of \emph{participating action}. An action
+\(a \in A\) participates in a goal \(G\) if and only if \(a\) has an
+effect \(f\) that is needed to accomplish \(G\) or to accomplish another
+participating action's preconditions. A proper plan is a partial plan
+that contains all participating actions as steps and causal links that
+bind them with the step they are participating in. Proper plan
+generation, detailed in Algorithm 2, recursively chooses all
+participating actions. It simply populate the proper plan with a quick
+and incomplete backward chaining.
+
+The partial plan doesn't have an initial state (because of its offline
+nature). This auxiliary algorithm is therefore used as a caching
+mechanism for online planning. The algorithm starts to populate the
+proper plan with a quick and incomplete backward chaining.
+
+Once applied on the example of figure \textbf{???}, proper plan
+generation returns the partial plan presented in figure
+\ref{fig:proper}. This partial plan doesn't have initial state because
+of its offline nature. It also shows several cycles and obvious
+problems. However, it has all the steps of the correct final plan.
+
+This algorithm helps the POP algorithm by prefetching all the actions
+subgoals might need but also need to be cleaned first to be helpful.
 
@@
 
-\begin{algorithm}\caption{Defect resolution algorithm}\label{defectresolution}\begin{algorithmic}[1]
+\begin{algorithm}\caption{Defect resolution}\label{defectresolution}\begin{algorithmic}[1]
 
@@
 present in it interfering in the resolution and sometimes making it
-impossible to solve. We emphasize that these defects are not regular POP
-flaws but new problems that classical POP can't solve. The aim of this
-auxiliary algorithm is to clean the plans from such defects in order to
-improve computational time, resilience and plan quality. It should be
-noted that in some cases cleaning plans will increase the number of
-flaws in the plan but will always improve the overall quality of it.
+impossible to solve. We emphasize that these \emph{defects are not
+regular POP flaws} but new problems that classical POP can't solve. The
+aim of this auxiliary algorithm is to clean the plans from such defects
+in order to improve computational time, resilience and plan quality. It
+should be noted that in some cases cleaning plans will increase the
+number of flaws in the plan but will always improve the overall quality
+of it.
 
@@
 From there it is obvious that plan quality will improve over POP since
-the present algorithm is guaranteed to remove all defects in a plan.
+our present algorithm is guaranteed to remove all defects in a plan.
 
@@
 output or by unchecked corrupted data. These defects will most of the
-time simply break regular POP algorithms (from existing cycles) or at
-least make the performances decrease significantly (from toxic actions).
+time simply break regular POP algorithms or at least make the
+performances decrease significantly Illegal defects and solutions to fix
+them are presented in the following section.
 
@@
 cycles. Upon cycle detection the algorithm can remove arbitrarily a link
-in the cycle to break it. The most effective solution is to remove the
-link that is the farthest from the goal traveling backward as it would
-be that link that would have been last added in the regular POP
-algorithm. But finding this is extremely time consuming and most of the
-time the cycles are of one or two actions so we choose to keep that
-algorithm simpler and faster.
+in the cycle to break it.
+
+In a plan some actions can be illegal for POP. Those are the actions
+that are inconsistent.
 
@@
 
-In a plan some actions can be illegal for POP. Those are the actions
-that are contradictory. An action \(a\) is contradictory if and only if
+An action \(a\) is contradictory if and only if
 \[\exists f \{f, \lnot f \} \in eff(a) \lor \{f, \lnot f \} \in pre(a)\]
@@
 of the action in the rest of the plan. If none of those are used, we
-choose to remove both. In our example in figure \ref{fig:problem} the
-action \(x\) is one of these inconsistent actions with fluent \(2\) and
-\(-2\) in its effects.
+choose to remove both. In our example in figure \textbf{???} the action
+\(x\) is one of these inconsistent actions with fluent \(2\) and \(-2\)
+in its effects.
 
@@
 
-These actions are those that have effects that are already in their
+Toxic actions are those that have effects that are already in their
 preconditions or empty effects. This can damage a plan as well as make
@@
 
-This is fixed by removing the toxic fluents
+They can damage a plan as well as make the execution of POP algorithm
+much longer than necessary. This is fixed by removing the toxic fluents
 (\(pre(a) \nsubseteq eff(a)\)) following \(eff(a) = eff(a)-pre(a)\). If
-the effects gets empty the action is removed altogether from plan and
-\(A\). For example in figure \ref{fig:problem} the actions \(u\) and
-\(v\) are a toxic action as the fluent \(4\) is in the effects and
-preconditions of \(v\). In this case these actions will be removed by
-the algorithm as it doesn't have any other effects.
+the effects becomes empty, the action is removed altogether from plan
+and \(A\). For example in figure \textbf{???} the actions \(u\) and
+\(v\) are toxic as the fluent \(4\) is in the effects and preconditions
+of \(v\), and \(u\) has empty effects. In this case these actions will
+be removed by the algorithm as they don't have any other effects.
+
+The defects can be related to incorrect links. The first of which are
+liar links.
 
@@
 
-The defects can be related to incorrect links. The first of which are
-liar links : a link that doesn't reflect the preconditions or effect of
-its source and target. We can note
+A liar link is a link that doesn't reflect the preconditions or effect
+of its source and target. We can note:
 \[a_i \xrightarrow{f} a_j | f \notin eff(a_i) \cap pre(a_j)\]
@@
 
-This kind of defects is not as toxic as the illegal ones: they won't
-make the plan unsolvable but they can still cause performance drops in
-POP execution. These can appear more often in regular POP results as
-they are not targeted by standard implementations.
+This kind of defects is not as problematic as the illegal ones: they
+won't make the plan unsolvable but they can still cause performance and
+quallity drops. These defects can happen in POP generated plans to some
+extends. Interference defects and solutions to fix them are presented in
+the following.
 
@@
 
-This defect can happen in POP generated plans to some extends. A
-redundant link have a transitive equivalent of longer length. It means
+A redundant link have a transitive equivalent of longer length. It means
 that a link \(a_i \to a_j\) is redundant if and only if it exists
@@
 the ones that were generated for threat removal purpose to simplify the
-plan. For example in the figure \ref{fig:pop} we can see that the
-ordering constraint from \(a\) to \(t\) is redundant with the path
+plan. For example in figure \ref{fig:pop} we can see that the ordering
+constraint from \(a\) to \(t\) is redundant with the path
 \(a \xrightarrow{5} c \to t\) in that it isn't needed to resolve the
-threat. Therefore, the algorithm would remove it. This reduce the number
-of edges in the plan and therefore simplify it.
+threat. Therefore, the algorithm would remove it. This reduces the
+number of edges in the plan and therefore simplifies it.
+
+Causal links can be found to compete with one another.
 
@@
 
-Causal links can be found to compete with one another. A competing link
-\(a_i \xrightarrow{f} a_k\) competes with another link
+A competing link \(a_i \xrightarrow{f} a_k\) competes with another link
 \(a_j \xrightarrow{f} a_k\) if it provides the same fluent to the same
@@
 
-This cannot happen in classical POP algorithm so it is not handled by
-it. The multiple links providing the same fluent to the same action is
-making the plan more complex like redundant links but also can hide
-useless actions. This is why they must be removed in a way that reveals
-them and reduce the need for extra unnecessary actions in the plan that
-would cause more flaws for POP to handle.
+The main difference with redundant links is that competing links are not
+related to threat resolution generated ordering constraint but confronts
+two causal links that can provide the same fluent. Another difference is
+that it cannot happen in classical POP algorithm. This kind of defect is
+making the plan more complex and can also hide useless actions which
+would potentially cause more flaws to handle than necessary.
 
@@
 
-In order to prune the least useful actions, we need to remove the least
-interesting link. In order to elect the best one, we compare their
-respective providing action.
+In order to remove the least interesting link in competing causal links,
+we need to compare their respective providing action to chose the most
+useful ones.
 
@@
 (outgoing causal links) divided by the number of needing links (incoming
-causal links). If there are no needing links, or the action is either an
-initial step or a goal the usefulness is \(+\infty\). The usefulness of
-savior action is \(0\).
+causal links). If there are no needing links, the usefulness is simmply
+the number of participating links.
+
+In the special cases if the action is either an initial step or a goal,
+the usefulness is \(+\infty\). The usefulness of savior action is \(0\).
 
@@
 We choose the link with the source action having the highest usefulness.
-This makes replacing unnecessary savior actions and allows to therefore
-reduce the usefulness of the least action in the hope it will become
-orphan and pruned from the plan.
+This replaces unnecessary savior actions and allows reducing the
+usefulness of the least action in order to eventually make it an orphan
+and prune it from the plan.
 
@@
 
+On the left example of figure \ref{fig:competing}, the action \(a_j\)
+participates much more than the action \(a_i\) and therefore the link to
+be removed would be \(a_i \xrightarrow{f} a_k\). On the right example
+the actions don't have different outgoing links but the action \(a_j\)
+is here much needier than its competitor. Therefore, the link to be
+removed is the link \(a_j \xrightarrow{f} a_k\).
+
+Actions can sometimes have no use in a plan as they don't contribute to
+it.
+
 \begin{definition}[Orphan actions]
 
-Actions can sometimes have no use in a plan as they don't contribute to
-it. It is the case of orphans actions (actions without any links) and
-action with no outgoing path to the goal (meaning that it doesn't
-participate in the plan). That also concerns action that would become
-orphan if another orphan action is removed.
-
-\end{definition}
-
-In order to fix this we derive the idea of the backward removal tree of
-{[}4{]}. The idea is to remove an action if all its outgoing causal
-links are leading to useless actions. We iterate over all actions until
-no new useless action is discovered. All useless actions are then
-removed from the plan.
-
-\begin{algorithm}\caption{Orphan actions finding algorithm}\label{orphanaction_find}\begin{algorithmic}[1]
+Orphans actions are actions without any links or action with no outgoing
+path to the goal (meaning that it doesn't participate in the plan). That
+also concerns action that would become orphan if another orphan action
+is removed.
+
+\end{definition}
+
+\begin{algorithm}\caption{Orphan actions finding}\label{orphanaction_find}\begin{algorithmic}[1]
 
@@
 
+In order to fix this we derive the idea of the backward removal tree of
+{[}4{]}. The algorithm, detailed in Algorithm 4, removes an action if
+all its outgoing causal links are leading to useless actions. It
+iterates over all actions until no new useless action is discovered. All
+useless actions are then removed from the plan.
+
 \begin{definition}[Competing actions]
@@
 
-\begin{algorithm}\caption{Soft resolution healing algorithm}\label{softresolution}\begin{algorithmic}[1]
+\begin{algorithm}\caption{Soft resolution healing}\label{softresolution}\begin{algorithmic}[1]
 
@@
 
+The concept of healer is made to target rogue flaws that caused total
+failure.
+
 \begin{definition}[Healers]
 
-The concept of healer is made to target rogue flaws that caused total
-failure. A healer is a resolver that is built around the savior of the
-flaw in order to provide the missing fluents to it. The general formula
-of a healer is the following : \[a_s \xrightarrow{p} a_n\] with \(a_s\)
-being the savior of the flaw.
+A healer is a resolver that is built around the savior of the flaw in
+order to provide the missing fluents to it. The general formula of a
+healer is the following : \[a_s \xrightarrow{p} a_n\] with \(a_s\) being
+the savior of the flaw.
+
+\end{definition}
 
@@
 proper fluent for the needer.
-
-\end{definition}
 
@@
 \(b | \forall p \in F, b \prec p\) to heal it. If two plans have the
-same violation degree, the algorithm chooses one arbitrarily .
+same violation degree, the algorithm chooses the first one to have
+happened.
 
@@
 
-After defining the way our algorithms work, we will focus on the
-properties that can be achieved by combining them together.
-
-\begin{algorithm}\caption{Combining all algorithms into SODA POP}\label{soda}\begin{algorithmic}[1]
+The combination of classical POP and all the auxiliary algorithms
+presented previously gives SODA POP algorithm detailed in Algorithm 6.
+In this section we will focus on the properties of SODA POP.
+
+\begin{algorithm}\caption{SODA POP}\label{soda}\begin{algorithmic}[1]
 
@@
 
-\begin{proof}[Convergence of POP over solvable problemes]
+\begin{proof}
 
@@
 
-\end{proof}
-
-Now for the more complex case of unsolvable problems we need to refer to
-the way POP works.
-
-\begin{proof}[Convergence of POP over unsolvable problemes]
-
-POP algorithm will seek to solve flaws. Be \(flaws(p)\) the set of flaws
-of a given partial plan.
-
-The number of flaws is the number of subgoals plus the number of threats
-\[flaws(p) = subgoals(p) \cup threats(p)\]
+Be \(flaws(p)\) the set of flaws of a given partial plan. The number of
+flaws is the number of subgoals plus the number of threats
+\(flaws(p) = subgoals(p) \cup threats(p)\)
 
@@
 assume that actions has a finite number of preconditions and effects
-(since we don't use functions over fluents). This leads to :
-\[\#subgoals(p) < \sum_{a \in A_p} \#pre(a) < \infty\]
-\[\#threats(p) < \#L \le \sum_{a \in A_p} \#pre(a) < \infty\]
+(since we don't use functions over fluents).
+
+This leads to \(\#subgoals(p) < \sum_{a \in A_p} \#pre(a) < \infty\) and
+\(\#threats(p) < \#L \le \sum_{a \in A_p} \#pre(a) < \infty\)
 
@@
 of the number of resolvers before failing and this proves that the
-algorithm terminates.
+algorithm terminates. \qedhere
 
@@
 The proper plan and defect fixing algorithms are obviously convergent.
-The proper plan algorithm can't iterate more than the number of actions
+The proper plan algorithm cannot iterate more than the number of actions
 (since duplicates are forbidden) and the defect resolution will fix the
@@
 
-POP is sound and converges. Therefore, if SODA converges it will return
-a valid solution for \(P'\). In the same way we proved for POP, the new
-healing process converges because it reduces the number of flaws in the
-partial plan and since this number is finite, the algorithm converges.
+POP is sound and converges. Therefore, if SODA POP converges it will
+return a valid solution for \(P'\). In the same way we proved for POP,
+the new healing process converges because it reduces the number of flaws
+in the partial plan and since this number is finite, the algorithm
+converges.\qedhere
 
@@
 
-SODA POP algorithms can be used in dynamic online environments to allow
-a robust way to replan an existing obsolete plan. The first thing to
-execute prior to the runtime is the generation of the proper plans of
+SODA POP algorithm can be used in dynamic online environments to allow a
+robust way to replan an existing obsolete plan. The first thing to
+execute prior to the runtime is the generation of the proper plans for
 all the goals that will be considered.
@@
 added to the problem and the defect detection is applied with the rest
-of the SODA POP algorithms. This will give the first plan.
-
-On change of environment the previous plan is modified accordingly and
-then fed to the defect detection and SODA algorithm again. This must be
-done each time the plan is modified in order to actualize the plan. The
-new plan will have all defects fixed. For example a savior action can be
-removed if the initial step or a new action becomes competing with it
-and actions with liar link to a removed fluent in the goal will become
-probably an orphan.
+of the SODA POP algorithm. This will give the first plan.
+
+For every change of the environment the previous plan is modified
+accordingly and then fed to the defect detection and SODA algorithm
+again. This must be done each time the plan is modified in order to
+actualize the plan. The new plan will have all defects fixed. For
+example a savior action can be removed if the initial step or a new
+action becomes competing with it and actions with liar link to a removed
+fluent in the goal will become probably an orphan.
 

### 2016-01-03 article/article.tex
New Algorithm ! Ongoing test and performance improvement

@@
 \hypersetup{unicode=true,
-            pdftitle={SODA POP : Robust online Partial Ordering Planning for real life applications},
+            pdftitle={SODA POP: SOft solving and Defect Aware Partial Ordering Planning},
             pdfauthor={Paper ID\#232},
@@
 
-\title{SODA POP : Robust online Partial Ordering Planning for real life
-applications}
+\title{SODA POP: SOft solving and Defect Aware Partial Ordering Planning}
 \author{Paper ID\#232}
@@
 
+%\setlength{\belowcaptionskip}{-2pt}
+\setlength{\abovecaptionskip}{-12pt}
+
 %%%% For links URL
@@
 like Partial Ordering Planning (POP) that has the advantage to be much
-more flexible. This approach \emph{generates} plans that can be refined
-easily and can be used to achieve greater resilience, repairing
-capabilities and soft resolution that applications \emph{based on}
-online plan recognition or decision-making can benefit from. \emph{This
-paper presents} a set of algorithms, named Soft Ordering and Defect
-Aware Partial Ordering Planning (SODA POP), that aims at targeting these
-objectives and maintain a high plan quality. Our algorithms create
-proper offline plans for goals and use an effective defect fixing
-\emph{algorithm} to repair input plans even if these plans are
-corrupted. SODA POP can also use healer actions and links in order to
-always return a valid plan even in cases where the problem is impossible
-to solve using problem derivation. Some relevant properties of these
-algorithms are analyzed in this article and experimental results show
-interesting performances for online planning and repairing.
+more flexible. This approach generates plans that can be refined easily
+and can be used to achieve greater resilience, repairing capabilities
+and soft resolution that applications based on online plan recognition
+or decision-making can benefit from. This paper presents a set of
+algorithms, named solving and Defect Aware Partial Ordering Planning
+(SODA POP), that aims at targeting these objectives and maintain a high
+plan quality. Our algorithms create proper offline plans for goals and
+use an effective defect fixing algorithm to repair input plans even if
+these plans are corrupted. SODA POP can also use healer actions and
+links in order to always return a valid plan even in cases where the
+problem is impossible to solve using problem derivation. Some relevant
+properties of these algorithms are analyzed in this article and
+experimental results show interesting performances for online planning
+and repairing.
 \end{abstract}
@@
 
-For some time Partial Order Planning (POP) has been the most popular
+For some time, Partial Order Planning (POP) has been the most popular
 approach to planning resolution. This kind of algorithms are based on
-\emph{least commitment strategy} on plan step ordering that can allow
+\emph{least commitment strategy} on plan step ordering that allow
 actions to be flexibly interleaved during execution {[}1{]}. Thus, the
@@
 allowed for more versatility for a wide variety of uses. As of more
-recent years, new state space search models and heuristics {[}2{]} have
-been demonstrated to be more efficient than POP planners due to the
-simplicity and relevance of states representation opposed to partial
+recent years, new state space search approach and heuristics {[}2{]}
+have been demonstrated to be more efficient than POP planners due to the
+simplicity and relevance of state representations opposed to partial
 plans {[}3{]}. This have made the search of performance the main axis of
-research for planning in the community .
+research for planning.
 
@@
 Planning (PSP) is an obvious advantage for applications needing online
-planning: plans can be repaired on the fly as new informations and
-objectives enter the system. The idea of using POP for online planning
-and repairing plans instead of replanning everything is not new {[}4{]},
-but has never been paired with the resilience that some other cognitive
+planning: plans can be repaired on the fly as new information and goals
+are considered. The idea of using POP for online planning and repairing
+plans instead of replanning from scratch is not new {[}4{]}, but has
+never been paired with the resilience that some other cognitive
 applications may need, especially when dealing with sensors noise in
-input data.
-
-This resilience makes fixing errors easier than with an external
-algorithm as the plan logic allows for context driven decision on the
-way to repair the issues. For example if an action becomes unrelevant or
-incoherent, the flaw in the partial plan makes the issue explicit and
-therefore easier to fix. Softwares might sometimes provide plans that
-can contain errors and imperfections that will decrease significantly
-the efficiency of the computation and the quality of the output plan.
-
-Adding to that, these plans may become totally unsolvable. This problem
-is to our knowledge not treated in planning of all forms (state
-planning, PSP, and even constraint satisfaction planning) as usually the
-aim is to find a solution relative to the original plan (which makes
-sense). But as we proceed a mechanism of \emph{problem derivation} may
-be required. This will allow soft solving of any problem regardless of
-its resolvability.
+input data. This resilience makes fixing errors easier than with an
+external algorithm as the plan logic allows for context driven decision
+on the way to repair the issues. For example, if an action becomes
+unrelevant or incoherent, the flaw in the partial plan makes the issue
+explicit and therefore easier to fix. Applications might sometimes
+provide plans that can contain errors and imperfections that will
+decrease significantly the efficiency of the computation and the quality
+of the output plan. Additionnaly, these plans may become totally
+unsolvable. This problem is to our knowledge not treated in planning of
+all forms (state planning, PSP, and even constraint satisfaction
+planning) as usually the aim is to find a solution relative to the
+original plan (which makes sense). However, as we proceed a mechanism of
+\emph{problem derivation} may be required. This will allow soft solving
+of any problem regardless of its resolvability.
 
@@
 particularly important {[}5{]}. This method adds dummy actions that need
-to be satisfied by modifying the goal to ensure that the observed plan
-is selected by the planner. A system that is able to repair plan in real
-time will ease such an application. Another application is
-decision-making in dynamical environments. Indeed, having a plan that
-details all steps and explicits the ones that are not possible, can help
-decide of the plan of action to take.
-
-These problems call for new ways to improve the answer of a planner.
-These improvements must provide relevant plan information pointing out
-exactly what needs to be done in order to make a planning problem
-solvable, even in the case of obviously inconsistent input data. This
-paper aims to solve this while preserving the advantages of PSP
+to be satisfied by modifying the goal, to ensure that the observed plan
+is selected by the planner. A system that is able to repair plan will
+ease such an application. Another application is decision-making in
+dynamic environments. Indeed, having a plan that details all steps and
+explicits the ones that are not possible, can help decide on the plan of
+actions to take. These problems call for new ways to improve the answer
+of a planner. These improvements must provide relevant plan information
+pointing out exactly what needs to be done in order to make a planning
+problem solvable, even in the case of obviously inconsistent input data.
+This paper aims to solve this while preserving the advantages of PSP
 algorithms (flexibility, easy fixing of plans, soundness and
-completeness). Our Soft Ordering and Defect Aware Partial Ordering
-Planning (SODA POP) algorithm will target those issues.
-
-Our new set of auxiliary algorithms allows making POP algorithm more
-resilient, efficient and relevant. This is done by pre-emptively
-computing proper plans for goals, by solving new kinds of defects that
-input plans may exhibit, and by healing compromised plan by deriving the
-initial problem with forged actions to allow resolution.
-
-To explain this work we first introduce a few notions, notations and
-specificities of existing POP algorithms. Then we present and illustrate
-their limitations, categorizing the different defects arising from the
-resilience problem and explaining our auxiliary algorithms, their uses
-and properties. To finish we compare the performance, resilience and
-quality of POP and our solution.
+completeness). We propose a new set of auxiliary algorithms that
+combined forms our SOft solving and Defect Aware Partial Ordering
+Planning (SODA POP) algorithm that targets those issues and allows
+making POP algorithm more resilient, efficient and relevant. This is
+done by pre-emptively computing proper plans for goals, by solving new
+kinds of defects that input plans may exhibit, and by healing
+compromised plan by deriving the initial problem with forged actions to
+allow resolution. To explain this work we first introduce a few notions,
+notations and specificities of existing POP algorithms. Then we present
+and illustrate their limitations, categorizing the different defects
+arising from the resilience problem and explaining our auxiliary
+algorithms, their uses and properties. We compare the performance,
+resilience and quality of POP and our solution.
 
@@
 
-First we introduce some definitions and notations for mathematical
+First, we introduce some definitions and notations for mathematical
 representation to present our model.
@@
 action can be used only in a state that verifies its preconditions. We
-note \(s \models a \Leftrightarrow pre(a) \subset s\) the verification
+note \(s \models a \Leftrightarrow pre(a) \subseteq s\) the verification
 of an action \(a\) by a state \(s\).
@@
 
-An action \(a\) can be functionally applied to a state \(s\) as follows
-: \[a:= \substack{ \left\{ s \models a \middle| s \in S\right\} \to S\\
+An action \(a\) can be functionally applied to a state \(s\) as follows:
+\[a:= \substack{ \left\{ s \models a \middle| s \in S\right\} \to S\\
     a(s) \mapsto s + eff(a)}\] with \(S\) being the set of all states.
-This means that an action adds all its effect to the state of the world
-on application (by removing complementary fluents if needed)
-
-We distinguish between two specific kinds of actions : actions with no
+This means that an action adds all its effects to the state of the world
+on application (by removing complementary fluents if needed). We
+distinguish between two specific kinds of actions: actions with no
 preconditions are synonymous to a state and those with empty effect are
@@
 We define a partial plan satisfaction problem as a tuple noted
-\(P = \langle A, I, G, p \rangle\) with :
+\(P = \langle A, I, G, p \rangle\) with:
 
@@
 of the form \(a_i \xrightarrow{f} a_j\), such that
-\(\{ a_i, a_j \} \subset A_p \land f \in eff(a_i) \cap pre(a_j)\) or
+\(\{ a_i, a_j \} \subseteq A_p \land f \in eff(a_i) \cap pre(a_j)\) or
 said otherwise, this causal link means that the fluent \(f\) is provided
@@
 \(a_i\) that is prior to the action \(a_j\) following all the causal
-links and ordering constraints \(a_i \succ a_j\) .
+links and ordering constraints \(a_i \succ a_j\). We can consider it as
+a graph formed by step as vertices and causal links as edges.
 
@@
 \includegraphics{graphics/legend.pdf}
-\caption{Global legend for how partial plans are represented in this
-paper\label{fig:legend}}
+\caption{Global legend for partial plans\label{fig:legend}}
 \end{figure}
 
-In this figure the fluent \(5\) is a precondition of the action \(a\)
-and the fluent \(6\) an effect. The causal link is providing the fluent
-\(7\) (only as a representation example or it would be a liar link). The
-dotted line is an ordering constraint that would mean that \(a\) should
-be placed before \(a\) (for representation still or it would be a
-cycle). \(I\) and \(G\) are respectively the initial and goal step.
+In this figure the fluent \(6\) is a precondition of the action \(a\)
+and also an effect. The causal link is providing the fluent \(6\). The
+dotted line is an ordering constraint specifying which action should be
+placed before another. \(I\) and \(G\) are respectively the initial and
+goal step.
 
@@
 \(s \in pre(a_s)\) that isn't satisfied by any causal link. We can note
-a subgoal as :
-\[a_i \xrightarrow{s} a_s \notin L \mid \{ a_i, a_s \} \subset A_p \]
+a subgoal as:
+\[a_i \xrightarrow{s} a_s \notin L \mid \{ a_i, a_s \} \subseteq A_p \]
 
@@
 
-In other words, the action has a possible complementary effect that can
-be inserted between two actions needing this fluent while being
-consistent with the ordering constraint in \(L\).
-
-\subsubsection{Resolvers}\label{resolvers}
+In other words, the action has a complementary effect that can be
+inserted between two actions needing this fluent while being consistent
+with the ordering constraint in \(L\).
+
+\begin{definition}[Resolvers]
 
 Resolvers are a set of actions and causal links
-\(r = \langle A_r , L_r \rangle\) that fixes flaws. A resolver for a
-subgoal is an action \(a_r \in A\) that has \(s\) as an effect
-\(s \in eff(a_r)\) inserted along with a causal link noted
-\(a_r \xrightarrow{s} a_s\). The usual resolvers for a threat are either
-\(a_t \to a_i\) or \(a_j \to a_t\) which are called respectively
-promotion and demotion links. Another resolver is called a white knight
-that is an action \(a_k\) that reestablishes \(t\) after \(a_t\) along
-with an ordering constraint \(a_t \to a_k\) and a causal link
-\(a_k \xrightarrow{t} a_j\).
-
-\subsubsection{Solution}\label{solution}
-
-The solution of a PSP problem is a valid partial plan that respect the
+\(r = \langle A_r , L_r \rangle\) that fixes flaws.
+
+\begin{itemize}
+\tightlist
+\item
+  A resolver for a subgoal is an action \(a_r \in A\) that has \(s\) as
+  an effect \(s \in eff(a_r)\) inserted along with a causal link noted
+  \(a_r \xrightarrow{s} a_s\).
+\item
+  The usual resolvers for a threat are either \(a_t \to a_i\) or
+  \(a_j \to a_t\) which are called respectively promotion and demotion
+  links.
+\end{itemize}
+
+\end{definition}
+
+\begin{definition}[Solution]
+
+The solution of a PSP problem is a valid partial plan that respects the
 specification of said problem (only using actions in \(A\) and having
@@
 
+\end{definition}
+
 \begin{definition}[Consistency]
 
-A partial plan is consistent if it contains no ordering cycles. That
-means that the directed graph formed by step as vertices and causal
-links as edges isn't cyclical. This is important to guarantee the
-soundness of the algorithm.
+A partial plan is consistent if it contains no ordering cycles. The
+directed graph formed by step as vertices and causal links as edges
+isn't cyclical. This is important to guarantee the soundness.
 
@@
 plan is an ordered sequence of actions \(\pi = [ a_1, a_2 \ldots a_n]\)
-that acts like a pseudo action
-\(\pi = \langle pre_\pi, eff_\pi \rangle\) and can be applied to a state
-\(s\) using functional composition operation
+that acts like a action \(\pi = \langle pre_\pi, eff_\pi \rangle\) and
+can be applied to a state \(s\) using functional composition operation
 \(\pi := \bigcirc_{i=1}^n a_n\).
@@
 
-\subsection{Description}\label{description}
-
 \begin{algorithm}\caption{Classical Partial Order Planning}\label{pop}\begin{algorithmic}[1]
 
+\footnotesize
 \Function{pop}{Queue of Flaws $agenda$, Problem $P$}
@@
 \Comment{Stop all recursion} \EndIf
-    \State Flaw \(f\gets agenda.pop\)
-\Comment{First element of the queue} \State Resolvers \(R \gets\)
-\Call{resolvers}{$f$, $P$} \Comment{Ordered list of resolvers to try}
-\ForAll{$r \in R$} \Comment{Choice operator}
-\State \Call{apply}{$r$, $P.p$} \If{\Call{consistent}{$P.p$}}
+    \State Flaw \(f\gets agenda.popFromQueue\)
+\Comment{Stop all recursion} \Comment{First element of the queue}
+\State Resolvers \(R \gets\) \Call{resolvers}{$f$, $P$}
+\State \Comment{Ordered resolvers to try} \ForAll{$r \in R$}
+\Comment{Non deterministic choice operator}
+\State \Call{apply}{$r$, $P.p$} \Comment{Apply resolver to partial plan}
+\If{\Call{consistent}{$P.p$}} \Comment{$P.p$ is the partial plan}
 \State \Call{pop}{$agenda \cup$ \protect\Call{relatedFlaws}{$f$}, $P$}
-\Else 
-            \State \Call{revert}{$r$, $P.p$} \EndIf
+\State \Comment{Finding new flaws introduced by the resolver} \Else 
+            \State \Call{revert}{$r$, $P.p$}
+\Comment{Undo resolver insertion} \EndIf
     \EndFor
-    \State \Return Failure \Comment{Return to last choice of resolver}
+    \State \Return Failure
+\State \Comment{Revert to last non deterministic choice of resolver}
 \EndFunction
@@
 flaw. The resolver is inserted in the plan and we recursively call the
-algorithm on the new plan. On failure we return to the last non
+algorithm on the new plan. On failure, we return to the last non
 deterministic choice to pick another resolver. The algorithm ends when
 the agenda is empty or when there is no more resolver to pick for a
-given flaw.
-
-\subsection{Limitations}\label{limitations}
-
-This standard way of doing have seen multiple improvements over
-expressiveness like with UCPOP {[}7{]}, hierarchical task network to add
-more user control over sub-plans {[}8{]}, cognition with defeasible
+given flaw. Before continuing, we present a simple example of classical
+POP execution with the following example of a problem.
+
+\begin{itemize}
+\tightlist
+\item
+  An initial state \(I = \langle \emptyset , \{ 1, 2 \} \rangle\) and a
+  goal \(G = \langle \{ 3, 4, -5, 6 \}, \emptyset \rangle\) encoded as
+  dummy steps.
+\item
+  \(a \langle \{1\}, \{3,5\} \rangle\),
+  \(b \langle \{2\}, \{4\} \rangle\) and
+  \(c \langle \{5\}, \{6\} \rangle\) are simple actions that are useful
+  to achieve the goal.
+\item
+  \(n \langle \{-8, 7\}, \{-7, 8\} \rangle\) and
+  \(l \langle \{-7, 8\}, \{-8, 7\} \rangle\) are looping actions that
+  are meant to cause cycles.
+\item
+  \(t \langle \{4\}, \{-5\} \rangle\) is meant to be threatening to the
+  plan's integrity and will generate threats.
+\item
+  \(u \langle \{4\}, \emptyset \rangle\),
+  \(v \langle \{4\}, \{4\} \rangle\),
+  \(w \langle \{9\}, \{3\} \rangle\),
+  \(x \langle \{7\}, \{-2,2\} \rangle\) are actions that will cause
+  problems. \protect\hyperlink{defects}{(cf.~Defects section)}.
+\end{itemize}
+
+This standard way of doing has seen multiple improvements over
+expressiveness like with UCPOP {[}7{]}, Hierarchical Tasks Network to
+add more user control over sub-plans {[}8{]}, cognition with defeasible
 reasoning {[}9{]}, or speed with multiple ways to implement the popular
@@
 variants do not treat the problem of online planning, resilience and
-soft solving.
-
-Some other closer works like {[}4{]} treats the problem of online
-planning by removing big chunks of the partial plan by identifying
-incorrect trees in the plan. This along with a heuristic of choice of
-unrefinemment strategies causes a heavy replanning of the problem even
-if only one action needs removal. This also lead to an exponential
-number of plan to consider. This is a big problem when trying to adapt a
-plan with minimal changes due to replanning.
-
-Indeed, all these problems can affect POP's performance and quality as
-they can interfere with POP's inner working when the algorithm is able
-to give an answer at all.
-
-Before continuing, we present a simple example of classical POP
-execution with the following problem. We have an initial state
-\(I = \langle \emptyset , \{ 1, 2 \} \rangle\) and a goal
-\(G = \langle \{ 3, 4, -5, 6 \}, \emptyset \rangle\) encoded as dummy
-steps. We also introduce actions that are not steps yet but that are
-provided by \(A\). The actions \(a \langle \{1\}, \{3,5\} \rangle\),
-\(b \langle \{2\}, \{4\} \rangle\) and
-\(c \langle \{5\}, \{6\} \rangle\) are normal actions that are useful to
-achieve the goal. The actions \(n \langle \{-8, 7\}, \{-7, 8\} \rangle\)
-and \(l \langle \{-7, 8\}, \{-8, 7\} \rangle\) are looping actions that
-are meant to cause cycles. The action
-\(t \langle \{4\}, \{-5\} \rangle\) is meant to be threatening to the
-plan's integrity and will generate threats. We introduce
-\(u \langle \{4\}, \emptyset \rangle\) and
-\(v \langle \{4\}, \{4\} \rangle\) as toxic actions,
-\(w \langle \{9\}, \{3\} \rangle\) as a dead-end action and
-\(x \langle \{7\}, \{-2,2\} \rangle\) as a contradictory action. These
-notions will be defined \protect\hyperlink{defects}{later}.
+soft solving. Some other closer works like {[}4{]} treat the problem of
+online planning by identifying and removing trees of the partial plan.
+This is done with a heuristic that choses an unrefinemment strategies
+that causes a heavy replanning of the problem even if only one action
+needs removal. This is a significant problem when trying, for example,
+to adapt a plan with minimal changes due to replanning. Indeed, all
+these problems can affect POP's performance and quality.
 
@@
 implementations. We give a possible resulting plan of standard POP in
-figure \ref{fig:pop}. We can see some issues as for how the plan has
-been built. The action \(v\) is being used even if it is useless since
-\(b\) already provided fluent \(4\). We can also notice that despite
-being contradictory the action \(x\) raised no alarm. As for ordering
+figure \ref{fig:pop}. There are some issues as for how the plan has been
+built. The action \(v\) is being used even if it is useless since \(b\)
+already provided fluent \(4\). We can also notice that despite being
+contradictory the action \(x\) raised no alarm. As for ordering
 constraints, we can clearly see that the link \(a \to t\) is redundant
-with the path \(a \xrightarrow{5} c \to t\) that already puts that
+with the path \(a \xrightarrow{5} c \to t\) that already ensures that
 constraint by transitivity. Also, some problems arise during execution
@@
 
-Of course the flaw selection mechanism of certain variant can prevent
+Of course the flaw selection mechanism of certain variants can prevent
 that to happen in that case. But often flaw selection mechanisms are
 more speed oriented and will do little if a toxic action seems to fit
-better than a more coherent but complex one .
-
-All these issues are caused by what we call \emph{defects} as they are
-not regular PSP flaws but they still cause problems with execution and
-results. We will address these defects and propose a way to fix them in
+better than a more coherent but complex one. All these issues are caused
+by what we call \emph{defects} as they are not regular PSP flaws but
+they still cause problems with execution and results. We will address
+these defects and propose a way to fix them in
 \protect\hyperlink{defects}{the next section}.
@@
 
+\footnotesize
 \Function{properPlan}{Goal $g$, Actions $A$} \State Partial Plan
@@
 \Call{satisfy}{$g$, $A$, $p$}
-\Comment{Satisfy given goal with all necessary actions and causal links}
+\State \Comment{Satisfy the goal with all participating actions and links}
 \State Queue of Actions \(open \gets relevants\)
-\While{$open \neq \emptyset$} \State Action \(a\gets open.pop\)
+\While{$open \neq \emptyset$} \State Action \(a\gets open.popFromQueue\)
 \State Actions \(candidates \gets\) \Call{satisfy}{$a$, $A$, $p$}
 \ForAll{$candidate \in candidates$} \If{$candidate \notin relevants$}
-\State \(open.push(candidate)\) \EndIf
+\State \(open.pushToQueue(candidate)\) \EndIf
         \EndFor
@@
 \end{algorithmic}\end{algorithm}
+
+\begin{figure}[htbp]
+\centering
+\includegraphics{graphics/proper.pdf}
+\caption{Proper plan of the example goal\label{fig:proper}}
+\end{figure}
 
@@
 not have the initial step at the time of the proper plan generation.
-
-\begin{figure}[htbp]
-\centering
-\includegraphics{graphics/proper.pdf}
-\caption{Proper plan of the example goal\label{fig:proper}}
-\end{figure}
-
-We define the concept of \emph{participating action}. An action
-\(a \in A\) participates in a goal \(G\) if and only if \(a\) has an
-effect \(f\) that is needed to accomplish \(G\) or to accomplish another
-participating action's preconditions. A proper plan is a partial plan
-that contains all participating actions as steps and causal links that
-bind them with the step they are participating in. Proper plan
-generation, detailed in Algorithm 2, recursively chooses all
-participating actions. It simply populate the proper plan with a quick
-and incomplete backward chaining.
-
-The partial plan doesn't have an initial state (because of its offline
-nature). This auxiliary algorithm is therefore used as a caching
-mechanism for online planning. The algorithm starts to populate the
-proper plan with a quick and incomplete backward chaining.
-
-Once applied on the example of figure \textbf{???}, proper plan
-generation returns the partial plan presented in figure
-\ref{fig:proper}. This partial plan doesn't have initial state because
-of its offline nature. It also shows several cycles and obvious
-problems. However, it has all the steps of the correct final plan.
-
-This algorithm helps the POP algorithm by prefetching all the actions
-subgoals might need but also need to be cleaned first to be helpful.
+Once applied on the previous example, proper plan generation returns the
+partial plan presented in figure \ref{fig:proper}. This partial plan
+doesn't have initial state because of its offline nature. It also shows
+several cycles and obvious problems. However, it has all the steps of
+the correct final plan. This algorithm helps the POP algorithm by
+prefetching all the actions subgoals might need. However, this result
+needs to be cleaned first to be helpful.
 
@@
 
+\footnotesize
 \Function{clean}{Problem $P$}
@@
 \Function{fix}{Defects $defects$, Problem $P$}
-\ForAll{Defect $d \in defects$} \State \(defect.\)\Call{fix}{}
+\ForAll{Defect $d \in defects$} \State \(defect.\)\Call{fix}{$P$}
 \Comment{Fixing is proper to the defect} \EndFor
@@
 \Function{findDefects}{Problem $P$} \State \Return \Call{illegal}{$P$}
-\(+\) \Call{interfering}{$P$} \EndFunction
+\(+\) \Call{interfering}{$P$}
+\State \Comment{Concatenate the found illegal and interfering defects}
+\EndFunction
 
@@
 aim of this auxiliary algorithm is to clean the plans from such defects
-in order to improve computational time, resilience and plan quality. It
-should be noted that in some cases cleaning plans will increase the
-number of flaws in the plan but will always improve the overall quality
-of it.
+in order to improve resilience and plan quality.
 
@@
 Plan quality is an indicator that is measured by the number of defects
-in a partial plan. There are two specific indicators for a plan quality
-: the action quality and the link quality. We define the link and action
-quality as respectively the number of link or action related defects
-divided by the number of links or actions in the resulting plan.
-\[quality_{action}(p) =  1 - \left( \#ActionDefects(p) \over \#p.A_p \right)\]
+in a partial plan. There are two specific indicators for a plan quality:
+
+\begin{itemize}
+\tightlist
+\item
+  Action quality is the number of defects related to actions divided by
+  the number of actions.
+  \[quality_{action}(p) =  1 - \left( |ActionDefects(p)| \over |p.A_p| \right)\]
+\item
+  Link quality is the number of defects related to links divided by the
+  number of links.
+\end{itemize}
 
@@
 From there it is obvious that plan quality will improve over POP since
-our present algorithm is guaranteed to remove all defects in a plan.
-
-There are two kinds of defects: the illegal defects that violate base
-hypothesis of PSP and the interference defects that can lead to
+SODA POP algorithm is guaranteed to remove all defects in a plan. There
+are two kinds of defects: the illegal defects that violate base
+hypothesis of POP and the interference defects that can lead to
 excessive computational time and to poor plan quality.
@@
 
-These defects are usually hypothesized out by regular models. They are
-illegal use of partial plan representation and shouldn't happen under
-regular circumstances. They may appear if the input is generated by an
-approximate cognitive model that doesn't ensure consistency of the
+These defects are usually hypothesized out by existing algorithms. They
+are illegal use of partial plan representation and shouldn't happen
+under regular circumstances. They may appear if the input is generated
+by an approximate cognitive model that doesn't ensure consistency of the
 output or by unchecked corrupted data. These defects will most of the
 time simply break regular POP algorithms or at least make the
-performances decrease significantly Illegal defects and solutions to fix
-them are presented in the following section.
+performances decrease significantly. Illegal defects and solutions to
+fix them are presented in the following section. The first of these
+defects is pre-existing cycles in the input plan.
 
 \begin{definition}[Cycles]
+
+A cycle is the corresponding notion as in graph theory. Let's consider
+the graph of a partial plan. A cycle in this graph corresponds to a
+cycle of actions in the partial plan.
+
+\end{definition}
 
@@
 Cycles are usually detected as they are inserted in a plan but poor
-input can potentially contain them and breaks the POP algorithm as it
-cannot undo cycles.
-
-\end{definition}
-
-We use strongly connected component detection algorithm to detect
-cycles. Upon cycle detection the algorithm can remove arbitrarily a link
-in the cycle to break it.
-
-In a plan some actions can be illegal for POP. Those are the actions
-that are inconsistent.
+input can potentially contain them and break the POP algorithm as it
+cannot undo cycles. We use strongly connected component detection
+algorithm to detect cycles. Upon cycle detection, the algorithm can
+remove arbitrarily a link in the cycle to break it. In our example the
+actions \(n\) and \(l\) are meant to cause such cycles. In a plan some
+actions can be illegal for POP. Those are the actions that are
+inconsistent.
 
@@
 
-We remove only one of those effect or preconditions based on the usage
+We remove only one of those effects or preconditions based on the usage
 of the action in the rest of the plan. If none of those are used, we
-choose to remove both. In our example in figure \textbf{???} the action
-\(x\) is one of these inconsistent actions with fluent \(2\) and \(-2\)
-in its effects.
+choose to remove both. In our previous example, the action \(x\) is one
+of these inconsistent actions with fluent \(2\) and \(-2\) in its
+effects.
 
@@
 Toxic actions are those that have effects that are already in their
-preconditions or empty effects. This can damage a plan as well as make
-the execution of POP algorithm much longer than necessary. They are
-defined as :
+preconditions or empty effects. They are defined as:
 \[a | pre(a) \cap eff(a) \neq \emptyset \lor eff(a) = \emptyset\]
@@
 
-They can damage a plan as well as make the execution of POP algorithm
-much longer than necessary. This is fixed by removing the toxic fluents
-(\(pre(a) \nsubseteq eff(a)\)) following \(eff(a) = eff(a)-pre(a)\). If
-the effects becomes empty, the action is removed altogether from plan
-and \(A\). For example in figure \textbf{???} the actions \(u\) and
-\(v\) are toxic as the fluent \(4\) is in the effects and preconditions
-of \(v\), and \(u\) has empty effects. In this case these actions will
-be removed by the algorithm as they don't have any other effects.
+Toxic actions can damage a plan as well as make the execution of POP
+algorithm much longer than necessary. This is fixed by removing the
+toxic fluents (\(pre(a) \nsubseteq eff(a)\)) by updating the effects
+with \(eff(a) = eff(a)-pre(a)\). If the effects become empty, the action
+is removed altogether from plan steps and \(A\). In our previous example
+the actions \(u\) and \(v\) are toxic as the fluent \(4\) is in the
+effects and preconditions of \(v\), and \(u\) has empty effects. In this
+case, these actions will be removed by the algorithm as they don't have
+any other effects.
 
@@
 
-A liar link is a link that doesn't reflect the preconditions or effect
-of its source and target. We can note:
+A liar link is a link that doesn't hold a fluent in the preconditions or
+effect of its source and target. We can note:
 \[a_i \xrightarrow{f} a_j | f \notin eff(a_i) \cap pre(a_j)\]
@@
 
-We call lies fluents that participates in the lies. To resolve the
-problem we remove \(f\) and add all savior fluents, i.e.~a fluent in
-\(eff(a_i) \cap pre(a_j)\) that isn't already provided. We delete the
-link all together if it doesn't link any fluents.
+We call lies, fluents that is held by links without being in the
+connected actions . To resolve the problem we remove all lies and add
+all savior fluents, i.e.~a fluent in \(eff(a_i) \cap pre(a_j)\) that
+isn't already held by the link. We delete the link all together if it
+doesn't link any fluent.
 
@@
 won't make the plan unsolvable but they can still cause performance and
-quallity drops. These defects can happen in POP generated plans to some
+quality drops. These defects can happen in POP generated plans to some
 extends. Interference defects and solutions to fix them are presented in
@@
 
-A redundant link have a transitive equivalent of longer length. It means
-that a link \(a_i \to a_j\) is redundant if and only if it exists
-another path from \(a_i\) to \(a_j\) of length greater to \(1\).
-
-\end{definition}
-
-Since POP relies on those additional links, this part focus on removing
-the ones that were generated for threat removal purpose to simplify the
-plan. For example in figure \ref{fig:pop} we can see that the ordering
-constraint from \(a\) to \(t\) is redundant with the path
-\(a \xrightarrow{5} c \to t\) in that it isn't needed to resolve the
+A redundant link is an ordering constraint (causal link without fluents)
+with another equivalent path of longer length int the graph form of the
+partial plan. It means that an ordering constraint \(a_i \to a_j\) is
+redundant if and only if it exists another path from \(a_i\) to \(a_j\)
+of length greater to \(1\).
+
+\end{definition}
+
+Since POP relies on those additional links, this part focuses on
+removing the ones that were generated for threat removal purpose to
+simplify the plan. For example, in figure \ref{fig:pop} we can see that
+the ordering constraint from \(a\) to \(t\) is redundant with the path
+\(a \xrightarrow{5} c \to t\) in that, it isn't needed to resolve the
 threat. Therefore, the algorithm would remove it. This reduces the
@@
 two causal links that can provide the same fluent. Another difference is
-that it cannot happen in classical POP algorithm. This kind of defect is
-making the plan more complex and can also hide useless actions which
-would potentially cause more flaws to handle than necessary.
+that it cannot happen in classical POP algorithm. This kind of defects
+is making the plan more complex and can also hide useless actions which
+would potentially cause more flaws to handle than necessary. In order to
+remove the least interesting link in competing causal links, we need to
+compare their respective providing actions, to chose the most useful
+ones.
+
+\begin{definition}[Usefulness of an action]
+
+The usefulness of an action is the number of participating links
+(outgoing causal links) divided by the number of needing links (incoming
+causal links). If there are no needing links, the usefulness is simply
+the number of participating links.
+
+In the special cases if the action is either an initial step or a goal,
+the usefulness is \(+\infty\). The usefulness of savior action is \(0\).
+
+\end{definition}
+
+We choose the link with the source action having the highest usefulness.
+This replaces unnecessary savior actions and allows reducing the
+usefulness of the least action in order to eventually make it an orphan
+and prune it from the plan.
 
@@
 
-In order to remove the least interesting link in competing causal links,
-we need to compare their respective providing action to chose the most
-useful ones.
-
-\begin{definition}[Usefulness of an action]
-
-The usefulness of an action is the number of participating links
-(outgoing causal links) divided by the number of needing links (incoming
-causal links). If there are no needing links, the usefulness is simmply
-the number of participating links.
-
-In the special cases if the action is either an initial step or a goal,
-the usefulness is \(+\infty\). The usefulness of savior action is \(0\).
-
-\end{definition}
-
-We choose the link with the source action having the highest usefulness.
-This replaces unnecessary savior actions and allows reducing the
-usefulness of the least action in order to eventually make it an orphan
-and prune it from the plan.
-
-In the example figure \ref{fig:competing} the action \(a_j\) on the left
-participates much more than the action \(a_i\) and therefore the link to
-be removed would be \(a_i \xrightarrow{f} a_k\). On the right example
-the actions doesn't have different outgoing links but the action \(a_j\)
-is here much needier than its competitor and therefore the link to be
-removed is the link \(a_j \xrightarrow{f} a_k\).
-
 On the left example of figure \ref{fig:competing}, the action \(a_j\)
 participates much more than the action \(a_i\) and therefore the link to
-be removed would be \(a_i \xrightarrow{f} a_k\). On the right example
+be removed would be \(a_i \xrightarrow{f} a_k\). On the right example,
 the actions don't have different outgoing links but the action \(a_j\)
@@
 
-Orphans actions are actions without any links or action with no outgoing
+Orphan actions are actions without any links or actions with no outgoing
 path to the goal (meaning that it doesn't participate in the plan). That
-also concerns action that would become orphan if another orphan action
+also concerns actions that would become orphans if another orphan action
 is removed.
@@
 
+\footnotesize
 \Function{$OrphanAction.$find}{Problem $P$} \State Actions
 \(orphan \gets \emptyset\) \State int \(oldSize\) \Repeat
-        \State \(oldSize \gets \#orphan\)
+        \State \(oldSize \gets |orphan|\)
 \ForAll{Action $step \in P.p.A_p$} \If{$step \in orphan$}
@@
             \State int \(towardOrphan \gets 0\) \State Causal Links
-\(outgoing \gets\) \protect\Call{outgoingEdgesOf}{$step$, $P.p$}
+\(outgoing \gets\) \State \Call{outgoingEdgesOf}{$step$, $P.p$}
 \ForAll{Causal Link $link \in outgoing$} \If{$link.target \in orphan$}
@@
             \EndFor
-            \If{$\#outgoing = towardOrphan \land step \notin \{ P.I, P.G\}$}
+            \If{$|outgoing| = towardOrphan \land step \notin \{ P.I, P.G\}$}
 \State \(orphan \gets orphan \cup \{step\}\) \EndIf
         \EndFor
-    \Until{$oldSize \neq \#orphan$} \State \Return \(orphan\)
+    \Until{$oldSize \neq |orphan|$} \State \Return \(orphan\)
 \EndFunction
@@
 
-In order to fix this we derive the idea of the backward removal tree of
-{[}4{]}. The algorithm, detailed in Algorithm 4, removes an action if
-all its outgoing causal links are leading to useless actions. It
-iterates over all actions until no new useless action is discovered. All
-useless actions are then removed from the plan.
+In order to fix this, we derive the idea of the backward removal tree of
+{[}4{]}. Algorithm 4, removes an action if all its outgoing causal links
+are leading to useless actions. It iterates over all actions until no
+new useless action is discovered. All useless actions are then removed
+from the plan.
 
@@
 
-In the same way links can be competing toward a common needer, there are
-sometimes in the plan actions that are more suited to achieve a goal.
-These actions are taken into account if they are more useful than the
-source of the link, if they wouldn't cause a cycle and if they have
-effects that are carried by the link.
+In the same way, links can be competing toward a common needer,
+sometimes some actions that are more suited to achieve a goal than
+others. These actions are taken into account if they have effects that
+are carried by the link, if they are more useful than the source of the
+existing link and if they wouldn't cause a cycle.
 
@@
 
+\footnotesize
 \Function{heal}{Problem $P$} \State int \(minViolation \gets \infty\)
@@
 
-This auxiliary algorithm is meant to deal with failure. It will heal the
+This auxiliary algorithm is meant to deal with failure. It heals the
 plan to make the failure recoverable for the next iteration of POP. Of
@@
 the specification of the input, but in exchange it will always issue a
-valid plan whatever happens. For more information on this property go
-take a look at the \protect\hyperlink{hypersoundness}{appropriate
-section bellow}.
+valid plan whatever happens.
+\protect\hyperlink{hypersoundness}{(cf.~Hypersoundness section)}.
 
@@
 not exact than no output at all. That is why we propose a soft failing
-mechanism for POP algorithms.
-
-\subsubsection{Definitions}\label{definitions-1}
-
-We define first some new notions, then we will explain the healing
-algorithm.
+mechanism for the POP algorithm. Following, we define first some
+notions, then we explain the healing algorithm.
 
@@
 A needer is an action that needs a resolution related to a flaw. We
-define different types of needer according to the type of the flaw.
+define different types of needers according to the type of the flaw.
 
@@
 \item
-  Subgoal needer For a subgoal \(a_n \xrightarrow{s} a_s\) the needer is
-  the action \(a_n\) that has an unsatisfied precondition in the current
-  partial plan.
-\item
-  Threat needer The needer of a threat \(a_t\) of a link
-  \(a_p \xrightarrow{t} a_n\) is the target \(a_n\) of the threatened
-  causal link.
+  For a subgoal \(a_s \xrightarrow{s} a_n\) the needer is the action
+  \(a_n\) that has an unsatisfied precondition provided by an eventual
+  action \(a_s\) in the current partial plan.
+\item
+  For a threat \(a_t\) of a link \(a_p \xrightarrow{t} a_n\) the needer
+  is the target \(a_n\) of the threatened causal link.
 \end{itemize}
@@
 A proper fluent of a flaw is the one that caused the flaw. For a subgoal
-\(a_n \xrightarrow{s} a_s\) it is the unsatisfied precondition \(s\).
-For a threat \(a_t\) of a causal link \(a_p \xrightarrow{t} a_n\) it is
+\(a_n \xrightarrow{s} a_s\), it is the unsatisfied precondition \(s\).
+For a threat \(a_t\) of a causal link \(a_p \xrightarrow{t} a_n\), it is
 the fluent \(t\) held by the threatened causal link.
@@
 
-A healer is a resolver that is built around the savior of the flaw in
-order to provide the missing fluents to it. The general formula of a
-healer is the following : \[a_s \xrightarrow{p} a_n\] with \(a_s\) being
-the savior of the flaw.
-
-\end{definition}
-
-For threats we need an additional healer specified as an ordering
+A healer is a resolver built using the savior of the flaw in order to
+provide the missing fluents to it. The general formula of a healer is
+\(a_s \xrightarrow{p} a_n\) with \(a_s\) being the savior of the flaw.
+
+\end{definition}
+
+For threats, we need an additional healer specified as an ordering
 constraint from the threatening action to the savior \(a_t \to a_s\) to
@@
 The violation degree \(v(p)\) of a plan \(p\) is an indicator of the
-health of a partial plan. It is the sum of the number of flaws and the
-number of saviors in the plan.
+violation regarding the initial problem. We note
+\(v(p) = |flaws(p)| + |saviors(A_p)|\). Said otherwise, it is the sum of
+the number of flaws and the number of saviors in the plan.
 
@@
 As the POP algorithm encounters a final failure, this auxiliary
-algorithm get invoked. The aim is to evaluate each backtracking partial
+algorithm get called. The aim is to evaluate each backtracked partial
 plan to choose the best one.
@@
 Therefore, we add an order relation for \(F\) noted
-\[\prec : p \prec q \iff v(p) < v(q) | \{p, q\} \subset F\]
+\[\prec : p \prec q \iff v(p) < v(q) | \{p, q\} \subseteq F\]
 
@@
 same violation degree, the algorithm chooses the first one to have
-happened.
-
-The healing process is similar to how POP works : we apply the healer of
-the flaw that caused the failure of the partial plan we chosen. We empty
-the set \(F\) to allow POP to iterate further since the flaw is
-resolved. The healing process can be done for each unsolved flaws as POP
-fails repeatedly. This ensures some interesting properties explained in
-the following section.
+happened. The healing process is similar to how POP works: we apply the
+healer of the flaw that caused the failure of the partial plan we
+chosen. We empty the set \(F\) to allow POP to iterate further since the
+flaw is resolved. The healing process can be done for each unsolved
+flaws as POP fails repeatedly. This ensures some interesting properties
+explained in the following section.
 
@@
 presented previously gives SODA POP algorithm detailed in Algorithm 6.
-In this section we will focus on the properties of SODA POP.
+In this section, we focus on the properties of SODA POP.
 
@@
 
+\footnotesize
 \Function{soda}{Problem $P$} \State \(P.p \gets\)
-\Call{properPlan}{$P.G$, $P.A$} \Comment Offline execution then this
-will be replaced by the previous online plan adjusted with the
-environment. \State \Call{clean}{$P$} \State bool \(valid \gets false\)
+\Call{properPlan}{$P.G$, $P.A$} \Comment Offline execution
+\State \Call{clean}{$P$} \State bool \(valid \gets false\)
 \While{$\lnot valid$} \State \(valid \gets\) \Call{pop}{$P$}
@@
 
-\subsection{Convergence of POP}\label{convergence}
-
-As to our knowledge, no proof of the convergence of POP has been done we
-want to explicitly formulate one.
-
-The classic planning problem is already proven to be decidable without
-functions in the fluents {[}3{]}. Therefore, we can categorize the
-termination cases.
-
-\begin{proof}
+\subsection{Convergence property of POP}\label{convergence}
+
+First, we prove the convergence of POP. The classic planning problem is
+already proven to be decidable without functions in the fluents {[}3{]}.
+Therefore, we can categorize the termination cases.
+
+\begin{proof}[Proof of convergence]
 
@@
 ensures that it will find a solution for the problem and therefore
-terminate.
-
-Be \(flaws(p)\) the set of flaws of a given partial plan. The number of
-flaws is the number of subgoals plus the number of threats
-\(flaws(p) = subgoals(p) \cup threats(p)\)
-
-We consider the number of actions \(\#A\) as being finite. Therefore,
-the number of steps in the plan is at worse \(\#A_p = \#A\). We also
-assume that actions has a finite number of preconditions and effects
-(since we don't use functions over fluents).
-
-This leads to \(\#subgoals(p) < \sum_{a \in A_p} \#pre(a) < \infty\) and
-\(\#threats(p) < \#L \le \sum_{a \in A_p} \#pre(a) < \infty\)
+terminate. Let \(flaws(p)\) be the set of flaws of a given partial plan.
+The number of flaws is the number of subgoals plus the number of threats
+since \(flaws(p) = subgoals(p) \cup threats(p)\). We consider the number
+of actions \(|A|\) as being finite. Therefore, the number of steps in
+the plan is at worse \(|A_p| = |A|\). We also assume that actions have a
+finite number of preconditions and effects (since we don't use functions
+over fluents). This leads to
+\(|subgoals(p)| < \sum_{a \in A_p} |pre(a)| < \infty\) and
+\(|threats(p)| < |L| \le \sum_{a \in A_p} |pre(a)| < \infty\).
 
 This means the number of all possible flaws is finite. As POP resolves
-these flaws it will decrease their numbers and iterate over resolvers.
-The number of resolver is \(\#subgoals(p) * \#A + \#threats(p) * 2\) and
+these flaws it will decrease their number and iterate over resolvers.
+The number of resolvers is \(|subgoals(p)| * |A| + |threats(p) * 2\) and
 is also finite. This means that the iteration will in the worst case be
-of the number of resolvers before failing and this proves that the
-algorithm terminates. \qedhere
+equal to the number of resolvers before failing. This proves termination
+and therefore that POP converges. \qedhere
 
@@
 
-Now that we proved that regular POP converges we can introduce the next
-property : hyper soundness.
+Now that we proved that regular POP converges, we can introduce the next
+property: hyper soundness.
 
@@
 soundness that implicitly states that the validity of a solution is
-relative to the problem. In the case of hypersoundness the problem is
-valid and a solution to a problem \(P' = \langle A', I, G, p\rangle\).
-We note the new set \(A' = A \cup S\) with \(S\) being the set of
-saviors for all flaws that made the POP algorithm fails during the
-execution of SODA.
-
-The hypersoundness of our combined algorithm is proven using the
+relative to the problem. In the case of hypersoundness, we find a
+solution to a derived problem \(P' = \langle A', I, G, p\rangle\). We
+note the new set \(A' = A \cup S\) with \(S\) being the set of saviors
+for all flaws that made the POP algorithm fail during the execution of
+SODA. Next we prove the hypersoundness of our algorithm using the
 convergence of POP and the way the Soft solving behaves.
 
-\begin{proof}[Hypersoundness of SODA POP]
+\begin{proof}[Proof of hypersoundness of SODA POP]
 
@@
 (since duplicates are forbidden) and the defect resolution will fix the
-finite numbers of defects present in the finite partial plan issued by
+finite number of defects present in the finite partial plan issued by
 the proper plan algorithm.
@@
 SODA POP algorithm can be used in dynamic online environments to allow a
-robust way to replan an existing obsolete plan. The first thing to
-execute prior to the runtime is the generation of the proper plans for
-all the goals that will be considered.
-
-For the first execution of the online planning the initial state is
-added to the problem and the defect detection is applied with the rest
-of the SODA POP algorithm. This will give the first plan.
-
-For every change of the environment the previous plan is modified
-accordingly and then fed to the defect detection and SODA algorithm
-again. This must be done each time the plan is modified in order to
-actualize the plan. The new plan will have all defects fixed. For
-example a savior action can be removed if the initial step or a new
-action becomes competing with it and actions with liar link to a removed
-fluent in the goal will become probably an orphan.
-
-In practice this will generate little to no iteration of the algorithm.
+robust way to replan an existing obsolete plan. The first step prior to
+the runtime is the generation of the proper plans for all the goals that
+will be considered. For each online iteration, we take the previous
+plan, clean all defects in it and makes it loop between POP and the
+healing mechanism (if necessary). The defect cleaning will also remove
+all unnecessary savior actions and eventually make the original problem
+solvable again. Since each previous plan is almost correct, the
+algorithm will have little to no iterations to make in order to repair
+it.
 
@@
 
-In order to test the validity of these algorithms we implemented a
-prototype in Java. This prototype is exactly derived from the
-definitions and pseudo code presented in this paper. We used basic
-actions with integer fluents to focus on the way the algorithm behaves.
-
-For the simulation runs we used a computer with an Intel® Core™
-i7-4720HQ CPU clocking at 2.60GHz for 8 cores and 8GB of memory. The
-speed was measured in nano seconds before and after the call to the
-solve function. The process has a warming up phase that compute random
-plans for a few seconds before starting the benchmarks. The computer was
-left idle during the test to remove any related noise to the
-measurements.
+In order to verify the validity of these algorithms we implemented a
+prototype in Java. We used basic actions with integer fluents to focus
+on the way the algorithm behaves. For the simulation runs, we used a
+computer with an Intel® Core™ i7-4720HQ CPU clocking 8 cores at 2.60GHz
+and 8GB of memory. The speed was measured in nano seconds before and
+after the call to the solve function. The process has a warming up phase
+that computes random plans for a few seconds before starting the
+benchmarks.
 
@@
 
-The first metric we decided to measure was the performance of our
-reference POP algorithm. We measured the solving time for valid problems
-and the quality of the resulting plans. In figure \ref{fig:quality} we
-can see a plot of these measures.
-
-\begin{figure}[htbp]
-\centering
-\includegraphics{graphics/quality.pdf}
-\caption{Action and link quality and solving time of POP over \(10 000\)
-valid problems for each difficulty\label{fig:quality}}
-\end{figure}
-
-We tested the algorithm with randomly generated valid problems. We
-generated those by randomly creating plans based on a difficulty setting
-that was the upper bound for the number of actions and half the possible
-number of fluents. This difficulty setting also made the initial and
-goal step larger accordingly. The actions were cleaned of any toxicity
-and was built using a forward chaining algorithm. We added also random
-unrelated actions. Each problem was verified by POP before being
-generated to ensure resolvability.
-
-As we clearly see in the figure \ref{fig:quality}, POP linearly increase
-its solving time depending on the problem difficulty. That obviously
-follows the fact that POP has more flaws to fix and therefore more
-iterations.
-
+The first metric we are interested in is the performance of classical
+POP algorithm. We measure the solving time for valid problems and the
+quality of the resulting plans. We tested the algorithm with randomly
+generated valid problems. We generated those by randomly creating plans
+based on a difficulty setting that was the upper bound for the number of
+actions and half the number of possible fluents. This difficulty setting
+also made the initial and goal step larger accordingly. The actions were
+cleaned of any toxicity and were built using a forward chaining
+algorithm. We added also random unrelated actions. Each problem was
+verified by POP before being generated to ensure resolvability. As we
+clearly see in the figure \ref{fig:quality}, POP linearly increases its
+solving time depending on the problem difficulty. That obviously follows
+the fact that POP has more flaws to fix and therefore more iterations.
 As we can observe, POP has a rather high link quality with almost no
@@
 plans or to a real tendency of POP to not create that kind of defects on
-its own.
-
-The action quality on the other hand drops significantly as the
+its own. The action quality on the other hand drops significantly as the
 difficulty gets higher. This is linked to the number of competing and
@@
 
+\begin{figure}[htbp]
+\centering
+\includegraphics{graphics/quality.pdf}
+\caption{Action and link quality and solving time of POP over \(10^4\)
+valid problems for each difficulty\label{fig:quality}}
+\end{figure}
+
 \subsection{Performance of SODA POP}\label{performance-of-soda-pop}
 
-As SODA POP and regular POP doesn't have the same range of capabilities
-we can't compare them hand to hand. Indeed, our algorithm will always
-output plans with 100\% quality since the defect detection system aims
-to remove them all and since our algorithms is hypersound it will give
-valid plans for unsolvable problems by derivation. In these case POP
-won't be able to return a result and will terminate much quicker as the
+As SODA POP and regular POP have not the same range of capabilities we
+can't compare them hand to hand. Indeed, our algorithm always outputs
+plans with 100\% quality since the defect detection system aims to
+remove all of them. Moreover, our algorithm is hypersound so it gives
+valid plans for unsolvable problems by derivation. In this specific case
+POP won't be able to return a result and terminates more quickly as the
 plan is found unsolvable.
 
-Therefore, we measured the performances of our set of algorithms on
-completely random problems. Each time the algorithm outputted a solution
+Therefore, we measured the performances of SODA POP algorithm on
+completely random problems. Each time the algorithm outputs a solution
 with the lowest possible violation despite the complete invalidity of
 the input. In figure \ref{fig:performance} we can see the way SODA POP
-scales up on larger problems.
+scales up on larger problems. The performances display logarithmic
+solving time. This is explained by the fact that POP has to be called
+recursively on the healed problems. The defect detection participates
+too in the increase of solving time especially the competing action
+detection that needs to iterate over all actions and edges and calculate
+usefulness for two actions each time.
 
@@
 \includegraphics{graphics/performance.pdf}
-\caption{Average solving time of SODA POP over \(10 000\) random
-problems for each difficulty\label{fig:performance}}
+\caption{Average solving time of SODA POP over \(10^4\) random problems
+for each difficulty\label{fig:performance}}
 \end{figure}
-
-The performances display logarithmic solving time. This is explained by
-the fact that POP has to be called recursively on the healed problems.
-The defect detection participates too in the increase of solving time
-especially the competing action detection that needs to iterate over all
-actions and edges and calculate usefulness for two actions each time.
 
@@
 making as the capabilities to derive plans and repair them will prove
-useful when comparing potential goals with observed plans.
-
-The algorithm can be improved with a better defect detection algorithm
-that can rank them and start fixing the most offensive defects before
-targeting others. Also, if the competing action detection can be
-improved, it can be used as heuristic for resolver selection to improve
-the performances.
-
+useful when comparing potential goals with observed plans. The algorithm
+can be improved with a better defect detection algorithm that can rank
+defects and start fixing the most offensive defects before targeting
+others. Also, if the competing action detection can be improved, it can
+be used as heuristic for resolver selection to improve the performances.
 Another way the present work can be improved is by extending it to the
-use of more expressive fluents and port all notions to variable choices.
-One possible goal would be to combine this work with ontologies or an
-argumentation language in order to significantly boost expressiveness.
-
-We hope that this work will be useful and that it will be extended and
-used in various applications in the future and that is why we plan to
-release the software with an open source license soon.
+use of more expressive fluents and transpose all notions to variable
+domains. One possible goal would be to improve fluent domain with an
+propositional language in order to significantly boost expressiveness.
+Finally, we plan to release the software with an open source license
+soon.
 

### 2016-01-03 src/me/grea/antoine/soda/algorithm/IllegalFixer.java

@@ -1,0 +1,203 @@
+/*
+ * To change this license header, choose License Headers in Project Properties.
+ * To change this template file, choose Tools | Templates
+ * and open the template in the editor.
+ */
+package me.grea.antoine.soda.algorithm;
+
+import java.util.Collections;
+import java.util.HashSet;
+import java.util.List;
+import java.util.Set;
+import me.grea.antoine.soda.heuristic.Usefullness;
+import me.grea.antoine.soda.type.Action;
+import me.grea.antoine.soda.type.Edge;
+import me.grea.antoine.soda.type.Problem;
+import static me.grea.antoine.utils.Collections.difference;
+import static me.grea.antoine.utils.Collections.intersection;
+import static me.grea.antoine.utils.Collections.set;
+import static me.grea.antoine.utils.Collections.union;
+import me.grea.antoine.utils.Log;
+import org.jgrapht.alg.StrongConnectivityInspector;
+
+/**
+ *
+ * @author antoine
+ */
+public class IllegalFixer {
+
+    public static void clean(Problem problem) {
+        for (Action action : union(problem.actions, problem.plan.vertexSet())) {
+
+            fixInconsistent(action, problem);
+
+            fixToxic(action, problem);
+        }
+
+        for (Edge edge : new HashSet<>(problem.plan.edgeSet())) {
+            fixLiar(edge, problem);
+        }
+
+        fixCycles(problem);
+    }
+
+    private static Set<Integer> lies(Edge edge, Action source, Action target) {
+        return difference(edge.labels, intersection(source.effects, target.preconditions));
+    }
+
+    private static Set<Integer> saviours(Edge edge, Action source, Action target) {
+        return difference(intersection(source.effects, target.preconditions), edge.labels);
+    }
+
+    private static Set<Integer> toxicEffects(Action action) {
+        Set<Integer> effects = intersection(action.preconditions, action.effects);
+        if (effects.isEmpty()) {
+            return set();
+        }
+        return effects;
+    }
+
+    private static Set<Integer> inconsistentEffects(Action action) {
+        Set<Integer> effects = new HashSet<>();
+        for (int fluent : action.effects) {
+            if (action.effects.contains(-fluent)) {
+                effects.add(fluent);
+            }
+        }
+        return effects;
+    }
+
+    private static Set<Integer> inconsistentPrecondition(Action action) {
+        Set<Integer> preconditions = new HashSet<>();
+        for (int fluent : action.effects) {
+            if (action.preconditions.contains(-fluent)) {
[…]

### 2016-01-03 src/me/grea/antoine/soda/algorithm/PartialOrderOptimizedPlanning.java

@@ -1,0 +1,151 @@
+/*
+ * To change this license header, choose License Headers in Project Properties.
+ * To change this template file, choose Tools | Templates
+ * and open the template in the editor.
+ */
+package me.grea.antoine.soda.algorithm;
+
+import java.util.ArrayDeque;
+import java.util.Deque;
+import java.util.HashSet;
+import java.util.Set;
+import me.grea.antoine.utils.Log;
+import me.grea.antoine.soda.exception.Success;
+import me.grea.antoine.soda.type.Action;
+import me.grea.antoine.soda.type.PartialSolution;
+import me.grea.antoine.soda.type.Plan;
+import me.grea.antoine.soda.type.flaw.Flaw;
+import me.grea.antoine.soda.type.Problem;
+import me.grea.antoine.soda.type.flaw.Alternative;
+import me.grea.antoine.soda.type.flaw.Orphan;
+import me.grea.antoine.soda.type.flaw.Resolver;
+import me.grea.antoine.soda.type.flaw.SubGoal;
+import me.grea.antoine.soda.type.flaw.Threat;
+
+/**
+ *
+ * @author antoine
+ */
+public class PartialOrderOptimizedPlanning {
+
+    private final Problem problem;
+    private final Deque<Flaw> agenda = new ArrayDeque<>();
+    private final Deque<PartialSolution> partialSolutions = new ArrayDeque<>();
+
+    public PartialOrderOptimizedPlanning(Problem problem) {
+        this.problem = problem;
+        IllegalFixer.clean(problem);
+        populateAgenda();
+    }
+
+    private void populateAgenda() {
+        agenda.addAll(Alternative.find(problem));
+        agenda.addAll(SubGoal.find(problem));
+        agenda.addAll(Threat.find(problem));
+        agenda.addAll(Orphan.find(problem));
+    }
+
+    public static void solve(Problem problem) {
+        PartialOrderOptimizedPlanning pop = new PartialOrderOptimizedPlanning(problem);
+        while (true) {
+            try {
+                pop.refine();
+            } catch (Success ex) {
+                Log.i("Success !");
+                return;
+            }
+            Log.w("Failure");
+            pop.soft();
+        }
+    }
+
+    public void refine() throws Success {
+        if (agenda.isEmpty()) {
+            throw new Success();
+        }
+        Log.d("Agenda " + agenda);
+        Flaw flaw = agenda.pop();
+
[…]

### 2016-01-03 src/me/grea/antoine/soda/algorithm/SoftSolving.java

@@ -1,42 +1,0 @@
-/*
- * To change this license header, choose License Headers in Project Properties.
- * To change this template file, choose Tools | Templates
- * and open the template in the editor.
- */
-package me.grea.antoine.soda.algorithm;
-
-import me.grea.antoine.log.Log;
-import me.grea.antoine.soda.type.PartialSolution;
-import me.grea.antoine.soda.type.flaw.Flaw;
-import me.grea.antoine.soda.type.Plan;
-import me.grea.antoine.soda.type.Problem;
-import me.grea.antoine.soda.type.flaw.Resolver;
-
-/**
- *
- * @author antoine
- */
-public class SoftSolving {
-
-    public static void heal(Problem problem) {
-        double minViolation = Double.POSITIVE_INFINITY; // double for infinity
-        Plan best = problem.plan;
-        Flaw annoyer = null;
-        for (PartialSolution partialSolution : problem.partialSolutions) {
-            double currentViolation = partialSolution.remaining.size() +
-                    (partialSolution.plan.vertexSet().stream().filter((action) -> (action.fake)).count());
-            if (currentViolation < minViolation) {
-                best = partialSolution.plan;
-                annoyer = partialSolution.cause;
-                minViolation = currentViolation;
-            }
-        }
-        problem.plan = best;
-        Log.i("Violation : " + minViolation);
-        problem.partialSolutions.clear();
-        for(Resolver resolver : annoyer.healers() ) { resolver.apply(best); };
-        Log.i("Plan healed !");
-    }
-    
-
-}

### 2016-01-03 src/me/grea/antoine/soda/exception/Failure.java

@@ -12,6 +12,7 @@ import me.grea.antoine.soda.type.flaw.Flaw;
  * @author antoine
  */
 public class Failure extends Exception {
+
     public Flaw cause;
 
     public Failure(Flaw cause) {
@@ -22,7 +23,5 @@ public class Failure extends Exception {
     public String getMessage() {
         return "Failure caused by " + cause;
     }
-    
-    
-    
+
 }

### 2016-01-03 src/me/grea/antoine/soda/heuristic/Usefullness.java

@@ -1,0 +1,56 @@
+/*
+ * To change this license header, choose License Headers in Project Properties.
+ * To change this template file, choose Tools | Templates
+ * and open the template in the editor.
+ */
+package me.grea.antoine.soda.heuristic;
+
+import java.util.Comparator;
+import me.grea.antoine.soda.type.Action;
+import me.grea.antoine.soda.type.Problem;
+import static java.lang.Math.round;
+
+/**
+ *
+ * @author antoine
+ */
+public class Usefullness {
+
+    public static double h(Problem problem, Action action) {
+        if (problem.plan.containsVertex(action)) {
+            return action.fake ? 0.0
+                    : action == problem.goal
+                    || action == problem.initial
+                            ? Double.POSITIVE_INFINITY
+                            : (problem.plan.outDegreeOf(action) * action.effects.size()) / (double) ((problem.plan.inDegreeOf(action) * action.preconditions.size()) + 0.1);
+        }
+        return h(action);
+    }
+
+    public static double h(Action action) {
+        return action.fake ? 0.0
+                : (action.effects.size()) / (double) ((action.preconditions.size()) + 0.1);
+    }
+
+    public static Comparator<Action> compare(Problem problem) {
+        return (Action a1, Action a2) -> falseEquality(cast(h(problem, a1) - h(problem, a2)), a1, a2);
+    }
+
+    public static Comparator<Action> compare() {
+        return (Action a1, Action a2) -> falseEquality(cast(h(a1) - h(a2)), a1, a2);
+    }
+    
+    private static int falseEquality(int compare, Action a1, Action a2)
+    {
+        return a1.equals(a2) ? 0 : (compare == 0 && !a1.equals(a2)) ? a1.hashCode() - a2.hashCode(): compare;
+    }
+
+    private static int cast(double l) {
+        if (l > Integer.MAX_VALUE) {
+            return Integer.MAX_VALUE;
+        } else if (l < Integer.MIN_VALUE) {
+            return Integer.MIN_VALUE;
+        }
+        return (int) round(l);
+    }
+}

### 2016-01-03 src/me/grea/antoine/soda/test/CrazyActionGenerator.java

@@ -5,6 +5,7 @@
  */
 package me.grea.antoine.soda.test;
 
+import me.grea.antoine.utils.Dice;
 import me.grea.antoine.soda.test.*;
 import java.util.HashSet;
 import java.util.Set;
@@ -18,10 +19,9 @@ public class CrazyActionGenerator {
 
     public static Set<Action> generate(int enthropy, int number) {
         Set<Action> actions = new HashSet<>(number);
-        while(actions.size() < number)
-        {
-            actions.add(new Action(Dice.roll(-enthropy, enthropy, Dice.roll((int) (Math.log10(enthropy)+1))), 
-                                   Dice.roll(-enthropy, enthropy, Dice.roll((int) (Math.log10(enthropy)+1)))));
+        while (actions.size() < number) {
+            actions.add(new Action(Dice.roll(-enthropy, enthropy, Dice.roll((int) (Math.log10(enthropy) + 1))),
+                    Dice.roll(-enthropy, enthropy, Dice.roll((int) (Math.log10(enthropy) + 1)))));
         }
         return actions;
     }

### 2016-01-03 src/me/grea/antoine/soda/test/QualityOfPop.java

@@ -1,102 +1,0 @@
-/*
- * To change this license header, choose License Headers in Project Properties.
- * To change this template file, choose Tools | Templates
- * and open the template in the editor.
- */
-package me.grea.antoine.soda.test;
-
-import java.io.File;
-import java.io.FileNotFoundException;
-import java.io.PrintStream;
-import java.time.LocalDateTime;
-import me.grea.antoine.soda.test.*;
-import java.util.ArrayList;
-import java.util.List;
-import java.util.Set;
-import java.util.logging.Level;
-import java.util.logging.Logger;
-import me.grea.antoine.log.Log;
-import me.grea.antoine.soda.algorithm.DefectResolver;
-import me.grea.antoine.soda.algorithm.PartialOrderPlanning;
-import me.grea.antoine.soda.algorithm.Soda;
-import me.grea.antoine.soda.exception.Failure;
-import me.grea.antoine.soda.type.Plan;
-import me.grea.antoine.soda.type.Problem;
-import me.grea.antoine.soda.type.defect.CompetingAction;
-import me.grea.antoine.soda.type.defect.CompetingLink;
-import me.grea.antoine.soda.type.defect.Cycle;
-import me.grea.antoine.soda.type.defect.Defect;
-import me.grea.antoine.soda.type.defect.InconsistentAction;
-import me.grea.antoine.soda.type.defect.LiarLink;
-import me.grea.antoine.soda.type.defect.OrphanAction;
-import me.grea.antoine.soda.type.defect.RedundantLink;
-import me.grea.antoine.soda.type.defect.ToxicAction;
-import me.grea.antoine.soda.utils.Collections.*;
-import static me.grea.antoine.soda.utils.Collections.union;
-import me.grea.antoine.soda.utils.Stats;
-
-/**
- *
- * @author antoine
- */
-public class QualityOfPop {
-
-    public static void main(String[] args) throws Failure {
-        Log.level = Log.Level.FATAL;
-        Chrono popChrono = new Chrono();
-        Chrono sodaChrono = new Chrono();
-        int number = 10000;
-        File file = new File(LocalDateTime.now() + "_" + QualityOfPop.class + ".csv");
-        System.out.println(file.getAbsolutePath());
-        try (PrintStream result = new PrintStream(file)) {
-            for (int i = 2; i < 100; i++) {
-                System.gc();
-                Set<Problem> problems = ValidProblemGenerator.generate(i, number);
-                List<Double> actionQuality = new ArrayList<>();
[…]

### 2016-01-03 src/me/grea/antoine/soda/test/RandomTest.java

@@ -1,0 +1,55 @@
+/*
+ * To change this license header, choose License Headers in Project Properties.
+ * To change this template file, choose Tools | Templates
+ * and open the template in the editor.
+ */
+package me.grea.antoine.soda.test;
+
+import java.io.File;
+import java.io.FileNotFoundException;
+import java.io.PrintStream;
+import java.time.LocalDateTime;
+import java.util.Set;
+import me.grea.antoine.soda.algorithm.PartialOrderOptimizedPlanning;
+import me.grea.antoine.soda.type.Problem;
+import me.grea.antoine.utils.Chrono;
+import me.grea.antoine.utils.Log;
+
+/**
+ *
+ * @author antoine
+ */
+public class RandomTest {
+    
+    public static void main(String... args)
+    {
+        Log.level = Log.Level.FATAL;
+        Chrono chrono = new Chrono();
+        int number = 10000;
+//        File file = new File(LocalDateTime.now() + "_" + RandomTest.class + ".csv");
+//        System.out.println(file.getAbsolutePath());
+//        try (PrintStream result = new PrintStream(file)) {
+            //echaufement
+            Set<Problem> problems = CrazyProblemGenerator.generate(40, 10000);
+            for (Problem problem : problems) {
+                PartialOrderOptimizedPlanning.solve(problem);
+            }
+//            for (int i = 1; i < 100; i++) {
+//                problems = CrazyProblemGenerator.generate(i, number);
+//                for (Problem problem : problems) {
+//                    chrono.start();
+//                    PartialOrderOptimizedPlanning.solve(problem);
+//                    chrono.stop();
+//                }
+//                System.out.println(i + " => " + chrono);
+////                result.println(i + "," + chrono.total / number);
+//                chrono.reset();
+//            }
+//            result.println("Iterations/enthropy : " + number);
+//            result.close();
+//        } catch (FileNotFoundException ex) {
+//            Log.e(ex);
+//        }
+    }
+    
+}

### 2016-01-03 src/me/grea/antoine/soda/test/ScalabilityOfSoda.java

@@ -1,58 +1,0 @@
-/*
- * To change this license header, choose License Headers in Project Properties.
- * To change this template file, choose Tools | Templates
- * and open the template in the editor.
- */
-package me.grea.antoine.soda.test;
-
-import java.io.File;
-import java.io.FileNotFoundException;
-import java.io.PrintStream;
-import java.time.LocalDateTime;
-import java.time.ZoneId;
-import java.util.ArrayList;
-import java.util.List;
-import java.util.Set;
-import java.util.logging.Level;
-import java.util.logging.Logger;
-import me.grea.antoine.log.Log;
-import me.grea.antoine.soda.algorithm.Soda;
-import me.grea.antoine.soda.exception.Failure;
-import me.grea.antoine.soda.type.Problem;
-
-/**
- *
- * @author antoine
- */
-public class ScalabilityOfSoda {
-
-    public static void main(String[] args) throws Failure {
-        Log.level = Log.Level.FATAL;
-        Chrono chrono = new Chrono();
-        int number = 10000;
-        File file = new File(LocalDateTime.now() + "_" + ScalabilityOfSoda.class + ".csv");
-        System.out.println(file.getAbsolutePath());
-        try (PrintStream result = new PrintStream(file)) {
-            //echaufement
-            Set<Problem> problems = CrazyProblemGenerator.generate(50, 10000);
-            for (Problem problem : problems) {
-                Soda.solve(problem);
-            }
-            for (int i = 1; i < 100; i++) {
-                problems = CrazyProblemGenerator.generate(i, number);
-                for (Problem problem : problems) {
-                    chrono.start();
-                    Soda.solve(problem);
-                    chrono.stop();
-                }
-                System.out.println(i + " => " + chrono);
-                result.println(i + "," + chrono.total / number);
-                chrono.reset();
-            }
-            result.println("Iterations/enthropy : " + number);
-            result.close();
-        } catch (FileNotFoundException ex) {
-            Log.e(ex);
-        }
-    }
-}

### 2016-01-03 src/me/grea/antoine/soda/type/Edge.java

@@ -14,11 +14,12 @@ import org.jgrapht.graph.DefaultEdge;
  * @author antoine
  */
 public class Edge extends DefaultEdge {
+
     public Set<Integer> labels = new HashSet<>();
 
     @Override
     public String toString() {
-        return getSource()+ " =("+ (labels.isEmpty() ? "☠" : labels) +")> " + getTarget();
+        return getSource() + " -" + (labels.isEmpty() ? "☠" : labels) + "> " + getTarget();
     }
-    
+
 }

### 2016-01-03 src/me/grea/antoine/soda/type/PartialSolution.java

@@ -5,6 +5,7 @@
  */
 package me.grea.antoine.soda.type;
 
+import java.util.ArrayDeque;
 import java.util.Deque;
 import me.grea.antoine.soda.type.flaw.Flaw;
 
@@ -13,15 +14,15 @@ import me.grea.antoine.soda.type.flaw.Flaw;
  * @author antoine
  */
 public class PartialSolution {
+
     public Plan plan;
     public Flaw cause;
     public Deque<Flaw> remaining;
 
     public PartialSolution(Plan plan, Flaw cause, Deque<Flaw> remaining) {
-        this.plan = (Plan) plan.clone();
+        this.plan = new Plan(plan);
         this.cause = cause;
-        this.remaining = remaining;
+        this.remaining = new ArrayDeque<>(remaining);
     }
-    
-    
+
 }

### 2016-01-03 src/me/grea/antoine/soda/type/Plan.java

@@ -7,26 +7,59 @@ package me.grea.antoine.soda.type;
 
 import java.util.ArrayDeque;
 import java.util.Deque;
+import java.util.HashMap;
 import java.util.HashSet;
+import java.util.Map;
 import java.util.Set;
-import org.jgrapht.graph.DefaultDirectedGraph;
+import org.jgrapht.DirectedGraph;
+import org.jgrapht.graph.AbstractBaseGraph;
+import org.jgrapht.graph.ClassBasedEdgeFactory;
 
 /**
  *
  * @author antoine
  */
-public class Plan extends DefaultDirectedGraph<Action, Edge> {
+public class Plan extends AbstractBaseGraph<Action, Edge> implements DirectedGraph<Action, Edge> {
+
+    private final Map<Action, Integer> outDegree = new HashMap<Action, Integer>() {
+        {
+            vertexSet().stream().forEach((action) -> {
+                put(action, outDegreeOf(action));
+            });
+        }
+    };
+    private final Map<Action, Integer> inDegree = new HashMap<Action, Integer>() {
+        {
+            vertexSet().stream().forEach((action) -> {
+                put(action, inDegreeOf(action));
+            });
+        }
+    };
+
+    private int violation = 0;
 
     public Plan() {
-        super(Edge.class);
+        super(new ClassBasedEdgeFactory<>(Edge.class), false, true);
+    }
+
+    public Plan(Plan other) {
+        this();
+        for (Action action : other.vertexSet()) {
+            addVertex(action);
+        }
+        for (Edge edge : other.edgeSet()) {
+            addEdge(other.getEdgeSource(edge), other.getEdgeTarget(edge), edge);
+        }
     }
 
     public boolean reachable(Action source, Action target, int k, Set<Edge> forbiden) {
         if (source == target) {
             return true;
         }
-        if(forbiden == null)
-        {
+        if (!containsVertex(source) || !containsVertex(target)) {
+            return false;
+        }
+        if (forbiden == null) {
             forbiden = new HashSet<>();
         }
         Set<Action> visited = new HashSet<>();
@@ -55,13 +88,96 @@ public class Plan extends DefaultDirectedGraph<Action, Edge> {
     public boolean reachable(Action source, Action target, int k) {
         return reachable(source, target, k, null);
     }
-    
+
     public boolean reachable(Action source, Action target, Set<Edge> forbiden) {
[…]

### 2016-01-03 src/me/grea/antoine/soda/type/Problem.java

@@ -22,10 +22,8 @@ public class Problem {
     public Action goal;
     public Set<Action> actions; // not including those above
     public Plan plan;
-    public Deque<PartialSolution> partialSolutions = new ArrayDeque<>();
-    
-    public Problem()
-    {
+
+    public Problem() {
         this(new Action(), new Action(), new HashSet<>(), new Plan());
     }
 
@@ -43,10 +41,6 @@ public class Problem {
         this.goal = other.goal;
         this.actions = other.actions;
         this.plan = other.plan;
-    }
-
-    public long violation() {
-        return plan.vertexSet().stream().filter((action) -> (action.fake)).count();
     }
 
     @Override

### 2016-01-03 src/me/grea/antoine/soda/type/defect/CompetingLink.java

@@ -1,81 +1,0 @@
-/*
- * To change this license header, choose License Headers in Project Properties.
- * To change this template file, choose Tools | Templates
- * and open the template in the editor.
- */
-package me.grea.antoine.soda.type.defect;
-
-import java.util.HashSet;
-import java.util.Map;
-import java.util.Set;
-import me.grea.antoine.log.Log;
-import me.grea.antoine.soda.type.Action;
-import me.grea.antoine.soda.type.Edge;
-import me.grea.antoine.soda.type.Problem;
-import static me.grea.antoine.soda.utils.Collections.difference;
-import static me.grea.antoine.soda.utils.Collections.intersection;
-
-/**
- *
- * @author antoine
- */
-public class CompetingLink extends Defect {
-
-    public Edge greater;
-    public Edge lesser;
-    public Set<Integer> competing;
-
-    public CompetingLink(Edge greater, Edge lesser, Set<Integer> competing, Problem problem) {
-        super(problem);
-        this.greater = greater;
-        this.lesser = lesser;
-        this.competing = competing;
-    }
-
-    @Override
-    public void fix() {
-        lesser.labels.removeAll(competing);
-        if (lesser.labels.isEmpty()) {
-            problem.plan.removeEdge(lesser);
-        }
-    }
-
-    public static Set<CompetingLink> find(Problem problem) {
-        Set<CompetingLink> result = new HashSet<>();
-        Set<Edge> concurents = new HashSet<>();
-        for (Edge edge : problem.plan.edgeSet()) {
-            for (Edge concurent : problem.plan.incomingEdgesOf(problem.plan.getEdgeTarget(edge))) {
-                if (concurent != edge && !concurents.contains(edge) && !concurents.contains(concurent)) {
-                    CompetingLink competingLink = is(edge, concurent, problem);
-                    if (competingLink != null) {
-                        concurents.add(edge);
-                        concurents.add(concurent); //FIXME check if this doesn't cause duplicates
-                        result.add(competingLink);
-                    }
-                }
-            }
-        }
-        return result;
-    }
-
-    public static CompetingLink is(Edge pretender, Edge challenger, Problem problem) {
-        Set<Integer> competing = intersection(pretender.labels, challenger.labels);
-        if (problem.plan.getEdgeTarget(pretender) == problem.plan.getEdgeTarget(challenger)
-                && !competing.isEmpty()) {
-            Action pretenderSource = problem.plan.getEdgeSource(pretender);
[…]

### 2016-01-03 src/me/grea/antoine/soda/type/defect/Cycle.java

@@ -1,71 +1,0 @@
-/*
- * To change this license header, choose License Headers in Project Properties.
- * To change this template file, choose Tools | Templates
- * and open the template in the editor.
- */
-package me.grea.antoine.soda.type.defect;
-
-import java.util.HashMap;
-import java.util.HashSet;
-import java.util.List;
-import java.util.Set;
-import me.grea.antoine.soda.type.Action;
-import me.grea.antoine.soda.type.Edge;
-import me.grea.antoine.soda.type.Problem;
-import org.jgrapht.alg.StrongConnectivityInspector;
-import static me.grea.antoine.soda.utils.Collections.*;
-
-/**
- *
- * @author antoine
- */
-public class Cycle extends Defect {
-
-    Set<Action> cycling;
-
-    public Cycle(Set<Action> cycling, Problem problem) {
-        super(problem);
-        this.cycling = cycling;
-    }
-
-    @Override
-    public void fix() {
-        for (Action action : cycling) {
-            for (Edge edge : problem.plan.edgesOf(action)) {
-                if (cycling.contains(problem.plan.getEdgeTarget(edge))) {
-
-                    problem.plan.removeEdge(edge);
-                    return;
-                }
-            }
-        } // already solved
-    }
-
-    public static Set<Cycle> find(Problem problem) {
-        List<Set<Action>> components = new StrongConnectivityInspector<>(problem.plan).stronglyConnectedSets();
-
-        // A vertex participates in a cycle if either of the following is
-        // true:  (a) it is in a component whose size is greater than 1
-        // or (b) it is a self-loop
-        Set<Cycle> cycles = set();
-        for (Set<Action> component : components) {
-            if (component.size() > 1) {
-                // cycle
-                cycles.add(new Cycle(component, problem));
-            } else {
-                Action action = component.iterator().next();
-                if (problem.plan.containsEdge(action, action)) {
-                    // self-loop
-                    cycles.add(new Cycle(component, problem));
-                }
-            }
-        }
-        return cycles;
-    }
-
-    @Override
-    public String toString() {
-        return "Actions " + cycling + " forms a cycle";
-    }
-
-}

### 2016-01-03 src/me/grea/antoine/soda/type/defect/Defect.java

@@ -1,39 +1,0 @@
-/*
- * To change this license header, choose License Headers in Project Properties.
- * To change this template file, choose Tools | Templates
- * and open the template in the editor.
- */
-package me.grea.antoine.soda.type.defect;
-
-import java.util.Deque;
-import me.grea.antoine.soda.type.Action;
-import me.grea.antoine.soda.type.Problem;
-import me.grea.antoine.soda.type.flaw.Resolver;
-
-/**
- *
- * @author antoine
- */
-public abstract class Defect {
-
-    public final Problem problem;
-
-    public Defect(Problem problem) {
-        this.problem = problem;
-    }
-
-    public abstract void fix();
-
-    public static double usefullness(Action action, Problem problem) {
-        return action.fake ? 0.0
-                : action == problem.goal
-                || action == problem.initial
-                || problem.plan.inDegreeOf(action) == 0
-                ? Double.POSITIVE_INFINITY
-                : problem.plan.outDegreeOf(action) / (double) problem.plan.inDegreeOf(action);
-    }
-
-    @Override
-    public abstract String toString();
-
-}

### 2016-01-03 src/me/grea/antoine/soda/type/defect/InconsistentAction.java

@@ -1,120 +1,0 @@
-/*
- * To change this license header, choose License Headers in Project Properties.
- * To change this template file, choose Tools | Templates
- * and open the template in the editor.
- */
-package me.grea.antoine.soda.type.defect;
-
-import java.util.HashMap;
-import java.util.HashSet;
-import java.util.Map;
-import java.util.Set;
-import me.grea.antoine.log.Log;
-import me.grea.antoine.soda.type.Action;
-import me.grea.antoine.soda.type.Edge;
-import me.grea.antoine.soda.type.Problem;
-import static me.grea.antoine.soda.utils.Collections.set;
-import static me.grea.antoine.soda.utils.Collections.union;
-
-/**
- *
- * @author antoine
- */
-public class InconsistentAction extends Defect {
-
-    public Action inconsistent;
-    public Set<Integer> preconditions;
-    public Set<Integer> effects;
-
-    public InconsistentAction(Action inconsistent, Set<Integer> preconditions, Set<Integer> effects, Problem problem) {
-        super(problem);
-        this.inconsistent = inconsistent;
-        this.preconditions = preconditions;
-        this.effects = effects;
-    }
-
-    @Override
-    public void fix() {
-        Set<Integer> outGoing = set();
-        if (problem.plan.containsVertex(inconsistent)) {
-            for (Edge edge : problem.plan.outgoingEdgesOf(inconsistent)) {
-                outGoing.addAll(edge.labels);
-            }
-        }
-        Set<Integer> inComing = set();
-        if (problem.plan.containsVertex(inconsistent)) {
-            for (Edge edge : problem.plan.incomingEdgesOf(inconsistent)) {
-                inComing.addAll(edge.labels);
-            }
-        }
-
-        for (int precondition : preconditions) {
-            if (inComing.contains(precondition) && inComing.contains(-precondition)) {
-                inconsistent.preconditions.remove(precondition);
-                inComing.remove(precondition);
-            } else if (inComing.contains(precondition)) {
-                inconsistent.preconditions.remove(-precondition);
-                inComing.remove(-precondition);
-            } else {
-                inconsistent.preconditions.remove(precondition);
-                inComing.remove(precondition);
-                inconsistent.preconditions.remove(-precondition);
-                inComing.remove(-precondition);
-            }
-        }
-        for (int effect : effects) {
-            if (inComing.contains(effect) && inComing.contains(-effect)) {
-                inconsistent.effects.remove(effect);
-                inComing.remove(effect);
[…]

### 2016-01-03 src/me/grea/antoine/soda/type/defect/LiarLink.java

@@ -1,72 +1,0 @@
-/*
- * To change this license header, choose License Headers in Project Properties.
- * To change this template file, choose Tools | Templates
- * and open the template in the editor.
- */
-package me.grea.antoine.soda.type.defect;
-
-import java.util.HashSet;
-import java.util.Map;
-import java.util.Set;
-import me.grea.antoine.log.Log;
-import me.grea.antoine.soda.type.Action;
-import me.grea.antoine.soda.type.Edge;
-import me.grea.antoine.soda.type.Problem;
-import static me.grea.antoine.soda.utils.Collections.difference;
-import static me.grea.antoine.soda.utils.Collections.union;
-
-/**
- *
- * @author antoine
- */
-public class LiarLink extends Defect {
-
-    public Edge liar;
-    public Set<Integer> lies;
-    public Set<Integer> saviours;
-
-    public LiarLink(Edge liar, Set<Integer> lies, Set<Integer> saviours, Problem problem) {
-        super(problem);
-        this.liar = liar;
-        this.lies = lies;
-        this.saviours = saviours;
-    }
-
-    @Override
-    public void fix() {
-        liar.labels.removeAll(lies);
-        liar.labels.addAll(saviours);
-        if (liar.labels.isEmpty()) {
-            problem.plan.removeEdge(liar);
-        }
-    }
-
-    public static Set<LiarLink> find(Problem problem) {
-        Set<LiarLink> result = new HashSet<>();
-        for (Edge edge : problem.plan.edgeSet()) {
-            LiarLink liarLink = is(edge, problem);
-            if (liarLink != null) {
-                result.add(liarLink);
-            }
-        }
-        return result;
-    }
-
-    public static LiarLink is(Edge edge, Problem problem) {
-        Set<Integer> common = union(
-                problem.plan.getEdgeSource(edge).effects,
-                problem.plan.getEdgeTarget(edge).preconditions);
-        Set<Integer> lies = difference(edge.labels, common);
-        if (lies.isEmpty()) {
-            return null;
-        }
-        return new LiarLink(edge, lies, difference(common, edge.labels), problem);
-
-    }
-
-    @Override
-    public String toString() {
-        return  "Link " + liar + " is lying about " + lies + " without mentioning " + saviours;
-    }
-
-}

### 2016-01-03 src/me/grea/antoine/soda/type/defect/RedundantLink.java

@@ -1,62 +1,0 @@
-/*
- * To change this license header, choose License Headers in Project Properties.
- * To change this template file, choose Tools | Templates
- * and open the template in the editor.
- */
-package me.grea.antoine.soda.type.defect;
-
-import java.util.HashSet;
-import java.util.Set;
-import me.grea.antoine.soda.type.Action;
-import me.grea.antoine.soda.type.Edge;
-import me.grea.antoine.soda.type.Problem;
-import static me.grea.antoine.soda.utils.Collections.set;
-
-/**
- *
- * @author antoine
- */
-public class RedundantLink extends Defect {
-
-    public Edge redundant;
-
-    public RedundantLink(Edge redundant, Problem problem) {
-        super(problem);
-        this.redundant = redundant;
-    }
-
-    @Override
-    public void fix() {
-        problem.plan.removeEdge(redundant);
-    }
-
-    public static Set<RedundantLink> find(Problem problem) {
-        Set<RedundantLink> result = new HashSet<>();
-        for (Edge edge : problem.plan.edgeSet()) {
-            RedundantLink redundantLink = is(edge, problem);
-            if (redundantLink != null) {
-                result.add(redundantLink);
-            }
-        }
-        return result;
-    }
-
-    public static RedundantLink is(Edge edge, Problem problem) {
-        if (edge.labels.isEmpty()) {
-            Action source = problem.plan.getEdgeSource(edge);
-            Action target = problem.plan.getEdgeTarget(edge);
-//            problem.plan.removeEdge(edge);
-            if (problem.plan.reachable(source, target, set(edge))) {
-                return new RedundantLink(edge, problem);
-            }
-//            problem.plan.addEdge(source, target, edge);
-        }
-        return null;
-    }
-
-    @Override
-    public String toString() {
-        return "Link " + redundant + " is redundant";
-    }
-
-}

### 2016-01-03 src/me/grea/antoine/soda/type/flaw/Alternative.java

@@ -1,0 +1,108 @@
+/*
+ * To change this license header, choose License Headers in Project Properties.
+ * To change this template file, choose Tools | Templates
+ * and open the template in the editor.
+ */
+package me.grea.antoine.soda.type.flaw;
+
+import java.util.Deque;
+import java.util.HashMap;
+import java.util.HashSet;
+import java.util.Map;
+import java.util.Set;
+import me.grea.antoine.soda.heuristic.Usefullness;
+import me.grea.antoine.soda.type.Action;
+import me.grea.antoine.soda.type.Edge;
+import me.grea.antoine.soda.type.Problem;
+import static me.grea.antoine.utils.Collections.queue;
+import static me.grea.antoine.utils.Collections.set;
+import me.grea.antoine.utils.Log;
+
+/**
+ *
+ * @author antoine
+ */
+public class Alternative extends Flaw {
+
+    public Action provider;
+    private static final Map<Problem, Map<Integer, Deque<Resolver>>> cache = new HashMap<>();
+
+    public Alternative(int fluent, Action provider, Action needer, Problem problem) {
+        super(fluent, needer, problem);
+        this.provider = provider;
+    }
+
+    @Override
+    public Deque<Resolver> resolvers() {
+        return queue(new Resolver(provider, needer, fluent, true));
+    }
+
+    public static Set<Alternative> find(Problem problem) {
+        Set<Alternative> alternatives = new HashSet<>();
+        Map<Integer, Deque<Resolver>> competitors = cache.get(problem);
+        if (competitors == null) {
+            competitors = new HashMap<>();
+            cache.put(problem, competitors);
+        }
+        for (Edge edge : problem.plan.edgeSet()) {
+            Action provider = problem.plan.getEdgeSource(edge);
+            Action needer = problem.plan.getEdgeTarget(edge);
+            for (Integer label : edge.labels) {
+                Deque<Resolver> resolvers;
+                if (competitors.containsKey(label)) {
+                    resolvers = competitors.get(label);
+                } else {
+                    resolvers = new SubGoal(label, needer, problem).resolvers();
+                    competitors.put(label, resolvers);
+                }
+                for (Resolver resolver : resolvers) {
+                    if (!provider.equals(resolver.source) && Usefullness.h(problem, provider) < Usefullness.h(problem, resolver.source)) {
+                        Log.d("⎇ " + resolver.source + " is more usefull for " + edge);
[…]

### 2016-01-03 src/me/grea/antoine/soda/type/flaw/Orphan.java

@@ -1,0 +1,73 @@
+/*
+ * To change this license header, choose License Headers in Project Properties.
+ * To change this template file, choose Tools | Templates
+ * and open the template in the editor.
+ */
+package me.grea.antoine.soda.type.flaw;
+
+import java.util.ArrayDeque;
+import java.util.Deque;
+import java.util.HashSet;
+import java.util.Set;
+import me.grea.antoine.soda.type.Action;
+import me.grea.antoine.soda.type.Edge;
+import me.grea.antoine.soda.type.Plan;
+import me.grea.antoine.soda.type.Problem;
+import me.grea.antoine.utils.Collections;
+import static me.grea.antoine.utils.Collections.set;
+import static me.grea.antoine.utils.Collections.queue;
+
+/**
+ *
+ * @author antoine
+ */
+public class Orphan extends Flaw {
+
+    public Orphan(Action orphan, Problem problem) {
+        super(0, orphan, problem);
+    }
+
+    @Override
+    public Deque<Resolver> resolvers() {
+        return queue(new Resolver(needer, null, 0, true));
+    }
+
+    public static Set<Orphan> find(Problem problem) {
+        Set<Orphan> orphans = new HashSet<>();
+        problem.plan.vertexSet().stream().filter((candidate)
+                -> (problem.plan.outDegreeOf(candidate) == 0
+                && !problem.goal.equals(candidate)
+                && !problem.initial.equals(candidate))
+        ).forEach((candidate) -> {
+            orphans.add(new Orphan(candidate, problem));
+        });
+        return orphans;
+    }
+
+    @Override
+    public Set<Resolver> healers() {
+        return set();
+    }
+
+    public static int count(Problem problem) {
+        return (int) problem.plan.vertexSet().stream().filter((candidate)
+                -> (problem.plan.outDegreeOf(candidate) == 0
+                && !problem.goal.equals(candidate)
+                && !problem.initial.equals(candidate))
+        ).count();
+    }
+
+    public static Set<Orphan> related(Set<Action> children, Problem problem) {
+        Set<Orphan> related = new HashSet<>();
+        children.stream().filter((child) -> (problem.plan.outDegreeOf(child) == 0)).forEach((child) -> {
+            related.add(new Orphan(child, problem));
+        });
+        return related;
+    }
+
+    @Override
+    public String toString() {
+        return "☹ " + needer;
+    }
+
+}

### 2016-01-03 src/me/grea/antoine/soda/type/flaw/Resolver.java

@@ -5,39 +5,72 @@
  */
 package me.grea.antoine.soda.type.flaw;
 
-import me.grea.antoine.soda.type.flaw.SubGoal;
-import me.grea.antoine.soda.type.flaw.Threat;
 import java.util.HashSet;
 import java.util.Set;
-import me.grea.antoine.log.Log;
 import me.grea.antoine.soda.type.Action;
 import me.grea.antoine.soda.type.Edge;
 import me.grea.antoine.soda.type.Plan;
 import me.grea.antoine.soda.type.Problem;
-import org.jgrapht.DirectedGraph;
-import static me.grea.antoine.soda.utils.Collections.*;
+import static me.grea.antoine.utils.Collections.*;
 
 /**
  *
  * @author antoine
  */
-public class Resolver {
+public class Resolver { // TODO : Put in interface and make that an additive resolver then make the alternative resolver and then the substracting resolver
 
     public Action source;
     public Action target;
     public int fluent;
+    public boolean negative = false;
     private Edge edge;
+    private boolean edgeCreated = false;
+    private boolean sourceCreated = false;
+    private boolean targetCreated = false;
+    private Set<Action> posibleOrphans = new HashSet<>();
 
-    public Resolver(Action source, Action target, int fluent) {
+    public Resolver(Action source, Action target, int fluent, boolean negative) {
         this.source = source;
         this.target = target;
         this.fluent = fluent;
+        this.negative = negative;
+    }
+
+    public Resolver(Action source, Action target, int fluent) {
+        this(source, target, fluent, false);
+    }
+
+    public Resolver(Action source, Action target) {
+        this(source, target, 0);
     }
 
     public void apply(Plan plan) {
-        plan.addVertex(source);
-        plan.addVertex(target);
+        if (negative) {
+            edge = plan.getEdge(source, target);
+            if (edge == null) {
+                for (Edge child : plan.incomingEdgesOf(source)) {
+                    posibleOrphans.add(plan.getEdgeSource(child));
+                }
+                plan.removeVertex(source);
+                return;
+            }
+            if (edge.labels.equals(set(fluent))) {
+                posibleOrphans.add(source);
+                plan.removeEdge(edge);
+            } else {
+                edge.labels.remove(fluent);
+            }
+            return;
+        }
+        if(fluent == 0 && plan.reachable(source, target))
+        {
+            return;
+        }
+        
+        sourceCreated = plan.addVertex(source);
+        targetCreated = plan.addVertex(target);
[…]

### 2016-01-03 src/me/grea/antoine/soda/utils/Collections.java

@@ -1,85 +1,0 @@
-/*
- * To change this license header, choose License Headers in Project Properties.
- * To change this template file, choose Tools | Templates
- * and open the template in the editor.
- */
-package me.grea.antoine.soda.utils;
-
-import java.util.ArrayDeque;
-import java.util.ArrayList;
-import java.util.Arrays;
-import java.util.Collection;
-import java.util.Deque;
-import java.util.HashSet;
-import java.util.List;
-import java.util.Map;
-import java.util.Set;
-import jdk.nashorn.internal.runtime.arrays.ArrayLikeIterator;
-
-/**
- *
- * @author
- * http://www.java2s.com/Code/Java/Collections-Data-Structure/Setoperationsunionintersectiondifferencesymmetricdifferenceissubsetissuperset.htm
- */
-public class Collections {
-
-    public static <T> List<T> concat(Collection<? extends T>... collections) {
-        List<T> tmp = new ArrayList<>();
-        for (Collection<? extends T> collection : collections) {
-            tmp.addAll(collection);
-        }
-        return tmp;
-    }
-    
-    public static <T> Set<T> union(Set<? extends T>... sets) {
-        Set<T> tmp = new HashSet<>();
-        for (Set<? extends T> set : sets) {
-            tmp.addAll(set);
-        }
-        return tmp;
-    }
-
-    public static <T> Set<T> intersection(Set<? extends T>... sets) {
-        Set<T> tmp = new HashSet<>(sets[0]);
-        for (Set<? extends T> set : sets) {
-            tmp.retainAll(set);
-        }
-        return tmp;
-    }
-
-    public static <T> Set<T> difference(Set<? extends T> setA, Set<? extends T> setB) {
-        Set<T> tmp = new HashSet<>(setA);
-        tmp.removeAll(setB);
-        return tmp;
-    }
-
-    public static <T> Set<T> symDifference(Set<? extends T> setA, Set<? extends T> setB) {
-        Set<T> tmpA;
-        Set<T> tmpB;
-
-        tmpA = union(setA, setB);
-        tmpB = intersection(setA, setB);
-        return difference(tmpA, tmpB);
-    }
-
-    public static <T> boolean isSubset(Set<? extends T> setA, Set<? extends T> setB) {
-        return setB.containsAll(setA);
-    }
-
-    public static <T> boolean isSuperset(Set<? extends T> setA, Set<? extends T> setB) {
[…]

### 2016-01-03 src/me/grea/antoine/soda/utils/Stats.java

@@ -14,12 +14,11 @@ import java.util.List;
  * @author antoine
  */
 public class Stats {
-    
-    public static Double average(Collection<? extends Number> collection)
-    {
+
+    public static Double average(Collection<? extends Number> collection) {
         return (Double) sum(collection) / collection.size();
     }
-    
+
     public static <T extends Number> T sum(Collection<T> collection) {
         T sum = (T) (Number) (Integer) 0;
         for (T item : collection) {
@@ -27,5 +26,5 @@ public class Stats {
         }
         return sum;
     }
-    
+
 }

### 2016-01-28 src/me/grea/antoine/lolipop/algorithm/Correlator.java
LOLIPOP : Start of Project based on SODA

@@ -1,0 +1,110 @@
+/*
+ * To change this license header, choose License Headers in Project Properties.
+ * To change this template file, choose Tools | Templates
+ * and open the template in the editor.
+ */
+package me.grea.antoine.lolipop.algorithm;
+
+import java.util.HashSet;
+import java.util.List;
+import java.util.Map;
+import java.util.Set;
+import org.jgrapht.DirectedGraph;
+import me.grea.antoine.lolipop.type.Action;
+import me.grea.antoine.lolipop.type.Edge;
+import me.grea.antoine.lolipop.type.Goal;
+import me.grea.antoine.lolipop.type.Plan;
+import me.grea.antoine.utils.Collections;
+
+/**
+ *
+ * @author antoine
+ */
+public class Correlator {
+
+    public Map<Set<Goal>, List<Count>> correlation;
+
+    private static int countProperties(Plan plan1) {
+        int count = 0;
+        count = plan1.vertexSet().stream().map((action)
+                -> action.preconditions.size() + action.effects.size()
+        ).reduce(count, Integer::sum);
+        return count;
+    }
+
+    private static Set<Integer> preconditions(Plan plan1) {
+        Set<Integer> properties = new HashSet();
+        for (Action action : plan1.vertexSet()) {
+            properties.addAll(action.preconditions);
+        }
+        return properties;
+    }
+
+    private static Set<Integer> effects(Plan plan1) {
+        Set<Integer> properties = new HashSet();
+        for (Action action : plan1.vertexSet()) {
+            properties.addAll(action.effects);
+        }
+        return properties;
+    }
+
+    public static class Count {
+
+        public int properties;
+        public int actions;
+
+        public Count() {
+            this(0, 0);
+        }
+
+        public Count(int properties, int actions) {
+            this.properties = properties;
+            this.actions = actions;
+        }
+
+        @Override
+        public String toString() {
+            return "#p=" + properties + "#a=" + actions;
+        }
+
+        public Count min(Count other) {
+            return new Count(Math.min(properties, other.properties),
+                    Math.min(actions, other.actions));
+        }
+
+        public double correlation(Count divisor) {
+            return (((double) properties) / divisor.properties)
+                    * (((double) actions) / divisor.actions);
+        }
+
+    }
+
+    public double correlation(Plan plan1, Plan plan2) {
+        Count total = new Count(countProperties(plan1), plan1.vertexSet().size()).min(
+                new Count(countProperties(plan2), plan2.vertexSet().size()));
[…]

### 2016-01-28 src/me/grea/antoine/lolipop/algorithm/IllegalFixer.java

@@ -1,0 +1,179 @@
+/*
+ * To change this license header, choose License Headers in Project Properties.
+ * To change this template file, choose Tools | Templates
+ * and open the template in the editor.
+ */
+package me.grea.antoine.lolipop.algorithm;
+
+import java.util.Collections;
+import java.util.HashSet;
+import java.util.List;
+import java.util.Set;
+import me.grea.antoine.lolipop.heuristic.Usefullness;
+import me.grea.antoine.lolipop.type.Action;
+import me.grea.antoine.lolipop.type.Edge;
+import me.grea.antoine.lolipop.type.Problem;
+import static me.grea.antoine.utils.Collections.difference;
+import static me.grea.antoine.utils.Collections.intersection;
+import static me.grea.antoine.utils.Collections.set;
+import static me.grea.antoine.utils.Collections.union;
+import me.grea.antoine.utils.Log;
+import org.jgrapht.alg.StrongConnectivityInspector;
+
+/**
+ *
+ * @author antoine
+ */
+public class IllegalFixer {
+
+    public static void clean(Problem problem) {
+        for (Action action : union(problem.actions, problem.plan.vertexSet())) {
+            fixAction(action, problem);
+        }
+
+        for (Edge edge : new HashSet<>(problem.plan.edgeSet())) {
+            fixEdge(edge, problem);
+        }
+
+//        fixCycles(problem);
+    }
+
+    private static Set<Integer> lies(Edge edge, Action source, Action target) {
+        return difference(edge.labels, intersection(source.effects, target.preconditions));
+    }
+
+    private static Set<Integer> saviours(Edge edge, Action source, Action target) {
+        return difference(intersection(source.effects, target.preconditions), edge.labels);
+    }
+
+    private static Set<Integer> toxicEffects(Action action) {
+        Set<Integer> effects = intersection(action.preconditions, action.effects);
+        if (effects.isEmpty()) {
+            return set();
+        }
+        return effects;
+    }
+
+    private static Set<Integer> inconsistentEffects(Action action) {
+        Set<Integer> effects = new HashSet<>();
+        for (int fluent : action.effects) {
+            if (action.effects.contains(-fluent)) {
+                effects.add(fluent);
+            }
+        }
+        return effects;
+    }
+
+    private static Set<Integer> inconsistentPrecondition(Action action) {
+        Set<Integer> preconditions = new HashSet<>();
+        for (int fluent : action.effects) {
+            if (action.preconditions.contains(-fluent)) {
+                preconditions.add(fluent);
+            }
[…]

### 2016-01-28 src/me/grea/antoine/lolipop/algorithm/PartialOrderOptimizedPlanning.java

@@ -1,0 +1,151 @@
+/*
+ * To change this license header, choose License Headers in Project Properties.
+ * To change this template file, choose Tools | Templates
+ * and open the template in the editor.
+ */
+package me.grea.antoine.lolipop.algorithm;
+
+import java.util.ArrayDeque;
+import java.util.Deque;
+import java.util.HashSet;
+import java.util.Set;
+import me.grea.antoine.utils.Log;
+import me.grea.antoine.lolipop.exception.Success;
+import me.grea.antoine.lolipop.type.Action;
+import me.grea.antoine.lolipop.type.PartialSolution;
+import me.grea.antoine.lolipop.type.Plan;
+import me.grea.antoine.lolipop.type.flaw.Flaw;
+import me.grea.antoine.lolipop.type.Problem;
+import me.grea.antoine.lolipop.type.flaw.Alternative;
+import me.grea.antoine.lolipop.type.flaw.Orphan;
+import me.grea.antoine.lolipop.type.flaw.Resolver;
+import me.grea.antoine.lolipop.type.flaw.SubGoal;
+import me.grea.antoine.lolipop.type.flaw.Threat;
+
+/**
+ *
+ * @author antoine
+ */
+public class PartialOrderOptimizedPlanning {
+
+    private final Problem problem;
+    private final Deque<Flaw> agenda = new ArrayDeque<>();
+    private final Deque<PartialSolution> partialSolutions = new ArrayDeque<>();
+
+    public PartialOrderOptimizedPlanning(Problem problem) {
+        this.problem = problem;
+        IllegalFixer.clean(problem);
+        populateAgenda();
+    }
+
+    private void populateAgenda() {
+        agenda.addAll(Alternative.find(problem));
+        agenda.addAll(SubGoal.find(problem));
+        agenda.addAll(Threat.find(problem));
+        agenda.addAll(Orphan.find(problem));
+    }
+
+    public static void solve(Problem problem) {
+        PartialOrderOptimizedPlanning pop = new PartialOrderOptimizedPlanning(problem);
+        while (true) {
+            try {
+                pop.refine();
+            } catch (Success ex) {
+                Log.i("Success !");
+                return;
+            }
+            Log.w("Failure");
+            pop.soft();
+        }
+    }
+
+    public void refine() throws Success {
+        if (agenda.isEmpty()) {
+            throw new Success();
+        }
+        Log.d("Agenda " + agenda);
[…]

### 2016-01-28 src/me/grea/antoine/lolipop/algorithm/PartialOrderPlanning.java

@@ -1,0 +1,86 @@
+/*
+ * To change this license header, choose License Headers in Project Properties.
+ * To change this template file, choose Tools | Templates
+ * and open the template in the editor.
+ */
+package me.grea.antoine.lolipop.algorithm;
+
+import java.util.ArrayDeque;
+import java.util.Deque;
+import java.util.Set;
+import me.grea.antoine.utils.Log;
+import me.grea.antoine.lolipop.exception.Failure;
+import me.grea.antoine.lolipop.exception.Success;
+import me.grea.antoine.lolipop.type.PartialSolution;
+import me.grea.antoine.lolipop.type.flaw.Flaw;
+import me.grea.antoine.lolipop.type.Problem;
+import me.grea.antoine.lolipop.type.flaw.Resolver;
+import me.grea.antoine.lolipop.type.flaw.SubGoal;
+import me.grea.antoine.lolipop.type.flaw.Threat;
+import org.jgrapht.alg.CycleDetector;
+
+/**
+ *
+ * @author antoine
+ */
+public class PartialOrderPlanning {
+
+    private final Problem problem;
+    private final Deque<Flaw> agenda = new ArrayDeque<>();
+
+    public PartialOrderPlanning(Problem problem) {
+        this.problem = problem;
+        populate(agenda, problem);
+    }
+
+    private static void populate(Deque<Flaw> agenda, Problem problem) {
+        agenda.addAll(SubGoal.find(problem));
+        agenda.addAll(Threat.find(problem));
+    }
+
+    public static void solve(Problem problem) throws Failure {
+        PartialOrderPlanning pop = new PartialOrderPlanning(problem);
+        try {
+            pop.refine();
+        } catch (Success ex) {
+        }
+        //Logically shouldn't go there
+    }
+
+    public void refine() throws Success, Failure {
+//        Log.d("Agenda " + agenda);
+        if (agenda.isEmpty()) {
+            throw new Success();
+        }
+        Flaw flaw = agenda.pop();
+//        Log.d("Resolving " + flaw);
+        Deque<Resolver> resolvers = flaw.resolvers();
+//        Log.d("Resolver " + resolvers);
+        for (Resolver resolver : resolvers) {
+//            Log.d("Trying with " + resolver);
+
+            if (resolver.appliable(problem.plan)) {
+                resolver.apply(problem.plan);
+            } else {
+                continue;
+            }
+
+            if (!new CycleDetector<>(problem.plan).detectCyclesContainingVertex(resolver.target)) {
[…]

### 2016-01-28 src/me/grea/antoine/lolipop/algorithm/ProperPlan.java

@@ -1,0 +1,68 @@
+/*
+ * To change this license header, choose License Headers in Project Properties.
+ * To change this template file, choose Tools | Templates
+ * and open the template in the editor.
+ */
+package me.grea.antoine.lolipop.algorithm;
+
+import java.util.ArrayDeque;
+import java.util.Deque;
+import java.util.HashSet;
+import java.util.Set;
+import me.grea.antoine.lolipop.type.Action;
+import me.grea.antoine.lolipop.type.Edge;
+import me.grea.antoine.lolipop.type.Goal;
+import me.grea.antoine.lolipop.type.Plan;
+import static me.grea.antoine.utils.Collections.*;
+
+/**
+ *
+ * @author antoine
+ */
+public class ProperPlan {
+
+    public static Plan properPlan(Goal goal, Set<Action> actions) {
+        Plan plan = new Plan();
+        Set<Action> relevants = satisfy(goal, actions, plan);
+        /* The satisfy function iterate throught 
+        participating actions and add the causal links */
+        Deque<Action> open = new ArrayDeque<>(relevants);
+        //queue of opened relevant actions
+        while (!open.isEmpty()) {
+            Action action = open.pop();
+            Set<Action> candidates = satisfy(action, actions, plan);
+            /* Searching for candidates that satisfy 
+            the selected providing action*/
+            for (Action candidate : candidates) {
+                if (!relevants.contains(candidate)) {
+                    /* Only the one not threated already 
+                    are added to ensure convergence */
+                    open.push(candidate);
+                }
+            }
+            relevants.addAll(candidates);
+        }
+        return plan;
+    }
+
+    private static Set<Action> satisfy(Goal goal, Set<Action> actions, Plan plan) {
+        Set<Action> relevants = new HashSet<>();
+        plan.addVertex((Action) goal);
+        for (int precondition : goal.preconditions) {
+            for (Action action : actions) {
+                if (action.effects.contains(precondition) && action != goal) {
+                    plan.addVertex(action);
+                    Edge edge = plan.addEdge(action, (Action) goal);
+                    if (edge != null) {
+                        edge.labels = set(precondition);
+                    } else {
+                        plan.getEdge(action, (Action) goal).labels.add(precondition);
+                    }
+                    relevants.add(action);
+                }
+            }
+        }
+        return relevants;
+    }
+
+}

### 2016-01-28 src/me/grea/antoine/lolipop/exception/Success.java

@@ -1,0 +1,24 @@
+/*
+ * To change this license header, choose License Headers in Project Properties.
+ * To change this template file, choose Tools | Templates
+ * and open the template in the editor.
+ */
+package me.grea.antoine.lolipop.exception;
+
+/**
+ *
+ * @author antoine
+ */
+public class Success extends Exception {
+
+    public Success() {
+    }
+
+    @Override
+    public String toString() {
+        return "Success !";
+    }
+    
+    
+
+}

### 2016-01-28 src/me/grea/antoine/lolipop/test/CrazyProblemGenerator.java

@@ -1,0 +1,48 @@
+/*
+ * To change this license header, choose License Headers in Project Properties.
+ * To change this template file, choose Tools | Templates
+ * and open the template in the editor.
+ */
+package me.grea.antoine.lolipop.test;
+
+import me.grea.antoine.utils.Dice;
+import java.util.HashSet;
+import java.util.Set;
+import me.grea.antoine.lolipop.type.Action;
+import me.grea.antoine.lolipop.type.Edge;
+import me.grea.antoine.lolipop.type.Plan;
+import me.grea.antoine.lolipop.type.Problem;
+
+/**
+ *
+ * @author antoine
+ */
+public class CrazyProblemGenerator {
+
+    public static Set<Problem> generate(int enthropy, int number) {
+        Set<Problem> problems = new HashSet<>(number);
+        while (problems.size() < number) {
+            Problem problem = new Problem(
+                    new Action(null, Dice.rollNonZero(-enthropy, enthropy, enthropy / 3)),
+                    new Action(Dice.rollNonZero(-enthropy, enthropy, enthropy / 2), null),
+                    CrazyActionGenerator.generate(enthropy, Dice.roll(enthropy)),
+                    new Plan()
+            );
+            for (int i = 0; i < problem.actions.size() / 2; i++) {
+                Action source = Dice.pick(problem.actions);
+                Action target = Dice.pick(problem.actions);
+                problem.plan.addVertex(source);
+                problem.plan.addVertex(target);
+                Edge edge = problem.plan.addEdge(source, target);
+                if (edge == null) {
+                    problem.plan.getEdge(source, target).labels.addAll(source.effects);
+                } else {
+                    edge.labels = source.effects;
+                }
+            }
+            problems.add(problem);
+        }
+        return problems;
+    }
+
+}

### 2016-01-28 src/me/grea/antoine/lolipop/test/RandomTest.java

@@ -1,0 +1,55 @@
+/*
+ * To change this license header, choose License Headers in Project Properties.
+ * To change this template file, choose Tools | Templates
+ * and open the template in the editor.
+ */
+package me.grea.antoine.lolipop.test;
+
+import java.io.File;
+import java.io.FileNotFoundException;
+import java.io.PrintStream;
+import java.time.LocalDateTime;
+import java.util.Set;
+import me.grea.antoine.lolipop.algorithm.PartialOrderOptimizedPlanning;
+import me.grea.antoine.lolipop.type.Problem;
+import me.grea.antoine.utils.Chrono;
+import me.grea.antoine.utils.Log;
+
+/**
+ *
+ * @author antoine
+ */
+public class RandomTest {
+    
+    public static void main(String... args)
+    {
+        Log.level = Log.Level.ERROR;
+        Chrono chrono = new Chrono();
+        int number = 10000;
+//        File file = new File(LocalDateTime.now() + "_" + RandomTest.class + ".csv");
+//        System.out.println(file.getAbsolutePath());
+//        try (PrintStream result = new PrintStream(file)) {
+            //echaufement
+            Set<Problem> problems = CrazyProblemGenerator.generate(20, 400);
+            for (Problem problem : problems) {
+                PartialOrderOptimizedPlanning.solve(problem);
+            }
+//            for (int i = 1; i < 100; i++) {
+//                problems = CrazyProblemGenerator.generate(i, number);
+//                for (Problem problem : problems) {
+//                    chrono.start();
+//                    PartialOrderOptimizedPlanning.solve(problem);
+//                    chrono.stop();
+//                }
+//                System.out.println(i + " => " + chrono);
+////                result.println(i + "," + chrono.total / number);
+//                chrono.reset();
+//            }
+//            result.println("Iterations/enthropy : " + number);
+//            result.close();
+//        } catch (FileNotFoundException ex) {
+//            Log.e(ex);
+//        }
+    }
+    
+}

### 2016-01-28 src/me/grea/antoine/lolipop/type/Edge.java

@@ -1,0 +1,25 @@
+/*
+ * To change this license header, choose License Headers in Project Properties.
+ * To change this template file, choose Tools | Templates
+ * and open the template in the editor.
+ */
+package me.grea.antoine.lolipop.type;
+
+import java.util.HashSet;
+import java.util.Set;
+import org.jgrapht.graph.DefaultEdge;
+
+/**
+ *
+ * @author antoine
+ */
+public class Edge extends DefaultEdge {
+
+    public Set<Integer> labels = new HashSet<>();
+
+    @Override
+    public String toString() {
+        return getSource() + " -" + (labels.isEmpty() ? "☠" : labels) + "> " + getTarget();
+    }
+
+}

### 2016-01-28 src/me/grea/antoine/lolipop/type/PartialSolution.java

@@ -1,0 +1,28 @@
+/*
+ * To change this license header, choose License Headers in Project Properties.
+ * To change this template file, choose Tools | Templates
+ * and open the template in the editor.
+ */
+package me.grea.antoine.lolipop.type;
+
+import java.util.ArrayDeque;
+import java.util.Deque;
+import me.grea.antoine.lolipop.type.flaw.Flaw;
+
+/**
+ *
+ * @author antoine
+ */
+public class PartialSolution {
+
+    public Plan plan;
+    public Flaw cause;
+    public Deque<Flaw> remaining;
+
+    public PartialSolution(Plan plan, Flaw cause, Deque<Flaw> remaining) {
+        this.plan = new Plan(plan);
+        this.cause = cause;
+        this.remaining = new ArrayDeque<>(remaining);
+    }
+
+}

### 2016-01-28 src/me/grea/antoine/lolipop/type/flaw/Alternative.java

@@ -1,0 +1,108 @@
+/*
+ * To change this license header, choose License Headers in Project Properties.
+ * To change this template file, choose Tools | Templates
+ * and open the template in the editor.
+ */
+package me.grea.antoine.lolipop.type.flaw;
+
+import java.util.Deque;
+import java.util.HashMap;
+import java.util.HashSet;
+import java.util.Map;
+import java.util.Set;
+import me.grea.antoine.lolipop.heuristic.Usefullness;
+import me.grea.antoine.lolipop.type.Action;
+import me.grea.antoine.lolipop.type.Edge;
+import me.grea.antoine.lolipop.type.Problem;
+import static me.grea.antoine.utils.Collections.queue;
+import static me.grea.antoine.utils.Collections.set;
+import me.grea.antoine.utils.Log;
+
+/**
+ *
+ * @author antoine
+ */
+public class Alternative extends Flaw {
+
+    public Action provider;
+    private static final Map<Problem, Map<Integer, Deque<Resolver>>> cache = new HashMap<>();
+
+    public Alternative(int fluent, Action provider, Action needer, Problem problem) {
+        super(fluent, needer, problem);
+        this.provider = provider;
+    }
+
+    @Override
+    public Deque<Resolver> resolvers() {
+        return queue(new Resolver(provider, needer, fluent, true));
+    }
+
+    public static Set<Alternative> find(Problem problem) {
+        Set<Alternative> alternatives = new HashSet<>();
+        Map<Integer, Deque<Resolver>> competitors = new HashMap<>();//cache.get(problem);
+//        if (competitors == null) {
+//            competitors = new HashMap<>();
+//            cache.put(problem, competitors);
+//        }
+        for (Edge edge : problem.plan.edgeSet()) {
+            Action provider = problem.plan.getEdgeSource(edge);
+            Action needer = problem.plan.getEdgeTarget(edge);
+            for (Integer label : edge.labels) {
+                Deque<Resolver> resolvers;
+                if (competitors.containsKey(label)) {
+                    resolvers = competitors.get(label);
+                } else {
+                    resolvers = new SubGoal(label, needer, problem).resolvers();
+                    competitors.put(label, resolvers);
+                }
+                for (Resolver resolver : resolvers) {
+                    if (Usefullness.compare(problem).compare(provider, resolver.source) < 0) {
+                        Log.d("⎇ " + resolver.source + " is more usefull for " + edge);
[…]

### 2016-01-28 src/me/grea/antoine/lolipop/type/flaw/Flaw.java

@@ -1,0 +1,70 @@
+/*
+ * To change this license header, choose License Headers in Project Properties.
+ * To change this template file, choose Tools | Templates
+ * and open the template in the editor.
+ */
+package me.grea.antoine.lolipop.type.flaw;
+
+import java.util.Deque;
+import java.util.Objects;
+import java.util.Set;
+import me.grea.antoine.lolipop.type.Action;
+import me.grea.antoine.lolipop.type.Problem;
+import static me.grea.antoine.utils.Collections.set;
+
+/**
+ *
+ * @author antoine
+ */
+public abstract class Flaw {
+
+    public int fluent;
+    public Action needer;
+    public Problem problem;
+
+    public Flaw(int fluent, Action needer, Problem problem) {
+        this.fluent = fluent;
+        this.needer = needer;
+        this.problem = problem;
+    }
+
+    public abstract Deque<Resolver> resolvers();
+
+    public Set<Resolver> healers() {
+        return set(new Resolver(new Action(null, set(fluent), true), needer, fluent));
+    }
+
+    @Override
+    public boolean equals(Object obj) {
+        if (this == obj) {
+            return true;
+        }
+        if (obj == null) {
+            return false;
+        }
+        if (getClass() != obj.getClass()) {
+            return false;
+        }
+        final Flaw other = (Flaw) obj;
+        if (this.fluent != other.fluent) {
+            return false;
+        }
+        if (!Objects.equals(this.needer, other.needer)) {
+            return false;
+        }
+        if (!Objects.equals(this.problem, other.problem)) {
+            return false;
+        }
+        return true;
+    }
+
+    @Override
+    public int hashCode() {
+        int hash = 5;
+        hash = 67 * hash + this.fluent;
+        hash = 67 * hash + Objects.hashCode(this.needer);
+        hash = 67 * hash + Objects.hashCode(this.problem);
+        return hash;
+    }
+
+}

### 2016-01-28 src/me/grea/antoine/lolipop/type/flaw/Orphan.java

@@ -1,0 +1,69 @@
+/*
+ * To change this license header, choose License Headers in Project Properties.
+ * To change this template file, choose Tools | Templates
+ * and open the template in the editor.
+ */
+package me.grea.antoine.lolipop.type.flaw;
+
+import java.util.Deque;
+import java.util.HashSet;
+import java.util.Set;
+import me.grea.antoine.lolipop.type.Action;
+import me.grea.antoine.lolipop.type.Problem;
+import static me.grea.antoine.utils.Collections.set;
+import static me.grea.antoine.utils.Collections.queue;
+
+/**
+ *
+ * @author antoine
+ */
+public class Orphan extends Flaw {
+
+    public Orphan(Action orphan, Problem problem) {
+        super(0, orphan, problem);
+    }
+
+    @Override
+    public Deque<Resolver> resolvers() {
+        return queue(new Resolver(needer, null, 0, true));
+    }
+
+    public static Set<Orphan> find(Problem problem) {
+        Set<Orphan> orphans = new HashSet<>();
+        for (Action candidate : problem.plan.vertexSet()) {
+            if (problem.plan.outDegreeOf(candidate) == 0
+                    && problem.goal != candidate
+                    && problem.initial != candidate) {
+                orphans.add(new Orphan(candidate, problem));
+            }
+        }
+        return orphans;
+    }
+
+    @Override
+    public Set<Resolver> healers() {
+        return set();
+    }
+
+    public static int count(Problem problem) {
+        return (int) problem.plan.vertexSet().stream().filter((candidate)
+                -> (problem.plan.outDegreeOf(candidate) == 0
+                && !problem.goal.equals(candidate)
+                && !problem.initial.equals(candidate))
+        ).count();
+    }
+
+    public static Set<Orphan> related(Set<Action> children, Problem problem) {
+        Set<Orphan> related = new HashSet<>();
+        children.stream().filter((child) -> (problem.plan.outDegreeOf(child) == 0)).forEach((child) -> {
+            related.add(new Orphan(child, problem));
+        });
+        return related;
+    }
+
+    @Override
+    public String toString() {
+        return "☹ " + needer;
+    }
+
+}

### 2016-01-28 src/me/grea/antoine/lolipop/type/flaw/Resolver.java

@@ -1,0 +1,135 @@
+/*
+ * To change this license header, choose License Headers in Project Properties.
+ * To change this template file, choose Tools | Templates
+ * and open the template in the editor.
+ */
+package me.grea.antoine.lolipop.type.flaw;
+
+import java.util.HashSet;
+import java.util.Set;
+import me.grea.antoine.lolipop.type.Action;
+import me.grea.antoine.lolipop.type.Edge;
+import me.grea.antoine.lolipop.type.Plan;
+import me.grea.antoine.lolipop.type.Problem;
+import static me.grea.antoine.utils.Collections.*;
+
+/**
+ *
+ * @author antoine
+ */
+public class Resolver { // TODO : Put in interface and make that an additive resolver then make the alternative resolver and then the substracting resolver
+
+    public Action source;
+    public Action target;
+    public int fluent;
+    public boolean negative = false;
+    private Edge edge;
+    private boolean edgeCreated = false;
+    private boolean sourceCreated = false;
+    private boolean targetCreated = false;
+    private Set<Action> posibleOrphans = new HashSet<>();
+
+    public Resolver(Action source, Action target, int fluent, boolean negative) {
+        this.source = source;
+        this.target = target;
+        this.fluent = fluent;
+        this.negative = negative;
+    }
+
+    public Resolver(Action source, Action target, int fluent) {
+        this(source, target, fluent, false);
+    }
+
+    public Resolver(Action source, Action target) {
+        this(source, target, 0);
+    }
+
+    public void apply(Plan plan) {
+        if (negative) {
+            edge = plan.getEdge(source, target);
+            if (edge == null) {
+                for (Edge child : plan.incomingEdgesOf(source)) {
+                    posibleOrphans.add(plan.getEdgeSource(child));
+                }
+                plan.removeVertex(source);
+                return;
+            }
+            if (edge.labels.equals(set(fluent))) {
+                posibleOrphans.add(source);
+                plan.removeEdge(edge);
+            } else {
+                edge.labels.remove(fluent);
+            }
+            return;
+        }
+        if(fluent == 0 && plan.reachable(source, target))
+        {
+            return;
+        }
+        
+        sourceCreated = plan.addVertex(source);
+        targetCreated = plan.addVertex(target);
+        edge = plan.addEdge(source, target);
+        edgeCreated = edge != null;
+        if (fluent != 0) {
+            if (edge == null) {
+                edge = plan.getEdge(source, target);
+                edge.labels.add(fluent);
[…]

### 2016-01-28 src/me/grea/antoine/lolipop/type/flaw/Threat.java

@@ -1,0 +1,114 @@
+/*
+ * To change this license header, choose License Headers in Project Properties.
+ * To change this template file, choose Tools | Templates
+ * and open the template in the editor.
+ */
+package me.grea.antoine.lolipop.type.flaw;
+
+import java.util.ArrayDeque;
+import java.util.Deque;
+import java.util.HashSet;
+import java.util.Set;
+import me.grea.antoine.lolipop.type.Action;
+import me.grea.antoine.lolipop.type.Edge;
+import me.grea.antoine.lolipop.type.Plan;
+import me.grea.antoine.lolipop.type.Problem;
+import static me.grea.antoine.utils.Collections.*;
+import me.grea.antoine.utils.Log;
+
+/**
+ *
+ * @author antoine
+ */
+public class Threat extends Flaw {
+
+    public Action breaker;
+    public Edge threatened;
+    private Edge demoter;
+    private Edge promoter;
+
+    public Threat(Action threat, Edge threatened, int fluent, Problem problem) {
+        super(fluent, problem.plan.getEdgeTarget(threatened), problem);
+        this.breaker = threat;
+        this.threatened = threatened;
+    }
+
+    @Override
+    public Deque<Resolver> resolvers() {
+        Deque<Resolver> resolvers = new ArrayDeque<>();
+        Action source = problem.plan.getEdgeSource(threatened);
+        Action target = problem.plan.getEdgeTarget(threatened);
+        if (target != problem.goal) {
+            Log.w("Can't demote after goal step !");
+            resolvers.add(new Resolver(target, breaker));
+        }
+        if (source != problem.initial) {
+            Log.w("Can't promote before initial step !");
+            resolvers.add(new Resolver(breaker, source));
+        }
+        return resolvers;
+    }
+
+    public static Set<Threat> find(Problem problem) {
+        Set<Threat> threats = new HashSet<>();
+        for (Action candidate : problem.plan.vertexSet()) {
+            threats.addAll(related(candidate, problem));
+        }
+        return threats;
+    }
+
+    @Override
+    public Set<Resolver> healers() {
+        Set<Resolver> healers = super.healers();
+
+        return union(healers, set(new Resolver(breaker, healers.iterator().next().source)));
+    }
+
+    public static int count(Problem problem) {
+        int count = 0;
+        for (Action troubleMaker : problem.plan.vertexSet()) {
+            if (troubleMaker != problem.goal && troubleMaker != problem.initial) {
[…]

### 2016-01-28 src/me/grea/antoine/soda/Main.java

@@ -1,55 +1,0 @@
-/*
- * To change this license header, choose License Headers in Project Properties.
- * To change this template file, choose Tools | Templates
- * and open the template in the editor.
- */
-package me.grea.antoine.soda;
-
-import me.grea.antoine.soda.type.Action;
-import java.util.Set;
-import me.grea.antoine.soda.algorithm.PartialOrderOptimizedPlanning;
-import me.grea.antoine.soda.algorithm.PartialOrderPlanning;
-import me.grea.antoine.soda.algorithm.ProperPlan;
-import me.grea.antoine.soda.exception.Failure;
-import me.grea.antoine.utils.Log;
-import me.grea.antoine.soda.type.Plan;
-import me.grea.antoine.soda.type.Problem;
-import static me.grea.antoine.utils.Collections.*;
-
-/**
- *
- * @author antoine
- */
-public class Main {
-
-    /**
-     * @param args the command line arguments
-     */
-    public static void main(String[] args) throws Failure {
-        // TODO code application logic here
-        Action initial = new Action(null, set(1, 2));
-        Action goal = new Action(set(-2, 3, 4, -5, 6), null);
-        Set<Action> actions = set(new Action(set(1), set(3, 5)),
-                new Action(set(2), set(4)),
-                new Action(set(4), set(-5)),
-                new Action(set(5), set(6)),
-                new Action(set(9), set(3)),
-                new Action(set(7), set(-2, 2)),
-                new Action(set(4), set()),
-                new Action(set(4), set(4)),
-                new Action(set(-7, 8), set(-8, 7)),
-                new Action(set(7, -8), set(8, -7))
-        );
-
-        Problem problem = new Problem(initial, goal, actions, ProperPlan.properPlan(goal, actions));
-
-        System.out.println(problem);
-        
-
-        PartialOrderOptimizedPlanning.solve(problem);
-
-        Log.out.println("Solution {\n\t" + problem.planToString() + "}");
-        Log.out.println("Violation : " + problem.plan.violation());
-    }
-
-}

### 2016-01-28 src/me/grea/antoine/soda/algorithm/Correlator.java

@@ -1,110 +1,0 @@
-/*
- * To change this license header, choose License Headers in Project Properties.
- * To change this template file, choose Tools | Templates
- * and open the template in the editor.
- */
-package me.grea.antoine.soda.algorithm;
-
-import java.util.HashSet;
-import java.util.List;
-import java.util.Map;
-import java.util.Set;
-import org.jgrapht.DirectedGraph;
-import me.grea.antoine.soda.type.Action;
-import me.grea.antoine.soda.type.Edge;
-import me.grea.antoine.soda.type.Goal;
-import me.grea.antoine.soda.type.Plan;
-import me.grea.antoine.utils.Collections;
-
-/**
- *
- * @author antoine
- */
-public class Correlator {
-
-    public Map<Set<Goal>, List<Count>> correlation;
-
-    private static int countProperties(Plan plan1) {
-        int count = 0;
-        count = plan1.vertexSet().stream().map((action)
-                -> action.preconditions.size() + action.effects.size()
-        ).reduce(count, Integer::sum);
-        return count;
-    }
-
-    private static Set<Integer> preconditions(Plan plan1) {
-        Set<Integer> properties = new HashSet();
-        for (Action action : plan1.vertexSet()) {
-            properties.addAll(action.preconditions);
-        }
-        return properties;
-    }
-
-    private static Set<Integer> effects(Plan plan1) {
-        Set<Integer> properties = new HashSet();
-        for (Action action : plan1.vertexSet()) {
-            properties.addAll(action.effects);
-        }
-        return properties;
-    }
-
-    public static class Count {
-
-        public int properties;
-        public int actions;
-
-        public Count() {
-            this(0, 0);
-        }
-
-        public Count(int properties, int actions) {
-            this.properties = properties;
-            this.actions = actions;
-        }
-
-        @Override
-        public String toString() {
-            return "#p=" + properties + "#a=" + actions;
-        }
-
-        public Count min(Count other) {
-            return new Count(Math.min(properties, other.properties),
-                    Math.min(actions, other.actions));
-        }
-
-        public double correlation(Count divisor) {
-            return (((double) properties) / divisor.properties)
-                    * (((double) actions) / divisor.actions);
-        }
-
-    }
-
-    public double correlation(Plan plan1, Plan plan2) {
-        Count total = new Count(countProperties(plan1), plan1.vertexSet().size()).min(
-                new Count(countProperties(plan2), plan2.vertexSet().size()));
-        Count common = new Count(
[…]

### 2016-01-28 src/me/grea/antoine/soda/algorithm/PartialOrderOptimizedPlanning.java

@@ -1,151 +1,0 @@
-/*
- * To change this license header, choose License Headers in Project Properties.
- * To change this template file, choose Tools | Templates
- * and open the template in the editor.
- */
-package me.grea.antoine.soda.algorithm;
-
-import java.util.ArrayDeque;
-import java.util.Deque;
-import java.util.HashSet;
-import java.util.Set;
-import me.grea.antoine.utils.Log;
-import me.grea.antoine.soda.exception.Success;
-import me.grea.antoine.soda.type.Action;
-import me.grea.antoine.soda.type.PartialSolution;
-import me.grea.antoine.soda.type.Plan;
-import me.grea.antoine.soda.type.flaw.Flaw;
-import me.grea.antoine.soda.type.Problem;
-import me.grea.antoine.soda.type.flaw.Alternative;
-import me.grea.antoine.soda.type.flaw.Orphan;
-import me.grea.antoine.soda.type.flaw.Resolver;
-import me.grea.antoine.soda.type.flaw.SubGoal;
-import me.grea.antoine.soda.type.flaw.Threat;
-
-/**
- *
- * @author antoine
- */
-public class PartialOrderOptimizedPlanning {
-
-    private final Problem problem;
-    private final Deque<Flaw> agenda = new ArrayDeque<>();
-    private final Deque<PartialSolution> partialSolutions = new ArrayDeque<>();
-
-    public PartialOrderOptimizedPlanning(Problem problem) {
-        this.problem = problem;
-        IllegalFixer.clean(problem);
-        populateAgenda();
-    }
-
-    private void populateAgenda() {
-        agenda.addAll(Alternative.find(problem));
-        agenda.addAll(SubGoal.find(problem));
-        agenda.addAll(Threat.find(problem));
-        agenda.addAll(Orphan.find(problem));
-    }
-
-    public static void solve(Problem problem) {
-        PartialOrderOptimizedPlanning pop = new PartialOrderOptimizedPlanning(problem);
-        while (true) {
-            try {
-                pop.refine();
-            } catch (Success ex) {
-                Log.i("Success !");
-                return;
-            }
-            Log.w("Failure");
-            pop.soft();
-        }
-    }
-
-    public void refine() throws Success {
-        if (agenda.isEmpty()) {
-            throw new Success();
-        }
-        Log.d("Agenda " + agenda);
-        Flaw flaw = agenda.pop();
-
-        if (flaw instanceof Threat) { //Fix associated subgoals before !
[…]

### 2016-01-28 src/me/grea/antoine/soda/algorithm/PartialOrderPlanning.java

@@ -1,86 +1,0 @@
-/*
- * To change this license header, choose License Headers in Project Properties.
- * To change this template file, choose Tools | Templates
- * and open the template in the editor.
- */
-package me.grea.antoine.soda.algorithm;
-
-import java.util.ArrayDeque;
-import java.util.Deque;
-import java.util.Set;
-import me.grea.antoine.utils.Log;
-import me.grea.antoine.soda.exception.Failure;
-import me.grea.antoine.soda.exception.Success;
-import me.grea.antoine.soda.type.PartialSolution;
-import me.grea.antoine.soda.type.flaw.Flaw;
-import me.grea.antoine.soda.type.Problem;
-import me.grea.antoine.soda.type.flaw.Resolver;
-import me.grea.antoine.soda.type.flaw.SubGoal;
-import me.grea.antoine.soda.type.flaw.Threat;
-import org.jgrapht.alg.CycleDetector;
-
-/**
- *
- * @author antoine
- */
-public class PartialOrderPlanning {
-
-    private final Problem problem;
-    private final Deque<Flaw> agenda = new ArrayDeque<>();
-
-    public PartialOrderPlanning(Problem problem) {
-        this.problem = problem;
-        populate(agenda, problem);
-    }
-
-    private static void populate(Deque<Flaw> agenda, Problem problem) {
-        agenda.addAll(SubGoal.find(problem));
-        agenda.addAll(Threat.find(problem));
-    }
-
-    public static void solve(Problem problem) throws Failure {
-        PartialOrderPlanning pop = new PartialOrderPlanning(problem);
-        try {
-            pop.refine();
-        } catch (Success ex) {
-        }
-        //Logically shouldn't go there
-    }
-
-    public void refine() throws Success, Failure {
-//        Log.d("Agenda " + agenda);
-        if (agenda.isEmpty()) {
-            throw new Success();
-        }
-        Flaw flaw = agenda.pop();
-//        Log.d("Resolving " + flaw);
-        Deque<Resolver> resolvers = flaw.resolvers();
-//        Log.d("Resolver " + resolvers);
-        for (Resolver resolver : resolvers) {
-//            Log.d("Trying with " + resolver);
-
-            if (resolver.appliable(problem.plan)) {
-                resolver.apply(problem.plan);
-            } else {
-                continue;
-            }
-
-            if (!new CycleDetector<>(problem.plan).detectCyclesContainingVertex(resolver.target)) {
-                Set<Flaw> related = resolver.related(problem);
[…]

### 2016-01-28 src/me/grea/antoine/soda/exception/Success.java

@@ -1,24 +1,0 @@
-/*
- * To change this license header, choose License Headers in Project Properties.
- * To change this template file, choose Tools | Templates
- * and open the template in the editor.
- */
-package me.grea.antoine.soda.exception;
-
-/**
- *
- * @author antoine
- */
-public class Success extends Exception {
-
-    public Success() {
-    }
-
-    @Override
-    public String toString() {
-        return "Success !";
-    }
-    
-    
-
-}

### 2016-01-28 src/me/grea/antoine/soda/heuristic/Usefullness.java

@@ -1,56 +1,0 @@
-/*
- * To change this license header, choose License Headers in Project Properties.
- * To change this template file, choose Tools | Templates
- * and open the template in the editor.
- */
-package me.grea.antoine.soda.heuristic;
-
-import java.util.Comparator;
-import me.grea.antoine.soda.type.Action;
-import me.grea.antoine.soda.type.Problem;
-import static java.lang.Math.round;
-
-/**
- *
- * @author antoine
- */
-public class Usefullness {
-
-    public static double h(Problem problem, Action action) {
-        if (problem.plan.containsVertex(action)) {
-            return action.fake ? 0.0
-                    : action == problem.goal
-                    || action == problem.initial
-                            ? Double.POSITIVE_INFINITY
-                            : (problem.plan.outDegreeOf(action) * action.effects.size()) / (double) ((problem.plan.inDegreeOf(action) * action.preconditions.size()) + 0.1);
-        }
-        return h(action);
-    }
-
-    public static double h(Action action) {
-        return action.fake ? 0.0
-                : (action.effects.size()) / (double) ((action.preconditions.size()) + 0.1);
-    }
-
-    public static Comparator<Action> compare(Problem problem) {
-        return (Action a1, Action a2) -> falseEquality(cast(h(problem, a1) - h(problem, a2)), a1, a2);
-    }
-
-    public static Comparator<Action> compare() {
-        return (Action a1, Action a2) -> falseEquality(cast(h(a1) - h(a2)), a1, a2);
-    }
-    
-    private static int falseEquality(int compare, Action a1, Action a2)
-    {
-        return a1.equals(a2) ? 0 : (compare == 0 && !a1.equals(a2)) ? a1.hashCode() - a2.hashCode(): compare;
-    }
-
-    private static int cast(double l) {
-        if (l > Integer.MAX_VALUE) {
-            return Integer.MAX_VALUE;
-        } else if (l < Integer.MIN_VALUE) {
-            return Integer.MIN_VALUE;
-        }
-        return (int) round(l);
-    }
-}

### 2016-01-28 src/me/grea/antoine/soda/test/CrazyActionGenerator.java

@@ -1,28 +1,0 @@
-/*
- * To change this license header, choose License Headers in Project Properties.
- * To change this template file, choose Tools | Templates
- * and open the template in the editor.
- */
-package me.grea.antoine.soda.test;
-
-import me.grea.antoine.utils.Dice;
-import me.grea.antoine.soda.test.*;
-import java.util.HashSet;
-import java.util.Set;
-import me.grea.antoine.soda.type.Action;
-
-/**
- *
- * @author antoine
- */
-public class CrazyActionGenerator {
-
-    public static Set<Action> generate(int enthropy, int number) {
-        Set<Action> actions = new HashSet<>(number);
-        while (actions.size() < number) {
-            actions.add(new Action(Dice.roll(-enthropy, enthropy, Dice.roll((int) (Math.log10(enthropy) + 1))),
-                    Dice.roll(-enthropy, enthropy, Dice.roll((int) (Math.log10(enthropy) + 1)))));
-        }
-        return actions;
-    }
-}

### 2016-01-28 src/me/grea/antoine/soda/test/CrazyProblemGenerator.java

@@ -1,49 +1,0 @@
-/*
- * To change this license header, choose License Headers in Project Properties.
- * To change this template file, choose Tools | Templates
- * and open the template in the editor.
- */
-package me.grea.antoine.soda.test;
-
-import me.grea.antoine.utils.Dice;
-import me.grea.antoine.soda.test.*;
-import java.util.HashSet;
-import java.util.Set;
-import me.grea.antoine.soda.type.Action;
-import me.grea.antoine.soda.type.Edge;
-import me.grea.antoine.soda.type.Plan;
-import me.grea.antoine.soda.type.Problem;
-
-/**
- *
- * @author antoine
- */
-public class CrazyProblemGenerator {
-
-    public static Set<Problem> generate(int enthropy, int number) {
-        Set<Problem> problems = new HashSet<>(number);
-        while (problems.size() < number) {
-            Problem problem = new Problem(
-                    new Action(null, Dice.roll(-enthropy, enthropy, enthropy / 2)),
-                    new Action(Dice.roll(-enthropy, enthropy, enthropy / 2), null),
-                    CrazyActionGenerator.generate(enthropy, Dice.roll(enthropy)),
-                    new Plan()
-            );
-            for (int i = 0; i < problem.actions.size() / 2; i++) {
-                Action source = Dice.pick(problem.actions);
-                Action target = Dice.pick(problem.actions);
-                problem.plan.addVertex(source);
-                problem.plan.addVertex(target);
-                Edge edge = problem.plan.addEdge(source, target);
-                if (edge == null) {
-                    problem.plan.getEdge(source, target).labels.addAll(source.effects);
-                } else {
-                    edge.labels = source.effects;
-                }
-            }
-            problems.add(problem);
-        }
-        return problems;
-    }
-
-}

### 2016-01-28 src/me/grea/antoine/soda/test/RandomTest.java

@@ -1,55 +1,0 @@
-/*
- * To change this license header, choose License Headers in Project Properties.
- * To change this template file, choose Tools | Templates
- * and open the template in the editor.
- */
-package me.grea.antoine.soda.test;
-
-import java.io.File;
-import java.io.FileNotFoundException;
-import java.io.PrintStream;
-import java.time.LocalDateTime;
-import java.util.Set;
-import me.grea.antoine.soda.algorithm.PartialOrderOptimizedPlanning;
-import me.grea.antoine.soda.type.Problem;
-import me.grea.antoine.utils.Chrono;
-import me.grea.antoine.utils.Log;
-
-/**
- *
- * @author antoine
- */
-public class RandomTest {
-    
-    public static void main(String... args)
-    {
-        Log.level = Log.Level.FATAL;
-        Chrono chrono = new Chrono();
-        int number = 10000;
-//        File file = new File(LocalDateTime.now() + "_" + RandomTest.class + ".csv");
-//        System.out.println(file.getAbsolutePath());
-//        try (PrintStream result = new PrintStream(file)) {
-            //echaufement
-            Set<Problem> problems = CrazyProblemGenerator.generate(40, 10000);
-            for (Problem problem : problems) {
-                PartialOrderOptimizedPlanning.solve(problem);
-            }
-//            for (int i = 1; i < 100; i++) {
-//                problems = CrazyProblemGenerator.generate(i, number);
-//                for (Problem problem : problems) {
-//                    chrono.start();
-//                    PartialOrderOptimizedPlanning.solve(problem);
-//                    chrono.stop();
-//                }
-//                System.out.println(i + " => " + chrono);
-////                result.println(i + "," + chrono.total / number);
-//                chrono.reset();
-//            }
-//            result.println("Iterations/enthropy : " + number);
-//            result.close();
-//        } catch (FileNotFoundException ex) {
-//            Log.e(ex);
-//        }
-    }
-    
-}

### 2016-01-28 src/me/grea/antoine/soda/test/ValidActionGenerator.java

@@ -1,67 +1,0 @@
-/*
- * To change this license header, choose License Headers in Project Properties.
- * To change this template file, choose Tools | Templates
- * and open the template in the editor.
- */
-package me.grea.antoine.soda.test;
-
-import me.grea.antoine.utils.Dice;
-import me.grea.antoine.soda.test.*;
-import java.util.Arrays;
-import java.util.HashSet;
-import java.util.Set;
-import me.grea.antoine.soda.type.Action;
-import me.grea.antoine.soda.type.Problem;
-import me.grea.antoine.soda.type.flaw.Flaw;
-import static me.grea.antoine.utils.Collections.*;
-import static java.lang.Math.*;
-import me.grea.antoine.utils.Log;
-
-/**
- *
- * @author antoine
- */
-public class ValidActionGenerator {
-
-    public static Set<Action> generate(int enthropy, int number) {
-        Set<Action> actions = new HashSet<>(number);
-        while (actions.size() < number) {
-            actions.add(generate(enthropy));
-        }
-        return actions;
-    }
-
-    public static Action generate(int enthropy) {
-        Action action = new Action(Dice.rollNonZero(-enthropy, enthropy, Dice.roll((int) round(log10(enthropy) + 1))),
-                Dice.rollNonZero(-enthropy, enthropy, Dice.roll((int) round(log10(enthropy) + 1))));
-        clean(action);
-        return action;
-    }
-
-    public static Action generateWith(Set<Integer> provided, int effect) {
-        Action action = new Action(Dice.pick(provided, Dice.roll(provided.size())), new HashSet<>());
-        action.effects.add(effect);
-        clean(action);
-        return action;
-    }
-
-    public static void clean(Action action) {
-        action.preconditions.removeAll(action.effects);
-        Set<Integer> dirty = new HashSet<>(action.effects);
-        Set<Integer> cleaned = new HashSet<>();
-        for (int effect : dirty) {
-            if (!cleaned.contains(effect)) {
-                action.effects.remove(-effect);
-                cleaned.add(-effect);
-            }
-        }
-        dirty = new HashSet<>(action.preconditions);
-        cleaned = new HashSet<>();
-        for (int precondition : dirty) {
-            if (!cleaned.contains(precondition)) {
-                action.preconditions.remove(-precondition);
-                cleaned.add(-precondition);
-            }
-        }
-    }
-}

### 2016-01-28 src/me/grea/antoine/soda/test/ValidProblemGenerator.java

@@ -1,84 +1,0 @@
-/*
- * To change this license header, choose License Headers in Project Properties.
- * To change this template file, choose Tools | Templates
- * and open the template in the editor.
- */
-package me.grea.antoine.soda.test;
-
-import me.grea.antoine.utils.Dice;
-import me.grea.antoine.soda.test.*;
-import java.util.HashSet;
-import java.util.Set;
-import me.grea.antoine.utils.Log;
-import me.grea.antoine.soda.algorithm.PartialOrderPlanning;
-import me.grea.antoine.soda.exception.Failure;
-import me.grea.antoine.soda.exception.Success;
-import me.grea.antoine.soda.type.Action;
-import me.grea.antoine.soda.type.Plan;
-import me.grea.antoine.soda.type.Problem;
-import me.grea.antoine.soda.type.flaw.Threat;
-
-/**
- *
- * @author antoine
- */
-public class ValidProblemGenerator {
-
-    public static Set<Problem> generate(int enthropy, int number) {
-        Set<Problem> problems = new HashSet<>(number);
-        while (problems.size() < number) {
-            Action initial = new Action(null, Dice.rollNonZero(-enthropy, enthropy, Dice.roll(1, 3 * (int) Math.round(Math.log(enthropy)))));
-            Action goal = new Action(Dice.rollNonZero(-enthropy, enthropy, Dice.roll(3 * (int) Math.round(Math.log(enthropy)), 4 * (int) Math.round(Math.log(enthropy)))), null);
-            ValidActionGenerator.clean(initial);
-            ValidActionGenerator.clean(goal);
-
-            Problem problem = new Problem(
-                    initial,
-                    goal,
-                    new HashSet<>(),
-                    new Plan()
-            );
-
-            int tries = enthropy * 2; // I died a little inside
-            while (tries-- != 0) {
-                for (int i = 0; i < enthropy; i++) {
-                    problem.actions.add(ValidActionGenerator.generate(enthropy));
-                }
-                Set<Integer> current = new HashSet<>(initial.effects);
-                for (int precondition : goal.preconditions) {
-                    Action action = ValidActionGenerator.generateWith(current, precondition);
-                    problem.actions.add(action);
-                    current.add(precondition);
-                }
-                PartialOrderPlanning pop = new PartialOrderPlanning(problem);
-                Log.i(problem);
-                try {
-                    pop.refine();
-                } catch (Success ex) {
-                    break;
-                } catch (Failure ex) {
-                    problem.actions.clear();
[…]

### 2016-01-28 src/me/grea/antoine/soda/type/Edge.java

@@ -1,25 +1,0 @@
-/*
- * To change this license header, choose License Headers in Project Properties.
- * To change this template file, choose Tools | Templates
- * and open the template in the editor.
- */
-package me.grea.antoine.soda.type;
-
-import java.util.HashSet;
-import java.util.Set;
-import org.jgrapht.graph.DefaultEdge;
-
-/**
- *
- * @author antoine
- */
-public class Edge extends DefaultEdge {
-
-    public Set<Integer> labels = new HashSet<>();
-
-    @Override
-    public String toString() {
-        return getSource() + " -" + (labels.isEmpty() ? "☠" : labels) + "> " + getTarget();
-    }
-
-}

### 2016-01-28 src/me/grea/antoine/soda/type/Plan.java

@@ -1,183 +1,0 @@
-/*
- * To change this license header, choose License Headers in Project Properties.
- * To change this template file, choose Tools | Templates
- * and open the template in the editor.
- */
-package me.grea.antoine.soda.type;
-
-import java.util.ArrayDeque;
-import java.util.Deque;
-import java.util.HashMap;
-import java.util.HashSet;
-import java.util.Map;
-import java.util.Set;
-import org.jgrapht.DirectedGraph;
-import org.jgrapht.graph.AbstractBaseGraph;
-import org.jgrapht.graph.ClassBasedEdgeFactory;
-
-/**
- *
- * @author antoine
- */
-public class Plan extends AbstractBaseGraph<Action, Edge> implements DirectedGraph<Action, Edge> {
-
-    private final Map<Action, Integer> outDegree = new HashMap<Action, Integer>() {
-        {
-            vertexSet().stream().forEach((action) -> {
-                put(action, outDegreeOf(action));
-            });
-        }
-    };
-    private final Map<Action, Integer> inDegree = new HashMap<Action, Integer>() {
-        {
-            vertexSet().stream().forEach((action) -> {
-                put(action, inDegreeOf(action));
-            });
-        }
-    };
-
-    private int violation = 0;
-
-    public Plan() {
-        super(new ClassBasedEdgeFactory<>(Edge.class), false, true);
-    }
-
-    public Plan(Plan other) {
-        this();
-        for (Action action : other.vertexSet()) {
-            addVertex(action);
-        }
-        for (Edge edge : other.edgeSet()) {
-            addEdge(other.getEdgeSource(edge), other.getEdgeTarget(edge), edge);
-        }
-    }
-
-    public boolean reachable(Action source, Action target, int k, Set<Edge> forbiden) {
-        if (source == target) {
-            return true;
-        }
-        if (!containsVertex(source) || !containsVertex(target)) {
-            return false;
-        }
-        if (forbiden == null) {
-            forbiden = new HashSet<>();
-        }
-        Set<Action> visited = new HashSet<>();
-        Deque<Action> stack = new ArrayDeque<>();
-        stack.push(source);
-        while (!stack.isEmpty()) {
-            Action current = stack.pop();
-            for (Edge edge : outgoingEdgesOf(current)) {
-                if (forbiden.contains(edge)) {
-                    continue;
-                }
-                Action frontier = getEdgeTarget(edge);
[…]

### 2016-01-28 src/me/grea/antoine/soda/type/flaw/Alternative.java

@@ -1,108 +1,0 @@
-/*
- * To change this license header, choose License Headers in Project Properties.
- * To change this template file, choose Tools | Templates
- * and open the template in the editor.
- */
-package me.grea.antoine.soda.type.flaw;
-
-import java.util.Deque;
-import java.util.HashMap;
-import java.util.HashSet;
-import java.util.Map;
-import java.util.Set;
-import me.grea.antoine.soda.heuristic.Usefullness;
-import me.grea.antoine.soda.type.Action;
-import me.grea.antoine.soda.type.Edge;
-import me.grea.antoine.soda.type.Problem;
-import static me.grea.antoine.utils.Collections.queue;
-import static me.grea.antoine.utils.Collections.set;
-import me.grea.antoine.utils.Log;
-
-/**
- *
- * @author antoine
- */
-public class Alternative extends Flaw {
-
-    public Action provider;
-    private static final Map<Problem, Map<Integer, Deque<Resolver>>> cache = new HashMap<>();
-
-    public Alternative(int fluent, Action provider, Action needer, Problem problem) {
-        super(fluent, needer, problem);
-        this.provider = provider;
-    }
-
-    @Override
-    public Deque<Resolver> resolvers() {
-        return queue(new Resolver(provider, needer, fluent, true));
-    }
-
-    public static Set<Alternative> find(Problem problem) {
-        Set<Alternative> alternatives = new HashSet<>();
-        Map<Integer, Deque<Resolver>> competitors = cache.get(problem);
-        if (competitors == null) {
-            competitors = new HashMap<>();
-            cache.put(problem, competitors);
-        }
-        for (Edge edge : problem.plan.edgeSet()) {
-            Action provider = problem.plan.getEdgeSource(edge);
-            Action needer = problem.plan.getEdgeTarget(edge);
-            for (Integer label : edge.labels) {
-                Deque<Resolver> resolvers;
-                if (competitors.containsKey(label)) {
-                    resolvers = competitors.get(label);
-                } else {
-                    resolvers = new SubGoal(label, needer, problem).resolvers();
-                    competitors.put(label, resolvers);
-                }
-                for (Resolver resolver : resolvers) {
-                    if (!provider.equals(resolver.source) && Usefullness.h(problem, provider) < Usefullness.h(problem, resolver.source)) {
-                        Log.d("⎇ " + resolver.source + " is more usefull for " + edge);
-                        alternatives.add(new Alternative(resolver.fluent, provider, resolver.target, problem));
-                        break;
-                    }
-                }
[…]

### 2016-01-28 src/me/grea/antoine/soda/type/flaw/SubGoal.java

@@ -1,134 +1,0 @@
-/*
- * To change this license header, choose License Headers in Project Properties.
- * To change this template file, choose Tools | Templates
- * and open the template in the editor.
- */
-package me.grea.antoine.soda.type.flaw;
-
-import java.util.ArrayDeque;
-import java.util.ArrayList;
-import java.util.Collections;
-import java.util.Deque;
-import java.util.HashMap;
-import java.util.HashSet;
-import java.util.List;
-import java.util.Map;
-import java.util.Set;
-import me.grea.antoine.soda.heuristic.Usefullness;
-import me.grea.antoine.soda.type.Action;
-import me.grea.antoine.soda.type.Edge;
-import me.grea.antoine.soda.type.Plan;
-import me.grea.antoine.soda.type.Problem;
-import static me.grea.antoine.utils.Collections.*;
-import me.grea.antoine.utils.Log;
-
-/**
- *
- * @author antoine
- */
-public class SubGoal extends Flaw {
-
-    public SubGoal(int fluent, Action needer, Problem problem) {
-        super(fluent, needer, problem);
-    }
-
-    @Override
-    public Deque<Resolver> resolvers() {
-        Deque<Resolver> resolvers = new ArrayDeque<>();
-        if (problem.initial.effects.contains(fluent)) {
-            resolvers.addLast(new Resolver(problem.initial, needer, fluent));
-        }
-        List<Action> steps = new ArrayList<>(problem.plan.vertexSet());
-        steps.remove(problem.initial);
-        steps.remove(problem.goal);
-        steps.remove(needer); // Order the actions by utility
-        try{
-        Collections.sort(steps, Usefullness.compare(problem));
-        } catch (IllegalArgumentException ex)
-        {
-            Log.f(problem);
-        }
-        for (Action step : steps) {
-            if (step.effects.contains(fluent)) {
-                resolvers.addLast(new Resolver(step, needer, fluent));
-            }
-        }
-        Set<Action> actions = new HashSet<>(problem.actions);
-        actions.remove(problem.initial);
-        actions.remove(problem.goal);
-        actions.remove(needer);
-        actions.removeAll(steps);
-        for (Action action : actions) {
-            if (action.effects.contains(fluent)) {
-                resolvers.addLast(new Resolver(action, needer, fluent));
-            }
-        }
-        return resolvers;
-    }
-
-    public static Set<SubGoal> find(Problem problem) {
[…]

### 2016-01-28 src/me/grea/antoine/soda/type/flaw/Threat.java

@@ -1,109 +1,0 @@
-/*
- * To change this license header, choose License Headers in Project Properties.
- * To change this template file, choose Tools | Templates
- * and open the template in the editor.
- */
-package me.grea.antoine.soda.type.flaw;
-
-import java.util.ArrayDeque;
-import java.util.Deque;
-import java.util.HashSet;
-import java.util.Set;
-import me.grea.antoine.soda.type.Action;
-import me.grea.antoine.soda.type.Edge;
-import me.grea.antoine.soda.type.Plan;
-import me.grea.antoine.soda.type.Problem;
-import static me.grea.antoine.utils.Collections.*;
-
-/**
- *
- * @author antoine
- */
-public class Threat extends Flaw {
-
-    public Action breaker;
-    public Edge threatened;
-    private Edge demoter;
-    private Edge promoter;
-
-    public Threat(Action threat, Edge threatened, int fluent, Problem problem) {
-        super(fluent, problem.plan.getEdgeTarget(threatened), problem);
-        this.breaker = threat;
-        this.threatened = threatened;
-    }
-
-    @Override
-    public Deque<Resolver> resolvers() {
-        Deque<Resolver> resolvers = new ArrayDeque<>();
-        Action source = problem.plan.getEdgeSource(threatened);
-        Action target = problem.plan.getEdgeTarget(threatened);
-        if (target != problem.goal) {
-//                Log.w("Can't demote after goal step !");
-            resolvers.add(new Resolver(target, breaker));
-        }
-        if (source != problem.initial) {
-//                Log.w("Can't promote before initial step !");
-            resolvers.add(new Resolver(breaker, source));
-        }
-        return resolvers;
-    }
-
-    public static Set<Threat> find(Problem problem) {
-        Set<Threat> threats = new HashSet<>();
-        for (Action candidate : problem.plan.vertexSet()) {
-            threats.addAll(related(candidate, problem));
-        }
-        return threats;
-    }
-
-    @Override
-    public Set<Resolver> healers() {
-        Set<Resolver> healers = super.healers();
-
-        return union(healers, set(new Resolver(breaker, healers.iterator().next().source)));
-    }
-
-    public static int count(Plan plan) {
-        int count = 0;
-        for (Action troubleMaker : plan.vertexSet()) {
-            for (int effect : troubleMaker.effects) {
-                for (Edge oposite : plan.edgeSet()) {
-                    for (int fluent : oposite.labels) {
[…]

### 2016-02-10 article/filters/numerical-reference.hs
Switched pandoc for panzer. Multiple compilation improvement. Simpler source file. Lot of redacting and schemas.

@@ -1,0 +1,124 @@
+{-# LANGUAGE PatternGuards #-}
+
+{- This filter allows for numerical section references. It should be
+used with "--number-sections", since it uses a similar numbering
+scheme. It works by using the link notation: given a header with a
+given id, we can refer to that number by using a link with `#` in it:
+
+    My Header {#my-header-id}
+    =========
+
+    This refers back the [Section #](#my-header-id)
+
+It takes two metadata options, which can either be specified
+in YAML or on the command-line:
+
+  * `ref-num-sign`: This is the sign that will be used to indicate
+    numerical reference. It defaults to `#`.
+
+  * `ref-num-unlink`: Whether to make the the link a plain string, or
+    keep it a link. The default is false.
+-}
+
+import Text.Pandoc
+import Text.Pandoc.JSON
+import Text.Pandoc.Walk
+import Text.Pandoc.Shared
+import Control.Monad.State
+import Control.Monad.Reader
+import qualified Data.Map as M
+import Data.Maybe
+import Data.List
+import Control.Monad.Reader
+import Control.Monad.State
+import Control.Applicative ((<$>))
+
+data ScriptConfig = ScriptConfig { confNumSign :: String
+                                 , confUnlinkNum :: Bool
+                                 }
+
+getConfig :: Meta -> ScriptConfig
+getConfig meta = ScriptConfig { confNumSign = num
+                              , confUnlinkNum = bool}
+  where num = case lookupMeta "ref-num-sign" meta of
+          Just (MetaString s) -> s
+          Just (MetaInlines ils) -> concatMap stringify ils
+          _                      -> "#" --  default to number sign
+        bool = case lookupMeta "ref-num-unlink" meta of
+          Just (MetaBool b) -> b
+          _                 -> False
+
+data ScriptState = ScriptState { stCounter :: Counter
+                               , stNumMap :: M.Map String Counter
+                               }
+
+defaultState :: ScriptState
+defaultState = ScriptState [] M.empty
+
+type MyMonad = ReaderT ScriptConfig (State ScriptState)
+
+type Counter = [Int]
+
+incCounter :: Int -> Counter -> Counter
+incCounter lvl cntr
+  | lvl < 1 = cntr
+  | otherwise =
[…]

### 2016-02-10 article/filters/pandoc-svg.py

@@ -35,7 +35,7 @@ def svg_to_any(key, value, fmt, meta):
                 mtime = -1
             if mtime < os.path.getmtime(src):
                 cmd_line = ['inkscape', option[0], eps_name, src]
-                sys.stderr.write("Running %s\n" % " ".join(cmd_line))
+                #sys.stderr.write("Running %s\n" % " ".join(cmd_line))
                 subprocess.call(cmd_line, stdout=sys.stderr.fileno())
             return Image(['', [], []], alt, [eps_name, title])
 

### 2016-03-15 article/filters/pandoc-science.py
Work on the refactor of Lollipop : POP working. Heuristic mostly done. Article : checkpoint for Samir version

@@ -96,7 +96,7 @@ def pandoc_science(key, value, format, meta):
             if format == "latex":
                 return(RawInline('latex', name + '~\\ref{' + citationid + '}'))
             else:
-                return Str(name + ' ' + str(refs[class_].get(citationid, '???' )))
+                return Str(name + ' ' + str(refs[class_].get(citationid, '??' )))
 
 if __name__ == "__main__":
     toJSONFilter(pandoc_science)

### 2016-03-15 src/me/grea/antoine/lollipop/algorithm/GoalProperPlan.java

@@ -1,68 +1,0 @@
-/*
- * To change this license header, choose License Headers in Project Properties.
- * To change this template file, choose Tools | Templates
- * and open the template in the editor.
- */
-package me.grea.antoine.lollipop.algorithm;
-
-import java.util.ArrayDeque;
-import java.util.Deque;
-import java.util.HashSet;
-import java.util.Set;
-import me.grea.antoine.lollipop.type.Action;
-import me.grea.antoine.lollipop.type.Edge;
-import me.grea.antoine.lollipop.type.Goal;
-import me.grea.antoine.lollipop.type.Plan;
-import static me.grea.antoine.utils.Collections.*;
-
-/**
- *
- * @author antoine
- */
-public class GoalProperPlan {
-
-    public static Plan properPlan(Goal goal, Set<Action> actions) {
-        Plan plan = new Plan();
-        Set<Action> relevants = satisfy(goal, actions, plan);
-        /* The satisfy function iterate throught 
-        participating actions and add the causal links */
-        Deque<Action> open = new ArrayDeque<>(relevants);
-        //queue of opened relevant actions
-        while (!open.isEmpty()) {
-            Action action = open.pop();
-            Set<Action> candidates = satisfy(action, actions, plan);
-            /* Searching for candidates that satisfy 
-            the selected providing action*/
-            for (Action candidate : candidates) {
-                if (!relevants.contains(candidate)) {
-                    /* Only the one not threated already 
-                    are added to ensure convergence */
-                    open.push(candidate);
-                }
-            }
-            relevants.addAll(candidates);
-        }
-        return plan;
-    }
-
-    private static Set<Action> satisfy(Goal goal, Set<Action> actions, Plan plan) {
-        Set<Action> relevants = new HashSet<>();
-        plan.addVertex((Action) goal);
-        for (int precondition : goal.preconditions) {
-            for (Action action : actions) {
-                if (action.effects.contains(precondition) && action != goal) {
-                    plan.addVertex(action);
-                    Edge edge = plan.addEdge(action, (Action) goal);
-                    if (edge != null) {
-                        edge.labels = set(precondition);
-                    } else {
-                        plan.getEdge(action, (Action) goal).labels.add(precondition);
-                    }
-                    relevants.add(action);
-                }
-            }
-        }
-        return relevants;
-    }
-
-}

### 2016-03-15 src/me/grea/antoine/lollipop/algorithm/Lollipop.java

@@ -1,0 +1,83 @@
+/*
+ * To change this license header, choose License Headers in Project Properties.
+ * To change this template file, choose Tools | Templates
+ * and open the template in the editor.
+ */
+package me.grea.antoine.lollipop.algorithm;
+
+import java.util.Deque;
+import java.util.Set;
+import me.grea.antoine.lollipop.agenda.Agenda;
+import me.grea.antoine.lollipop.agenda.ClassicalAgenda;
+import me.grea.antoine.lollipop.exception.Success;
+import me.grea.antoine.lollipop.type.Problem;
+import me.grea.antoine.lollipop.type.flaw.Flaw;
+import me.grea.antoine.lollipop.type.flaw.Resolver;
+import me.grea.antoine.utils.Log;
+
+/**
+ *
+ * @author antoine
+ */
+public class Lollipop {
+
+    private final Problem problem;
+    private Agenda agenda;
+
+    public Lollipop(Problem problem) {
+        this.problem = problem;
+        agenda = new ClassicalAgenda(problem);
+    }
+
+    public static void solve(Problem problem) {
+        Lollipop pop = new Lollipop(problem);
+        while (true) {
+            try {
+                pop.refine();
+            } catch (Success ex) {
+                Log.i("Success !");
+                return;
+            }
+            Log.w("Failure");
+//            pop.agenda = new ClassicalAgenda(problem);
+//            problem.plan = new Plan();
+//            problem.plan.addVertex(problem.initial);
+//            problem.plan.addVertex(problem.goal);
+            
+            return;
+        }
+    }
+
+    public void refine() throws Success {
+        if (agenda.isEmpty()) {
+            throw new Success();
+        }
+        Log.d("Agenda " + agenda);
+        
+        Flaw flaw = agenda.choose();
+        Log.d("Resolving " + flaw);
+        
+        Deque<Resolver> resolvers = flaw.resolvers();
+        Log.d("Resolvers " + resolvers);
+        
+        for (Resolver resolver : resolvers) {
+            Log.d("Trying with " + resolver);
+
+            if (resolver.appliable(problem.plan)) {
+                resolver.apply(problem.plan);
+            } else {
+                Log.w(resolver + " isn't appliable !");
+                continue;
+            }
+            Set<Flaw> related = resolver.related(problem);
+            agenda.addAll(related);
+            refine();
+            resolver.revert(problem.plan); // Return means failure
+            agenda.removeAll(related);
[…]

### 2016-03-15 src/me/grea/antoine/lollipop/heuristic/Scalaire.java

@@ -1,0 +1,33 @@
+/*
+ * To change this license header, choose License Headers in Project Properties.
+ * To change this template file, choose Tools | Templates
+ * and open the template in the editor.
+ */
+package me.grea.antoine.lollipop.heuristic;
+
+import java.util.Comparator;
+import me.grea.antoine.lollipop.type.Action;
+import me.grea.antoine.lollipop.type.Problem;
+
+/**
+ *
+ * @author antoine
+ */
+public class Scalaire extends Heuristic {
+
+    public Scalaire(Problem problem) {
+        super(problem);
+    }
+
+    public static Comparator<Action> comparator(Problem problem) {
+        return new Scalaire(problem).comparator();
+    }
+
+    @Override
+    public double h(Action action) { 
+        return (action.effects.size() * -action.preconditions.size()) 
+                + (problem.domain.operatorGraph.outDegreeOf(action) * -problem.domain.operatorGraph.inDegreeOf(action)) 
+                + (problem.plan.outDegreeOf(action) * -problem.plan.inDegreeOf(action));
+    }
+
+}

### 2016-03-15 src/me/grea/antoine/lollipop/heuristic/SimpleDegree.java

@@ -1,0 +1,33 @@
+/*
+ * To change this license header, choose License Headers in Project Properties.
+ * To change this template file, choose Tools | Templates
+ * and open the template in the editor.
+ */
+package me.grea.antoine.lollipop.heuristic;
+
+import java.util.Comparator;
+import me.grea.antoine.lollipop.type.Action;
+import me.grea.antoine.lollipop.type.Problem;
+
+/**
+ *
+ * @author antoine
+ */
+public class SimpleDegree extends Heuristic{
+
+    public SimpleDegree(Problem problem) {
+        super(problem);
+    }
+    
+    public static Comparator<Action> comparator(Problem problem) {
+        return new SimpleDegree(problem).comparator();
+    }
+
+    @Override
+    public double h(Action action) {
+        return (action.effects.size() - action.preconditions.size()) * 
+                (problem.domain.operatorGraph.outDegreeOf(action) - problem.domain.operatorGraph.inDegreeOf(action)) *
+                (problem.plan.outDegreeOf(action) - problem.plan.inDegreeOf(action));
+    }
+    
+}

### 2016-03-15 src/me/grea/antoine/lollipop/heuristic/Usefullness.java

@@ -1,86 +1,0 @@
-/*
- * To change this license header, choose License Headers in Project Properties.
- * To change this template file, choose Tools | Templates
- * and open the template in the editor.
- */
-package me.grea.antoine.lollipop.heuristic;
-
-import static java.lang.Math.pow;
-import static java.lang.Math.round;
-import java.util.Comparator;
-import me.grea.antoine.lollipop.type.Action;
-import me.grea.antoine.lollipop.type.Problem;
-
-/**
- *
- * @author antoine
- */
-public class Usefullness {
-
-    public static double h(Problem problem, Action action) {
-        if (problem.plan.containsVertex(action)) {
-            return (problem.plan.outDegreeOf(action) + action.effects.size()) / (double) pow(2, (problem.plan.inDegreeOf(action) + action.preconditions.size()));
-        }
-        return h(action);
-    }
-
-    public static double h(Action action) {
-        return (action.effects.size()) / (double) pow(2, action.preconditions.size());
-    }
-
-    public static Comparator<Action> compare(Problem problem) {
-        return (Action a1, Action a2) -> {
-            if (a1.equals(a2)) {
-                return 0;
-            }
-            int value = cast(h(problem, a1) - h(problem, a2));
-            if ((a1.fake && a2.fake)
-                    || (isSpecial(problem, a1) && isSpecial(problem, a2))
-                    || (value == 0)) {
-                return 0;//a1.hashCode() - a2.hashCode();
-            } else if (isSpecial(problem, a1)) {
-                return 1;
-            } else if (isSpecial(problem, a2)) {
-                return -1;
-            } else if (a1.fake) {
-                return -1;
-            } else if (a2.fake) {
-                return 1;
-            }
-
-            return value;
-        };
-    }
-
-    public static Comparator<Action> compare() {
-        return (Action a1, Action a2) -> {
-            if (a1.equals(a2)) {
-                return 0;
-            }
-            int value = cast(h(a1) - h(a2));
-            if ((a1.fake && a2.fake)
-                    || (value == 0)) {
-                return a1.hashCode() - a2.hashCode();
-            } else if (a1.fake) {
-                return -1;
-            } else if (a2.fake) {
-                return 1;
-            }
-
-            return value;
-        };
-    }
-
-    private static boolean isSpecial(Problem problem, Action action) {
-        return action == problem.goal || action == problem.initial;
-    }
-
[…]

### 2016-03-15 src/me/grea/antoine/lollipop/type/Domain.java

@@ -1,0 +1,30 @@
+/*
+ * To change this license header, choose License Headers in Project Properties.
+ * To change this template file, choose Tools | Templates
+ * and open the template in the editor.
+ */
+package me.grea.antoine.lollipop.type;
+
+import java.util.Collection;
+import java.util.HashSet;
+
+/**
+ *
+ * @author antoine
+ */
+public class Domain extends HashSet<Action>{
+    
+    public final Plan operatorGraph;
+
+    public Domain() {
+        this.operatorGraph = operatorGraph;
+    }
+
+    public Domain(Collection<? extends Action> c) {
+        super(c);
+        this.operatorGraph = operatorGraph;
+    }
+    
+    
+    
+}

### 2016-03-15 src/me/grea/antoine/lollipop/type/Problem.java

@@ -16,17 +16,18 @@ public class Problem {
 
     public Action initial;
     public Action goal;
-    public Set<Action> actions; // not including those above
+    public Domain domain; // not including those above
     public Plan plan;
+    private Heuri
 
     public Problem() {
-        this(new Action(), new Action(), new HashSet<>(), new Plan());
+        this(new Action(), new Action(), new Domain(), new Plan());
     }
 
-    public Problem(Action initial, Action goal, Set<Action> actions, Plan plan) {
+    public Problem(Action initial, Action goal, Domain domain, Plan plan) {
         this.initial = initial;
         this.goal = goal;
-        this.actions = actions;
+        this.domain = domain;
         this.plan = plan;
         plan.addVertex(initial);
         plan.addVertex(goal);
@@ -35,13 +36,17 @@ public class Problem {
     public Problem(Problem other) {
         this.initial = other.initial;
         this.goal = other.goal;
-        this.actions = other.actions;
+        this.domain = other.domain;
         this.plan = other.plan;
+    }
+    
+    public boolean isSpecial(Action action) {
+        return action == goal || action == initial;
     }
 
     @Override
     public String toString() {
-        return "Problem {" + "\n\tinitial:" + initial.effects + " => goal:" + goal.preconditions + "\n\tactions:" + actions + "\n\tplan:" + planToString() + "}";
+        return "Problem {" + "\n\tdomain:" + domain + "\n\tinitial:" + initial.effects + " => goal:" + goal.preconditions + "\n\tplan:" + planToString() + "}";
     }
 
     public String planToString() {

### 2016-03-15 src/me/grea/antoine/lollipop/type/flaw/ClassicalSubGoal.java

@@ -12,6 +12,7 @@ import java.util.Set;
 import me.grea.antoine.lollipop.type.Action;
 import me.grea.antoine.lollipop.type.Problem;
 import static me.grea.antoine.utils.Collections.union;
+import static me.grea.antoine.utils.Collections.union;
 
 /**
  *
@@ -30,7 +31,7 @@ public class ClassicalSubGoal extends Flaw<ClassicalSubGoal> {
     @Override
     public Deque<Resolver> resolvers() {
         Deque<Resolver> resolvers = new ArrayDeque<>();
-        Set<Action> actions = union(problem.plan.vertexSet(), problem.actions);
+        Set<Action> actions = union(problem.plan.vertexSet(), problem.domain);
         for (Action action : actions) {
             if (action.effects.contains(fluent)) {
                 resolvers.addLast(new Resolver(action, needer, fluent));

### 2016-03-15 src/me/grea/antoine/lollipop/type/flaw/SubGoal.java

@@ -12,7 +12,7 @@ import java.util.Deque;
 import java.util.HashSet;
 import java.util.List;
 import java.util.Set;
-import me.grea.antoine.lollipop.heuristic.Usefullness;
+import me.grea.antoine.lollipop.heuristic.SimpleDegree;
 import me.grea.antoine.lollipop.type.Action;
 import me.grea.antoine.lollipop.type.Problem;
 
@@ -37,7 +37,7 @@ public class SubGoal extends ClassicalSubGoal {
         steps.remove(problem.goal);
         steps.remove(needer);
         try {
-            Collections.sort(steps, Usefullness.compare(problem)); // Order the actions by utility
+            Collections.sort(steps, SimpleDegree.comparator(problem)); // Order the domain by utility
         } catch (IllegalArgumentException ex) { // I DON'T CARE !!!!
         }
         for (Action step : steps) {
@@ -45,7 +45,7 @@ public class SubGoal extends ClassicalSubGoal {
                 resolvers.addLast(new Resolver(step, needer, fluent));
             }
         }
-        Set<Action> actions = new HashSet<>(problem.actions);
+        Set<Action> actions = new HashSet<>(problem.domain);
         actions.remove(problem.initial);
         actions.remove(problem.goal);
         actions.remove(needer);

### 2016-03-28 article/filters/pandoc-science.py
Lots of redaction and tunning on the article.
LOLLIPOP broken but POP works with automatic solution checker and problem generator.

@@ -97,6 +97,8 @@ def pandoc_science(key, value, format, meta):
                 return(RawInline('latex', name + '~\\ref{' + citationid + '}'))
             else:
                 return Str(name + ' ' + str(refs[class_].get(citationid, '??' )))
+        elif prefix == 'line':
+            return(RawInline('latex', 'line \\ref{' + citationid + '}'))
 
 if __name__ == "__main__":
     toJSONFilter(pandoc_science)

### 2016-03-28 src/me/grea/antoine/lollipop/agenda/RandomAgenda.java

@@ -5,6 +5,7 @@
  */
 package me.grea.antoine.lollipop.agenda;
 
+import java.util.Collection;
 import me.grea.antoine.lollipop.type.Action;
 import me.grea.antoine.lollipop.type.Problem;
 import me.grea.antoine.lollipop.type.flaw.ClassicalSubGoal;
@@ -34,7 +35,17 @@ public class RandomAgenda extends Agenda {
 
     @Override
     public boolean add(Flaw flaw) {
+        if(contains(flaw))
+            return false;
         return super.add(flaw);
+    }
+    
+    @Override
+    public boolean addAll(Collection<? extends Flaw> flaws) {
+        boolean modified = false;
+        modified = flaws.stream().map((flaw) -> add(flaw)).
+                reduce(modified, (accumulator, _item) -> accumulator | _item);
+        return modified;
     }
 
     @Override

### 2016-03-28 src/me/grea/antoine/lollipop/algorithm/DomainProperPlan.java

@@ -1,0 +1,94 @@
+/*
+ * To change this license header, choose License Headers in Project Properties.
+ * To change this template file, choose Tools | Templates
+ * and open the template in the editor.
+ */
+package me.grea.antoine.lollipop.algorithm;
+
+import java.util.Collection;
+import java.util.Deque;
+import java.util.HashMap;
+import java.util.HashSet;
+import java.util.Map;
+import java.util.Set;
+import me.grea.antoine.lollipop.type.Action;
+import me.grea.antoine.lollipop.type.Domain;
+import me.grea.antoine.lollipop.type.Edge;
+import me.grea.antoine.lollipop.type.Plan;
+import me.grea.antoine.lollipop.type.Problem;
+import static me.grea.antoine.utils.Collections.set;
+import static me.grea.antoine.utils.Collections.queue;
+
+/**
+ *
+ * @author antoine
+ */
+public class DomainProperPlan {
+    
+    public static void inject(Problem problem)
+    {
+        add(set(problem.initial, problem.goal), problem.plan, problem.providing);
+        thunderPrunning(problem.initial, problem.goal, problem.plan);
+    }
+
+    public static void add(Collection<Action> actions, Plan properPlan, Map<Integer, Set<Action>> providing) {
+        for (Action target : actions) {
+            properPlan.addVertex(target);
+        }
+        for (Action target : properPlan.vertexSet()) {
+            for (int precondition : target.preconditions) {
+                if (providing.containsKey(precondition)) {
+                    for (Action source : providing.get(precondition)) {
+                        properPlan.addVertex(source);
+                        Edge edge = properPlan.getEdge(source, target);
+                        if (edge == null) {
+                            edge = properPlan.addEdge(source, target);
+                        }
+                        edge.labels.add(precondition);
+
+                    }
+                }
+            }
+        }
+    }
+
+    public static Plan build(Domain domain) {
+        Plan operatorGraph = new Plan();
+        add(domain, operatorGraph, domain.providing);
+        return operatorGraph;
+    }
+
+    public static Map<Integer, Set<Action>> add(Collection<Action> actions, Map<Integer, Set<Action>> providing) {
+        Map<Integer, Set<Action>> result = new HashMap<>(providing);
+
+        for (Action action : actions) {
+            for (int effect : action.effects) {
+                if (result.containsKey(effect)) {
+                    result.get(effect).add(action);
+                } else {
[…]

### 2016-03-28 src/me/grea/antoine/lollipop/benchmark/Benchmark.java

@@ -1,0 +1,25 @@
+/*
+ * To change this license header, choose License Headers in Project Properties.
+ * To change this template file, choose Tools | Templates
+ * and open the template in the editor.
+ */
+package me.grea.antoine.lollipop.benchmark;
+
+import me.grea.antoine.utils.Log;
+
+/**
+ *
+ * @author antoine
+ */
+public class Benchmark {
+    
+    static {
+        Log.level = Log.Level.INFO;
+    }
+    
+    public static void main(String[] args)
+    {
+        Log.i(ProblemGenerator.generate(1000, 50));
+    }
+    
+}

### 2016-03-28 src/me/grea/antoine/lollipop/benchmark/ProblemGenerator.java

@@ -1,0 +1,173 @@
+/*
+ * To change this license header, choose License Headers in Project Properties.
+ * To change this template file, choose Tools | Templates
+ * and open the template in the editor.
+ */
+package me.grea.antoine.lollipop.benchmark;
+
+import java.util.Deque;
+import java.util.HashSet;
+import java.util.Set;
+import me.grea.antoine.lollipop.algorithm.PartialOrderPlanning;
+import me.grea.antoine.lollipop.type.Action;
+import me.grea.antoine.lollipop.type.Domain;
+import me.grea.antoine.lollipop.type.Edge;
+import me.grea.antoine.lollipop.type.Plan;
+import me.grea.antoine.lollipop.type.Problem;
+import me.grea.antoine.lollipop.type.flaw.ClassicalResolver;
+import me.grea.antoine.lollipop.type.flaw.ClassicalSubGoal;
+import me.grea.antoine.lollipop.type.flaw.ClassicalThreat;
+import me.grea.antoine.lollipop.type.flaw.Flaw;
+import me.grea.antoine.lollipop.type.flaw.Resolver;
+import me.grea.antoine.utils.Collections;
+import static me.grea.antoine.utils.Collections.set;
+import static me.grea.antoine.utils.Collections.union;
+import me.grea.antoine.utils.Dice;
+import me.grea.antoine.utils.Log;
+
+/**
+ *
+ * @author antoine
+ */
+public class ProblemGenerator {
+
+    public static Set<Problem> generate(int number, int enthropy) {
+        assert (enthropy > 3);
+        Set<Problem> problems = new HashSet<>(); // Why does it had to be PROBLEMS ?!?!
+        problemgen:
+        for (int i = 0; i < number; i++) {
+            Action initial = new Action(null, Dice.roll(1, enthropy, enthropy / 5)); // 2 outta 10
+            Action goal = new Action(set(), null);
+            Domain domain = new Domain();
+            Problem problem = new Problem(initial, goal, domain, new Plan());
+
+            generateUsefull(problem, enthropy);
+
+            for (Action action : Dice.pick(domain, enthropy / 2)) {
+                domain.add(noise(action, enthropy));
+            }
+
+            while (goal.preconditions.size() < enthropy / 3) {
+                Set<Integer> effects = Dice.pick(problem.plan.vertexSet()).effects;
+                if (!effects.isEmpty()) {
[…]

### 2016-03-28 src/me/grea/antoine/lollipop/benchmark/SolutionChecker.java

@@ -1,0 +1,109 @@
+/*
+ * To change this license header, choose License Headers in Project Properties.
+ * To change this template file, choose Tools | Templates
+ * and open the template in the editor.
+ */
+package me.grea.antoine.lollipop.benchmark;
+
+import java.util.ArrayList;
+import java.util.Collection;
+import java.util.HashMap;
+import java.util.HashSet;
+import java.util.List;
+import java.util.Map;
+import java.util.Set;
+import me.grea.antoine.lollipop.type.Action;
+import me.grea.antoine.lollipop.type.Edge;
+import me.grea.antoine.lollipop.type.Plan;
+import me.grea.antoine.lollipop.type.Problem;
+import me.grea.antoine.utils.Collections;
+import static me.grea.antoine.utils.Collections.list;
+import static me.grea.antoine.utils.Collections.permute;
+import static me.grea.antoine.utils.Collections.set;
+import me.grea.antoine.utils.Log;
+
+/**
+ *
+ * @author antoine
+ */
+public class SolutionChecker {
+
+    public static boolean check(Problem problem) {
+        Set<Integer> state = new HashSet<>();
+        Set<Action> open = set(problem.initial);
+        for (Action action : problem.plan.vertexSet()) {
+            if(problem.plan.inDegreeOf(action) == 0 && problem.plan.outDegreeOf(action) > 0)
+                open.add(action);
+        }
+        
+        Set<Action> closed = new HashSet<>();
+        while (!open.isEmpty()) {
+            Set<Integer> additive = new HashSet<>(state);
+            for (List<Action> permutation : possiblePermutation(open, problem.plan)) {
+                additive = new HashSet<>(state);
+                permutee:
+                for (Action action : permutation) {
+                    if (!state.containsAll(action.preconditions)) {
+                        for (Edge edge : problem.plan.incomingEdgesOf(action)) {
+                            if (!state.containsAll(edge.labels)) {
+//                                open.remove(action);
+//                                open.add(problem.plan.getEdgeSource(edge));
+                                continue permutee;
+                            }
+                        }
+
+                        Log.w(action + " can't be applied on state " + state);
+                        return false;
+                    }
+                    additive.addAll(action.effects);
+                }
+            }
+            state.addAll(additive);
+            HashSet<Action> next = new HashSet<>();
+            closed.addAll(open);
+            for (Action action : open) {
+                choice:
+                for (Edge edge : problem.plan.outgoingEdgesOf(action)) {
[…]

### 2016-03-28 src/me/grea/antoine/lollipop/heuristic/Heuristic.java

@@ -25,10 +25,18 @@ public abstract class Heuristic {
     public abstract double h(Action action);
     
     public Comparator<Action> comparator() {
-        return (Action a1, Action a2) -> {
+        return (Action a1, Action a2) -> { 
             if (a1.equals(a2)) {
                 return 0;
             }
+            boolean a1Special = problem.isSpecial(a1);
+            boolean a2Special = problem.isSpecial(a2);
+            if(a1Special && a2Special)
+                return 0;
+            else if (a1Special)
+                return 1;
+            else if (a2Special)
+                return -1;
             return cast(h(a1)-h(a2));
         };
     }

### 2016-03-28 src/me/grea/antoine/lollipop/heuristic/Scalaire.java

@@ -26,7 +26,7 @@ public class Scalaire extends Heuristic {
     @Override
     public double h(Action action) { 
         return (action.effects.size() * -action.preconditions.size()) 
-                + (problem.domain.operatorGraph.outDegreeOf(action) * -problem.domain.operatorGraph.inDegreeOf(action)) 
+                + (problem.domain.properPlan.outDegreeOf(action) * -problem.domain.properPlan.inDegreeOf(action)) 
                 + (problem.plan.outDegreeOf(action) * -problem.plan.inDegreeOf(action));
     }
 

### 2016-03-28 src/me/grea/antoine/lollipop/type/flaw/Alternative.java

@@ -23,7 +23,6 @@ import me.grea.antoine.utils.Log;
 public class Alternative extends Flaw<Alternative> {
 
     public Action provider;
-    private static final Map<Problem, Map<Integer, Deque<Resolver>>> cache = new HashMap<>();
 
     private Alternative(Problem problem) {
         super(problem);
@@ -78,30 +77,18 @@ public class Alternative extends Flaw<Alternative> {
         for (Edge edge : problem.plan.incomingEdgesOf(troubleMaker)) {
             Action provider = problem.plan.getEdgeSource(edge);
             for (Integer label : edge.labels) {
-                Deque<Resolver> resolvers;
-                if (competitors.containsKey(label)) {
-                    resolvers = competitors.get(label);
-                } else {
-                    resolvers = new SubGoal(label, needer, problem).resolvers();
-                    competitors.put(label, resolvers);
-                }
-                for (Resolver resolver : resolvers) {
-                    if (Usefullness.compare(problem).compare(provider, resolver.source) < 0) {
-                        Log.d("⎇ " + resolver.source + " is more usefull for " + edge);
-                        alternatives.add(new Alternative(resolver.fluent, provider, resolver.target, problem));
-                        break;
-                    }
+                for (Action pretender : problem.providing.get(label)) {
+                    if(problem.heuristic.comparator().compare(provider, pretender) < 0)
+                        alternatives.add(new Alternative(label, pretender, troubleMaker, problem));
                 }
             }
         }
         return alternatives;
     }
 
-        @Override
-        public String toString
-        
-            () {
+    @Override
+    public String toString() {
         return provider + " ⎇ " + needer;
-        }
-
     }
+
+}

### 2016-03-28 src/me/grea/antoine/lollipop/type/flaw/ClassicalSubGoal.java

@@ -34,7 +34,7 @@ public class ClassicalSubGoal extends Flaw<ClassicalSubGoal> {
         Set<Action> actions = union(problem.plan.vertexSet(), problem.domain);
         for (Action action : actions) {
             if (action.effects.contains(fluent)) {
-                resolvers.addLast(new Resolver(action, needer, fluent));
+                resolvers.addLast(new ClassicalResolver(action, needer, fluent));
             }
         }
         return resolvers;

### 2016-03-28 src/me/grea/antoine/lollipop/type/flaw/Resolver.java

@@ -6,7 +6,9 @@
 package me.grea.antoine.lollipop.type.flaw;
 
 import java.util.HashSet;
+import java.util.Objects;
 import java.util.Set;
+import me.grea.antoine.lollipop.agenda.Agenda;
 import me.grea.antoine.lollipop.type.Action;
 import me.grea.antoine.lollipop.type.Edge;
 import me.grea.antoine.lollipop.type.Plan;
@@ -59,7 +61,7 @@ public class Resolver {
                 plan.removeVertex(source);
                 return;
             }
-            if (edge.labels.equals(set(fluent))) {
+            if (fluent == 0 || edge.labels.contains(fluent) && edge.labels.size() == 1) {
                 plan.removeEdge(edge);
             } else {
                 edge.labels.remove(fluent);
@@ -107,25 +109,58 @@ public class Resolver {
     }
 
     public boolean appliable(Plan plan) {
-        return negative
+        return negative  
                 ? (plan.containsEdge(source, target) || plan.containsVertex(source))
                 : //((!plan.containsEdge(source, target)
-//                || !plan.getEdge(source, target).labels.contains(fluent))
-//                && 
+                //                || !plan.getEdge(source, target).labels.contains(fluent))
+                //                && 
                 !plan.reachable(target, source);
+    }
+
+    public Set<Flaw> invalidated(Agenda agenda, Problem problem) {
+        Set<Flaw> invalidated = new HashSet<>();
+        if (negative) {
+            for (Flaw flaw : agenda) {
+                if (flaw.needer.equals(source)) {
+                    invalidated.add(flaw);
+                }
+            }
+        } else {
+            for (Flaw flaw : agenda) {
+                if (flaw instanceof Threat) {
+                    Action threatSource = problem.plan.getEdgeSource(((Threat) flaw).threatened);
+                    Action threatTarget = problem.plan.getEdgeTarget(((Threat) flaw).threatened);
+                    if ((source == threatTarget && target == ((Threat) flaw).breaker)
+                            || (source == ((Threat) flaw).breaker && target == threatSource)) {
+                        invalidated.add(flaw); // Removed solved threats
+                    }
+                }
+
+            }
+        }
+        return invalidated;
     }
 
     public Set<Flaw> related(Problem problem) {
         Set<Flaw> related = new HashSet<>();
-//        if (negative) {
-//            if (target != null) { //FIXME redo that
-//                related.addAll(SubGoal.related(target, problem));
-//            }
-//            related.addAll(Orphan.related(source, problem));
[…]

### 2016-04-11 src/me/grea/antoine/lollipop/agenda/Agenda.java
Arrrggg ! Damn you lollipop !

@@ -17,6 +17,12 @@ public abstract class Agenda extends ArrayList<Flaw> {
 
     protected final Problem problem;
     
+    public Agenda(Agenda other)
+    {
+        super(other);
+        problem = other.problem;
+    }
+    
     public Agenda(Problem problem)
     {
         this.problem = problem;

### 2016-04-11 src/me/grea/antoine/lollipop/agenda/RandomAgenda.java

@@ -19,6 +19,10 @@ import me.grea.antoine.utils.Dice;
  */
 public class RandomAgenda extends Agenda {
 
+    public RandomAgenda(Agenda other) {
+        super(other);
+    }
+    
     public RandomAgenda(Problem problem) {
         super(problem);
     }

### 2016-04-11 src/me/grea/antoine/lollipop/algorithm/PartialOrderPlanning.java

@@ -6,6 +6,7 @@
 package me.grea.antoine.lollipop.algorithm;
 
 import java.util.Deque;
+import java.util.HashSet;
 import java.util.Set;
 import me.grea.antoine.lollipop.agenda.Agenda;
 import me.grea.antoine.lollipop.agenda.ClassicalAgenda;
@@ -30,18 +31,22 @@ public class PartialOrderPlanning {
         agenda = new RandomAgenda(problem);
     }
 
-    public static void solve(Problem problem) {
-        PartialOrderPlanning pop = new PartialOrderPlanning(problem);
-        while (true) {
-            try {
-                pop.refine();
-            } catch (Success ex) {
-                Log.i("Success !");
-                return;
-            }
-            Log.w("Failure");
-            return;
+    public static boolean solve(Problem problem) {
+        if (problem.goal.preconditions.isEmpty()) {
+            problem.plan.addEdge(problem.initial, problem.goal);
+            Log.i("Goal is empty !");
+            return true;
         }
+
+        PartialOrderPlanning pop = new PartialOrderPlanning(problem);
+        try {
+            pop.refine();
+        } catch (Success ex) {
+            Log.i("Success !");
+            return true;
+        }
+        Log.w("Failure");
+        return false;
     }
 
     public void refine() throws Success {
@@ -49,13 +54,13 @@ public class PartialOrderPlanning {
             throw new Success();
         }
         Log.d("Agenda " + agenda);
-        
+
         Flaw flaw = agenda.choose();
         Log.d("Resolving " + flaw);
-        
+
         Deque<Resolver> resolvers = flaw.resolvers();
         Log.d("Resolvers " + resolvers);
-        
+
         for (Resolver resolver : resolvers) {
             Log.d("Trying with " + resolver);
 
@@ -65,15 +70,18 @@ public class PartialOrderPlanning {
                 Log.w(resolver + " isn't appliable !");
                 continue;
             }
+            Agenda oldAgenda = new RandomAgenda(agenda);
             Set<Flaw> related = resolver.related(problem);
             agenda.addAll(related);
             refine();
+            Log.w("Failure reverting the application of " + resolver);
             resolver.revert(problem.plan); // Return means failure
-            agenda.removeAll(related);
+            Log.w("Restoring agenda to " + oldAgenda);
+            agenda = oldAgenda;
         }
         agenda.add(flaw);
         Log.w("No suitable resolver for " + flaw);
[…]

### 2016-04-11 src/me/grea/antoine/lollipop/benchmark/Scalability.java

@@ -10,6 +10,7 @@ import java.io.FileNotFoundException;
 import java.io.PrintStream;
 import java.time.LocalDateTime;
 import java.util.Set;
+import me.grea.antoine.lollipop.algorithm.Lollipop;
 import me.grea.antoine.lollipop.algorithm.PartialOrderPlanning;
 import me.grea.antoine.lollipop.type.Problem;
 import me.grea.antoine.utils.Chrono;
@@ -20,28 +21,54 @@ import me.grea.antoine.utils.Log;
  * @author antoine
  */
 public class Scalability {
+
     public static void main(String[] args) {
-        Log.level = Log.Level.FATAL;
+//        Log.level = Log.Level.WARNING;
         Chrono chrono = new Chrono();
-        int number = 10000;
-        File file = new File(LocalDateTime.now() + "_" + Scalability.class + ".csv");
-        System.out.println(file.getAbsolutePath());
-        try (PrintStream result = new PrintStream(file)) {
-            for (int i = 3; i < 100; i++) {
-                Set<Problem> problems = ProblemGenerator.generate(number, i, i/2);
-                for (Problem problem : problems) {
-                    chrono.start();
-                    PartialOrderPlanning.solve(problem);
-                    chrono.stop();
+        int number = 1000;
+//        File file = new File(LocalDateTime.now() + "_" + Scalability.class + ".csv");
+//        System.out.println(file.getAbsolutePath());
+//        try (PrintStream result = new PrintStream(file)) {
+        for (int i = 5; i < 20; i++) {
+            Log.level = Log.Level.FATAL;
+            Set<Problem> problems = ProblemGenerator.generate(number, i, (int) (i * 0.3));
+            Log.level = Log.Level.VERBOSE;
+            int count = 0;
+            for (Problem problem : problems) {
+                Log.i("LOL : problem #" + count++);
+                chrono.start();
+                if (!Lollipop.solve(problem)) {
+                    Log.f("FAILLURE !!! Problem :" + problem);
                 }
-                System.out.println(i + " => " + chrono);
-                result.println(i + "," + chrono.total / number);
-                chrono.reset();
+                chrono.stop();
+                SolutionChecker.display(problem);
             }
-            result.println("Iterations/enthropy : " + number);
-            result.close();
-        } catch (FileNotFoundException ex) {
-            Log.e(ex);
+            long pop = chrono.total / number;
+//                System.out.println(i + " => POP " + chrono.total / number);
+            chrono.reset();
+
+            count = 0;
[…]

### 2016-04-11 src/me/grea/antoine/lollipop/benchmark/SolutionChecker.java

@@ -13,6 +13,7 @@ import me.grea.antoine.lollipop.type.Action;
 import me.grea.antoine.lollipop.type.Edge;
 import me.grea.antoine.lollipop.type.Plan;
 import me.grea.antoine.lollipop.type.Problem;
+import me.grea.antoine.lollipop.type.flaw.ClassicalThreat;
 import static me.grea.antoine.utils.Collections.permute;
 import static me.grea.antoine.utils.Collections.set;
 import me.grea.antoine.utils.Log;
@@ -23,10 +24,31 @@ import me.grea.antoine.utils.Log;
  */
 public class SolutionChecker {
 
+    public static void display(Problem problem) {
+        if (!SolutionChecker.check(problem)) {
+            Log.f("Solution invalid :{\n\t" + problem + "}");
+        }
+    }
+
     public static boolean check(Problem problem) {
+        if (problem.plan.edgeSet().isEmpty()) {
+            Log.w("Empty plan !");
+            return false;
+        }
+        
+        if (!problem.plan.cycles().isEmpty()) {
+            Log.w("Cycles " + problem.plan.cycles());
+            return false;
+        }
+
         Set<Integer> state = new HashSet<>();
         Set<Action> open = set(problem.initial);
         for (Action action : problem.plan.vertexSet()) {
+            Set<ClassicalThreat> threats = ClassicalThreat.related(action, problem);
+            if (!threats.isEmpty()) {
+                Log.w(action + " is threatening : " + threats);
+                return false;
+            }
             if (problem.plan.inDegreeOf(action) == 0 && problem.plan.outDegreeOf(action) > 0) {
                 if (!action.preconditions.isEmpty()) {
                     Log.w(action + " isn't satisfied at all");
@@ -55,10 +77,13 @@ public class SolutionChecker {
                         Log.w(action + " can't be applied on state " + state);
                         return false;
                     }
-                    additive.addAll(action.effects);
+                    for (int effect : action.effects) {
+                        additive.add(effect);
+                        additive.remove(-effect);
+                    }
                 }
             }
-            state.addAll(additive);
+            state = additive;
             HashSet<Action> next = new HashSet<>();
             closed.addAll(open);
             for (Action action : open) {

### 2016-04-11 src/me/grea/antoine/lollipop/mechanism/IllegalFixer.java

@@ -66,7 +66,7 @@ public class IllegalFixer {
 
     private static Set<Integer> inconsistentPrecondition(Action action) {
         Set<Integer> preconditions = new HashSet<>();
-        for (int fluent : action.effects) {
+        for (int fluent : action.preconditions) {
             if (action.preconditions.contains(-fluent)) {
                 preconditions.add(fluent);
             }
@@ -128,15 +128,14 @@ public class IllegalFixer {
     }
     
     public static boolean fixAction(Action action) { //☣
-        
-        if (action.effects.isEmpty()) {
+        if (action.effects.isEmpty() && !action.isSpecial()) {
             Log.d("◯\t" + action + " is useless ! Getting rid of it.");
             return false;
         }
 
         Set<Integer> toxic = toxicEffects(action);
         if (!toxic.isEmpty()) {
-            if (action.effects.containsAll(toxic)) {
+            if (toxic.containsAll(action.effects)) {
                 Log.d("☣\t" + action + " is entirely toxic ! Getting rid of it.");
                 return false;
             }

### 2016-04-11 src/me/grea/antoine/lollipop/mechanism/ProperPlan.java

@@ -110,6 +110,10 @@ public class ProperPlan extends Plan {
                     open.push(next);
                 }
                 Edge edge = problem.plan.addEdge(next, current);
+                if(edge == null)
+                {
+                    edge = problem.plan.getEdge(next, current);
+                }
                 edge.labels.add(precondition);
             }
         }

### 2016-04-11 src/me/grea/antoine/lollipop/type/Action.java

@@ -80,6 +80,9 @@ public class Action {
         if (this.fake != other.fake) {
             return false;
         }
+        if (!Objects.equals(this.symbol, other.symbol)) {
+            return false;
+        }
         if (!Objects.equals(this.preconditions, other.preconditions)) {
             return false;
         }

### 2016-04-11 src/me/grea/antoine/lollipop/type/Problem.java

@@ -56,4 +56,11 @@ public class Problem {
         }
         return result;
     }
+    
+    public void clear(){
+        plan = new Plan();
+        plan.addVertex(initial);
+        plan.addVertex(goal);
+        domain = new Domain(domain);
+    }
 }

### 2016-04-11 src/me/grea/antoine/lollipop/type/flaw/ClassicalThreat.java

@@ -75,7 +75,7 @@ public class ClassicalThreat extends Flaw<ClassicalThreat> {
                 forEach((fluent) -> {
                     Action source = plan.getEdgeSource(threatened);
                     Action target = plan.getEdgeTarget(threatened);
-                    if (!plan.reachable(breaker, source)
+                    if (breaker != source && breaker != target && !plan.reachable(breaker, source)
                             && !plan.reachable(target, breaker)) {
                         fluents.add(fluent);
                     }

### 2016-04-11 src/me/grea/antoine/lollipop/type/flaw/Threat.java

@@ -75,7 +75,7 @@ public class Threat extends Flaw<Threat> {
                 forEach((fluent) -> {
                     Action source = plan.getEdgeSource(threatened);
                     Action target = plan.getEdgeTarget(threatened);
-                    if (!plan.reachable(breaker, source)
+                    if (breaker != source && breaker != target && !plan.reachable(breaker, source)
                             && !plan.reachable(target, breaker)) {
                         fluents.add(fluent);
                     }

### 2016-04-15 article/article.tex
Finih ?

@@
-\documentclass[]{article}
-\usepackage{lmodern}
-\usepackage{amssymb,amsmath}
-\usepackage{ifxetex,ifluatex}
-\usepackage{fixltx2e} % provides \textsubscript
-\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
-  \usepackage[T1]{fontenc}
-  \usepackage[utf8]{inputenc}
-\else % if luatex or xelatex
-  \ifxetex
-    \usepackage{mathspec}
-  \else
-    \usepackage{fontspec}
-  \fi
-  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
-  \newcommand{\euro}{€}
-\fi
-% use upquote if available, for straight quotes in verbatim environments
-\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
-% use microtype if available
-\IfFileExists{microtype.sty}{%
-\usepackage{microtype}
-\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
-}{}
-\usepackage{hyperref}
-\PassOptionsToPackage{usenames,dvipsnames}{color} % color is loaded by hyperref
-\hypersetup{unicode=true,
-            pdftitle={SODA POP: SOft solving and Defect Aware Partial Ordering Planning},
-            pdfauthor={Paper ID\#232},
-            pdfborder={0 0 0},
-            breaklinks=true}
-\urlstyle{same}  % don't use monospace font for urls
-\usepackage{listings}
-\usepackage{graphicx,grffile}
-\makeatletter
-\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
-\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
-\makeatother
-% Scale images if necessary, so that they will not overflow the page
-% margins by default, and it is still possible to overwrite the defaults
-% using explicit options in \includegraphics[width, height, ...]{}
-\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
-\setlength{\parindent}{0pt}
-\setlength{\parskip}{6pt plus 2pt minus 1pt}
-\setlength{\emergencystretch}{3em}  % prevent overfull lines
-\providecommand{\tightlist}{%
-  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
-\setcounter{secnumdepth}{5}
-
-\title{SODA POP: SOft solving and Defect Aware Partial Ordering Planning}
-\author{Paper ID\#232}
-\date{}
-\usepackage{xcolor, listings}
-\usepackage{latex/aaai}
-\usepackage{times}
-\usepackage{helvet}
-\usepackage{courier}
-\usepackage{algorithm}
-\usepackage[noend]{algpseudocode}
-\usepackage{amsthm}
-
-% We now define the sixteen \solarized{} colors.
-\definecolor{solarized-base03} {RGB}{000, 043, 054}
-\definecolor{solarized-base02} {RGB}{007, 054, 066}
-\definecolor{solarized-base01} {RGB}{088, 110, 117}
-\definecolor{solarized-base00} {RGB}{101, 123, 131}
-\definecolor{solarized-base0}  {RGB}{131, 148, 150}
-\definecolor{solarized-base1}  {RGB}{147, 161, 161}
-\definecolor{solarized-base2}  {RGB}{238, 232, 213}
-\definecolor{solarized-base3}  {RGB}{253, 246, 227}
-\definecolor{solarized-yellow} {RGB}{181, 137, 000}
-\definecolor{solarized-orange} {RGB}{203, 075, 022}
-\definecolor{solarized-red}    {RGB}{220, 050, 047}
-\definecolor{solarized-magenta}{RGB}{211, 054, 130}
-\definecolor{solarized-violet} {RGB}{108, 113, 196}
-\definecolor{solarized-blue}   {RGB}{038, 139, 210}
-\definecolor{solarized-cyan}   {RGB}{042, 161, 152}
-\definecolor{solarized-green}  {RGB}{133, 153, 000}
-
-\newtheorem{definition}{Definition}
-
-%%%%%% for algorithms
-\errorcontextlines\maxdimen
-\algrenewcommand\alglinenumber[1]{\tiny\color{solarized-base0} #1}
-
-% begin vertical rule patch for algorithmicx (http://tex.stackexchange.com/questions/144840/vertical-loop-block-lines-in-algorithmicx-with-noend-option)
-\makeatletter
-% start with some helper code
-% This is the vertical rule that is inserted
-    \newcommand*{\algrule}[1][\algorithmicindent]{\makebox[#1][l]{\color{solarized-base0}\hspace*{.5em}\thealgruleextra\vrule height \thealgruleheight depth \thealgruledepth}}%
-% its height and depth need to be adjustable
-\newcommand*{\thealgruleextra}{}
-\newcommand*{\thealgruleheight}{.75\baselineskip}
-\newcommand*{\thealgruledepth}{.25\baselineskip}
-
-\newcount\ALG@printindent@tempcnta
-\def\ALG@printindent{%
-    \ifnum \theALG@nested>0% is there anything to print
-        \ifx\ALG@text\ALG@x@notext% is this an end group without any text?
-            % do nothing
-        \else
-            \unskip
-            \addvspace{-1pt}% FUDGE to make the rules line up
-            % draw a rule for each indent level
-            \ALG@printindent@tempcnta=1
-            \loop
-                \algrule[\csname ALG@ind@\the\ALG@printindent@tempcnta\endcsname]%
-                \advance \ALG@printindent@tempcnta 1
-            \ifnum \ALG@printindent@tempcnta<\numexpr\theALG@nested+1\relax% can't do <=, so add one to RHS and use < instead
-            \repeat
-        \fi
-    \fi
-    }%
-\usepackage{etoolbox}
-% the following line injects our new indent handling code in place of the default spacing
-\patchcmd{\ALG@doentity}{\noindent\hskip\ALG@tlm}{\ALG@printindent}{}{\errmessage{failed to patch}}
-\makeatother
-
-% the required height and depth are set by measuring the content to be shown
-% this means that the content is processed twice
-\newbox\statebox
-\newcommand{\myState}[1]{%
-    \setbox\statebox=\vbox{#1}%
-    \edef\thealgruleheight{\dimexpr \the\ht\statebox+1pt\relax}%
-    \edef\thealgruledepth{\dimexpr \the\dp\statebox+1pt\relax}%
-    \ifdim\thealgruleheight<.75\baselineskip
-        \def\thealgruleheight{\dimexpr .75\baselineskip+1pt\relax}%
-    \fi
-    \ifdim\thealgruledepth<.25\baselineskip
-        \def\thealgruledepth{\dimexpr .25\baselineskip+1pt\relax}%
-    \fi
-    %\showboxdepth=100
-    %\showboxbreadth=100
-    %\showbox\statebox
-    \State #1%
-    %\State \usebox\statebox
-    %\State \unvbox\statebox
-    %reset in case the next command is not wrapped in \myState
-    \def\thealgruleheight{\dimexpr .75\baselineskip+1pt\relax}%
-    \def\thealgruledepth{\dimexpr .25\baselineskip+1pt\relax}%
-}
-% end vertical rule patch for algorithmicx
-
-%%%% For listings (code blocks)
-\lstset{
-    basicstyle={\footnotesize\ttfamily},
-    numbers=left,
-    keywordstyle=\color{solarized-orange}\bfseries,
-%    identifierstyle=\color{solarized-base02},
-    stringstyle=\color{solarized-cyan},
-    commentstyle=\color{solarized-base1}\itshape,
-    numberstyle=\tiny\color{solarized-base0},
-    columns=flexible,
-    stepnumber=1,
-    numbersep=5pt,
-    backgroundcolor=\color{solarized-base3},
-    showspaces=false,
-    showstringspaces=false,
-    showtabs=false,
-    tabsize=2,
-    captionpos=b,
-    breaklines=true,
-    breakatwhitespace=true,
-    breakautoindent=true,
-    escapeinside={\%*}{*)},
-    linewidth=\textwidth,
-    basewidth=0.5em,
-}
-
-%\setlength{\belowcaptionskip}{-2pt}
-\setlength{\abovecaptionskip}{-12pt}
-
-%%%% For links URL
-\hypersetup{colorlinks=true, linkcolor=solarized-blue, citecolor=solarized-base1, filecolor=solarized-magenta, urlcolor=solarized-cyan}
-
-% Redefines (sub)paragraphs to behave more like sections
-\ifx\paragraph\undefined\else
-\let\oldparagraph\paragraph
-\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
-\fi
-\ifx\subparagraph\undefined\else
-\let\oldsubparagraph\subparagraph
-\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
-\fi
-
-\begin{document}
-\maketitle
-\begin{abstract}
-As of recent years, automated planning domain has mainly focused on
-performances and advances in state space planning to improve
-scalability. That orientation shadows other less efficient ways of doing
-like Partial Ordering Planning (POP) that has the advantage to be much
-more flexible. This approach generates plans that can be refined easily
-and can be used to achieve greater resilience, repairing capabilities
-and soft resolution that applications based on online plan recognition
-or decision-making can benefit from. This paper presents a set of
-algorithms, named solving and Defect Aware Partial Ordering Planning
-(SODA POP), that aims at targeting these objectives and maintain a high
-plan quality. Our algorithms create proper offline plans for goals and
-use an effective defect fixing algorithm to repair input plans even if
-these plans are corrupted. SODA POP can also use healer actions and
-links in order to always return a valid plan even in cases where the
-problem is impossible to solve using problem derivation. Some relevant
-properties of these algorithms are analyzed in this article and
-experimental results show interesting performances for online planning
-and repairing.
-\end{abstract}
-
 \section*{Introduction}\label{introduction}
@@
 
-For some time, Partial Order Planning (POP) has been the most popular
-approach to planning resolution. This kind of algorithms are based on
-\emph{least commitment strategy} on plan step ordering that allow
-actions to be flexibly interleaved during execution {[}1{]}. Thus, the
-way the search is made using flexible partial plan as a search space
-allowed for more versatility for a wide variety of uses. As of more
-recent years, new state space search approach and heuristics {[}2{]}
-have been demonstrated to be more efficient than POP planners due to the
-simplicity and relevance of state representations opposed to partial
-plans {[}3{]}. This have made the search of performance the main axis of
-research for planning.
-
-While this goal is justified, it shadows other problems that some
-practical applications cause. For example, the flexibility of Plan Space
-Planning (PSP) is an obvious advantage for applications needing online
-planning: plans can be repaired on the fly as new information and goals
-are considered. The idea of using POP for online planning and repairing
-plans instead of replanning from scratch is not new {[}4{]}, but has
-never been paired with the resilience that some other cognitive
-applications may need, especially when dealing with sensors noise in
-input data. This resilience makes fixing errors easier than with an
-external algorithm as the plan logic allows for context driven decision
-on the way to repair the issues. For example, if an action becomes
-unrelevant or incoherent, the flaw in the partial plan makes the issue
-explicit and therefore easier to fix. Applications might sometimes
-provide plans that can contain errors and imperfections that will
-decrease significantly the efficiency of the computation and the quality
-of the output plan. Additionnaly, these plans may become totally
-unsolvable. This problem is to our knowledge not treated in planning of
-all forms (state planning, PSP, and even constraint satisfaction
-planning) as usually the aim is to find a solution relative to the
-original plan (which makes sense). However, as we proceed a mechanism of
-\emph{problem derivation} may be required. This will allow soft solving
-of any problem regardless of its resolvability.
-
-One of the applications that needs these improvements is plan
-recognition with the particular use of off-the-shelf planners to infer
-the pursued goal of an agent where online planning and resilience is
-particularly important {[}5{]}. This method adds dummy actions that need
-to be satisfied by modifying the goal, to ensure that the observed plan
-is selected by the planner. A system that is able to repair plan will
-ease such an application. Another application is decision-making in
-dynamic environments. Indeed, having a plan that details all steps and
-explicits the ones that are not possible, can help decide on the plan of
-actions to take. These problems call for new ways to improve the answer
-of a planner. These improvements must provide relevant plan information
-pointing out exactly what needs to be done in order to make a planning
-problem solvable, even in the case of obviously inconsistent input data.
-This paper aims to solve this while preserving the advantages of PSP
-algorithms (flexibility, easy fixing of plans, soundness and
-completeness). We propose a new set of auxiliary algorithms that
-combined forms our SOft solving and Defect Aware Partial Ordering
-Planning (SODA POP) algorithm that targets those issues and allows
-making POP algorithm more resilient, efficient and relevant. This is
-done by pre-emptively computing proper plans for goals, by solving new
-kinds of defects that input plans may exhibit, and by healing
-compromised plan by deriving the initial problem with forged actions to
-allow resolution. To explain this work we first introduce a few notions,
-notations and specificities of existing POP algorithms. Then we present
-and illustrate their limitations, categorizing the different defects
-arising from the resilience problem and explaining our auxiliary
-algorithms, their uses and properties. We compare the performance,
-resilience and quality of POP and our solution.
-
-\section{Definitions}\label{definitions}
-
-First, we introduce some definitions and notations for mathematical
-representation to present our model.
-
-\subsection{Classical planning}\label{classical-planning}
-
-\begin{definition}[Fluents]
-
-A fluent is a property of the world. We note \(\lnot f\) the
-complementary fluent of \(f\) meaning that \(f\) is true when
-\(\lnot f\) is false and vice-versa.
-
-\end{definition}
-
-It is often represented by first order logical propositions but in this
-paper we choose to focus on the algorithm and to represent fluents as
-simple literals (fully instantiated) using \(\mathbb{Q}^*\), the set of
-relative integers without \(0\), as the fluent domain. We use negative
-integers to represent opposite fluents.
-
-\begin{definition}[State]
-
-A state is defined as a set of fluents. States can be additively
-combined. We note
-\(s_1 + s_2 = \left( s_1 \cup s_2 \right) - \left\{ f \middle| f \in s_1 \land \lnot f \in s_2 \right\}\)
-such operation. It is the union of the fluents with an erasure of the
-complementary ones.
-
-\end{definition}
-
-\begin{definition}[Action]
-
-An action is a state operator. It is represented as a tuple
-\(a = \langle pre, eff \rangle\) with \(pre\) and \(eff\) being sets of
-fluents, respectively the preconditions and the effects of \(a\). An
-action can be used only in a state that verifies its preconditions. We
-note \(s \models a \Leftrightarrow pre(a) \subseteq s\) the verification
-of an action \(a\) by a state \(s\).
-
-\end{definition}
-
-An action \(a\) can be functionally applied to a state \(s\) as follows:
-\[a:= \substack{ \left\{ s \models a \middle| s \in S\right\} \to S\\
-    a(s) \mapsto s + eff(a)}\] with \(S\) being the set of all states.
-This means that an action adds all its effects to the state of the world
-on application (by removing complementary fluents if needed). We
-distinguish between two specific kinds of actions: actions with no
-preconditions are synonymous to a state and those with empty effect are
-called a goal.
-
-\subsection{Plan Space Planning}\label{plan-space-planning}
-
-\subsubsection{Problem}\label{problem}
-
-We define a partial plan satisfaction problem as a tuple noted
-\(P = \langle A, I, G, p \rangle\) with:
+Until the end of the 90s, Plan-Space Planning (PSP) was generally
+preferred by the automated planning community. Its early commitment,
+expressiveness, and flexibility were clear advantages over State-Space
+Planning (SSP). However, more recently, drastic improvements in state
+search planning were made possible by advanced and efficient heuristics.
+This allowed those planners to scale up more efficiently than plan-space
+search ones, notably thanks to approaches like GraphPlan
+{[}\protect\hyperlink{ref-blumux5ffastux5f1997}{1}{]}, fast-forward
+{[}\protect\hyperlink{ref-hoffmannux5fffux5f2001}{2}{]}, LAMA
+{[}\protect\hyperlink{ref-richterux5flamaux5f2011}{3}{]} and Fast
+Downward Stone Soup
+{[}\protect\hyperlink{ref-rogerux5ffastux5f2014}{4}{]}. This evolution
+led to a preference for performances upon other aspects of the problem
+of automated planning. However, some of these aspects can be more easily
+addressed in Partial Order Planning (POP), also known as Partial Order
+Causal Link (POCL) planning. For example POP, can take advantage of
+least commitment
+{[}\protect\hyperlink{ref-mccluskeyux5fengineeringux5f1997}{5}{]} that
+offers more flexibility with a partial plan that describes only the
+necessary order of the actions and not a fixed sequence of steps. POP
+has been proven to be well suited for multi-agent planning
+{[}\protect\hyperlink{ref-kvarnstromux5fplanningux5f2011}{6}{]} and
+temporal planning
+{[}\protect\hyperlink{ref-bentonux5ftemporalux5f2012}{7}{]} . These
+advantages made UCPOP
+{[}\protect\hyperlink{ref-penberthyux5fucpopux5f1992}{8}{]} one of the
+preferred POP planners of its time with works made to port some of its
+characteristics into state-based planning
+{[}\protect\hyperlink{ref-gazenux5fcombiningux5f1997}{9}{]}.
+
+Related works already tried to explore new ideas to make POP an
+attractive alternative to regular state-based planners like the
+appropriately named ``Reviving partial order planning''
+{[}\protect\hyperlink{ref-nguyenux5frevivingux5f2001}{10}{]} and VHPOP
+{[}\protect\hyperlink{ref-younesux5fvhpopux5f2003}{11}{]}. More recent
+efforts
+{[}\protect\hyperlink{ref-colesux5fforwardchainingux5f2010}{12}{]},
+{[}\protect\hyperlink{ref-sapenaux5fcombiningux5f2014}{13}{]} are trying
+to adapt the powerful heuristics from state-based planning to POP's
+approach. An interesting approach of these last efforts is found in
+{[}\protect\hyperlink{ref-shekharux5flearningux5f2016}{14}{]} with
+meta-heuristics based on offline training on the domain. However, we
+clearly note that only a few papers lay the emphasis upon plan quality
+using POP {[}\protect\hyperlink{ref-ambiteux5fplanningux5f1997}{15}{]},
+{[}\protect\hyperlink{ref-estlinux5flearningux5f1997}{16}{]}.
+
+The present paper lays the base for our project for an intelligent
+robotic system that aims to use inverted planning for plan inference in
+order to help dependent persons to accomplish tasks. This project is
+based on the works of Ramirez et al.
+{[}\protect\hyperlink{ref-ramirezux5fplanux5f2009}{17}{]} on inverted
+planning for plan inference. This context led us to seek ways to improve
+POP with better refining techniques and resolver selection. Since we
+need to handle data derived from limited robotic sensors, we need a way
+for the planner to be able to be resilient to misleading input plans.
+Another aspect of this work lies in the fact that the final system will
+need to compute online planning with a feed of observational data. In
+order to achieve this we need a planner that can:
 
@@
 \item
-  \(I\) and \(G\) being the pseudo actions representing respectively the
-  initial state and the goal.
-\item
-  \(p\) being a partial plan to refine.
-\item
-  \(A\) the set of all actions.
+  repair and optimize existing plans,
+\item
+  perform online planning efficiently
+\item
+  retain performances on complex but medium sized problems.
 \end{itemize}
 
-\begin{definition}[Partial Plan]
-
-A \emph{partial plan} is a tuple \(p = \langle A_p, L\rangle\) where
-\(A_p\) is a set of steps (actions) and \(L\) is a set of causal links
-of the form \(a_i \xrightarrow{f} a_j\), such that
-\(\{ a_i, a_j \} \subseteq A_p \land f \in eff(a_i) \cap pre(a_j)\) or
-said otherwise, this causal link means that the fluent \(f\) is provided
-by an effect of \(a_i\) to a precondition of \(a_j\). We include the
-ordering constraints of PSP in the causal links. An ordering constraint
-is noted \(a_i \to a_j\) and means that the plan means \(a_i\) as a step
-that is prior to \(a_j\) without specific cause (usually because of
-threat resolution). We note the order relation over \(A\) for an action
-\(a_i\) that is prior to the action \(a_j\) following all the causal
-links and ordering constraints \(a_i \succ a_j\). We can consider it as
-a graph formed by step as vertices and causal links as edges.
-
-\end{definition}
-
-The figure \ref{fig:legend} details how the elements of partial plans
-are represented in the rest of this paper.
+Classical POP algorithms don't meet most of these criteria but can be
+enhanced to fit the first one. Usually, POP algorithms take a problem as
+an input and use a loop or a recursive function to refine the plan into
+a solution. We can't simply use the refining recursive function in order
+to be able to use our existing partial plan. This causes multiples side
+effects if the input plan is suboptimal. \emph{Our view} on the problem
+diverges from other works: PSP is a very different approach compared to
+SSP. It is usually more computationally expensive than modern state
+space planners but brings several advantages. We want to make the most
+of them instead of trying to change POP's fundamental nature. That view
+is at the core of our model: we use the refining and least commitment
+abilities of POP in order to improve online performances and quality. In
+order to achieve this, we start by computing a \emph{proper plan} that
+is computed offline with the input of the domain. The explanation of the
+way this notion is defined and used is given in \cref{sec:properplan} of
+the present paper. Using existing partial plans as input leads to
+several issues, mainly with new flaw types that aren't treated in
+classical POP. This is why we focus the \cref{sec:negative} of our paper
+on plan quality and negative refinements. We, therefore, introduce new
+negative flaws and resolvers that aim to fix and optimize the plan: the
+\emph{alternative} and the \emph{orphan} flaws. Side effects of negative
+flaws and resolvers can lead to conflicts. In order to avoid them and
+enhance performances and quality, the algorithm needs resolver and flaw
+selection mechanisms that are explained in the \cref{sec:selection}. All
+these mechanisms are part of our aLternative Optimization with partiaL
+pLan Injection Partial Ordered Planning (LOLLIPOP) algorithm presented
+in details in \cref{sec:algorithm}. We prove that the use of these new
+mechanisms keeps LOLLIPOP sound and complete in \cref{sec:analysis}.
+Experimental results and benchmarks are presented and explained in the
+\cref{sec:results} of this paper.
+
+\section{Partial Order Planning
+Preliminaries}\label{partial-order-planning-preliminaries}
+
+\subsection{Notation}\label{notation}
+
+For the rest of this paper, we will use the notation defined in
+\cref{tbl:symbols}. In order to make some writings more concise, we use
+the symbol \(\pm\) to signify that there is a notation for the positive
+and negative symbols but the current formula works regardless the sign.
+All related notions will be defined later.
+
+\begin{table}\footnotesize
+\centering
+
+\caption{\label{tbl:symbols}Most used symbols in the paper. }
+
+\begin{tabular}{@{}ll@{}}
+\toprule
+
+Symbol & Description \\\midrule
+
+\(pre(o)\), \(eff(o)\) & Preconditions and effects of the operator
+\(o\) \\
+\(\Delta\) & Planning domain \\
+\(\Pi\) & Planning problem \\
+\(T.x\) & Access element \(x\) of tuple \(T\) \\
+\(l_{\rightarrow}\), \(l_{\leftarrow}\) & Source and target of the
+causal link \(l\) \\
+\(o_1 \succ o_2\) & Precedence operator (\(o_1\) precedes \(o_2\)) \\
+\(O^P\) & Proper plan of the set of operators \(O\) \\
+\(p.d^\pm(o)\) & Outgoing and incoming degrees of \(o\) \\
+\(o.d^\pm\) & Proper degrees of \(o\) (\(|pre(o)|\) and \(|eff(o)|\)) \\
+\(p.L^\pm(o)\) & Outgoing and incoming causal links of \(o\) \\
+\(C(p)\) & Set of cycles in partial plan \(p\) \\
+\(C_p(o)\) & Set of cycles in \(p\), \(o\) is part of \\
+\(SC_p(o)\) & \(\{o\}\) if \(o\) has a self cycle in \(p\),
+\(\emptyset\) otherwise \\
+\(F^\pm(p)\) & Set of flaws in \(p\) \\
+\(r(f)\) & Resolvers of the flaw \(f\) \\
+\(f.n\) & Needer of the flaw \(f\) \\
+\(f(p)\) & Application of the flaw \(f\) on plan \(p\) \\
+\(fs(p)\) & Full support of \(p\) \\
+\(p \models \Pi\) & The partial plan \(p\) is a valid solution of
+\(\Pi\) \\
+
+\bottomrule
+\end{tabular}
+
+\end{table}
+
+\subsection{Basic Definitions}\label{basic-definitions}
+
+Planning systems need a representation of its fluents and operators. Our
+framework is based on a classical domain definition. This is defined in
+the following definition from
+{[}\protect\hyperlink{ref-gobelbeckerux5fcomingux5f2010}{18}{]}.
+
+\begin{definition}[Domain]\label{def:domain}
+
+We define our planning domain as a tuple
+\(\Delta = \langle T, C, P, F, O \rangle\) where
+
+\begin{itemize}
+\tightlist
+\item
+  \(T\) are the \textbf{types},
+\item
+  \(C\) is the set of \textbf{domain constants},
+\item
+  \(P\) is the set of \textbf{properties} with their arities and typing
+  signatures,
+\item
+  \(F\) represents the set of \textbf{fluents} defined as potential
+  equations over the terms of the domain,
+\item
+  \(O\) is the set of optionally parameterized \textbf{operators} with
+  preconditions and effects.
+\end{itemize}
+
+\end{definition}
+
+Along with a domain, every planner needs a problem representation. For
+this, we use the classical problem representation with some special
+additions.
+
+\begin{definition}[Problem]\label{def:problem}
+
+The planning problem is defined as a tuple
+\(\Pi = \langle \Delta, C_\Pi, I, G, p\rangle\) where
+
+\begin{itemize}
+\tightlist
+\item
+  \(\Delta\) is a planning domain,
+\item
+  \(C_\Pi\) is the set of \textbf{problem constants} disjoint from the
+  domain constraints \(C\),
+\item
+  \(I\) is the \textbf{initial state},
+\item
+  \(G\) is the \textbf{goal},
+\item
+  \(p\) is a given \textbf{partial plan}.
+\end{itemize}
+
+\end{definition}
+
+The framework uses the \emph{closed world assumption} in which all
+predicates and properties that aren't defined in the initial step are
+assumed false or don't have a value.
+
+\Cref{fig:example} portrays an example of a planning domain and problem
+that we use as a guideline throughout the article.
 
@@
 \centering
-\includegraphics{graphics/legend.pdf}
-\caption{Global legend for partial plans\label{fig:legend}}
+\includegraphics{graphics/example.pdf}
+\caption{\label{fig:example}Example domain and problem featuring a robot
+that aims to fetch a lollipop in a locked kitchen. The operator
+\lstinline!go! is used for movable objects (such as the robot) to move
+to another room. The \lstinline!grab! operator is used by grabbers to
+hold objects and the \lstinline!unlock! operator is used to open a door
+when the robot holds the key.}
 \end{figure}
 
-In this figure the fluent \(6\) is a precondition of the action \(a\)
-and also an effect. The causal link is providing the fluent \(6\). The
-dotted line is an ordering constraint specifying which action should be
-placed before another. \(I\) and \(G\) are respectively the initial and
-goal step.
-
-\subsubsection{Flaws}\label{flaws}
-
-When refining a partial plan, we need to fix flaws. Those could be
-present in the input or created by the refining process. Flaws can
-either be unsatisfied subgoals or threats to causal links.
+In order to simplify this framework, we need to introduce some
+differences from the classical partial plan representation. First, the
+partial plan is a part of the problem tuple as it is a needed input of
+the LOLLIPOP algorithm.
+
+\begin{definition}[Partial Plan]
+
+We define a partial plan as a tuple \(\langle S, L, B\rangle\) with
+\(S\) the set of \textbf{steps} (semi or fully instantiated operators
+also called \emph{actions}), \(L\) the set of \textbf{causal links}, and
+\(B\) the set of \textbf{binding constraints}.
+
+\end{definition}
+
+Second we factorize the set of \emph{ordering constraints}, used in
+classical representations, as being part of the causal links. Indeed,
+causal links are always supported by an ordering constraint. The only
+case where bare ordering constraints are needed is in threats. We
+represent them with \textbf{bare causal links}. These are stored as
+causal links without bearing any fluents. Causal links can be
+represented by their bore fluents called \emph{causes}. We note
+\(f \in l\) the fact that a causal link \(l\) bears the fluent \(f\)
+(bare causal links are noted \(l = \emptyset\)). That allows us to
+introduce the \textbf{precedence operator} noted \(a_i \succ a_j\) with
+\(a_i, a_j \in S\) iff there is a path of causal links that connects
+\(a_i\) to \(a_j\). We call \(a_i\) \emph{anterior} to \(a_j\).
+
+A specificity of Partial Order Planning is that it fixes flaws in a
+partial plan in order to refine it into a valid plan that is a solution
+to the given problem. Next, we define the classical flaws in our
+framework.
 
@@
 
-A subgoal \(s\) is a precondition of an action \(a_s \in A_p\) with
-\(s \in pre(a_s)\) that isn't satisfied by any causal link. We can note
-a subgoal as:
-\[a_i \xrightarrow{s} a_s \notin L \mid \{ a_i, a_s \} \subseteq A_p \]
+A flaw in a partial plan, called subgoal, is a missing causal link
+required to satisfy a precondition of a step. We can note a subgoal as:
+\(a_p \xrightarrow{s} a_n \notin L \mid \{ a_p, a_n \} \subseteq S\)
+with \(a_n\) called the \textbf{needer} and \(a_p\) an eventual
+\textbf{provider} of the fluent \(s\). This fluent is called \emph{open
+condition} or \textbf{proper fluent} of the subgoal.
 
@@
 
-A step \(a_t\) is said to threaten a causal link
-\(a_i \xrightarrow{t} a_j\) if and only if
-\[\neg t \in eff(a_t) \land a_i \succ a_t \succ a_j \models L\]
-
-\end{definition}
-
-In other words, the action has a complementary effect that can be
-inserted between two actions needing this fluent while being consistent
-with the ordering constraint in \(L\).
-
-\begin{definition}[Resolvers]
-
-Resolvers are a set of actions and causal links
-\(r = \langle A_r , L_r \rangle\) that fixes flaws.
+A flaw in a partial plan called threat consists of having an effect of a
+step that can be inserted between two actions with a causal link that is
+threatened by the said effect. We say that a step \(a_b\) is threatening
+a causal link \(a_p \xrightarrow{t} a_n\) iff
+\(a_b \neq a_p \neq a_n \land \neg t \in eff(a_b) \land a_p \succ a_b \succ a_n\)
+with \(a_b\) being the \textbf{breaker}, \(a_n\) the \emph{needer} and
+\(a_p\) a \emph{provider} of the \emph{proper fluent} \(t\).
+
+\end{definition}
+
+Flaws are fixed via the application of a resolver to the plan. A flaw
+can have several resolvers that match its needs.
+
+\begin{definition}[Resolvers]\label{def:resolver}
+
+A resolver is a potential causal link defined as a tuple
+\(r = \langle a_s, a_t, f\rangle\) with:
 
@@
 \item
-  A resolver for a subgoal is an action \(a_r \in A\) that has \(s\) as
-  an effect \(s \in eff(a_r)\) inserted along with a causal link noted
-  \(a_r \xrightarrow{s} a_s\).
-\item
-  The usual resolvers for a threat are either \(a_t \to a_i\) or
-  \(a_j \to a_t\) which are called respectively promotion and demotion
-  links.
+  \(a_s, a_t \in S\) being the source and the target of the resolver,
+\item
+  \(f\) being the considered fluent.
 \end{itemize}
@@
 
-\begin{definition}[Solution]
-
-The solution of a PSP problem is a valid partial plan that respects the
-specification of said problem (only using actions in \(A\) and having
-the correct initial and goal step).
-
-\end{definition}
-
-\begin{definition}[Consistency]
-
-A partial plan is consistent if it contains no ordering cycles. The
-directed graph formed by step as vertices and causal links as edges
-isn't cyclical. This is important to guarantee the soundness.
-
-\end{definition}
-
-\begin{definition}[Flat Plan]
-
-We can instantiate one or several flat plans from a partial plan. A flat
-plan is an ordered sequence of actions \(\pi = [ a_1, a_2 \ldots a_n]\)
-that acts like a action \(\pi = \langle pre_\pi, eff_\pi \rangle\) and
-can be applied to a state \(s\) using functional composition operation
-\(\pi := \bigcirc_{i=1}^n a_n\).
-
-\end{definition}
-
-We call a flat plan valid if and only if it can be functionally applied
-on an empty state. We note that this is different from classic state
-planning because in our case the initial state is the first action that
-is already included in the plan.
-
-\begin{definition}[Validity]
-
-A partial plan is valid if and only if it is consistent and if all flat
-plans that can be generated are valid.
-
-\end{definition}
-
-\section{Classical POP}\label{classical-pop}
-
-Partial Order Planning (POP) is a popular implementation of the general
-PSP algorithm. It refines a partial plan by trying to fix its flaws and
-is proven to be sound and complete {[}6{]}.
-
-\begin{algorithm}\caption{Classical Partial Order Planning}\label{pop}\begin{algorithmic}[1]
-
-\footnotesize
-\Function{pop}{Queue of Flaws $agenda$, Problem $P$}
-\State \Call{populate}{$agenda$, $P$} \Comment{Only on first call}
-\If{$agenda = \emptyset$} \State \Return Success
-\Comment{Stop all recursion} \EndIf
-    \State Flaw \(f\gets agenda.popFromQueue\)
-\Comment{Stop all recursion} \Comment{First element of the queue}
-\State Resolvers \(R \gets\) \Call{resolvers}{$f$, $P$}
-\State \Comment{Ordered resolvers to try} \ForAll{$r \in R$}
-\Comment{Non deterministic choice operator}
-\State \Call{apply}{$r$, $P.p$} \Comment{Apply resolver to partial plan}
-\If{\Call{consistent}{$P.p$}} \Comment{$P.p$ is the partial plan}
-\State \Call{pop}{$agenda \cup$ \protect\Call{relatedFlaws}{$f$}, $P$}
-\State \Comment{Finding new flaws introduced by the resolver} \Else 
-            \State \Call{revert}{$r$, $P.p$}
-\Comment{Undo resolver insertion} \EndIf
-    \EndFor
-    \State \Return Failure
-\State \Comment{Revert to last non deterministic choice of resolver}
-\EndFunction
-
-\end{algorithmic}\end{algorithm}
-
-Algorithm 1 presents the base algorithm for a planer in the plan space.
-POP implementation uses an agenda of flaws that is efficiently updated
-after each refinement of the plan. A flaw is selected for resolution and
-we use a non deterministic choice operator to pick a resolver for the
-flaw. The resolver is inserted in the plan and we recursively call the
-algorithm on the new plan. On failure, we return to the last non
-deterministic choice to pick another resolver. The algorithm ends when
-the agenda is empty or when there is no more resolver to pick for a
-given flaw. Before continuing, we present a simple example of classical
-POP execution with the following example of a problem.
+For classical flaws, the resolvers are simple to find. For a
+\emph{subgoal} the resolvers are sets of the potential causal links
+between a possible provider of the proper fluent and the needer. To
+solve a \emph{threat} there are mainly two resolvers: a causal link
+between the needer and the breaker called \textbf{demotion} or a causal
+link between the breaker and the provider called \textbf{promotion}.
+
+Once the resolver is applied, another important step is needed in order
+to be able to keep refining. The algorithm needs to take into account
+the \textbf{side effects} the application of the resolver had on the
+partial plan. Side effects are searched by type.
+
+\begin{definition}[Side effects]\label{def:sideeffect}
+
+Flaws that arise because of the application of a resolver on the partial
+plan are called causal side effects or \emph{related flaws}. They are
+caused by an action \(a_t\) called the \textbf{trouble maker} of a
+resolver. This action is the \emph{source} of the resolver applied onto
+the plan.
+
+\end{definition}
+
+We can derive this definition for subgoals and threats:
 
@@
 \item
-  An initial state \(I = \langle \emptyset , \{ 1, 2 \} \rangle\) and a
-  goal \(G = \langle \{ 3, 4, -5, 6 \}, \emptyset \rangle\) encoded as
-  dummy steps.
-\item
-  \(a \langle \{1\}, \{3,5\} \rangle\),
-  \(b \langle \{2\}, \{4\} \rangle\) and
-  \(c \langle \{5\}, \{6\} \rangle\) are simple actions that are useful
-  to achieve the goal.
-\item
-  \(n \langle \{-8, 7\}, \{-7, 8\} \rangle\) and
-  \(l \langle \{-7, 8\}, \{-8, 7\} \rangle\) are looping actions that
-  are meant to cause cycles.
-\item
-  \(t \langle \{4\}, \{-5\} \rangle\) is meant to be threatening to the
-  plan's integrity and will generate threats.
-\item
-  \(u \langle \{4\}, \emptyset \rangle\),
-  \(v \langle \{4\}, \{4\} \rangle\),
-  \(w \langle \{9\}, \{3\} \rangle\),
-  \(x \langle \{7\}, \{-2,2\} \rangle\) are actions that will cause
-  problems. \protect\hyperlink{defects}{(cf.~Defects section)}.
+  \textbf{Related Subgoals} are all the open conditions inserted with
+  the \emph{trouble maker}. The subgoals are often searched using the
+  preconditions of the trouble maker and added when no causal links
+  satisfy them.
+\item
+  \textbf{Related Threats} are the causal links threatened by the
+  insertion of the \emph{trouble maker}. They are added when there is no
+  causal path that prevents the action to interfere with the threatened
+  causal link.
 \end{itemize}
-
-This standard way of doing has seen multiple improvements over
-expressiveness like with UCPOP {[}7{]}, Hierarchical Tasks Network to
-add more user control over sub-plans {[}8{]}, cognition with defeasible
-reasoning {[}9{]}, or speed with multiple ways to implement the popular
-fast forward method from state planning {[}10{]}. However, all these
-variants do not treat the problem of online planning, resilience and
-soft solving. Some other closer works like {[}4{]} treat the problem of
-online planning by identifying and removing trees of the partial plan.
-This is done with a heuristic that choses an unrefinemment strategies
-that causes a heavy replanning of the problem even if only one action
-needs removal. This is a significant problem when trying, for example,
-to adapt a plan with minimal changes due to replanning. Indeed, all
-these problems can affect POP's performance and quality.
 
@@
 \centering
-\includegraphics{graphics/pop.pdf}
-\caption{Standard POP result to the problem\label{fig:pop}}
+\includegraphics{graphics/partialplan1.pdf}
+\caption{\label{fig:partialplan1}Example of a partial plan occurring
+during the computation of POP on the previous example domain illustrated
+by \cref{fig:example}. Full arrows are existing causal links. The dotted
+arrow and operator depict the current resolver.}
 \end{figure}
 
-This example has been crafted to illustrate problems with standard POP
-implementations. We give a possible resulting plan of standard POP in
-figure \ref{fig:pop}. There are some issues as for how the plan has been
-built. The action \(v\) is being used even if it is useless since \(b\)
-already provided fluent \(4\). We can also notice that despite being
-contradictory the action \(x\) raised no alarm. As for ordering
-constraints, we can clearly see that the link \(a \to t\) is redundant
-with the path \(a \xrightarrow{5} c \to t\) that already ensures that
-constraint by transitivity. Also, some problems arise during execution
-with the selection of \(w\) that causes a dead-end.
-
-Of course the flaw selection mechanism of certain variants can prevent
-that to happen in that case. But often flaw selection mechanisms are
-more speed oriented and will do little if a toxic action seems to fit
-better than a more coherent but complex one. All these issues are caused
-by what we call \emph{defects} as they are not regular PSP flaws but
-they still cause problems with execution and results. We will address
-these defects and propose a way to fix them in
-\protect\hyperlink{defects}{the next section}.
-
-\section{Auxiliary algorithms to POP}\label{auxiliary-algorithms-to-pop}
-
-In order to improve POP algorithms' resilience, online performance and
-plan quality, we propose a set of auxiliary algorithms that provides POP
-with a clean and efficiently populated initial plan. The complete
-algorithm will be presented in \protect\hyperlink{soda}{the next
-section} as a combination of all auxiliary algorithms and classical POP.
-
-\subsection{Proper plan generation}\label{proper-plan-generation}
-
-\begin{algorithm}\caption{Proper plan generation for a given goal $g$}\label{properplan}\begin{algorithmic}[1]
+In the partial plan presented in \cref{fig:partialplan1}, we consider
+that a resolver providing the fluent \lstinline!robot holds key! is
+considered. This resolver will introduce the open conditions
+\lstinline!robot holds nothing, key room _room, robot room _room! since
+it just introduced this instantiation of the \lstinline!grab! operator
+in the partial plan. These will trigger the insertion of a subgoal that
+will have this new \lstinline!grab! operator as needer. The potentially
+related threat of this resolver is that the effect
+\lstinline!robot holds key! might threaten the link between the existing
+\lstinline!unlock! and \lstinline!grab! steps, but won't be considered
+since there are no way the new step can be inserted after
+\lstinline!unlock!.
+
+\subsection{Classical POP Algorithm}\label{classical-pop-algorithm}
+
+The classical POP algorithm is pretty straight forward: it starts with a
+simple partial plan and refines its \emph{flaws} until they are all
+resolved to make the found plan a solution of the problem.
+
+\begin{algorithm}\caption{Classical Partial Order Planning}\label{alg:pop}\begin{algorithmic}[1]
 
 \footnotesize
-\Function{properPlan}{Goal $g$, Actions $A$} \State Partial Plan
-\(p \gets \emptyset\) \State Actions \(relevants \gets\)
-\Call{satisfy}{$g$, $A$, $p$}
-\State \Comment{Satisfy the goal with all participating actions and links}
-\State Queue of Actions \(open \gets relevants\)
-\While{$open \neq \emptyset$} \State Action \(a\gets open.popFromQueue\)
-\State Actions \(candidates \gets\) \Call{satisfy}{$a$, $A$, $p$}
-\ForAll{$candidate \in candidates$} \If{$candidate \notin relevants$}
-\State \(open.pushToQueue(candidate)\) \EndIf
+\Function{pop}{Queue of Flaws $a$, Problem $\Pi$}
+\State \Call{populate}{$a$, $\Pi$}
+\Comment{Populate agenda only on first call} \If{$\Pi.G = \emptyset$}
+\Comment{Goal is empty, default solution is provided}
+\State \(\Pi.p.L \gets (I \rightarrow G)\) \label{line:emptygoal} \EndIf
+ \If{$a = \emptyset$} \State \Return Success
+\Comment{Stop all recursion} \EndIf
+ \State Flaw \(f \gets\) \Call{choose}{$a$} \label{line:flawselection}
+\Comment{Non deterministic choice} \State Resolvers \(R \gets\)
+\Call{resolvers}{$f$, $\Pi$} \ForAll{$r \in R$}
+\Comment{Non deterministic choice operator}
+\State \Call{apply}{$r$, $\Pi.p$} \label{line:resolverapplication}
+\Comment{Apply resolver to partial plan} \State SideEffects \(s \gets\)
+\Call{sideEffect}{$r$} \label{line:sideeffectapplication}
+\State \Call{apply}{$s$, $a$} \Comment{Side effects of the resolver}
+\If{\protect\Call{pop}{$a$, $\Pi$} = Success}
+\Comment{Refining recursively} \State \Return Success \EndIf
+ \State \Call{revert}{$r$, $\Pi.p$}
+\Comment{Failure, undo resolver insertion}
+\State \Call{revert}{$s$, $a$}
+\Comment{Failure, undo side effects application} \EndFor
+ \State \Return Failure
+\Comment{Revert to last non deterministic choice of resolver}
+\EndFunction
+
+\end{algorithmic}\end{algorithm}
+
+The algorithm~\ref{alg:pop} is inspired by
+{[}\protect\hyperlink{ref-ghallabux5fautomatedux5f2004}{19}{]}. This POP
+implementation uses an agenda of flaws that is efficiently updated after
+each refinement of the plan. At each iteration, a flaw is selected and
+removed from the agenda (line~\ref{line:flawselection}). A resolver for
+this flaw is then selected and applied
+(line~\ref{line:resolverapplication}). If all resolvers cause failures,
+the algorithm backtracks to the last resolver selection to try another
+one. The algorithm terminates when no more resolver fits a flaw
+(\lstinline!Failure!) or when all flaws have been fixed
+(\lstinline!Success!).
+
+This standard implementation has several limitations. First, it can
+easily make poor choices that will lead to excessive backtracking. It
+also can't undo redundant or non-optimal links if they don't lead to
+backtracking. To explain these limitations, we use the example described
+in \cref{fig:example} where a robot must fetch a lollipop in a locked
+room. This problem is solvable by regular POP algorithms. However, we
+can have some cases where small changes in POP's inputs can cause a lot
+of unnecessary back-tracking. For example, if we add a new action called
+\lstinline!dig_through_wall! that has as effect to be in the desired
+room but that requires a \emph{jackhammer}, the algorithm will simply
+need more backtracking. The effects could be worse if obtaining a
+jackhammer would require numerous steps (for example needing to build
+it). This problem can be solved most of the time using simple flaw
+selection mechanisms. The other limitation arises when the plan has been
+modified. This can arise in the context of dynamic environments of
+online planning applications. When POP is modified to use input plans
+{[}\protect\hyperlink{ref-sebastiaux5fgraph-basedux5f2000}{20}{]}, these
+partial plans are carefully designed not to infringe the properties
+required by POP to operate. In our case, the plan can contain misleading
+information and this can cause a variety of new problems that can only
+be fixed using new refinements methods.
+
+\section{LOLLIPOP's Approach}\label{lollipops-approach}
+
+LOLLIPOP makes use of proper plans in order to ease the initial
+backchaining of POP and to drive the flaw and resolver selection,
+including the new negative flaws we introduced for online planning
+refinements.
+
+\subsection{Proper Plan Generation}\label{sec:properplan}
+
+One of the main contributions of the present paper is our use of the
+concept of \emph{proper plan}. First of all, we define this notion.
+
+\begin{definition}[Proper Plan]
+
+A proper plan \(O^P\) of a set of operators \(O\) is a labeled directed
+graph that binds two operators with the causal link
+\(o_1 \xrightarrow{f} o_2\) iff it exists at least a unifying fluent
+\(f \in eff(o_1) \cap pre(o_2)\).
+
+\end{definition}
+
+This definition was inspired by the notion of domain causal graph as
+explained in
+{[}\protect\hyperlink{ref-gobelbeckerux5fcomingux5f2010}{18}{]} and
+originally used as heuristic in
+{[}\protect\hyperlink{ref-helmertux5ffastux5f2006}{21}{]}. Causal graphs
+have fluents as their nodes and operators as their edges. Proper plans
+are the opposite: an \emph{operator dependency graph} for a set of
+actions. A similar structure was used in
+{[}\protect\hyperlink{ref-smithux5fpostponingux5f1993}{22}{]} that
+builds the operator dependency graph of goals and uses precondition
+nodes instead of labels. This structure is very useful for getting
+information on the \emph{shape of a problem}. This shape leads to an
+intuition based on the potential usefulness or hurtfulness of operators.
+Cycles in this graph denote the dependencies of operators. We call
+\emph{co-dependent} operators that form a cycle. If the cycle is made of
+only one operator (self-loop), then it is called \emph{auto-dependent}.
+
+While building this proper plan, we need a \textbf{providing map} that
+indicates, for each fluent, the list of operators that can provide it.
+This is a simpler version of the causal graphs that is reduced to an
+associative table easier to update. The list of providers can be sorted
+in order to drive resolver selection (like detailed in
+\cref{sec:selection}). A \textbf{needing map} is also built but is only
+used for proper plan generation. We note \(\Delta^P\) the proper plan
+built with the set of operators in the domain \(\Delta\). In the
+\cref{fig:properplan}, we illustrate the application of this mechanism
+on our example from \cref{fig:example}. Continuous lines correspond the
+\emph{domain proper plan}.
+
+\begin{figure}[htbp]
+\centering
+\includegraphics{graphics/properplan.pdf}
+\caption{\label{fig:properplan}Diagram of the proper plan of example
+domain. In full arrows the proper plan computed during domain
+compilation time and in dotted arrows the dependencies are added to
+inject the initial and goal steps.}
+\end{figure}
+
+The generation of the proper plan is based upon the previous definition.
+It will explore the operators space and build a providing and needing
+map that gives the provided and needed fluents for each operator. Once
+done it iterates on every precondition and search for a satisfying cause
+in order to add the causal links to the proper plan. The
+algorithm~\ref{alg:properplan} details this procedure.
+
+\begin{algorithm}\caption{Proper plan generation and update algorithm}\label{alg:properplan}\begin{algorithmic}[1]
+
+\footnotesize
+\Function{addVertex}{Operator $o$} \State \Call{cache}{$o$}
+\Comment{Update of the providing and needing map} \If {binding}
+\Comment{boolean that indicates if the binding was requested}
+\State \Call{bind}{$o$} \EndIf
+\EndFunction
+\Function{cache}{Operator $o$} \ForAll{$eff \in eff(o)$}
+\Comment{Adds $o$ to the list of providers of $eff$}
+\State \Call{add}{$providing, eff, o$} \EndFor
+ \State \ldots{} \Comment{Same operation with needing and preconditions}
+\EndFunction
+\Function{bind}{Operator $o$} \ForAll{$pre \in pre(o)$}
+\If{$pre \in providing$} \ForAll{$p \in$ \Call{get}{$providing$, $pre$}}
+\State Link \(l \gets\) \Call{getEdge}{$p$, $o$}
+\Comment{Create the link if needed} \State \(l \gets l \cup \{pre\}\)
+\Comment{Add the fluent as a cause} \EndFor
+ \EndIf
+ \EndFor
+ \State \ldots{} \Comment{Same operation with needing and effects}
+\EndFunction
+
+\end{algorithmic}\end{algorithm}
+
+Applying the notion of proper plan for problems only needs the initial
+and goal steps added in the proper plan. In \cref{fig:properplan}, we
+depict this insertion with our previous example using dotted lines.
+However, since proper plans feature cycles, they can't be used directly
+as input to POP algorithms to ease the initial backchaining. Moreover,
+the process of refining a proper plan into a usable one could be more
+computationally expensive than POP itself.
+
+In order to give a head start to the LOLLIPOP algorithm, we propose to
+build proper plans differently with the algorithm detailed in
+algorithm~\ref{alg:safeproperplan}. A similar notion was already
+presented as ``basic plans'' in
+{[}\protect\hyperlink{ref-sebastiaux5fgraph-basedux5f2000}{20}{]}. These
+partial plans uses a more complete but slower solution for generation
+that ensures that each selected steps is \emph{necessary} for the
+solution. In our case, we built a simpler solution that can solve some
+basic planning problems but that also make early assumption (since our
+algorithm can handle them). It does a simple and fast backward
+construction of a partial plan driven by the providing map. Therefore,
+it can be tweaked with the powerful heuristics of state search planning.
+
+\begin{algorithm}\caption{Safe proper plan generation algorithm}\label{alg:safeproperplan}\begin{algorithmic}[1]
+
+\footnotesize
+\Function{safe}{Problem $\Pi$} \State Stack \(open \gets [\Pi.G]\)
+\State Stack \(closed \gets \emptyset\) \While{$open \neq \emptyset$}
+\State Operator \(o \gets\) \Call{pop}{$open$}
+\Comment{Remove $o$ from $open$} \State \Call{push}{$closed$, $o$}
+\ForAll {$pre \in pre(o)$} \State Operators \(p \gets\)
+\Call{getProviding}{$\pi$, $pre$} \Comment{Sorted by usefulness}
+\If{$p = \emptyset$} \Comment{(see section~\ref{sec:selection})}
+\State \(\Pi.p.S \gets \Pi.p.S \setminus \{p\}\) \Continue
+ \EndIf
+ \State Operator \(o' \gets\) \Call{getFirst}{$p$}
+\label{line:safefirst} \If{$o' \in closed$} \Continue
+ \EndIf
+ \If{$o' \not \in \Pi.p.S$} \State \Call{push}{$open$, $o'$} \EndIf
+ \State \(\Pi.p.S \gets \Pi.p.S \cup \{o'\}\) \State Link \(l \gets\)
+\Call{getEdge}{$o'$, $o$} \Comment{Create the link if needed}
+\State \(l \gets l \cup \{pre\}\) \Comment{Add the fluent as a cause}
 \EndFor
@@
 
+This algorithm is very useful since it is specifically used on goals.
+The result is a valid partial plan that can be used as input to POP
+algorithms.
+
+\subsection{Negative Refinements and Plan
+Optimization}\label{sec:negative}
+
+Classical POP algorithm works upon a principle of positive plan
+refinements. The two standard flaws (subgoals and threats) are fixed by
+\emph{adding} steps, causal links, or variable binding constraints to
+the partial plan. Online planning needs to be able to \emph{remove} part
+of the plan that isn't necessary for the solution. Since we assume that
+the input partial plan is quite complete, we need to define new flaws to
+optimize and fix this plan. These flaws are called \emph{negative} as
+their resolvers apply subtractive refinements on partial plans.
+
+\begin{definition}[Alternative]\label{def:alternative}
+
+An alternative is a negative flaw that occurs when it exists a better
+provider choice for a given link. An alternative to a causal link
+\(a_p \xrightarrow{f} a_n\) is a provider \(a_b\) that has a better
+\emph{utility value} than \(a_p\).
+
+\end{definition}
+
+The \textbf{utility value} of an operator is a measure of usefulness at
+the heart of our ranking mechanism detailed in \cref{sec:selection}. It
+uses the incoming and outgoing degrees of the operator in the domain
+proper plan to measure its usefulness.
+
+Finding an alternative to an operator is computationally expensive. It
+requires searching a better provider for every fluent needed by a step.
+In order to simplify that search, we select only the best provider for a
+given fluent and check if the one used is the same one. If not, we add
+the alternative as a flaw. This search is done only on updated steps for
+online planning. Indeed, the safe proper plan mechanism is guaranteed to
+only choose the best provider (algorithm~\ref{alg:safeproperplan} at
+line~\ref{line:safefirst}). Furthermore, subgoals won't introduce new
+fixable alternative as they are guaranteed to select the best possible
+provider.
+
+\begin{definition}[Orphan]
+
+An orphan is a negative flaw that means that a step in the partial plan
+(other than the initial or goal step) is not participating in the plan.
+Formally, \(a_o\) is an orphan iff
+\(a_o \neq I \land a_o \neq G \land \left( p.d^+(a_o) = 0 \right) \lor \forall l \in p.L^+(a_o), l=\emptyset\).
+
+\end{definition}
+
+With \(p.d^+(a_o)\) being the \emph{outgoing degree} of \(a_o\) in the
+directed graph formed by \(p\) and \(p.L^+(a_o)\) being the set of
+\emph{outgoing causal links} of \(a_o\) in \(p\). This last condition
+checks for \emph{hanging orphans} that are bound with the goal with only
+bare causal links introduced by threat resolution.
+
+The introduction of negative flaws requires modifying the resolver
+definition (cf. definition~\ref{def:resolver}).
+
+\begin{definition}[Signed Resolvers]
+
+A signed resolver is a resolver with a notion of sign. We add to the
+resolver tuple the sign of the resolver noted \(s \in \{+, -\}\).
+
+\end{definition}
+
+The previously defined negative flaws have all their associated negative
+resolvers. The solution to an alternative is a negative refinement that
+simply removes the targeted causal link. This causes a new subgoal as a
+side effect, that will prioritize its resolver by its rank (explained in
+\cref{sec:selection}) and then pick the first provider (the most useful
+one). The resolver for orphans is the negative refinement that is meant
+to remove a step and its incoming causal link while tagging its
+providers as potential orphans.
+
 \begin{figure}[htbp]
 \centering
-\includegraphics{graphics/proper.pdf}
-\caption{Proper plan of the example goal\label{fig:proper}}
+\includegraphics{graphics/sideeffects.pdf}
+\caption{\label{fig:sideeffects}Schema representing flaws with their
+signs, resolvers and side effects relative to each other}
 \end{figure}
 
-As in online planning goals can be known in advance, we propose a new
-mechanism that generates proper plans for goals. We take advantage of
-the fact that this step can be done offline to improve the performance
-of online planning. This offline execution prevents us to access the
-details of the initial state of the world as it will be defined at
-runtime. We define for that the concept of \emph{participating action}.
-An action \(a \in A\) participates in a goal \(G\) if and only if \(a\)
-has an effect \(f\) that is needed to accomplish \(G\) or that is needed
-to accomplish another participating action's preconditions. A proper
-plan is a partial plan that contains all participating actions as steps
-and causal links that bind them with the step they are participating in.
-This proper plan is independent from the initial step because we might
-not have the initial step at the time of the proper plan generation.
-Once applied on the previous example, proper plan generation returns the
-partial plan presented in figure \ref{fig:proper}. This partial plan
-doesn't have initial state because of its offline nature. It also shows
-several cycles and obvious problems. However, it has all the steps of
-the correct final plan. This algorithm helps the POP algorithm by
-prefetching all the actions subgoals might need. However, this result
-needs to be cleaned first to be helpful.
-
-\hypertarget{defects}{\subsection{Defect resolution}\label{defects}}
-
-\begin{algorithm}\caption{Defect resolution}\label{defectresolution}\begin{algorithmic}[1]
-
-\footnotesize
-\Function{clean}{Problem $P$}
-\State \Call{assert}{$pre(P.I) = \emptyset$}
-\State \Call{assert}{$eff(P.G) = \emptyset$}
-\State \(P.p.A_p \gets P.p.A_p \cup \{P.I, P.G\}\)
-\State \(defects \gets\) \Call{findDefects}{$P$}
-\State \Call{fix}{$defects$, $P$} \EndFunction
-
-\Function{fix}{Defects $defects$, Problem $P$}
-\ForAll{Defect $d \in defects$} \State \(defect.\)\Call{fix}{$P$}
-\Comment{Fixing is proper to the defect} \EndFor
-\EndFunction
-
-\Function{findDefects}{Problem $P$} \State \Return \Call{illegal}{$P$}
-\(+\) \Call{interfering}{$P$}
-\State \Comment{Concatenate the found illegal and interfering defects}
-\EndFunction
-
-\end{algorithmic}\end{algorithm}
-
-When the POP algorithm is used to refine a given plan (that was not
-generated with POP or that was altered), a set of new defects can be
-present in it interfering in the resolution and sometimes making it
-impossible to solve. We emphasize that these \emph{defects are not
-regular POP flaws} but new problems that classical POP can't solve. The
-aim of this auxiliary algorithm is to clean the plans from such defects
-in order to improve resilience and plan quality.
-
-\begin{definition}[Plan Quality]
-
-Plan quality is an indicator that is measured by the number of defects
-in a partial plan. There are two specific indicators for a plan quality:
+The side effect mechanism also needs an upgrade since the new kind of
+flaws can easily interfere with one another. This is why we extend the
+side effect definition (definition~\ref{def:sideeffect}) with a notion
+of sign.
+
+\begin{definition}[Signed Side Effects]
+
+A signed side effect is either a regular \emph{causal side effect} or an
+\emph{invalidating side effect}. The sign of a side effect indicates if
+the related flaw needs to be added or removed from the agenda.
+
+\end{definition}
+
+The \cref{fig:sideeffects} exposes the extended notion of signed
+resolvers and side effects. When treating positive resolvers, nothing
+needs to change from the classical method. When dealing with negative
+resolvers, we need to search for additional subgoals and threats.
+Deletion of causal links and steps can cause orphan flaws that need to
+be identified for removal.
+
+In {[}\protect\hyperlink{ref-peotux5fthreatremovalux5f1993}{23}{]}, a
+\textbf{invalidating side effect} is explained under the name of
+\emph{DEnd} strategy. In classical POP, it has been noticed that threats
+can disappear in some cases if subgoals or other threats were applied
+before them. For our formalism, we decide to gather under this notion
+every side effects that removes the need to consider a flaw. For
+example, orphans can be ``saved'' if a subgoal selects the orphan step.
+Alternatives can remove the need to compute further subgoal of a now
+orphan step as orphans simply remove the need to fix any flaws that
+concern the selected step.
+
+These interactions between flaws are decisive in the validity and
+efficiency of the whole model, that is why we aim to drive flaw
+selection in a very rigorous manner.
+
+\subsection{Driving Flaws and Resolvers Selection}\label{sec:selection}
+
+Resolvers and flaws selection are the keys to improving performances.
+Choosing a good resolver helps to reduce the branching factor that
+accounts for most of the time spent on running POP algorithms
+{[}\protect\hyperlink{ref-kambhampatiux5fdesignux5f1994}{24}{]}. Flaw
+selection is also very important for efficiency, especially when
+considering negative flaws which can conflict with other flaws.
+
+Conflicts between flaws occur when two flaws of opposite sign target the
+same element of the partial plan. This can happen for example if an
+orphan removes a step needed by a subgoal or when a threat tries to add
+a promoting link against an alternative. The use of side effects will
+prevent most of these occurrences in the agenda but a base ordering will
+increase the general efficiency of the algorithm.
+
+Based on the \cref{fig:sideeffects}, we create a base ordering of flaws
+by type. This order takes into account the number of flaw types affected
+by causal side effects.
+
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi}.}
+\tightlist
+\item
+  \textbf{Alternatives} will cut causal links that have a better
+  provider. It is necessary to identify them early since they will add
+  at least another subgoal to be fixed as a related flaw.
+\item
+  \textbf{Subgoals} are the flaws that cause most of the branching
+  factor in POP algorithms. This is why we need to make sure that all
+  open conditions are fixed before proceeding on finer refinements.
+\item
+  \textbf{Orphans} remove unneeded branches of the plan. However, these
+  branches can be found out to be necessary for the plan in order to
+  meet a subgoal. Since a branch can contain numerous actions, it is
+  preferable to let the orphan in the plan until they are no longer
+  needed. Also, threats concerning orphans are invalidated if the orphan
+  is resolved first.
+\item
+  \textbf{Threats} occur quite often in the computation. They cost a lot
+  of processing power since they need to check if there are no paths
+  that fix the flaw already. Numerous threats are generated without the
+  need of intervention
+  {[}\protect\hyperlink{ref-peotux5fthreatremovalux5f1993}{23}{]}. That
+  is why we prioritize all related subgoals and orphans before threats
+  because they can add causal links or remove threatening actions that
+  will fix the threat.
+\end{enumerate}
+
+Resolvers need to be ordered as well, especially for the subgoal flaw.
+Ordering resolvers for a subgoal is the same operation as choosing a
+provider. Therefore, the problem becomes ``how to rank operators?''. The
+most relevant information on an operator is its usefulness and
+hurtfulness. These indicate how much an operator will help and how much
+it may cause branching after selection.
+
+\begin{definition}[Degree of an operator]
+
+Degrees are a measurement of the usefulness of an operator. The notion
+is derived from the incoming and outgoing degrees of a node in a graph.
+
+We note \(p.d^+(o)\) and \(p.d^-(o)\) respectively the outgoing and
+incoming degrees of an operator in a plan \(p\). These represent the
+number of causal links that goes out or toward the operator. We call
+proper degree of an operator \(o.d^+ = |eff(o)|\) and
+\(o.d^- = |pre(o)|\) the number of preconditions and effects that
+reflects its intrinsic usefulness.
+
+\end{definition}
+
+There are several ways to use the degrees as indicators. \emph{Utility
+value} increases with every \(d^+\), since this reflects a positive
+participation in the plan. It decreases with every \(d^-\) since actions
+with higher incoming degrees are harder to satisfy. The utility value
+bounds are useful when selecting special operators. For example, a
+user-specified constraint could be laid upon an operator to ensure it is
+only selected as a last resort. This operator will be affected with the
+minimum value for the utility value. More commonly, the maximum value is
+used for initial and goal step to ensure their selection.
+
+Our ranking mechanism includes several computation steps. The first step
+is the computation of the \textbf{base scores} noted
+\(Z_0(o)=\langle o^+, o^-\rangle\). It is a tuple that contains two
+components: a positive score that acts as a participation measurement
+and a negative score that represents the dependencies of the operator.
+For each component of the score we consider a \emph{sub score array}
+noted \(S_z(o^\pm)\). We define them as follows:
 
@@
 \item
-  Action quality is the number of defects related to actions divided by
-  the number of actions.
-  \[quality_{action}(p) =  1 - \left( |ActionDefects(p)| \over |p.A_p| \right)\]
-\item
-  Link quality is the number of defects related to links divided by the
-  number of links.
+  \(S_z(o^+)\) containing only \(\Delta^P.d^+(o)\), the positive degree
+  of \(o\) in the domain proper plan. This will give a measurement of
+  the predicted usefulness of the operator.
+\item
+  \(S_z(o^-)\) containing the following sub-scores:
+
+  \begin{enumerate}
+  \def\labelenumi{\arabic{enumi}.}
+  \tightlist
+  \item
+    \(o.d^-\) the proper negative degree of \(o\). Having more
+    preconditions can lead to a potentially higher need for subgoals.
+  \item
+    \(\sum_{c \in C_{\Delta^P}(o)}|c|\) with \(C_{\Delta^P}(o)\) being
+    the set of cycles where \(o\) participates in the domain proper
+    plan. If an action is co-dependent it may lead to a dead end when
+    searching for precondition as it will form a cycle.
+  \item
+    \(|SC(o)|\) with \(SC(o)\) is the set of self-cycle \(o\)
+    participates in. This is usually symptomatic of a \emph{toxic
+    operator} (cf. definition~\ref{def:toxic}). Having an operator
+    behaving this way can lead to problems in the operator
+    instantiation.
+  \item
+    \(\left|pre(o) \setminus \Delta^P.L^-(o)\right|\) with
+    \(\Delta^P.L^-(o)\) being the set of incoming edges of \(o\) in the
+    proper plan of the domain. This represents the number of open
+    conditions in the domain proper plan. This is symptomatic of action
+    that can't be satisfied without a compliant initial step.
+  \end{enumerate}
 \end{itemize}
 
-\end{definition}
-
-From there it is obvious that plan quality will improve over POP since
-SODA POP algorithm is guaranteed to remove all defects in a plan. There
-are two kinds of defects: the illegal defects that violate base
-hypothesis of POP and the interference defects that can lead to
-excessive computational time and to poor plan quality.
-
-\subsubsection{Illegal defects}\label{illegal-defects}
-
-These defects are usually hypothesized out by existing algorithms. They
-are illegal use of partial plan representation and shouldn't happen
-under regular circumstances. They may appear if the input is generated
-by an approximate cognitive model that doesn't ensure consistency of the
-output or by unchecked corrupted data. These defects will most of the
-time simply break regular POP algorithms or at least make the
-performances decrease significantly. Illegal defects and solutions to
-fix them are presented in the following section. The first of these
-defects is pre-existing cycles in the input plan.
-
-\begin{definition}[Cycles]
-
-A cycle is the corresponding notion as in graph theory. Let's consider
-the graph of a partial plan. A cycle in this graph corresponds to a
-cycle of actions in the partial plan.
-
-\end{definition}
-
-A plan cannot contain cycles as it makes it impossible to complete.
-Cycles are usually detected as they are inserted in a plan but poor
-input can potentially contain them and break the POP algorithm as it
-cannot undo cycles. We use strongly connected component detection
-algorithm to detect cycles. Upon cycle detection, the algorithm can
-remove arbitrarily a link in the cycle to break it. In our example the
-actions \(n\) and \(l\) are meant to cause such cycles. In a plan some
-actions can be illegal for POP. Those are the actions that are
-inconsistent.
-
-\begin{definition}[Inconsistent actions]
-
-An action \(a\) is contradictory if and only if
-\[\exists f \{f, \lnot f \} \in eff(a) \lor \{f, \lnot f \} \in pre(a)\]
-
-\end{definition}
-
-We remove only one of those effects or preconditions based on the usage
-of the action in the rest of the plan. If none of those are used, we
-choose to remove both. In our previous example, the action \(x\) is one
-of these inconsistent actions with fluent \(2\) and \(-2\) in its
-effects.
-
-\begin{definition}[Toxic actions]
-
-Toxic actions are those that have effects that are already in their
-preconditions or empty effects. They are defined as:
-\[a | pre(a) \cap eff(a) \neq \emptyset \lor eff(a) = \emptyset\]
+A parameter is reserved for each sub-score. It is noted \(P_n^\pm\) with
+\(n\) being the index of the subgoal in the list. The final formula for
+the score is then defined as:
+\(o^\pm = \sum_{n=1}^{|S_z(o^\pm)|}{P_n^\pm S_z^n(o^\pm)}\)
+
+Once this score is computed, the ranking mechanism starts the second
+phase, it computes the \textbf{realization scores} that are potential
+scores that are realized once the problem is specified. It first
+searches the \emph{inapplicable operators} that are all operators in the
+domain proper plan that have a precondition that isn't satisfied with a
+causal link. Then it searches the \emph{eager operators} that provide
+fluents with no corresponding causal link (as they are not needed).
+These operators are stored in relation with their inapplicable or eager
+fluents.
+
+The third phase starts with the beginning of the solving algorithm, once
+the problem has been provided. It computes the \emph{effective
+realization scores} based on the initial and goal step. It will add
+\(P_1^+\) to \(o^+\) for each realized eager operators (if the goal
+contains the related fluent) and subtract \(P_4^-\) from \(o^-\) for
+each inapplicable operators realized by the initial step.
+
+Last, the \textbf{final score} of each operator \(o\), noted \(r_o\), is
+computed from positive and negative scores using the following formula:
+\(r_o = o^+ \alpha^{-o^-}\). This respects the criteria of having a
+bounded value for the \emph{utility value} as it ensures that the value
+is positive with \(0\) as a minimum bound and \(+\infty\) for a maximum.
+The initial and goal steps have their utility value set to the upper
+bound in order to ensure their selection of other steps.
+
+Choosing to compute the resolver selection at operator level has some
+interesting consequences on the performances. Indeed, this computation
+is much lighter than approaches with heuristics on plan space
+{[}\protect\hyperlink{ref-shekharux5flearningux5f2016}{14}{]} as it
+reduce the overhead caused by real time computation of heuristics on
+complex data. In order to reduce this overhead more, the algorithm sorts
+the providing associative array in order to easily retrieve the best
+operator for each fluent. This means that the evaluation of the
+heuristic is done only once for each operator. This reduces the overhead
+and allows for faster results on smaller plans.
+
+\subsection{LOLLIPOP Algorithm}\label{sec:algorithm}
+
+The LOLLIPOP algorithm uses the same refinement algorithm as described
+in algorithm~\ref{alg:pop}. The differences reside in the changes made
+on the notions of resolvers and side effects. In
+line~\ref{line:resolverapplication} of algorithm~\ref{alg:pop}, LOLLIPOP
+algorithm will apply negative resolvers if the selected flaw is
+negative. In line~\ref{line:sideeffectapplication}, it will search for
+both sign of side effects. Another change resides in the initialization
+of the solving mechanism and the domain as detailed in
+algorithm~\ref{alg:lollipopinit}. This algorithm contains several parts.
+First, the \textproc{domainInit} function corresponds to the code
+computed during the domain compilation time. It will prepare the
+rankings, the proper plan and its caching mechanisms. It will also use
+strongly connected component detection algorithm to detect cycles. These
+cycles are used during the base score computation
+(line~\ref{line:basescore}). We added a detection of illegal fluents and
+operators in our domain initialization (line~\ref{line:isillegal}).
+Illegal operators are either inconsistent or toxic.
+
+\begin{algorithm}\caption{LOLLIPOP initialization mechanisms}\label{alg:lollipopinit}\begin{algorithmic}[1]
+
+\footnotesize
+\Function{domainInit}{Operators $O$} \State ProperPlan \(P\)
+\State Ranking \(R\) \ForAll{Operator $o \in O$}
+\If{\Call{isIllegal}{$o$}} \Comment{Remove toxic and useless fluents}
+\label{line:isillegal} \State \(O \gets O \setminus \{o\}\)
+\Comment{If entirely toxic or useless} \Continue
+ \EndIf
+ \State \(P.\)\Call{addVertex}{$o$}
+\Comment{Add, cache and bind all operators} \EndFor
+ \State Cycles \(C \gets\) \Call{stronglyConnectedComponent}{$P$}
+\Comment{Using DFS} \State \(R.Z \gets\) \Call{baseScores}{$O$, $P$}
+\label{line:basescore} \State \(R.I \gets\) \Call{inapplicables}{$P$}
+\State \(R.E \gets\) \Call{eagers}{$P$} \EndFunction
+\Function{lollipopInit}{Problem $\Pi$}
+\State \Call{realize}{$\Pi.\Delta.R, \Pi$} \Comment{Realize the scores}
+\State \Call{cache}{$\Pi.\Delta.P, \Pi.I$}
+\Comment{Cache initial step in providing …}
+\State \Call{cache}{$\Pi.\Delta.P, \Pi.G$}
+\Comment{… as well as goal step}
+\State \Call{sort}{$\Pi.\Delta.P.providing$, $\Pi.\Delta.R$}
+\Comment{Sort the providing map} \If{$\Pi.p.L = \emptyset$}
+\State \Call{safe}{$\Pi$}
+\Comment{Computing the safe proper plan if the plan is empty} \EndIf
+ \State \Call{populate}{$a$, $\Pi$}
+\Comment{populate agenda with first flaws} \label{line:populate}
+\EndFunction
+\Function{populate}{Agenda $a$, Problem $\Pi$}
+\ForAll{Update $u \in \Pi.U$} \Comment{Updates due to online planning}
+\State Fluents \(F \gets eff(u.new) \setminus eff(u.old)\)
+\Comment{Added effects} \ForAll{Fluent $f \in F$}
+\ForAll{Operator $o \in$ \Call{better}{$\Pi.\Delta.P.providing$, $f$, $o$}}
+\ForAll{Link $l \in \Pi.P.L^+(o)$} \If{$f \in l$}
+\State \Call{addAlternative}{$a$, $f$, $o$, $\rightarrow(l)$, $\Pi$}
+\State \Comment{With $\rightarrow(l)$ the target of $l$} \EndIf
+ \EndFor
+ \EndFor
+ \EndFor
+ \State \(F \gets eff(u.old) \setminus eff(u.new)\)
+\Comment{Removed effects} \ForAll{Fluent $f \in F$}
+\ForAll{Link $l \in \Pi.P.L^+(u.new)$} \If{\Call{isLiar}{$l$}}
+\State \(\Pi.L \gets \Pi.L \setminus \{l\}\)
+\State \Call{addOrphans}{$a$, $u.new$, $\Pi$} \EndIf
+ \EndFor
+ \EndFor
+ \State \ldots{}
+\Comment{Same with removed preconditions and incomming liar links}
+\EndFor
+ \ForAll{Operator $o \in \Pi.p.S$}
+\State \Call{addSubgoals}{$a$, $o$, $\Pi$}
+\State \Call{addThreats}{$a$, $o$, $\Pi$} \EndFor
+\EndFunction
+
+\end{algorithmic}\end{algorithm}
+
+\begin{definition}[Inconsistent operators]
+
+An operator \(a\) is contradictory iff
+\(\exists f \{f, \lnot f \} \in eff(o) \lor \{f, \lnot f \} \in pre(o)\)
+
+\end{definition}
+
+\begin{definition}[Toxic operators]\label{def:toxic}
+
+Toxic operators have effects that are already in their preconditions or
+empty effects. An operator \(o\) is toxic iff
+\(pre(o) \cap eff(o) \neq \emptyset \lor eff(o) = \emptyset\)
 
@@
 Toxic actions can damage a plan as well as make the execution of POP
-algorithm much longer than necessary. This is fixed by removing the
-toxic fluents (\(pre(a) \nsubseteq eff(a)\)) by updating the effects
-with \(eff(a) = eff(a)-pre(a)\). If the effects become empty, the action
-is removed altogether from plan steps and \(A\). In our previous example
-the actions \(u\) and \(v\) are toxic as the fluent \(4\) is in the
-effects and preconditions of \(v\), and \(u\) has empty effects. In this
-case, these actions will be removed by the algorithm as they don't have
-any other effects.
-
-The defects can be related to incorrect links. The first of which are
-liar links.
+algorithm longer than necessary. This is fixed by removing the toxic
+fluents (\(pre(a) \nsubseteq eff(a)\)) and by updating the effects with
+\(eff(a) = eff(a) \setminus pre(a)\). If the effects become empty, the
+operator is removed from the domain.
+
+The \textproc{lollipopInit} function is executed during the
+initialization of the solving algorithm. We start by realizing the
+scores, then we add the initial and goal step in the providing map by
+caching them. Once the ranking mechanism is ready, we sort the providing
+map. With the ordered providing map the algorithm runs the fast
+generation of the safe proper plan for the problem's goal.
+
+The last part of this initialization (line~\ref{line:populate}) is the
+agenda population that is detailed in the \textproc{populate} function.
+During this step, we perform a search of alternatives based on the list
+of updated fluents. A big problem with online updates is that the plan
+can become outdated relative to the domain.
 
@@
 A liar link is a link that doesn't hold a fluent in the preconditions or
-effect of its source and target. We can note:
+effect of its source and target. We note:
 \[a_i \xrightarrow{f} a_j | f \notin eff(a_i) \cap pre(a_j)\]
@@
 
-A liar link can be either already present in the data or created by the
-removal of an effect of an inconsistent or toxic action (with the causal
-link still remaining).
-
-We call lies, fluents that is held by links without being in the
-connected actions . To resolve the problem we remove all lies and add
-all savior fluents, i.e.~a fluent in \(eff(a_i) \cap pre(a_j)\) that
-isn't already held by the link. We delete the link all together if it
-doesn't link any fluent.
-
-\subsubsection{Interference defects}\label{interference-defects}
-
-This kind of defects is not as problematic as the illegal ones: they
-won't make the plan unsolvable but they can still cause performance and
-quality drops. These defects can happen in POP generated plans to some
-extends. Interference defects and solutions to fix them are presented in
-the following.
-
-\begin{definition}[Redundant links]
-
-A redundant link is an ordering constraint (causal link without fluents)
-with another equivalent path of longer length int the graph form of the
-partial plan. It means that an ordering constraint \(a_i \to a_j\) is
-redundant if and only if it exists another path from \(a_i\) to \(a_j\)
-of length greater to \(1\).
-
-\end{definition}
-
-Since POP relies on those additional links, this part focuses on
-removing the ones that were generated for threat removal purpose to
-simplify the plan. For example, in figure \ref{fig:pop} we can see that
-the ordering constraint from \(a\) to \(t\) is redundant with the path
-\(a \xrightarrow{5} c \to t\) in that, it isn't needed to resolve the
-threat. Therefore, the algorithm would remove it. This reduces the
-number of edges in the plan and therefore simplifies it.
-
-Causal links can be found to compete with one another.
-
-\begin{definition}[Competing causal links]
-
-A competing link \(a_i \xrightarrow{f} a_k\) competes with another link
-\(a_j \xrightarrow{f} a_k\) if it provides the same fluent to the same
-action.
-
-\end{definition}
-
-The main difference with redundant links is that competing links are not
-related to threat resolution generated ordering constraint but confronts
-two causal links that can provide the same fluent. Another difference is
-that it cannot happen in classical POP algorithm. This kind of defects
-is making the plan more complex and can also hide useless actions which
-would potentially cause more flaws to handle than necessary. In order to
-remove the least interesting link in competing causal links, we need to
-compare their respective providing actions, to chose the most useful
-ones.
-
-\begin{definition}[Usefulness of an action]
-
-The usefulness of an action is the number of participating links
-(outgoing causal links) divided by the number of needing links (incoming
-causal links). If there are no needing links, the usefulness is simply
-the number of participating links.
-
-In the special cases if the action is either an initial step or a goal,
-the usefulness is \(+\infty\). The usefulness of savior action is \(0\).
-
-\end{definition}
-
-We choose the link with the source action having the highest usefulness.
-This replaces unnecessary savior actions and allows reducing the
-usefulness of the least action in order to eventually make it an orphan
-and prune it from the plan.
+A liar link can be created by the removal of an effect or preconditions
+during online updates (with the causal link still remaining).
+
+We call lies, fluents that are held by links without being in the
+connected operators. To resolve the problem we remove all lies. We
+delete the link altogether if it doesn't bear any fluent as a result of
+this operation. This removal triggers the addition of orphan flaws.
+
+While updated operators is very important for LOLLIPOP to be able to
+solve online planning problems, another mechanism is used in order to
+ensure that LOLLIPOP is complete. This mechanism is explained in
+lemma~\ref{lem:deadend-validity}.
+
+\section{Theoretical Analysis}\label{sec:analysis}
+
+As proven in
+{[}\protect\hyperlink{ref-penberthyux5fucpopux5f1992}{8}{]}, the
+classical POP algorithm is \emph{sound} and \emph{complete}. In order to
+prove that these properties apply to LOLLIPOP, we need to introduce some
+hypothesis:
+
+\begin{itemize}
+\tightlist
+\item
+  operators updated by online planning are known.
+\item
+  user provided steps are known.
+\item
+  user provided plans don't contain illegal artifacts. This includes
+  toxic or inconsistent actions, lying links and cycles.
+\end{itemize}
+
+First, we define some additional properties of partial plans.
+
+\begin{definition}[Full Support]\label{def:fullsupport}
+
+A partial plan \(p\) is fully supported if each of its steps
+\(o \in p.S\) is fully supported. A step is fully supported if each of
+its preconditions \(f \in pre(o)\) is supported. A precondition is fully
+supported if it exists a causal link \(l\) that provides it. We note:
+\[fs(p) \equiv
+\begin{array}{l}
+    \forall o \in p.S \thickspace \forall f \in pre(o) \thickspace \exists l \in p.L^-(o): \\
+        \left(f \in l \land \not \exists t \in p.S (l_{\rightarrow} \succ t \succ o \land \lnot f \in eff(t))\right)
+\end{array}\] with \(p.L^-(o)\) being the incoming causal links of \(o\)
+in \(p\) and \(l_{\rightarrow}\) being the source of the link.
+
+\end{definition}
+
+The following property is taken from the original proof. We present it
+again for convenience.
+
+\begin{definition}[Partial Plan Validity]\label{def:partialplanvalidity}
+
+A partial plan is a \textbf{valid solution} of a problem \(\Pi\) iff it
+is \emph{fully supported} and \emph{contains no cycles}. The validity of
+\(p\) regarding a problem \(\Pi\) is noted
+\(p \models \Pi \equiv fs(p) \land \left(C(p) = \emptyset \right)\) with
+\(C(p)\) being the set of cycles in \(p\).
+
+\end{definition}
+
+\subsection{Proof of Soundness}\label{proof-of-soundness}
+
+Based on the definition~\ref{def:partialplanvalidity} we state that:
+\begin{equation}
+\left(
+\begin{array}{l}
+    \forall pre \in pre(\Pi.G): \\
+    fs(pre) \land
+    \begin{array}{l}
+        \forall o \in \Pi.L^-_{\rightarrow}(\Pi.G) \thickspace \forall pre' \in pre(o): \\
+        \left(fs(pre')\land C_p(o) = \emptyset\right)
+    \end{array}
+\end{array}
+\right) \implies p \models \Pi\label{eq:recursivevalidity}\end{equation}
+where \(\Pi.L^-_{\rightarrow}(\Pi.G)\) is the set of direct antecedents
+of \(\Pi.G\) and \(C_p(o)\) is the set of fluents containing \(o\) in
+\(p\).
+
+This means that \(p\) is a solution if all preconditions of \(G\) are
+satisfied. We can satisfy these preconditions using operators iff their
+precondition are all satisfied and if there is no other operator that
+threatens their supporting links.
+
+First, we need to prove that \cref{eq:recursivevalidity} holds on
+LOLLIPOP initialization. We use our hypothesis to rule out the case when
+the input plan is invalid. The algorithm~\ref{alg:safeproperplan} will
+only solve open conditions in the same way subgoals do it. Therefore,
+safe proper plans are valid input plans.
+
+Since the soundness is proven for regular refinements and flaw
+selection, we need to consider the effects of the added mechanisms of
+LOLLIPOP. The newly introduced refinements are negative, they don't add
+new links:
+
+\begin{equation}\forall f \in F(p) \thickspace \forall r \in r(f): C_p(f.n) = C_{f(p)}(f.n)\label{eq:nocycle}\end{equation}
+with \(F(p)\) being the set of flaws in \(p\), \(r(f)\) being the set of
+resolvers of \(f\), \(f.n\) being the needer of the flaw and \(f(p)\)
+being the result partial plan after application of the flaw. Said
+otherwise, an iteration of LOLLIPOP won't add cycles inside a partial
+plan.
+
+The orphan flaw targets steps that have no path to the goal and
+therefore can't add new open conditions or threats. The alternative
+targets existing causal links. Removing a causal link in a plan breaks
+the full support of the target step. This is why an alternative will
+always insert a subgoal in the agenda corresponding to the target of the
+removed causal link. Invalidating side effects also don't affect the
+soundness of the algorithm since the removed flaws are already solved.
+This makes: \begin{equation}
+\forall f \in F^-(p): fs(p) \implies fs(f(p))
+\label{eq:conssupport}\end{equation} with \(F^-(p)\) being the set of
+negative flaws in the plan \(p\). This means that negative flaws don't
+compromise the full support of the plan.
+
+\Cref{eq:nocycle,eq:conssupport} leads to \cref{eq:recursivevalidity}
+being valid after the execution of LOLLIPOP. The algorithm is,
+therefore, sound.
+
+\subsection{Proof of Completeness}\label{proof-of-completeness}
+
+The soundness proof shows that LOLLIPOP's refinements don't affect the
+support of plans in term of validity. It was proven that POP is
+complete. There are several cases to explore in order to transpose the
+property to LOLLIPOP:
+
+\begin{lemma}[Conservation of Validity]
+
+If the input plan is a valid solution, LOLLIPOP returns a valid
+solution.
+
+\end{lemma}
+
+\begin{proof}
+
+With \cref{eq:nocycle,eq:conssupport} and the previous proof, the
+conservation of validity is already proved. \qedhere
+
+\end{proof}
+
+\begin{lemma}[Reaching Validity with incomplete partial plans]\label{lem:incompletevalidity}
+
+If the input plan is incomplete, LOLLIPOP returns a valid solution.
+
+\end{lemma}
+
+\begin{proof}
+
+Since POP is complete and the \cref{eq:conssupport} proves the
+conservation of support by LOLLIPOP, then the algorithm will return a
+valid solution if the provided plan is an incomplete plan and the
+problem solvable. \qedhere
+
+\end{proof}
+
+\begin{lemma}[Reaching Validity with empty partial plans]
+
+If the input plan is empty, LOLLIPOP returns a valid solution.
+
+\end{lemma}
+
+\begin{proof}
+
+This is proven using lemma~\ref{lem:incompletevalidity} and POP's
+completeness. However, we want to add a trivial case to the proof:
+\(pre(G) = \emptyset\). In this case the line~\ref{line:emptygoal} of
+the algorithm~\ref{alg:pop} will return a valid plan. \qedhere
+
+\end{proof}
+
+\begin{lemma}[Reaching Validity with a dead-end partial plan]\label{lem:deadend-validity}
+
+If the input plan is in a dead-end, LOLLIPOP returns a valid solution.
+
+\end{lemma}
+
+\begin{proof}
+
+Using input plans that can be in a undermined state is not covered by
+the original proof. The problem lies in the existing steps in the input
+plan. However, using our hypothesis we can add a failure mechanism that
+makes LOLLIPOP complete. On failure, the needer of the last flaw is
+deleted if it wasn't added by LOLLIPOP. User defined steps are deleted
+until the input plan acts like an empty plan. Each deletion will cause
+corresponding subgoals to be added to the agenda. In this case, the
+backtracking is preserved and all possibilities are explored as in POP.
+\qedhere
+
+\end{proof}
+
+As all cases are covered, these proofs show that LOLLIPOP is complete.
+
+\section{Experimental Results}\label{sec:results}
+
+The experimental results were focused around the properties of the
+algorithm for online planning. Since classical POP is unable to perform
+online planning, we tested our algorithm in relation to the time taken
+for solving the problem for the first time. We profiled the algorithm on
+a benchmark problem containing each of the possible issues described
+previously.
+
+\begin{table}\footnotesize
+\centering
+
+\caption{\label{tbl:results}Average times of \(1.000\) executions on the
+problem. First column is for a simple run on the problem. Second and
+third columns are experiments with one and two changes in the plan after
+a first solving. }
+
+\begin{tabular}{@{}llll@{}}
+\toprule
+
+\textbf{Experiment} & \emph{Single} & \emph{Online 1} & \emph{Online
+2} \\\midrule
+
+\textbf{Time (\(ms\))} & \(0.86937\) & \(0.38754\) & \(0.48123\) \\
+
+\bottomrule
+\end{tabular}
+
+\end{table}
+
+The measurements exposed in table X was made with an Intel® Core™
+i7-4720HQ with a 2.60GHz clock. Only one core was used for the solving.
+The same experiment done only with the measurement code gave a result of
+\(70 ns\) of error. We can see an increase of performance in the online
+runs because of the way they are conducted by LOLLIPOP.
 
@@
 \centering
-\includegraphics{graphics/competing.pdf}
-\caption{Example of choice for cutting competing links based on
-usefulness of actions\label{fig:competing}}
+\includegraphics{graphics/experiment.pdf}
+\caption{\label{fig:experiment}Domain used to compute the results. First
+line is the initial and goal step along with the useful actions. Second
+line contains a threatening action \(t\), two co-dependent actions \(n\)
+and \(l\), a useless action \(u\), a toxic action \(v\), a deadend
+action \(w\) and an inconsistent action \(x\)}
 \end{figure}
 
-On the left example of figure \ref{fig:competing}, the action \(a_j\)
-participates much more than the action \(a_i\) and therefore the link to
-be removed would be \(a_i \xrightarrow{f} a_k\). On the right example,
-the actions don't have different outgoing links but the action \(a_j\)
-is here much needier than its competitor. Therefore, the link to be
-removed is the link \(a_j \xrightarrow{f} a_k\).
-
-Actions can sometimes have no use in a plan as they don't contribute to
-it.
-
-\begin{definition}[Orphan actions]
-
-Orphan actions are actions without any links or actions with no outgoing
-path to the goal (meaning that it doesn't participate in the plan). That
-also concerns actions that would become orphans if another orphan action
-is removed.
-
-\end{definition}
-
-\begin{algorithm}\caption{Orphan actions finding}\label{orphanaction_find}\begin{algorithmic}[1]
-
-\footnotesize
-\Function{$OrphanAction.$find}{Problem $P$} \State Actions
-\(orphan \gets \emptyset\) \State int \(oldSize\) \Repeat
-        \State \(oldSize \gets |orphan|\)
-\ForAll{Action $step \in P.p.A_p$} \If{$step \in orphan$}
-\State continue \EndIf
-            \State int \(towardOrphan \gets 0\) \State Causal Links
-\(outgoing \gets\) \State \Call{outgoingEdgesOf}{$step$, $P.p$}
-\ForAll{Causal Link $link \in outgoing$} \If{$link.target \in orphan$}
-\State \(towardOrphan ++\) \EndIf
-            \EndFor
-            \If{$|outgoing| = towardOrphan \land step \notin \{ P.I, P.G\}$}
-\State \(orphan \gets orphan \cup \{step\}\) \EndIf
-        \EndFor
-    \Until{$oldSize \neq |orphan|$} \State \Return \(orphan\)
-\EndFunction
-
-\end{algorithmic}\end{algorithm}
-
-In order to fix this, we derive the idea of the backward removal tree of
-{[}4{]}. Algorithm 4, removes an action if all its outgoing causal links
-are leading to useless actions. It iterates over all actions until no
-new useless action is discovered. All useless actions are then removed
-from the plan.
-
-\begin{definition}[Competing actions]
-
-In the same way, links can be competing toward a common needer,
-sometimes some actions that are more suited to achieve a goal than
-others. These actions are taken into account if they have effects that
-are carried by the link, if they are more useful than the source of the
-existing link and if they wouldn't cause a cycle.
-
-\end{definition}
-
-In such a case the link is removed and another one is formed by the
-better suited action.
-
-\subsection{Soft resolution}\label{soft-resolution}
-
-\begin{algorithm}\caption{Soft resolution healing}\label{softresolution}\begin{algorithmic}[1]
-
-\footnotesize
-\Function{heal}{Problem $P$} \State int \(minViolation \gets \infty\)
-\State Plan \(best \gets P.p\) \State Flaw \(annoyer\)
-\ForAll{$\langle flaw, plan \rangle \in P.partialSolutions$} \State int
-\(currentViolation \gets\) \Call{violation}{$plan$, $P.G$}
-\If{$currentViolation < minViolation$} \State \(best \gets plan\)
-\State \(annoyer \gets flaw\)
-\State \(minViolation \gets currentViolation\) \EndIf
-    \EndFor
-    \State \(P.p \gets best\)
-\State \(P.partialSolutions \gets \emptyset\)
-\ForAll{Resolver $resolver \in$ \Call{healers}{$annoyer$}}
-\State \Call{apply}{$resolver$, $P.p$} \EndFor
-\EndFunction
-
-\end{algorithmic}\end{algorithm}
-
-This auxiliary algorithm is meant to deal with failure. It heals the
-plan to make the failure recoverable for the next iteration of POP. Of
-course it can't fix the plan by keeping the problem as it is. This
-obviously breaks some properties as the algorithm no longer adheres to
-the specification of the input, but in exchange it will always issue a
-valid plan whatever happens.
-\protect\hyperlink{hypersoundness}{(cf.~Hypersoundness section)}.
-
-Soft failure is useful when the precision and validity of the output is
-not the most important criteria we look for. In some cases (like in
-recognition processes) it is more useful to have an output even if it is
-not exact than no output at all. That is why we propose a soft failing
-mechanism for the POP algorithm. Following, we define first some
-notions, then we explain the healing algorithm.
-
-\begin{definition}[Needer]
-
-A needer is an action that needs a resolution related to a flaw. We
-define different types of needers according to the type of the flaw.
-
-\begin{itemize}
-\item
-  For a subgoal \(a_s \xrightarrow{s} a_n\) the needer is the action
-  \(a_n\) that has an unsatisfied precondition provided by an eventual
-  action \(a_s\) in the current partial plan.
-\item
-  For a threat \(a_t\) of a link \(a_p \xrightarrow{t} a_n\) the needer
-  is the target \(a_n\) of the threatened causal link.
-\end{itemize}
-
-\end{definition}
-
-\begin{definition}[Proper fluents]
-
-A proper fluent of a flaw is the one that caused the flaw. For a subgoal
-\(a_n \xrightarrow{s} a_s\), it is the unsatisfied precondition \(s\).
-For a threat \(a_t\) of a causal link \(a_p \xrightarrow{t} a_n\), it is
-the fluent \(t\) held by the threatened causal link.
-
-\end{definition}
-
-\begin{definition}[Savior]
-
-The savior of a flaw is the forged action
-\(a_s = \langle \emptyset, \{p\} \rangle | a_s \notin A\) with \(p\)
-being the proper fluent of the flaw.
-
-\end{definition}
-
-The concept of healer is made to target rogue flaws that caused total
-failure.
-
-\begin{definition}[Healers]
-
-A healer is a resolver built using the savior of the flaw in order to
-provide the missing fluents to it. The general formula of a healer is
-\(a_s \xrightarrow{p} a_n\) with \(a_s\) being the savior of the flaw.
-
-\end{definition}
-
-For threats, we need an additional healer specified as an ordering
-constraint from the threatening action to the savior \(a_t \to a_s\) to
-ensure that the savior acts after the threat and therefore provides the
-proper fluent for the needer.
-
-\begin{definition}[Violation degree]
-
-The violation degree \(v(p)\) of a plan \(p\) is an indicator of the
-violation regarding the initial problem. We note
-\(v(p) = |flaws(p)| + |saviors(A_p)|\). Said otherwise, it is the sum of
-the number of flaws and the number of saviors in the plan.
-
-\end{definition}
-
-\subsubsection{Healing process}\label{healing-process}
-
-The healing method is to keep track of reversions in the algorithm by
-storing the partial plan and the unsatisfiable flaw each time a non
-deterministic choice fails. We note the set of these failed plans \(F\).
-As the POP algorithm encounters a final failure, this auxiliary
-algorithm get called. The aim is to evaluate each backtracked partial
-plan to choose the best one.
-
-Therefore, we add an order relation for \(F\) noted
-\[\prec : p \prec q \iff v(p) < v(q) | \{p, q\} \subseteq F\]
-
-Once the POP algorithm fails completely, the soft failing algorithm can
-be invoked to heal the plan. It chooses the best plan
-\(b | \forall p \in F, b \prec p\) to heal it. If two plans have the
-same violation degree, the algorithm chooses the first one to have
-happened. The healing process is similar to how POP works: we apply the
-healer of the flaw that caused the failure of the partial plan we
-chosen. We empty the set \(F\) to allow POP to iterate further since the
-flaw is resolved. The healing process can be done for each unsolved
-flaws as POP fails repeatedly. This ensures some interesting properties
-explained in the following section.
-
-\hypertarget{soda}{\section{SODA POP and its properties}\label{soda}}
-
-The combination of classical POP and all the auxiliary algorithms
-presented previously gives SODA POP algorithm detailed in Algorithm 6.
-In this section, we focus on the properties of SODA POP.
-
-\begin{algorithm}\caption{SODA POP}\label{soda}\begin{algorithmic}[1]
-
-\footnotesize
-\Function{soda}{Problem $P$} \State \(P.p \gets\)
-\Call{properPlan}{$P.G$, $P.A$} \Comment Offline execution
-\State \Call{clean}{$P$} \State bool \(valid \gets false\)
-\While{$\lnot valid$} \State \(valid \gets\) \Call{pop}{$P$}
-\(= Success\) \If{$valid$} \State \Call{clean}{$P$}
-\State \Return \(Success\) \EndIf
-        \State \Call{heal}{$P$} \EndWhile
-\EndFunction
-
-\end{algorithmic}\end{algorithm}
-
-\subsection{Convergence property of POP}\label{convergence}
-
-First, we prove the convergence of POP. The classic planning problem is
-already proven to be decidable without functions in the fluents {[}3{]}.
-Therefore, we can categorize the termination cases.
-
-\begin{proof}[Proof of convergence]
-
-In the case of a solvable problem, POP is proven to be complete. This
-ensures that it will find a solution for the problem and therefore
-terminate. Let \(flaws(p)\) be the set of flaws of a given partial plan.
-The number of flaws is the number of subgoals plus the number of threats
-since \(flaws(p) = subgoals(p) \cup threats(p)\). We consider the number
-of actions \(|A|\) as being finite. Therefore, the number of steps in
-the plan is at worse \(|A_p| = |A|\). We also assume that actions have a
-finite number of preconditions and effects (since we don't use functions
-over fluents). This leads to
-\(|subgoals(p)| < \sum_{a \in A_p} |pre(a)| < \infty\) and
-\(|threats(p)| < |L| \le \sum_{a \in A_p} |pre(a)| < \infty\).
-
-This means the number of all possible flaws is finite. As POP resolves
-these flaws it will decrease their number and iterate over resolvers.
-The number of resolvers is \(|subgoals(p)| * |A| + |threats(p) * 2\) and
-is also finite. This means that the iteration will in the worst case be
-equal to the number of resolvers before failing. This proves termination
-and therefore that POP converges. \qedhere
-
-\end{proof}
-
-\subsection{Hypersoundness}\label{hypersoundeness}
-
-Now that we proved that regular POP converges, we can introduce the next
-property: hyper soundness.
-
-\begin{definition}[Hypersoundness]
-
-An algorithm is said to be hypersound when it gives a valid solution for
-all problems regardless of their resolvability.
-
-\end{definition}
-
-We note that this property isn't compatible with consistency regarding
-the original problem and then doesn't fit the classical idea of
-soundness that implicitly states that the validity of a solution is
-relative to the problem. In the case of hypersoundness, we find a
-solution to a derived problem \(P' = \langle A', I, G, p\rangle\). We
-note the new set \(A' = A \cup S\) with \(S\) being the set of saviors
-for all flaws that made the POP algorithm fail during the execution of
-SODA. Next we prove the hypersoundness of our algorithm using the
-convergence of POP and the way the Soft solving behaves.
-
-\begin{proof}[Proof of hypersoundness of SODA POP]
-
-The proper plan and defect fixing algorithms are obviously convergent.
-The proper plan algorithm cannot iterate more than the number of actions
-(since duplicates are forbidden) and the defect resolution will fix the
-finite number of defects present in the finite partial plan issued by
-the proper plan algorithm.
-
-POP is sound and converges. Therefore, if SODA POP converges it will
-return a valid solution for \(P'\). In the same way we proved for POP,
-the new healing process converges because it reduces the number of flaws
-in the partial plan and since this number is finite, the algorithm
-converges.\qedhere
-
-\end{proof}
-
-\subsection{Enhancement for online
-planning}\label{enhancement-for-online-planning}
-
-SODA POP algorithm can be used in dynamic online environments to allow a
-robust way to replan an existing obsolete plan. The first step prior to
-the runtime is the generation of the proper plans for all the goals that
-will be considered. For each online iteration, we take the previous
-plan, clean all defects in it and makes it loop between POP and the
-healing mechanism (if necessary). The defect cleaning will also remove
-all unnecessary savior actions and eventually make the original problem
-solvable again. Since each previous plan is almost correct, the
-algorithm will have little to no iterations to make in order to repair
-it.
-
-\section{Experimental results}\label{experimental-results}
-
-In order to verify the validity of these algorithms we implemented a
-prototype in Java. We used basic actions with integer fluents to focus
-on the way the algorithm behaves. For the simulation runs, we used a
-computer with an Intel® Core™ i7-4720HQ CPU clocking 8 cores at 2.60GHz
-and 8GB of memory. The speed was measured in nano seconds before and
-after the call to the solve function. The process has a warming up phase
-that computes random plans for a few seconds before starting the
-benchmarks.
-
-\subsection{Quality of classical POP}\label{quality-of-classical-pop}
-
-The first metric we are interested in is the performance of classical
-POP algorithm. We measure the solving time for valid problems and the
-quality of the resulting plans. We tested the algorithm with randomly
-generated valid problems. We generated those by randomly creating plans
-based on a difficulty setting that was the upper bound for the number of
-actions and half the number of possible fluents. This difficulty setting
-also made the initial and goal step larger accordingly. The actions were
-cleaned of any toxicity and were built using a forward chaining
-algorithm. We added also random unrelated actions. Each problem was
-verified by POP before being generated to ensure resolvability. As we
-clearly see in the figure \ref{fig:quality}, POP linearly increases its
-solving time depending on the problem difficulty. That obviously follows
-the fact that POP has more flaws to fix and therefore more iterations.
-As we can observe, POP has a rather high link quality with almost no
-problems issued with causal link regardless of the difficulty of the
-problem. This can be linked to either the way we generated our valid
-plans or to a real tendency of POP to not create that kind of defects on
-its own. The action quality on the other hand drops significantly as the
-difficulty gets higher. This is linked to the number of competing and
-useless actions that can make the plan simpler but are kept by the flaw
-selection mechanism of POP.
-
-\begin{figure}[htbp]
-\centering
-\includegraphics{graphics/quality.pdf}
-\caption{Action and link quality and solving time of POP over \(10^4\)
-valid problems for each difficulty\label{fig:quality}}
-\end{figure}
-
-\subsection{Performance of SODA POP}\label{performance-of-soda-pop}
-
-As SODA POP and regular POP have not the same range of capabilities we
-can't compare them hand to hand. Indeed, our algorithm always outputs
-plans with 100\% quality since the defect detection system aims to
-remove all of them. Moreover, our algorithm is hypersound so it gives
-valid plans for unsolvable problems by derivation. In this specific case
-POP won't be able to return a result and terminates more quickly as the
-plan is found unsolvable.
-
-Therefore, we measured the performances of SODA POP algorithm on
-completely random problems. Each time the algorithm outputs a solution
-with the lowest possible violation despite the complete invalidity of
-the input. In figure \ref{fig:performance} we can see the way SODA POP
-scales up on larger problems. The performances display logarithmic
-solving time. This is explained by the fact that POP has to be called
-recursively on the healed problems. The defect detection participates
-too in the increase of solving time especially the competing action
-detection that needs to iterate over all actions and edges and calculate
-usefulness for two actions each time.
-
-\begin{figure}[htbp]
-\centering
-\includegraphics{graphics/performance.pdf}
-\caption{Average solving time of SODA POP over \(10^4\) random problems
-for each difficulty\label{fig:performance}}
-\end{figure}
+In \cref{fig:experiment}, we expose the planning domain used for the
+experiments. During the domain initialization the action \(u\) and \(v\)
+are eleminated from the domain since they serve no purpose in the
+solving process. The action \(x\) is stripped of its negative effect
+\(-2\) because it is inconsistent with the effect \(2\).
+
+\begin{minipage}{\linewidth}
+
+\begin{lstlisting}
+[DEBUG] A(⊧[4]) is useless ! Getting rid of it.
+[DEBUG] A(⊧[4]+[4]) is entirely toxic ! Getting rid of it.
+\end{lstlisting}
+
+\end{minipage}
 
@@
 
-We defined our SODA POP algorithm and demonstrated its properties. The
-set of algorithms has extended capabilities of plan repairing and soft
-solving as shown in examples and simulations. While slower than POP, the
-resilience of SODA POP can be used in various applications. We aim to
-use it on the particular case of online plan recognition and decision
-making as the capabilities to derive plans and repair them will prove
-useful when comparing potential goals with observed plans. The algorithm
-can be improved with a better defect detection algorithm that can rank
-defects and start fixing the most offensive defects before targeting
-others. Also, if the competing action detection can be improved, it can
-be used as heuristic for resolver selection to improve the performances.
-Another way the present work can be improved is by extending it to the
-use of more expressive fluents and transpose all notions to variable
-domains. One possible goal would be to improve fluent domain with an
-propositional language in order to significantly boost expressiveness.
-Finally, we plan to release the software with an open source license
-soon.
+We proved that LOLLIPOP is sound and complete like POP. It also can be
+used for online planning and can refine plans further than POP with
+negative refinements that allow it to optimize plans that are already
+solution to the problem. These properties make LOLLIPOP suitable for use
+in dynamic environments often encountered in robotic applications.
+
+For future works we aim to improve the performance of our algorithm and
+its expressiveness in order to represent complex real life problems
+encountered by dependent persons. We also aim to develop a soft solving
+mechanism that aims to give the best probable plan in case of having an
+unsolvable problem. Once ready this planner will be used for plan
+recognition using inverted planning.
+
+\textbf{\#TODO Say that we are too shameful to release the source code
+to the public}
 
@@
 \hypertarget{refs}{}
-\hypertarget{ref-weldux5fintroductionux5f1994}{}
-{[}1{]} D. S. Weld, ``An introduction to least commitment planning,''
-\emph{AI magazine}, vol. 15, no. 4, p. 27, 1994.
+\hypertarget{ref-blumux5ffastux5f1997}{}
+{[}1{]} A. L. Blum and M. L. Furst, ``Fast planning through planning
+graph analysis,'' \emph{Artificial intelligence}, vol. 90, no. 1, pp.
+281--300, 1997.
+
+\hypertarget{ref-hoffmannux5fffux5f2001}{}
+{[}2{]} J. Hoffmann, ``FF: The fast-forward planning system,'' \emph{AI
+magazine}, vol. 22, no. 3, p. 57, 2001.
 
 \hypertarget{ref-richterux5flamaux5f2011}{}
-{[}2{]} S. Richter, M. Westphal, and M. Helmert, ``LAMA 2008 and 2011,''
+{[}3{]} S. Richter, M. Westphal, and M. Helmert, ``LAMA 2008 and 2011,''
 in \emph{International Planning Competition}, 2011, pp. 117--124.
 
-\hypertarget{ref-ghallabux5fautomatedux5f2004}{}
-{[}3{]} M. Ghallab, D. S. Nau, and P. Traverso, \emph{Automated
-planning: theory and practice}. Amsterdam ; Boston: Elsevier/Morgan
-Kaufmann, 2004.
-
-\hypertarget{ref-vanux5fderux5fkrogtux5fplanux5f2005}{}
-{[}4{]} R. Van Der Krogt and M. De Weerdt, ``Plan Repair as an Extension
-of Planning.'' in \emph{ICAPS}, 2005, vol. 5, pp. 161--170.
+\hypertarget{ref-rogerux5ffastux5f2014}{}
+{[}4{]} G. Röger, F. Pommerening, and J. Seipp, ``Fast Downward Stone
+Soup,'' 2014.
+
+\hypertarget{ref-mccluskeyux5fengineeringux5f1997}{}
+{[}5{]} T. L. McCluskey and J. M. Porteous, ``Engineering and compiling
+planning domain models to promote validity and efficiency,''
+\emph{Artificial Intelligence}, vol. 95, no. 1, pp. 1--65, 1997.
+
+\hypertarget{ref-kvarnstromux5fplanningux5f2011}{}
+{[}6{]} J. Kvarnström, ``Planning for Loosely Coupled Agents Using
+Partial Order Forward-Chaining.'' in \emph{ICAPS}, 2011.
+
+\hypertarget{ref-bentonux5ftemporalux5f2012}{}
+{[}7{]} J. Benton, A. J. Coles, and A. Coles, ``Temporal Planning with
+Preferences and Time-Dependent Continuous Costs.'' in \emph{ICAPS},
+2012, vol. 77, p. 78.
+
+\hypertarget{ref-penberthyux5fucpopux5f1992}{}
+{[}8{]} J. S. Penberthy, D. S. Weld, and others, ``UCPOP: A Sound,
+Complete, Partial Order Planner for ADL.'' \emph{Kr}, vol. 92, pp.
+103--114, 1992.
+
+\hypertarget{ref-gazenux5fcombiningux5f1997}{}
+{[}9{]} B. C. Gazen and C. A. Knoblock, ``Combining the expressivity of
+UCPOP with the efficiency of Graphplan,'' in \emph{Recent Advances in AI
+Planning}, Springer, 1997, pp. 221--233.
+
+\hypertarget{ref-nguyenux5frevivingux5f2001}{}
+{[}10{]} X. Nguyen and S. Kambhampati, ``Reviving partial order
+planning,'' in \emph{IJCAI}, 2001, vol. 1, pp. 459--464.
+
+\hypertarget{ref-younesux5fvhpopux5f2003}{}
+{[}11{]} H. akan L. Younes and R. G. Simmons, ``VHPOP: Versatile
+heuristic partial order planner,'' \emph{Journal of Artificial
+Intelligence Research}, pp. 405--430, 2003.
+
+\hypertarget{ref-colesux5fforwardchainingux5f2010}{}
+{[}12{]} A. J. Coles, A. Coles, M. Fox, and D. Long, ``Forward-Chaining
+Partial-Order Planning.'' in \emph{ICAPS}, 2010, pp. 42--49.
+
+\hypertarget{ref-sapenaux5fcombiningux5f2014}{}
+{[}13{]} O. Sapena, E. Onaindia, and A. Torreno, ``Combining heuristics
+to accelerate forward partial-order planning,'' \emph{Constraint
+Satisfaction Techniques for Planning and Scheduling}, p. 25, 2014.
+
+\hypertarget{ref-shekharux5flearningux5f2016}{}
+{[}14{]} S. Shekhar and D. Khemani, ``Learning and Tuning
+Meta-heuristics in Plan Space Planning,'' \emph{arXiv preprint
+arXiv:1601.07483}, 2016.
+
+\hypertarget{ref-ambiteux5fplanningux5f1997}{}
+{[}15{]} J. L. Ambite and C. A. Knoblock, ``Planning by Rewriting:
+Efficiently Generating High-Quality Plans.'' DTIC Document, 1997.
+
+\hypertarget{ref-estlinux5flearningux5f1997}{}
+{[}16{]} T. A. Estlin and R. J. Mooney, ``Learning to improve both
+efficicency and quality of planning,'' in \emph{Proceedings of the
+Fifteenth International Joint Conference on Artificial Intelligence},
+1997, pp. 1227--1233.
 
 \hypertarget{ref-ramirezux5fplanux5f2009}{}
-{[}5{]} M. Ramırez and H. Geffner, ``Plan recognition as planning,'' in
+{[}17{]} M. Ramirez and H. Geffner, ``Plan recognition as planning,'' in
 \emph{Proceedings of the 21st international joint conference on
@@
 
-\hypertarget{ref-erolux5fumcp:ux5f1994}{}
-{[}6{]} K. Erol, J. A. Hendler, and D. S. Nau, ``UMCP: A Sound and
-Complete Procedure for Hierarchical Task-network Planning.'' in
-\emph{AIPS}, 1994, vol. 94, pp. 249--254.
-
-\hypertarget{ref-penberthyux5fucpop:ux5f1992}{}
-{[}7{]} J. S. Penberthy, D. S. Weld, and others, ``UCPOP: A Sound,
-Complete, Partial Order Planner for ADL.'' \emph{Kr}, vol. 92, pp.
-103--114, 1992.
-
-\hypertarget{ref-bechonux5fhipop:ux5f2014}{}
-{[}8{]} P. Bechon, M. Barbier, G. Infantes, C. Lesire, and V. Vidal,
-``HiPOP: Hierarchical Partial-Order Planning,'' in \emph{STAIRS 2014:
-Proceedings of the 7th European Starting AI Researcher Symposium}, 2014,
-vol. 264, p. 51.
-
-\hypertarget{ref-garciaux5fdefeasibleux5f2008}{}
-{[}9{]} D. R. García, A. J. García, and G. R. Simari, ``Defeasible
-reasoning and partial order planning,'' in \emph{Foundations of
-Information and Knowledge Systems}, Springer, 2008, pp. 311--328.
-
-\hypertarget{ref-colesux5fforward-chainingux5f2010}{}
-{[}10{]} A. J. Coles, A. Coles, M. Fox, and D. Long, ``Forward-Chaining
-Partial-Order Planning.'' in \emph{ICAPS}, 2010, pp. 42--49.
-
-\end{document}
+\hypertarget{ref-gobelbeckerux5fcomingux5f2010}{}
+{[}18{]} M. Göbelbecker, T. Keller, P. Eyerich, M. Brenner, and B.
+Nebel, ``Coming Up With Good Excuses: What to do When no Plan Can be
+Found.'' in \emph{ICAPS}, 2010, pp. 81--88.
+
+\hypertarget{ref-ghallabux5fautomatedux5f2004}{}
+{[}19{]} M. Ghallab, D. Nau, and P. Traverso, \emph{Automated planning:
+theory \& practice}. Elsevier, 2004.
+
+\hypertarget{ref-sebastiaux5fgraph-basedux5f2000}{}
+{[}20{]} L. Sebastia, E. Onaindia, and E. Marzal, ``A Graph-based
+Approach for POCL Planning,'' in \emph{ECAI}, 2000, pp. 531--535.
+
+\hypertarget{ref-helmertux5ffastux5f2006}{}
+{[}21{]} M. Helmert, ``The Fast Downward Planning System.'' \emph{J.
+Artif. Intell. Res.(JAIR)}, vol. 26, pp. 191--246, 2006.
+
+\hypertarget{ref-smithux5fpostponingux5f1993}{}
+{[}22{]} D. E. Smith and M. A. Peot, ``Postponing threats in
+partial-order planning,'' in \emph{Proceedings of the Eleventh National
+Conference on Artificial Intelligence}, 1993, pp. 500--506.
+
+\hypertarget{ref-peotux5fthreatremovalux5f1993}{}
+{[}23{]} M. A. Peot and D. E. Smith, ``Threat-removal strategies for
+partial-order planning,'' in \emph{AAAI}, 1993, vol. 93, pp. 492--499.
+
+\hypertarget{ref-kambhampatiux5fdesignux5f1994}{}
+{[}24{]} S. Kambhampati, ``Design Tradeoffs in Partial Order (Plan
+space) Planning.'' in \emph{AIPS}, 1994, pp. 92--97.

### 2016-04-15 article/filters/code-minipage.hs

@@ -18,3 +18,5 @@ addMinipages [] = []
 
 beginsWithEndMinipage (RawBlock (Format "latex") "\\end{minipage}":_) = True
 beginsWithEndMinipage _ = False
+
+--https://github.com/jgm/pandoc/issues/703

### 2016-04-15 article/filters/pandoc-table.py

@@ -26,7 +26,8 @@ def tbl_headers(s):
     result = s[0][0]['c'][:]
     for i in range(1, len(s)):
         result.append(inlatex(' & '))
-        result.extend(s[i][0]['c'])
+        if len(s[i]) > 0 :
+            result.extend(s[i][0]['c'])
     result.append(inlatex(r' \\\midrule'))
     return pf.Para(result)
 

### 2016-04-15 src/me/grea/antoine/lollipop/algorithm/PartialOrderPlanning.java

@@ -30,9 +30,10 @@ public class PartialOrderPlanning {
     }
 
     public static boolean solve(Problem problem) {
+        Log.v(problem);
         if (problem.goal.preconditions.isEmpty()) {
             problem.plan.addEdge(problem.initial, problem.goal);
-            Log.i("Goal is empty !");
+//            Log.i("Goal is empty !");
             return true;
         }
 
@@ -40,10 +41,10 @@ public class PartialOrderPlanning {
         try {
             pop.refine();
         } catch (Success ex) {
-            Log.i("Success !");
+//            Log.i("Success !");
             return true;
         }
-        Log.w("Failure");
+//        Log.w("Failure");
         return false;
     }
 
@@ -51,36 +52,36 @@ public class PartialOrderPlanning {
         if (agenda.isEmpty()) {
             throw new Success();
         }
-        Log.d("Agenda " + agenda);
+//        Log.d("Agenda " + agenda);
 
         Flaw flaw = agenda.choose();
-        Log.d("Resolving " + flaw);
+//        Log.d("Resolving " + flaw);
 
         Deque<Resolver> resolvers = flaw.resolvers();
-        Log.d("Resolvers " + resolvers);
+//        Log.d("Resolvers " + resolvers);
 
         for (Resolver resolver : resolvers) {
-            Log.d("Trying with " + resolver);
+//            Log.d("Trying with " + resolver);
 
             if (resolver.appliable(problem.plan)) {
                 resolver.apply(problem.plan);
             } else {
-                Log.w(resolver + " isn't appliable !");
+//                Log.w(resolver + " isn't appliable !");
                 continue;
             }
             Agenda oldAgenda = new RandomAgenda(agenda);
             Set<Flaw> related = resolver.related(problem);
             agenda.addAll(related);
             refine();
-            Log.w("Failure reverting the application of " + resolver);
+//            Log.w("Failure reverting the application of " + resolver);
             resolver.revert(problem.plan); // Return means failure
-            Log.w("Restoring agenda to " + oldAgenda);
+//            Log.w("Restoring agenda to " + oldAgenda);
             agenda = oldAgenda;
         }
         agenda.add(flaw);
-        Log.w("No suitable resolver for " + flaw);
-        Log.d(agenda);
-        Log.v(problem.planToString());
+//        Log.w("No suitable resolver for " + flaw);
+//        Log.d(agenda);
+//        Log.v(problem.planToString());
         return flaw;
     }
 

### 2016-04-15 src/me/grea/antoine/lollipop/benchmark/Benchmark.java

@@ -22,6 +22,7 @@ import me.grea.antoine.lollipop.algorithm.PartialOrderPlanning;
 import me.grea.antoine.lollipop.persistence.ActionSerializer;
 import me.grea.antoine.lollipop.persistence.ProblemSerializer;
 import me.grea.antoine.lollipop.type.Action;
+import me.grea.antoine.lollipop.type.Domain;
 import me.grea.antoine.lollipop.type.Problem;
 import me.grea.antoine.utils.Chrono;
 import me.grea.antoine.utils.Log;
@@ -34,7 +35,7 @@ import me.grea.antoine.utils.Strings;
 public class Benchmark {
 
     static {
-        Log.level = Log.Level.FATAL;
+//        Log.level = Log.Level.FATAL;
     }
 
     public static void main(String[] args) throws FileNotFoundException {
@@ -44,32 +45,37 @@ public class Benchmark {
         Gson gson = bob.create(); //Damn son
 
         Chrono chrono = new Chrono();
-        File output = new File("results/" + LocalDateTime.now() + "_" + Lollipop.class + ".csv");
-        System.out.println(output.getAbsolutePath());
-        try (PrintStream result = new PrintStream(output)) {
-            for (File data : new File("data").listFiles()) {
-                Set<Problem> problems = gson.fromJson(new FileReader(data), new TypeToken<Set<Problem>>() {
+        File data = new File("results/" + LocalDateTime.now() + "_" + Lollipop.class + ".csv");
+        System.out.println(data.getAbsolutePath());
+        try (PrintStream result = new PrintStream(data)) {
+            for (File json : new File("data").listFiles()) {
+                Set<Problem> problems = gson.fromJson(new FileReader(json), new TypeToken<Set<Problem>>() {
                 }.getType());
-                
-                String[] extract = Strings.extract(data.getName(), "\\[(\\d+),(\\d+)\\]").get(0);
+
+                String[] extract = Strings.extract(json.getName(), "\\[(\\d+),(\\d+)\\]").get(0);
                 int enthropy = Integer.parseInt(extract[0]);
                 int hardness = Integer.parseInt(extract[1]);
-                
+                System.out.println(enthropy + "," + hardness);
+
                 double quality = 0;
 
                 for (Problem problem : problems) {
+                    problem.domain = new Domain(problem.domain);
                     chrono.start();
-                    Lollipop.solve(problem);
+                    if (!Lollipop.solve(problem)) {
[…]

### 2016-04-15 src/me/grea/antoine/lollipop/benchmark/ProblemGenerator.java

@@ -10,6 +10,14 @@ import static java.lang.Integer.min;
 import java.util.Collection;
 import java.util.HashSet;
 import java.util.Set;
+import java.util.concurrent.ExecutionException;
+import java.util.concurrent.Executors;
+import java.util.concurrent.TimeUnit;
+import java.util.concurrent.TimeoutException;
+import java.util.logging.Level;
+import java.util.logging.Logger;
+import me.grea.antoine.lollipop.algorithm.Lollipop;
+import me.grea.antoine.lollipop.algorithm.PartialOrderPlanning;
 import me.grea.antoine.lollipop.type.Action;
 import me.grea.antoine.lollipop.type.Domain;
 import me.grea.antoine.lollipop.type.Edge;
@@ -41,9 +49,8 @@ public class ProblemGenerator {
         problemgen:
         for (int i = 0; i < number; i++) {
             Log.i("i=>" + i);
-            Log.level = Log.Level.FATAL;
             Action initial = new Action(null, new HashSet<>()); // 2 outta 10
-            Action goal = new Action(Dice.roll(1, enthropy, max(Dice.roll(1, enthropy), hardness)), null);
+            Action goal = new Action(Dice.roll(1, enthropy, max(1, min(Dice.roll(1, enthropy / 2), hardness))), null);
             Domain domain = new Domain();
             Problem problem = new Problem(initial, goal, domain, new Plan());
 
@@ -61,13 +68,31 @@ public class ProblemGenerator {
             }
 
 //            Log.i(problem);
+            yanamar = YANAMAR;
             if (!SolutionChecker.check(problem)) {
-                Log.f("Generated solution is INVALID !!! \n" + problem);
+                Log.e("Generated solution is INVALID !!! \n" + problem);
+                i--;
+
+                continue;
             }
             problem.expectedLength = problem.plan.vertexSet().size();
             problem.clear();
+            try {
+                if (!Executors.newSingleThreadExecutor().submit(() -> {
+                    return Lollipop.solve(problem);
+                }).get(1200, TimeUnit.MILLISECONDS)) {
+                    Log.e("POP didn't make it !!! \n" + problem);
+                    i--;
+                    continue;
+                }
+            } catch (ExecutionException | InterruptedException | TimeoutException ex) {
+                Log.e("POP took too long !!! \n");
+                i--;
+                continue;
+            }
+            problem.clear();
+
             problems.add(problem);
-            Log.level = Log.Level.VERBOSE;
[…]

### 2016-04-15 src/me/grea/antoine/lollipop/mechanism/Ranking.java

@@ -29,13 +29,15 @@ import static java.lang.Math.round;
  */
 public class Ranking implements Comparator<Action> {
 
-    public static final double ALPHA = 2.0;
+    public static final double ALPHA = 4;
+    public static final double[] PARAM_PLUS = {1.0};
+    public static final double[] PARAM_MINUS = {1.0, 2.0, 4.0, 3.0};
 
     private Domain domain;
     private Problem problem;
     public Map<Action, Double> ranks;
-    private Map<Action, Integer[]> scores;
-    private Map<Action, Integer[]> bonuses;
+    private Map<Action, Double[]> scores;
+    private Map<Action, Double[]> bonuses;
     private Map<Integer, Set<Action>> unappliables;
     private Map<Integer, Set<Action>> eagers;
 
@@ -84,11 +86,11 @@ public class Ranking implements Comparator<Action> {
             if (action.fake) {
                 ranks.put(action, 0.0);
             } else {
-                Integer[] score = scores.get(action);
-                Integer[] bonus = bonuses.get(action);
+                Double[] score = scores.get(action);
+                Double[] bonus = bonuses.get(action);
                 if (bonus == null) {
-                    bonus = new Integer[2];
-                    Arrays.fill(bonus, 0);
+                    bonus = new Double[2];
+                    Arrays.fill(bonus, 0.0);
                 }
                 ranks.put(action, score[0] + bonus[0] * pow(ALPHA, -(score[1] + bonus[1]))); // POWOWW
             }
@@ -97,35 +99,34 @@ public class Ranking implements Comparator<Action> {
     }
 
     private void boost(Action action, int boost) {
-        Integer[] bonus = bonuses.get(action);
+        Double[] bonus = bonuses.get(action);
         if (bonus == null) {
-            bonus = new Integer[2];
-            Arrays.fill(bonus, 0);
+            bonus = new Double[2];
+            Arrays.fill(bonus, 0.0);
             bonuses.put(action, bonus);
         }
-        bonus[boost > 0 ? 0 : 1] += abs(boost);
+        bonus[boost > 0 ? 0 : 1] += boost > 0 ? PARAM_PLUS[0] : PARAM_MINUS[3];
     }
 
-    private Map<Action, Integer[]> scores() {
-        Map<Action, Integer[]> scores = new HashMap<>();
+    private Map<Action, Double[]> scores() {
+        Map<Action, Double[]> scores = new HashMap<>();
         for (Action action : domain) {
-            int good = domain.properPlan.outDegreeOf(action);
[…]

### 2016-04-15 src/me/grea/antoine/lollipop/type/flaw/Resolver.java

@@ -163,7 +163,7 @@ public class Resolver {
             }
         }
 
-        Log.d("Related flaws " + related);
+//        Log.d("Related flaws " + related);
 
         return related;
     }

### 2016-04-15 src/me/grea/antoine/lollipop/type/flaw/Threat.java

@@ -42,11 +42,11 @@ public class Threat extends Flaw<Threat> {
         Action source = problem.plan.getEdgeSource(threatened);
         Action target = problem.plan.getEdgeTarget(threatened);
         if (target != problem.goal) {
-            Log.w("Can't demote after goal step !");
+//            Log.w("Can't demote after goal step !");
             resolvers.add(new Resolver(target, breaker));
         }
         if (source != problem.initial) {
-            Log.w("Can't promote before initial step !");
+//            Log.w("Can't promote before initial step !");
             resolvers.add(new Resolver(breaker, source));
         }
         return resolvers;
